### 2020-03-19 tex/ms.tex
tex

% !TeX root = ./ms.tex
\documentclass[modern]{aastex62}

% Load the corTeX style definitions
\input{cortex}

% Bibliography stuff
\bibliographystyle{aasjournal}

% Begin!
\begin{document}

% Title
\title{Title here}

% Author list
\author[0000-0002-0296-3826]{Rodrigo Luger}
\email{rluger@flatironinstitute.org}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
%

\begin{abstract} 
Abstract here.
%
\href{https://github.com/rodluger/starrynight}{\color{linkcolor}\faGithub}
\end{abstract}

%
\section{Introduction}
%
Intro here \citep{Luger2019}.
Here's an equation with a proof:
%
\begin{proof}{dummy}
    \label{eq:dummy}
    1 + 1 = 2.
\end{proof}
The proof is a Jupyter notebook with a formal derivation of the solution,
an informal justification, a numerical validation, or whatever you want it
to be.
%
And here's a figure with a link:
%
\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=0.5\linewidth]{figures/dummy.pdf}
    \oscaption{pretty_function}{%
        This is a plot of a pretty function. And at the end of this
        caption is a symbol with a link to the \emph{exact} script
        that generated it, hosted on \textsf{GitHub}.
        \label{fig:dummy}
    }
    \end{centering}
\end{figure}

% Bibliography
\bibliography{bib}

\end{document}

### 2020-03-19 tex/figures/dummy.py

@@ -1,0 +1,20 @@
+"""Plot the function sin(1 / XY)."""
+import matplotlib.pyplot as plt
+import numpy as np
+
+# Compute sin(1 / xy)
+sz = 1000
+X = np.linspace(-1, 1, sz)
+Y = np.linspace(-1, 1, sz)
+X, Y = np.meshgrid(X, Y)
+Z = np.sin(1 / (X * Y))
+
+# Plot it
+fig, ax = plt.subplots(1)
+im = ax.imshow(Z, cmap=plt.get_cmap("plasma"), origin="lower", extent=(-1, 1, -1, 1))
+plt.colorbar(im, shrink=1, aspect=10)
+ax.set_xlabel("X", fontsize=16)
+ax.set_ylabel("Y", fontsize=16)
+
+# Save it
+fig.savefig("dummy.pdf", bbox_inches="tight")

### 2020-03-19 tex/gen_links.py

@@ -1,0 +1,27 @@
+from __future__ import print_function
+import subprocess
+import os
+
+# Generate the github links
+hash = subprocess.check_output(["git", "rev-parse", "HEAD"]).decode("utf-8")[:-1]
+slug = os.getenv("TRAVIS_REPO_SLUG", "user/repo")
+with open("gitlinks.tex", "w") as f:
+    print(
+        r"\newcommand{\codelink}[1]{\href{https://github.com/%s/blob/%s/tex/figures/#1.py}{\codeicon}\,\,}"
+        % (slug, hash),
+        file=f,
+    )
+    print(
+        r"\newcommand{\animlink}[1]{\href{https://github.com/%s/blob/%s/tex/figures/#1.gif}{\animicon}\,\,}"
+        % (slug, hash),
+        file=f,
+    )
+    print(
+        r"\newcommand{\prooflink}[1]{\href{https://github.com/%s/blob/%s/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}"
+        % (slug, hash),
+        file=f,
+    )
+    print(
+        r"\newcommand{\cilink}[1]{\href{https://dev.azure.com/%s/_build}{#1}}" % (slug),
+        file=f,
+    )

### 2020-03-26 tex/ms.tex
tmp

@@
 
+\section{Integration}
+
+Define the pairwise difference operator
+%
+\begin{align}
+    \label{eq:pairdiff}
+    \Delta \bvec{v} \equiv \sum_{i=0}^{2N} (-1)^{i + 1} v_i
+\end{align}
+%
+which sums the difference of successive pairs of values in 
+an array $\bvec{v} = \{ v_0, v_1, v_2, v_3, {\cdot\cdot\cdot}, v_{2N}\}$.
+
+\newcommand{\kap}{\boldsymbol{\kappa}}
+\newcommand{\kmt}{k^{-2}}
+
+\subsection{The integral $\mathcal{J}$}
+%
+\begin{align}
+    \label{eq:J}
+    \mathcal{J}_v(k, \kap) = 
+        \int_{\frac{\kappa_i}{2}}^{\frac{\kappa_{i+1}}{2}}
+        \sin^{2v}\varphi
+        \left(1 - \kmt\sin^2\varphi\right)^\frac{3}{2} 
+        \mathrm{d}\varphi
+\end{align}
+%
+Given the lower boundary condition
+%
+\begin{proof}{J0}
+    \label{eq:J0}
+    \mathcal{J}_0(k, \kap) &= 
+        \frac{1}{3} \bigg(
+            2 (2 - \kmt) \Delta \mathbf{E}(k, \kap) + 
+            (\kmt - 1) \Delta \mathbf{F}(k, \kap) + 
+            \kmt \Delta \mathbf{z}(k, \kap)
+        \bigg)
+%
+    \nonumber \\
+%
+    \mathbf{z}(k, \boldsymbol{\kappa}) &= 
+        \sin\left(\frac{\kap}{2}\right) 
+        \cos\left(\frac{\kap}{2}\right) 
+        \sqrt{1 - \kmt \sin^2\left(\frac{\kap}{2}\right)}
+\end{proof}
+%
+and an upper boundary condition $\mathcal{J}_N$ 
+(computed by numerical integration of Equation~\ref{eq:J}),
+the values of all intermediate $J_v$ can be obtained by solving the following
+tridiagonal problem:
+%
+\begin{proof}{Jtri}
+    \label{eq:Jtri}
+    \begin{pmatrix}
+        a_0   & 1     &       &       &       &       \\
+        b_1   & a_1   & 1     &       &       &       \\
+            & b_2   & a_2   & 1     &       &       \\
+            &       & b_0   & a_3   & 1     &       \\
+            &       &       & \ddots& \ddots&\ddots \\
+            &       &       &       & b_N   & a_N   
+    \end{pmatrix}
+    \begin{pmatrix}
+        \mathcal{J}_1 \\
+        \mathcal{J}_2 \\
+        \mathcal{J}_3 \\
+        \mathcal{J}_4 \\
+        \cdot\cdot\cdot \\
+        \mathcal{J}_{N-1}
+    \end{pmatrix}
+    =
+    \begin{pmatrix}
+        c_0 - b_0 \mathcal{J}_0 \\
+        c_1 \\
+        c_2 \\
+        c_3 \\
+        \cdot\cdot\cdot \\
+        c_N - \mathcal{J}_N
+    \end{pmatrix}
+\end{proof}
+%
+where the recursion coefficients are given by
+%
+\begin{proof}{Jtri}
+    \label{eq:Jtri_coeffs}
+    a_v(k) &= -2\frac{(v + 1) + (v - 1) k^2}{2v + 3} \nonumber \\
+    b_v(k) &= \frac{(2v - 3) k^2}{2v + 3} \nonumber \\
+    c_v(k, \kap) &= \frac{\Delta \mathbf{q_v}(k, \kap)}{2v + 3} \nonumber \\
+    \mathbf{q_v}(k, \kap) &= 
+        k^2 
+        \sin^{2v + 1}\left(\frac{\kap}{2}\right) 
+        \cos\left(\frac{\kap}{2}\right) 
+        \bigg(1 - \kmt \sin^2\left(\frac{\kap}{2}\right)\bigg)^\frac{5}{2}
+\end{proof}
+
 % Bibliography

### 2020-03-26 tex/figures/speed.py

@@ -7,7 +7,7 @@ import theano
 import theano.tensor as tt
 import theano.sparse as ts
 from theano.ifelse import ifelse
-from starry._core.utils import autocompile
+from scipy.optimize import root_scalar
 from tqdm import tqdm
 import time
 import warnings
@@ -17,218 +17,314 @@ import warnings
 plt.switch_backend("MacOSX")
 starry.config.lazy = False
 starry.config.quiet = True
-warnings.simplefilter("ignore")
+# warnings.simplefilter("ignore")
 HUGE = 1e30
 np.random.seed(1234)
+
+
+_y = tt.dvector()
+_x = tt.dvector()
+_xs = tt.dvector()
+_ys = tt.dvector()
+_zs = tt.dvector()
+_xo = tt.dvector()
+_yo = tt.dvector()
+_ro = tt.dscalar()
 
 
 class Compare(object):
     """Compare different ways of evaluating the flux."""
 
-    def __init__(self, ydeg):
-        self.ydeg = ydeg
+    def __init__(self, y):
+        self.y = y
 
     @property
-    def ydeg(self):
-        return self._ydeg
+    def y(self):
+        return self._y
 
-    @ydeg.setter
-    def ydeg(self, ydeg):
-        self._ydeg = ydeg
-        self.map_ref = starry.Map(ydeg=ydeg, reflected=True)
-        self.map_emi = starry.Map(ydeg=ydeg)
-        if ydeg > 0:
-            self.map_ref[1:, :] = 1
-            self.map_emi[1:, :] = 1
-        self._A1y = ts.dot(
-            self.map_ref.ops.A1, tt.as_tensor_variable(np.ones((ydeg + 1) ** 2))
+    @y.setter
+    def y(self, y):
+        self._y = np.array(y)
+        self.ydeg = int(np.sqrt(len(y)) - 1)
+        self.map_ref = starry.Map(ydeg=self.ydeg, reflected=True)
+        self.map_emi = starry.Map(ydeg=self.ydeg)
+        if self.ydeg > 0:
+            self.map_ref[1:, :] = y[1:]
+            self.map_emi[1:, :] = y[1:]
+        self._A1y = ts.dot(self.map_ref.ops.A1, tt.as_tensor_variable(y))
+
+        # Reset
+        self.intensity_occulted(
+            0.0, 0.0, [0.0], [0.0], [0.0], [0.0], [0.0], 0.0, reset=True
[…]

### 2020-03-27 tex/ms.tex
woot

@@
 %
-Intro here \citep{Luger2019}.
-Here's an equation with a proof:
-%
-\begin{proof}{dummy}
-    \label{eq:dummy}
-    1 + 1 = 2.
-\end{proof}
-The proof is a Jupyter notebook with a formal derivation of the solution,
-an informal justification, a numerical validation, or whatever you want it
-to be.
-%
-And here's a figure with a link:
+This is an extension of \citep{Luger2019}.
+
 %
@@
     \begin{centering}
-    \includegraphics[width=0.5\linewidth]{figures/dummy.pdf}
-    \oscaption{pretty_function}{%
-        This is a plot of a pretty function. And at the end of this
-        caption is a symbol with a link to the \emph{exact} script
-        that generated it, hosted on \textsf{GitHub}.
-        \label{fig:dummy}
+    \includegraphics[width=\linewidth]{figures/speed.pdf}
+    \oscaption{speed}{%
+        Evaluation time for the starry algorithm.
+        \label{fig:speed}
     }
@@
     b_v(k) &= \frac{(2v - 3) k^2}{2v + 3} \nonumber \\
-    c_v(k, \kap) &= \frac{\Delta \mathbf{q_v}(k, \kap)}{2v + 3} \nonumber \\
-    \mathbf{q_v}(k, \kap) &= 
+    c_v(k, \kap) &= \frac{\Delta \mathbf{q}_v(k, \kap)}{2v + 3} \nonumber \\
+    \mathbf{q}_v(k, \kap) &= 
         k^2 

### 2020-03-27 tex/figures/speed.py

@@ -1,4 +1,4 @@
-"""Starry speed tests."""
+"""Starry speed and stability tests."""
 import starry
 import numpy as np
 import matplotlib.pyplot as plt
@@ -7,7 +7,6 @@ import theano
 import theano.tensor as tt
 import theano.sparse as ts
 from theano.ifelse import ifelse
-from scipy.optimize import root_scalar
 from tqdm import tqdm
 import time
 import warnings
@@ -17,11 +16,12 @@ import warnings
 plt.switch_backend("MacOSX")
 starry.config.lazy = False
 starry.config.quiet = True
-# warnings.simplefilter("ignore")
+warnings.simplefilter("ignore")
 HUGE = 1e30
 np.random.seed(1234)
 
 
+# Theano dummy variables
 _y = tt.dvector()
 _x = tt.dvector()
 _xs = tt.dvector()
@@ -54,19 +54,16 @@ class Compare(object):
         self._A1y = ts.dot(self.map_ref.ops.A1, tt.as_tensor_variable(y))
 
         # Reset
-        self.intensity_occulted(
-            0.0, 0.0, [0.0], [0.0], [0.0], [0.0], [0.0], 0.0, reset=True
-        )
-        self.intensity(0.0, 0.0, [0.0], [0.0], [0.0], reset=True)
+        self.intensity(0.0, 0.0, [0.0], [0.0], [0.0], [0.0], [0.0], 0.0, reset=True)
         self.flux([0.0], [0.0], [0.0], [0.0], [0.0], 0.0, reset=True)
         self.dfluxdro([0.0], [0.0], [0.0], [0.0], [0.0], 0.0, reset=True)
         if self.ydeg > 0:
             self.flux_emitted([0.0], [0.0], [0.0], [0.0], [0.0], 0.0, reset=True)
             self.dfluxdro_emitted([0.0], [0.0], [0.0], [0.0], [0.0], 0.0, reset=True)
 
-    def intensity_occulted(self, y, x, xs, ys, zs, xo, yo, ro, reset=False):
+    def intensity(self, y, x, xs, ys, zs, xo, yo, ro, reset=False):
 
-        if reset or not hasattr(self, "_intensity_occulted"):
+        if reset or not hasattr(self, "_intensity"):
 
             def theano_code(y, x, xs, ys, zs, xo, yo, ro):
 
@@ -105,48 +102,12 @@ class Compare(object):
                 )
                 return result
 
[…]

### 2020-03-27 tex/figures/speed.py
tweak

@@ -13,7 +13,6 @@ import warnings
 
 
 # Config
-plt.switch_backend("MacOSX")
 starry.config.lazy = False
 starry.config.quiet = True
 warnings.simplefilter("ignore")

### 2020-03-27 tex/ms.tex
tweak
more text

@@
 \documentclass[modern]{aastex62}
+
+% Shorthand
+\newcommand{\STARRYQUADPOINTS}{100}
+\newcommand{\kap}{\boldsymbol{\kappa}}
+\newcommand{\kmt}{k^{-2}}
 
@@
 % Title
-\title{Title here}
+\title{Analytic Light Curves in Reflected Light}
 
@@
     \label{eq:pairdiff}
-    \Delta \bvec{v} \equiv \sum_{i=0}^{2N} (-1)^{i + 1} v_i
+    \Delta \bvec{v} \equiv \sum_{i=0}^N \left( v_{2i + 1} - v_{2i} \right)
 \end{align}
@@
 
-\newcommand{\kap}{\boldsymbol{\kappa}}
-\newcommand{\kmt}{k^{-2}}
-
-\subsection{The integral $\mathcal{J}$}
+\subsection{$\mathcal{J}_v$}
+%
+The function $\mathcal{J}_v$ is given by
 %
@@
     \mathcal{J}_v(k, \kap) =
-        \int_{\frac{\kappa_i}{2}}^{\frac{\kappa_{i+1}}{2}}
+    \sum_{i = 0}^N
+    \int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
     \sin^{2v}\varphi
@@
     \mathrm{d}\varphi
+    \quad.
 \end{align}
 %
-Given the lower boundary condition
-%
-\begin{proof}{J0}
-    \label{eq:J0}
-    \mathcal{J}_0(k, \kap) &= 
-        \frac{1}{3} \bigg(
-            2 (2 - \kmt) \Delta \mathbf{E}(k, \kap) + 
-            (\kmt - 1) \Delta \mathbf{F}(k, \kap) + 
-            \kmt \Delta \mathbf{z}(k, \kap)
-        \bigg)
-%
-    \nonumber \\
-%
-    \mathbf{z}(k, \boldsymbol{\kappa}) &= 
-        \sin\left(\frac{\kap}{2}\right) 
-        \cos\left(\frac{\kap}{2}\right) 
-        \sqrt{1 - \kmt \sin^2\left(\frac{\kap}{2}\right)}
-\end{proof}
-%
-and an upper boundary condition $\mathcal{J}_N$ 
-(computed by numerical integration of Equation~\ref{eq:J}),
-the values of all intermediate $J_v$ can be obtained by solving the following
-tridiagonal problem:
+The integral in this expression is the same as that in Equation (D39)
+of \citet{Luger2019}, except for a change in the limits of integration.
+In that paper, we computed all terms
+$\{ \mathcal{J}_0, {\cdot\cdot\cdot}, \mathcal{J}_N \}$ from a three-term
+recurrence relation and two boundary conditions. In the case of upward recursion,
+the boundary conditions $\mathcal{J}_0$ and $\mathcal{J}_1$ were computed
+analytically from the complete elliptic
+integrals $K(k^2)$ and $E(k^2)$. In cases where upward recursion was not
+numerically stable, we evaluated $\mathcal{J}_N$ and $\mathcal{J}_{N-1}$
+via a quickly convergent series expansion and recursed downward.
+
+In order to solve Equation~(\ref{eq:J}), it is possible to
+replace the complete elliptic integrals $K(k^2)$ and $E(k^2)$ in the lower
+boundary conditions \citep[Equation D46 in ][]{Luger2019} with the
+incomplete elliptic integrals $F(k^2, \kappa)$ and $E(k^2, \kappa)$,
+then use the same upward
+recursion relation to obtain analytic solutions for all $\mathcal{J}_v$.
+However, in practice we find that this procedure is even more numerically
+unstable than it was in \citet{Luger2019}.
+Instead, here we express the recurrence structure of the problem as
+a tridiagonal system with one lower boundary condition $\mathcal{J}_0$
+and one upper boundary condition $\mathcal{J}_N$:
 %
@@
             &     & b_0 & a_3    & 1      &        \\
-            &       &       & \ddots& \ddots&\ddots \\
+            &     &     & \ddots & \ddots & \ddots \\
             &     &     &        & b_N    & a_N
@@
 \end{proof}
+%
+Solving this matrix system yields values for all
+intermediate $\{ \mathcal{J}_1, {\cdot\cdot\cdot}, \mathcal{J}_{N - 1} \}$.
+While efficient algorithms exist for solving tridiagonal problems, we obtain
+far better numerical stability by instead performing traditional LU
+decomposition. We find that this algorithm is stable in all regimes that we
+tested.
+
+We evaluate the upper boundary condition $\mathcal{J}_{N}$ by numerical
+integration of Equation~(\ref{eq:J}) via Gauss-Legendre quadrature with
+\STARRYQUADPOINTS points. The lower boundary condition may be computed
+analytically from the incomplete elliptic integrals $\mathbf{F}(k^2, \kap)$
+and $\mathbf{E}(k^2, \kap)$:
+%
+\begin{proof}{J0}
+    \label{eq:J0}
+    \mathcal{J}_0(k, \kap) &=
+    \frac{1}{3} \bigg(
+    2 (2 - \kmt) \Delta \mathbf{E}(k^2, \kap) +
+    (\kmt - 1) \Delta \mathbf{F}(k^2, \kap) +
+    \kmt \Delta \mathbf{z}(k, \kap)
+    \bigg)
+    %
+    \nonumber \\
+    %
+    \mathbf{z}(k, \boldsymbol{\kappa}) &=
+    \sin\left(\frac{\kap}{2}\right)
+    \cos\left(\frac{\kap}{2}\right)
+    \sqrt{1 - \kmt \sin^2\left(\frac{\kap}{2}\right)}
+    \quad.
+\end{proof}
+%
+However, in practice we achieve better numerical precision via numerical
+integration (as above), with negligible effects on computational performance.
 

### 2020-03-27 tex/ms.tex
more text

@@
 \newcommand{\kmt}{k^{-2}}
+\newcommand{\vmax}{{v_\mathrm{max}}}
 
@@
     \label{eq:pairdiff}
-    \Delta \bvec{v} \equiv \sum_{i=0}^N \left( v_{2i + 1} - v_{2i} \right)
+    \Delta \bvec{v} \equiv \sum_{i=0}^{\frac{N - 1}{2}} \left( v_{2i + 1} - v_{2i} \right)
 \end{align}
@@
 which sums the difference of successive pairs of values in
-an array $\bvec{v} = \{ v_0, v_1, v_2, v_3, {\cdot\cdot\cdot}, v_{2N}\}$.
+an array $\bvec{v} = \{ v_0, v_1, v_2, v_3, {\cdot\cdot\cdot}, v_N\}$.
 
@@
     \mathcal{J}_v(k, \kap) =
-    \sum_{i = 0}^N
+    \sum_{i = 0}^{\frac{N - 1}{2}}
     \int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
@@
 In that paper, we computed all terms
-$\{ \mathcal{J}_0, {\cdot\cdot\cdot}, \mathcal{J}_N \}$ from a three-term
+$\{ \mathcal{J}_0, {\cdot\cdot\cdot}, \mathcal{J}_\vmax \}$ from a three-term
 recurrence relation and two boundary conditions. In the case of upward recursion,
@@
 integrals $K(k^2)$ and $E(k^2)$. In cases where upward recursion was not
-numerically stable, we evaluated $\mathcal{J}_N$ and $\mathcal{J}_{N-1}$
+numerically stable, we evaluated $\mathcal{J}_\vmax$ and $\mathcal{J}_{\vmax-1}$
 via a quickly convergent series expansion and recursed downward.
@@
 a tridiagonal system with one lower boundary condition $\mathcal{J}_0$
-and one upper boundary condition $\mathcal{J}_N$:
+and one upper boundary condition $\mathcal{J}_\vmax$:
 %
@@
             &     &     & \ddots & \ddots  & \ddots  \\
-            &     &     &        & b_N    & a_N
+            &     &     &        & b_\vmax & a_\vmax
     \end{pmatrix}
@@
         \cdot\cdot\cdot \\
-        \mathcal{J}_{N-1}
+        \mathcal{J}_{\vmax-1}
     \end{pmatrix}
@@
         \cdot\cdot\cdot         \\
-        c_N - \mathcal{J}_N
+        c_\vmax - \mathcal{J}_\vmax
     \end{pmatrix}
@@
 Solving this matrix system yields values for all
-intermediate $\{ \mathcal{J}_1, {\cdot\cdot\cdot}, \mathcal{J}_{N - 1} \}$.
+intermediate $\{ \mathcal{J}_1, {\cdot\cdot\cdot}, \mathcal{J}_{\vmax - 1} \}$.
 While efficient algorithms exist for solving tridiagonal problems, we obtain
 far better numerical stability by instead performing traditional LU
-decomposition. We find that this algorithm is stable in all regimes that we
+decomposition. We find that this algorithm is stable in all the regimes that we
 tested.
 
-We evaluate the upper boundary condition $\mathcal{J}_{N}$ by numerical
+We evaluate the upper boundary condition $\mathcal{J}_{\vmax}$ by numerical
 integration of Equation~(\ref{eq:J}) via Gauss-Legendre quadrature with

### 2020-03-29 tex/ms.tex
added J proof

@@
 % Shorthand
-\newcommand{\STARRYQUADPOINTS}{100}
+\newcommand{\STARRYQUADPOINTS}{100\xspace}
 \newcommand{\kap}{\boldsymbol{\kappa}}
@@
 \newcommand{\vmax}{{v_\mathrm{max}}}
+
+\newcommand{\DE}{\Delta \mathbf{E}(k^2, \kap)}
+\newcommand{\DF}{\Delta \mathbf{F}(k^2, \kap)}
 
@@
 %
-\begin{figure}[h!]
+\begin{figure}[t!]
     \begin{centering}
@@
 
+\subsection{Definitions}
+%
 Define the pairwise difference operator
@@
     \label{eq:pairdiff}
-    \Delta \bvec{v} \equiv \sum_{i=0}^{\frac{N - 1}{2}} \left( v_{2i + 1} - v_{2i} \right)
+    \Delta \bvec{v} \equiv \sum_{i=0}^{\frac{N - 1}{2}}
+    \left( v_{2i + 1} - v_{2i} \right)
 \end{align}
@@
 an array $\bvec{v} = \{ v_0, v_1, v_2, v_3, {\cdot\cdot\cdot}, v_N\}$.
+
+Define the quantity
+%
+\begin{align}
+    \label{eq:q}
+    \mathbf{q}(k^2, \kap) = \sqrt{1 - \frac{\sin^2\left(\frac{\kap}{2}\right)}{k^2}}
+    \quad.
+\end{align}
 
@@
     \label{eq:J}
-    \mathcal{J}_v(k, \kap) =
+    \mathcal{J}_v(k^2, \kap) =
     \sum_{i = 0}^{\frac{N - 1}{2}}
@@
     \sin^{2v}\varphi
-    \left(1 - \kmt\sin^2\varphi\right)^\frac{3}{2}
+    \left(1 - \frac{\sin^2\varphi}{k^2}\right)^\frac{3}{2}
     \mathrm{d}\varphi
@@
 $\{ \mathcal{J}_0, {\cdot\cdot\cdot}, \mathcal{J}_\vmax \}$ from a three-term
-recurrence relation and two boundary conditions. In the case of upward recursion,
-the boundary conditions $\mathcal{J}_0$ and $\mathcal{J}_1$ were computed
-analytically from the complete elliptic
-integrals $K(k^2)$ and $E(k^2)$. In cases where upward recursion was not
-numerically stable, we evaluated $\mathcal{J}_\vmax$ and $\mathcal{J}_{\vmax-1}$
+recurrence relation and two boundary conditions. In the case of upward
+recursion, the boundary conditions $\mathcal{J}_0$ and $\mathcal{J}_1$ were
+computed analytically from the complete elliptic integrals $K(k^2)$
+and $E(k^2)$. In cases where upward recursion was not numerically stable, we
+evaluated $\mathcal{J}_\vmax$ and $\mathcal{J}_{\vmax-1}$
 via a quickly convergent series expansion and recursed downward.
@@
 then use the same upward
-recursion relation to obtain analytic solutions for all $\mathcal{J}_v$.
+recursion relation to obtain analytic solutions for all $\mathcal{J}_v$:
+%
+\begin{proof}{J}
+    \label{eq:Jrec}
+    \mathcal{J}_0(k^2, \kap) &=
+    \frac{1}{3} \bigg(
+    2 \left(2 - \frac{1}{k^2}\right) \DE +
+    \left(\frac{1}{k^2} - 1\right) \DF +
+    \Delta \mathbf{z}_0(k^2, \kap)
+    \bigg)
+    %
+    \nonumber \\
+    %
+    \mathcal{J}_1(k^2, \kap) &=
+    \frac{1}{15} \bigg(
+    \left(-3 k^2 + 13 - \frac{8}{k^2}\right) \DE +
+    \left(3 k^2 - 7 + \frac{4}{k^2}\right) \DF +
+    \Delta \mathbf{z}_1(k^2, \kap)
+    \bigg)
+    %
+    \nonumber \\
+    %
+    \mathcal{J}_v(k^2, \kap) &=
+    \frac{1}{2v + 3}
+    \bigg(
+    2 \left( v + 1 + (v - 1) k^2 \right) \mathcal{J}_{v - 1} -
+    (2v - 3) k^2 \mathcal{J}_{v - 2}
+    + \Delta \mathbf{z}_v(k^2, \kap)
+    \bigg)
+\end{proof}
+%
+%
+where the last expression is valid for all $v > 1$ and
+%
+\begin{proof}{J}
+    \label{eq:Jrec_z}
+    \mathbf{z}_0(k^2, \boldsymbol{\kappa}) & =
+    \frac{
+        \sin\left(\frac{\kap}{2}\right)
+        \cos\left(\frac{\kap}{2}\right)
+        \mathbf{q}(k^2, \kap)
+    }{
+        k^2
+    }
+    %
+    \nonumber                                  \\
+    %
+    \mathbf{z}_1(k^2, \boldsymbol{\kappa}) & =
+    \left(\left(3 \sin^2 \left( \frac{\kap}{2} \right) + 4\right) - 6k^2\right)
+    \mathbf{z}_0(k^2, \boldsymbol{\kappa})
+    %
+    \nonumber                                  \\
+    %
+    \mathbf{z}_v(k^2, \boldsymbol{\kappa}) & =
+    k^2
+    \sin^{2v - 3}\left( \frac{\kap}{2} \right)
+    \cos\left( \frac{\kap}{2} \right)
+    \mathbf{q}(k^2, \boldsymbol{\kappa})^5
+    \quad.
+\end{proof}
+%
 However, in practice we find that this procedure is even more numerically
 unstable than it was in \citet{Luger2019}.
-Instead, here we express the recurrence structure of the problem as
+To address this, we express the recurrence structure of the problem as
 a tridiagonal system with one lower boundary condition $\mathcal{J}_0$
@@
 %
-\begin{proof}{Jtri}
+\begin{proof}{J}
     \label{eq:Jtri}
@@
 %
-\begin{proof}{Jtri}
+\begin{proof}{J}
     \label{eq:Jtri_coeffs}
@@
     b_v(k) &= \frac{(2v - 3) k^2}{2v + 3} \nonumber \\
-    c_v(k, \kap) &= \frac{\Delta \mathbf{q}_v(k, \kap)}{2v + 3} \nonumber \\
-    \mathbf{q}_v(k, \kap) &=
-    k^2
-    \sin^{2v + 1}\left(\frac{\kap}{2}\right)
-    \cos\left(\frac{\kap}{2}\right)
-    \bigg(1 - \kmt \sin^2\left(\frac{\kap}{2}\right)\bigg)^\frac{5}{2}
+    c_v(k^2, \kap) &= \Delta
+    \bigg(
+    \frac{
+            \mathbf{z}_v(k^2, \boldsymbol{\kappa})
+        }{
+            2v + 3
+        }
+    \bigg)
+    \quad.
 \end{proof}
@@
 integration of Equation~(\ref{eq:J}) via Gauss-Legendre quadrature with
-\STARRYQUADPOINTS points. The lower boundary condition may be computed
-analytically from the incomplete elliptic integrals $\mathbf{F}(k^2, \kap)$
-and $\mathbf{E}(k^2, \kap)$:
+\STARRYQUADPOINTS points. While the lower boundary condition may be computed
+analytically from Equation~(\ref{eq:Jrec}),
+in practice we achieve better precision via numerical
+integration (as above), with negligible effects on computational performance.
+
+\subsection{$\mathcal{W}_n$}
 %
-\begin{proof}{J0}
-    \label{eq:J0}
-    \mathcal{J}_0(k, \kap) &=
-    \frac{1}{3} \bigg(
-    2 (2 - \kmt) \Delta \mathbf{E}(k^2, \kap) +
-    (\kmt - 1) \Delta \mathbf{F}(k^2, \kap) +
-    \kmt \Delta \mathbf{z}(k, \kap)
-    \bigg)
+The function $\mathcal{W}_n$ is given by
 %
-    \nonumber \\
+\begin{align}
+    \label{eq:W}
+    % TODO
+    \mathcal{W}_n = \int
+\end{align}
 %
-    \mathbf{z}(k, \boldsymbol{\kappa}) &=
-    \sin\left(\frac{\kap}{2}\right)
-    \cos\left(\frac{\kap}{2}\right)
-    \sqrt{1 - \kmt \sin^2\left(\frac{\kap}{2}\right)}
-    \quad.
-\end{proof}
+This integral has a closed-form solution:
 %
-However, in practice we achieve better numerical precision via numerical
-integration (as above), with negligible effects on computational performance.
+\begin{align}
+    \label{eq:Wsol}
+    \mathcal{W}_n =
+    \frac{\sin^{2n + 2}\left(\frac{\kap}{2}\right)}{2n + 5}
+    \left(
+    \frac{3}{n+1}
+        {_2F_1}\left(-\frac{1}{2}, n + 1; n + 2; 1 - q^2\right) + 2 q^3
+    \right)
+\end{align}
+%
+where ${_2F_1}(a, b; c; z)$ is the Gauss hypergeometric function.
+
+% by either upward recursion (stable for |1 - q^2| > 1/2) or downward
+% recursion (always stable).
 

### 2020-03-29 tex/ms.tex
added I proof

@@
 %
-\begin{figure}[t!]
+\begin{figure}[h!]
     \begin{centering}
@@
 
+\subsection{$\mathcal{I}_v$}
+%
+The function $\mathcal{I}_v$ is given by
+%
+\begin{align}
+    \label{eq:I}
+    \mathcal{I}_v(k^2, \kap) =
+    \sum_{i = 0}^{\frac{N - 1}{2}}
+    \int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
+    \sin^{2v}\varphi
+    \mathrm{d}\varphi
+    \quad.
+\end{align}
+%
+The integral in this expression is the same as that in Equation (D38)
+of \citet{Luger2019}, except for a change in the limits of integration.
+As in \citet{Luger2019}, we can compute this integral recursively given
+a trivial lower boundary condition:
+%
+\begin{proof}{I}
+    \label{eq:Irec}
+    \mathcal{I}_0(\kap) &=
+    \frac{\Delta \kap}{2}
+    %
+    \nonumber \\
+    %
+    \mathcal{I}_v(\kap) &=
+    \frac{1}{2v}
+    \bigg(
+    (2v - 1) \mathcal{I}_{v-1}(\kap) -
+    \Delta \left(\sin^{2v - 1}\left(\frac{\kap}{2}\right)
+    \cos\left(\frac{\kap}{2}\right)\right)
+    \bigg)
+\end{proof}
+%
+where the last expression is valid for all $v > 0$. We find that this algorithm
+is generally stable, except when $\sin\left(\frac{\kap}{2}\right)$ is small. In
+that limit, we evaluate $\mathcal{I}_N(\kap)$ by numerical integration of
+Equation~(\ref{eq:I}) using Gauss-Legendre quadrature with \STARRYQUADPOINTS
+points. We then recurse downward by substituting $v \rightarrow v + 1$ in
+Equation~(\ref{eq:Irec}) and solving for $\mathcal{I}_v(\kap)$.
+
 \subsection{$\mathcal{J}_v$}
@@
 %
-The integral in this expression is the same as that in Equation (D39)
+The integral in this expression is again the same as that in Equation (D39)
 of \citet{Luger2019}, except for a change in the limits of integration.

### 2020-03-29 tex/figures/dummy.py

@@ -1,20 +1,0 @@
-"""Plot the function sin(1 / XY)."""
-import matplotlib.pyplot as plt
-import numpy as np
-
-# Compute sin(1 / xy)
-sz = 1000
-X = np.linspace(-1, 1, sz)
-Y = np.linspace(-1, 1, sz)
-X, Y = np.meshgrid(X, Y)
-Z = np.sin(1 / (X * Y))
-
-# Plot it
-fig, ax = plt.subplots(1)
-im = ax.imshow(Z, cmap=plt.get_cmap("plasma"), origin="lower", extent=(-1, 1, -1, 1))
-plt.colorbar(im, shrink=1, aspect=10)
-ax.set_xlabel("X", fontsize=16)
-ax.set_ylabel("Y", fontsize=16)
-
-# Save it
-fig.savefig("dummy.pdf", bbox_inches="tight")

### 2020-03-30 tex/ms.tex
more stuffs

@@
 
-% Shorthand
-\newcommand{\STARRYQUADPOINTS}{100\xspace}
-\newcommand{\kap}{\boldsymbol{\kappa}}
-\newcommand{\kmt}{k^{-2}}
-\newcommand{\vmax}{{v_\mathrm{max}}}
-
-\newcommand{\DE}{\Delta \mathbf{E}(k^2, \kap)}
-\newcommand{\DF}{\Delta \mathbf{F}(k^2, \kap)}
-
 % Load the corTeX style definitions
 \input{cortex}
+
+% Shorthand for this paper
+\usepackage{xifthen}
+\newcommand{\dd}{\ensuremath{\mathrm{d}}}
+\newcommand{\STARRYQUADPOINTS}{100\xspace}
+\newcommand{\bkappa}{\boldsymbol{\kappa}}
+\newcommand{\blambda}{\boldsymbol{\lambda}}
+\newcommand{\bxi}{\boldsymbol{\xi}}
+\newcommand{\vmax}{{v_\mathrm{max}}}
+\newcommand{\kapint}[1]{%
+\sum_{i = 0}^{\frac{N - 1}{2}}
+\int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
+#1
+\dd\varphi
+}
+\newcommand{\lamint}[1]{%
+\sum_{i = 0}^{\frac{N - 1}{2}}
+\int\limits_{\frac{1}{2}\lambda_{2i}}^{\frac{1}{2}\lambda_{2i+1}}
+#1
+\dd\varphi
+}
+\newcommand{\coshalfkap}[1][]{%
+\ifthenelse{%
+    \equal{#1}{}
+}{
+    \cos\left(\frac{\bkappa}{2}\right)
+}{
+    \cos^{#1}\left(\frac{\bkappa}{2}\right)
+}}
+\newcommand{\sinhalfkap}[1][]{%
+\ifthenelse{%
+    \equal{#1}{}
+}{
+    \sin\left(\frac{\bkappa}{2}\right)
+}{
+    \sin^{#1}\left(\frac{\bkappa}{2}\right)
+}}
+\newcommand{\DE}{\Delta \boldsymbol{E}(k^2, \bkappa)}
+\newcommand{\DF}{\Delta \boldsymbol{F}(k^2, \bkappa)}
+\newcommand{\sgn}{{\mathrm{sgn}}}
+\newcommand{\xhat}{\ensuremath{\mathbf{\hat{x}}}\xspace}
+\newcommand{\yhat}{\ensuremath{\mathbf{\hat{y}}}\xspace}
+\newcommand{\zhat}{\ensuremath{\mathbf{\hat{z}}}\xspace}
 
@@
 
+\begin{figure}[h!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/cases.pdf}
+        \oscaption{cases}{%
+            The eight families of cases of occultations in reflected light.
+            In these figures, the night side of the occulted body is colored
+            black (dark grey if occulted), and the dayside is colored blue
+            (light grey if occulted). The cases in the top row involve
+            configurations in which the limb of the occultor does not intersect
+            with the terminator at any point, so the visible flux may be
+            computed in terms of classical \starry integrals. The remaining
+            cases require integration along the red boundary (the curves
+            $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$ of
+            \S\ref{sec:integration}), which
+            include the terminator. These involve the evaluation of incomplete
+            elliptic integrals and are derived below.
+            \label{fig:cases}
+        }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[h!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/geometry.pdf}
+        \oscaption{geometry}{%
+            Geometry of an occultation in reflected light, corresponding
+            to case 5 in Figure~\ref{fig:cases}. The surface integral over
+            the blue region is computed from the antiderivatives of the
+            surface intensity map counter-clockwise along the boundary curves
+            $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$.
+            \label{fig:geometry}
+        }
+    \end{centering}
+\end{figure}
+
+As in \citet{Luger2019}, the elements of the solution vector $\mathbf{s}^\top$
+are given by the line integral
+%
+\begin{align}
+    \label{eq:s}
+    \mathbf{s}_{n(\mu,\nu)} = \oint \mathbf{G}_{\mu,\nu} \cdot \dd\mathbf{r}
+\end{align}
+%
+where
+%
+\begin{align}
+    \label{eq:G}
+    \bvec{G}_{\mu,\nu} (x, y) & =
+    \begin{dcases}
+        %
+        x^{\frac{\mu + 2}{2}}
+        y^{\frac{\nu}{2}}
+        \,\yhat
+         & \qquad \mu, \nu \, \mathrm{even}
+        \\[1em]
+        %
+        \frac{1-z(x, y)^3}{3(1-z(x, y)^2)}\bigg(-y \, \xhat + x \, \yhat\bigg)
+         & \qquad \mu = \nu = 1
+        \\[1em]
+        %
+        x^{l-2}
+        z(x, y)^3
+        \,\xhat
+         & \qquad \nu \, \mathrm{odd}, \,
+        \mu = 1, \,
+        \frac{\mu + \nu}{2} \, \mathrm{even}
+        \\[1em]
+        %
+        x^{l-3}
+        y
+        z(x, y)^3
+        \,\xhat
+         & \qquad \nu \, \mathrm{odd}, \,
+        \mu = 1, \,
+        \frac{\mu + \nu}{2} \, \mathrm{odd}
+        \\[1em]
+        %
+        x^{\frac{\mu-3}{2}}
+        y^{\frac{\nu-1}{2}}
+        z(x, y)^3
+        \,\yhat
+         & \qquad \mathrm{otherwise,}
+    \end{dcases}
+\end{align}
+%
+and
+%
+\begin{align}
+    \dd \bvec{r} & = -r \sin\varphi \, \dd \varphi \, \xhat +
+    r \cos\varphi \, \dd \varphi \, \yhat
+    \quad,
+\end{align}
+%
+where $\varphi = \varphi(x, y)$ is the parametrized angle along the
+arc of integration. Generally, there are at most three arcs bounding a given
+closed surface of integration, which we will denote $\mathcal{P}$,
+$\mathcal{Q}$, and $\mathcal{T}$. These are shown for a typical occultor-occulted
+configuration in Figure~\ref{fig:geometry}.
+
 \section{Integration}
+\label{sec:integration}
 
@@
     \label{eq:pairdiff}
-    \Delta \bvec{v} \equiv \sum_{i=0}^{\frac{N - 1}{2}}
+    \Delta \boldsymbol{v} \equiv \sum_{i=0}^{\frac{N - 1}{2}}
     \left( v_{2i + 1} - v_{2i} \right)
@@
 which sums the difference of successive pairs of values in
-an array $\bvec{v} = \{ v_0, v_1, v_2, v_3, {\cdot\cdot\cdot}, v_N\}$.
+an array $\boldsymbol{v} = \{ v_0, v_1, v_2, v_3, {\cdot\cdot\cdot}, v_N\}$.
 
@@
     \label{eq:q}
-    \mathbf{q}(k^2, \kap) = \sqrt{1 - \frac{\sin^2\left(\frac{\kap}{2}\right)}{k^2}}
+    \boldsymbol{q}(k^2, \bkappa) = \sqrt{1 - \frac{\sinhalfkap[2]}{k^2}}
     \quad.
 \end{align}
+
+\subsection{$\mathcal{H}_{u,v}$}
+%
+The function $\mathcal{H}_{u,v}$ is given by
+%
+\begin{align}
+    \label{eq:H}
+    \mathcal{H}_{u,v}(\blambda) & =
+    \lamint{
+        \cos^u\varphi
+        \sin^v\varphi
+    }
+    \quad.
+\end{align}
+%
+The integral in this expression is the same as that in Equation (D27)
+of \citet{Luger2019}, except for a change in the limits of integration.
+We can compute this integral recursively given four lower boundary conditions:
+%
+\begin{proof}{H}
+    \label{eq:Hlower}
+    \mathcal{H}_{0,0}(\blambda) &= \Delta \blambda
+    %
+    \nonumber \\
+    %
+    \mathcal{H}_{1,0}(\blambda) &= \Delta \sin\blambda
+    %
+    \nonumber \\
+    %
+    \mathcal{H}_{0,1}(\blambda) &= -\Delta \cos\blambda
+    %
+    \nonumber \\
+    %
+    \mathcal{H}_{1,1}(\blambda) &= -\frac{\Delta\cos^2\blambda}{2}
+    %
+    \quad.
+\end{proof}
+%
+The remaining terms may be computed by upward recursion using the
+relations
+%
+\begin{proof}{H}
+    \label{eq:Hrec1}
+    \mathcal{H}_{u,v}(\blambda) &=
+    \frac{
+        -\Delta \left(
+        \cos^{u + 1} \blambda
+        \sin^{v - 1} \blambda
+        \right)
+        +(v - 1)\mathcal{H}_{u,v - 2}(\blambda)
+    }{u + v}
+\end{proof}
+%
+for $u < 2, v \ge 2$ and
+%
+\begin{proof}{H}
+    \label{eq:Hrec2}
+    \mathcal{H}_{u,v}(\blambda) &=
+    \frac{
+        \Delta \left(
+        \cos^{u - 1} \blambda
+        \sin^{v + 1} \blambda
+        \right)
+        + (u - 1)\mathcal{H}_{u - 2,v}(\blambda)
+    }{u + v}
+\end{proof}
+%
+for all remaining terms.
+
+\subsection{$\mathcal{T}_{2}$}
+%
+The function $\mathcal{T}_{2}$ is given by
+%
+\begin{align}
+    \label{eq:T2}
+    \mathcal{T}_{2}(b, \bxi) & = ?
+    \quad.
+\end{align}
+
+\begin{proof}{T2}
+    \mathcal{T}_{2}(b, \bxi) &= -\sgn(b) \Delta \boldsymbol{f}(b, \bxi)
+\end{proof}
+%
+where
+%
+\begin{proof}{T2}
+    \begin{split}
+        f_i(b, \xi_i) =
+        \frac{1}{3}\scalebox{1.4}{\Bigg(}
+        &\arctan\left( \frac{|b|\sin\xi_i}{\cos\xi_i} \right)
+        %
+        \\
+        %
+        &- \sgn\left({\sin\xi_i}\right)
+        \left(
+        \arctan
+        \left(
+            \frac{
+                \left(\frac{\sin\xi_i}{1 + \cos\xi_i}\right)^2 + 2 b^2 - 1
+            }{2 |b| \sqrt{1 - b^2}}
+            \right)
+        + |b| \sqrt{1 - b^2} \cos\xi_i
+        \right)
+        %
+        \\
+        %
+        &+ \phi(b, \xi_i)
+        \scalebox{1.4}{\Bigg)}
+    \end{split}
+\end{proof}
+%
+and
+%
+\begin{proof}{T2}
+    \phi(b, \xi_i) & =
+    \begin{cases}
+        0                          & \qquad 0 \leq \xi_i < \frac{\pi}{2}     \\
+        \pi                        & \qquad \frac{\pi}{2} \leq \xi_i < \pi   \\
+        2 |b| \sqrt{1 - b^2}       & \qquad \pi < \xi_i \leq \frac{3\pi}{2}  \\
+        \pi + 2 |b| \sqrt{1 - b^2} & \qquad \frac{3\pi}{2} \leq \xi_i < 2\pi
+        \quad.
+    \end{cases}
+\end{proof}
+
+\subsection{$\mathcal{U}_v$}
+%
+The function $\mathcal{U}_v$ is given by
+%
+\begin{align}
+    \label{eq:U}
+    \mathcal{U}_v(\bkappa) =
+    \kapint{\cos\varphi\sin^{2v}\varphi}
+    \quad.
+\end{align}
+%
+This integral has an analytic solution for all $v$:
+%
+\begin{proof}{U}
+    \label{eq:Usol}
+    \mathcal{U}_v(\bkappa) &= \frac{\Delta \sinhalfkap[v+1]}{v + 1}
+    \quad.
+\end{proof}
+%
 
@@
     \label{eq:I}
-    \mathcal{I}_v(k^2, \kap) =
-    \sum_{i = 0}^{\frac{N - 1}{2}}
-    \int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
-    \sin^{2v}\varphi
-    \mathrm{d}\varphi
+    \mathcal{I}_v(\bkappa) & =
+    \kapint{\sinhalfkap[2v]}
     \quad.
@@
     \label{eq:Irec}
-    \mathcal{I}_0(\kap) &=
-    \frac{\Delta \kap}{2}
+    \mathcal{I}_0(\bkappa) &=
+    \frac{\Delta \bkappa}{2}
     %
@@
     %
-    \mathcal{I}_v(\kap) &=
+    \mathcal{I}_v(\bkappa) &=
     \frac{1}{2v}
     \bigg(
-    (2v - 1) \mathcal{I}_{v-1}(\kap) -
-    \Delta \left(\sin^{2v - 1}\left(\frac{\kap}{2}\right)
-    \cos\left(\frac{\kap}{2}\right)\right)
+    (2v - 1) \mathcal{I}_{v-1}(\bkappa) -
+    \Delta \left(\sinhalfkap[2v - 1]\coshalfkap\right)
     \bigg)
@@
 where the last expression is valid for all $v > 0$. We find that this algorithm
-is generally stable, except when $\sin\left(\frac{\kap}{2}\right)$ is small. In
-that limit, we evaluate $\mathcal{I}_N(\kap)$ by numerical integration of
+is generally stable, except when $\sin\left(\frac{\bkappa}{2}\right)$ is small. In
+that limit, we evaluate $\mathcal{I}_N(\bkappa)$ by numerical integration of
 Equation~(\ref{eq:I}) using Gauss-Legendre quadrature with \STARRYQUADPOINTS
 points. We then recurse downward by substituting $v \rightarrow v + 1$ in
-Equation~(\ref{eq:Irec}) and solving for $\mathcal{I}_v(\kap)$.
+Equation~(\ref{eq:Irec}) and solving for $\mathcal{I}_v(\bkappa)$.
 
@@
     \label{eq:J}
-    \mathcal{J}_v(k^2, \kap) =
-    \sum_{i = 0}^{\frac{N - 1}{2}}
-    \int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
+    \mathcal{J}_v(k^2, \bkappa) =
+    \kapint{
         \sin^{2v}\varphi
         \left(1 - \frac{\sin^2\varphi}{k^2}\right)^\frac{3}{2}
-    \mathrm{d}\varphi
+    }
     \quad.
@@
     \label{eq:Jrec}
-    \mathcal{J}_0(k^2, \kap) &=
+    \mathcal{J}_0(k^2, \bkappa) &=
     \frac{1}{3} \bigg(
@@
     \left(\frac{1}{k^2} - 1\right) \DF +
-    \Delta \mathbf{z}_0(k^2, \kap)
+    \Delta \boldsymbol{z}_0(k^2, \bkappa)
     \bigg)
@@
     %
-    \mathcal{J}_1(k^2, \kap) &=
+    \mathcal{J}_1(k^2, \bkappa) &=
     \frac{1}{15} \bigg(
@@
     \left(3 k^2 - 7 + \frac{4}{k^2}\right) \DF +
-    \Delta \mathbf{z}_1(k^2, \kap)
+    \Delta \boldsymbol{z}_1(k^2, \bkappa)
     \bigg)
@@
     %
-    \mathcal{J}_v(k^2, \kap) &=
+    \mathcal{J}_v(k^2, \bkappa) &=
     \frac{1}{2v + 3}
@@
     (2v - 3) k^2 \mathcal{J}_{v - 2}
-    + \Delta \mathbf{z}_v(k^2, \kap)
+    + \Delta \boldsymbol{z}_v(k^2, \bkappa)
     \bigg)
@@
     \label{eq:Jrec_z}
-    \mathbf{z}_0(k^2, \boldsymbol{\kappa}) & =
+    \boldsymbol{z}_0(k^2, \boldsymbol{\kappa}) & =
     \frac{
-        \sin\left(\frac{\kap}{2}\right)
-        \cos\left(\frac{\kap}{2}\right)
-        \mathbf{q}(k^2, \kap)
+        \sinhalfkap
+        \coshalfkap
+        \boldsymbol{q}(k^2, \bkappa)
     }{
@@
     %
-    \nonumber                                  \\
+    \nonumber\\
     %
-    \mathbf{z}_1(k^2, \boldsymbol{\kappa}) & =
-    \left(\left(3 \sin^2 \left( \frac{\kap}{2} \right) + 4\right) - 6k^2\right)
-    \mathbf{z}_0(k^2, \boldsymbol{\kappa})
+    \boldsymbol{z}_1(k^2, \boldsymbol{\kappa}) & =
+    \left(\left(3 \sinhalfkap[2] + 4\right) - 6k^2\right)
+    \boldsymbol{z}_0(k^2, \boldsymbol{\kappa})
     %
-    \nonumber                                  \\
+    \nonumber\\
     %
-    \mathbf{z}_v(k^2, \boldsymbol{\kappa}) & =
+    \boldsymbol{z}_v(k^2, \boldsymbol{\kappa}) & =
     k^2
-    \sin^{2v - 3}\left( \frac{\kap}{2} \right)
-    \cos\left( \frac{\kap}{2} \right)
-    \mathbf{q}(k^2, \boldsymbol{\kappa})^5
+    \sinhalfkap[2v - 3]
+    \coshalfkap
+    \boldsymbol{q}(k^2, \boldsymbol{\kappa})^5
     \quad.
@@
     b_v(k) &= \frac{(2v - 3) k^2}{2v + 3} \nonumber \\
-    c_v(k^2, \kap) &= \Delta
+    c_v(k^2, \bkappa) &= \Delta
     \bigg(
     \frac{
-            \mathbf{z}_v(k^2, \boldsymbol{\kappa})
+            \boldsymbol{z}_v(k^2, \boldsymbol{\kappa})
         }{
@@
     \mathcal{W}_n =
-    \frac{\sin^{2n + 2}\left(\frac{\kap}{2}\right)}{2n + 5}
+    \frac{\sin^{2n + 2}\left(\frac{\bkappa}{2}\right)}{2n + 5}
     \left(

### 2020-03-30 tex/figures/cases.py

@@ -1,0 +1,33 @@
+from code import *
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+# Setup figure
+fig, ax = plt.subplots(2, 4, figsize=(12, 5))
+ax = ax.flatten()
+
+# Labels
+for i, axis in enumerate(ax):
+    axis.axis("off")
+    axis.annotate(
+        "case {}".format(i + 1),
+        xy=(0.5, 0.0),
+        xycoords="axes fraction",
+        xytext=(0, 0),
+        textcoords="offset points",
+        ha="center",
+        va="top",
+        fontsize=10,
+    )
+
+visualize_simple(ax[0], 0.5, 75 * np.pi / 180, 0, 1.1)
+visualize_simple(ax[1], 0.5, 75 * np.pi / 180, 0, 0.25)
+visualize_simple(ax[2], 0.25, 10 * np.pi / 180, 0.8, 0.3)
+visualize_simple(ax[3], -0.25, np.pi, 0.15, 1.05)
+visualize_simple(ax[4], 0.5, 75 * np.pi / 180, 0.5, 0.7)
+visualize_simple(ax[5], 0.5, -10 * np.pi / 180, 0.5, 0.7)
+visualize_simple(ax[6], 0.5, np.pi, 4.65, 5.0)
+visualize_simple(ax[7], -0.5, 0, 4.65, 5.0)
+
+fig.savefig("cases.pdf", bbox_inches="tight")

### 2020-03-30 tex/figures/code/__init__.py

@@ -1,0 +1,3 @@
+from .viz import visualize, visualize_simple
+from .geometry import get_angles
+from .utils import *

### 2020-03-30 tex/figures/code/geometry.py

@@ -1,0 +1,653 @@
+import numpy as np
+from .utils import *
+
+
+def on_dayside(b, theta, costheta, sintheta, x, y):
+    """Return True if a point is on the dayside."""
+    xr = x * costheta + y * sintheta
+    yr = -x * sintheta + y * costheta
+    term = 1 - xr ** 2
+    yt = b * np.sqrt(term)
+    return yr >= yt
+
+
+def sort_phi(b, theta, costheta, sintheta, bo, ro, phi):
+    """
+    Sort a pair of `phi` angles.
+    
+    The basic rule here: the direction phi1 -> phi2 must 
+    always span the dayside.
+    """
+    # First ensure the range is correct
+    phi1, phi2 = phi
+    phi = np.array([phi1, phi2]) % (2 * np.pi)
+    if phi[1] < phi[0]:
+        phi = np.array([phi[0], phi[1] + 2 * np.pi])
+
+    # Now take the midpoint and check that it's on-planet and on the
+    # dayside. If not, we swap the integration limits.
+    phim = np.mean(phi)
+    x = ro * np.cos(phim)
+    y = bo + ro * np.sin(phim)
+    if (x ** 2 + y ** 2 > 1) or not on_dayside(b, theta, costheta, sintheta, x, y):
+        phi = np.array([phi2, phi1]) % (2 * np.pi)
+    if phi[1] < phi[0]:
+        phi = np.array([phi[0], phi[1] + 2 * np.pi])
+    return phi
+
+
+def sort_xi(b, theta, costheta, sintheta, bo, ro, xi):
+    """Sort a pair of `xi` angles.
+    
+    The basic rule here: the direction xi2 --> xi1 must
+    always span the inside of the occultor. (Note that
+    the limits of the `T` integral are xi2 --> xi1, since
+    we integrate *clockwise* along the arc.) Since xi
+    is limited to the range [0, pi], enforcing this is
+    actually trivial: we just need to make sure they are
+    arranged in decreasing order.
+    """
+    xi1, xi2 = xi
+    xi = np.array([xi1, xi2]) % (2 * np.pi)
+    if xi[0] < xi[1]:
+        xi = np.array([xi[1], xi[0]])
+    return xi
+
+
+def sort_lam(b, theta, costheta, sintheta, bo, ro, lam):
+    """
+    Sort a pair of `lam` angles.
+    
+    The basic rule here: the direction lam1 --> lam2
[…]

### 2020-03-30 tex/figures/code/utils.py

@@ -1,0 +1,92 @@
+import numpy as np
+
+# Integration codes
+FLUX_ZERO = 0
+FLUX_DAY_OCC = 1
+FLUX_DAY_VIS = 2
+FLUX_NIGHT_OCC = 3
+FLUX_NIGHT_VIS = 4
+FLUX_SIMPLE_OCC = 5
+FLUX_SIMPLE_REFL = 6
+FLUX_SIMPLE_OCC_REFL = 7
+FLUX_TRIP_DAY_OCC = 8
+FLUX_TRIP_NIGHT_OCC = 9
+FLUX_QUAD_DAY_VIS = 10
+FLUX_QUAD_NIGHT_VIS = 11
+
+# Maximum number of iterations when computing `el2` and `rj`
+STARRY_EL2_MAX_ITER = 100
+STARRY_CRJ_MAX_ITER = 100
+
+# Tolerances in `rj`
+STARRY_CRJ_LO_LIM = 2e-26
+STARRY_CRJ_HI_LIM = 3e24
+STARRY_CRJ_TOL = 2e-2
+
+# Maximum number of iterations & tolerance when computing 2F1
+STARRY_2F1_MAXITER = 200
+STARRY_2F1_TOL = 1e-15
+
+# Square root of the desired precision in `el2`
+STARRY_EL2_CA = 1e-8
+
+# Replace `inf` with this value in argument to `el2`
+STARRY_HUGE_TAN = 1e15
+
+# If |sin(theta)| or |cos(theta)| is less than this, set = 0
+STARRY_T_TOL = 1e-12
+
+# Low, medium, and high tolerance for root polishing
+STARRY_ROOT_TOL_LOW = 1e-2
+STARRY_ROOT_TOL_MED = 1e-10
+STARRY_ROOT_TOL_HIGH = 1e-15
+
+# Tolerance for duplicate roots
+STARRY_ROOT_TOL_DUP = 1e-8
+
+# Maximum number of root polishing iterations
+STARRY_ROOT_MAX_ITER = 50
+
+# If |b| is less than this value, set = 0
+STARRY_B_ZERO_TOL = 1e-8
+
+# Tolerance for various functions that calculate phi, xi, and lam
+STARRY_ANGLE_TOL = 1e-13
+
+# Hacks. Determining the integration paths close to the singular
+# points of the occultation is quite hard, and the solution can
+# often oscillate between two regimes. These tolerances prevent us
+# from entering those regimes, at the cost of precision loss near
+# these singular points.
[…]

### 2020-03-30 tex/figures/code/viz.py

@@ -1,0 +1,529 @@
+from .utils import *
+from .geometry import get_angles
+import matplotlib.pyplot as plt
+from matplotlib.colors import LinearSegmentedColormap
+from matplotlib.patches import Arc
+import numpy as np
+
+
+def visualize_simple(ax, b, theta, bo, ro, res=4999):
+
+    # Find angles of intersection
+    kappa, lam, xi, code = get_angles(b, theta, np.cos(theta), np.sin(theta), bo, ro)
+    phi = kappa - np.pi / 2
+
+    # HACK
+    if code == FLUX_NIGHT_VIS or code == FLUX_DAY_VIS:
+        phi = phi[::-1]
+
+    color_day = (0.122, 0.467, 0.706, 0.33)
+    color_night = (0, 0, 0, 0.75)
+    color_day_occ = (0, 0, 0, 0.25)
+    color_night_occ = (0, 0, 0, 0.5)
+
+    # Equation of half-ellipse
+    x = np.linspace(-1, 1, 1000)
+    y = b * np.sqrt(1 - x ** 2)
+    x_t = x * np.cos(theta) - y * np.sin(theta)
+    y_t = x * np.sin(theta) + y * np.cos(theta)
+
+    # Shaded regions
+    p = np.linspace(-1, 1, res)
+    xpt, ypt = np.meshgrid(p, p)
+    cond1 = xpt ** 2 + (ypt - bo) ** 2 < ro ** 2  # inside occultor
+    cond2 = xpt ** 2 + ypt ** 2 < 1  # inside occulted
+    xr = xpt * np.cos(theta) + ypt * np.sin(theta)
+    yr = -xpt * np.sin(theta) + ypt * np.cos(theta)
+    cond3 = yr > b * np.sqrt(1 - xr ** 2)  # above terminator
+    img_day_occ = np.zeros_like(xpt)
+    img_day_occ[cond1 & cond2 & cond3] = 1
+    img_night_occ = np.zeros_like(xpt)
+    img_night_occ[cond1 & cond2 & ~cond3] = 1
+    img_day = np.zeros_like(xpt)
+    img_day[~cond1 & cond2 & cond3] = 1
+    img_night = np.zeros_like(xpt)
+    img_night[~cond1 & cond2 & ~cond3] = 1
+
+    # Draw basic shapes
+    ax.axis("off")
[…]

### 2020-03-30 tex/figures/geometry.py

@@ -1,0 +1,11 @@
+from code import visualize
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+b = 0.5
+theta = 75 * np.pi / 180
+bo = 0.5
+ro = 0.7
+fig, ax = visualize(b, theta, bo, ro)
+fig.savefig("geometry.pdf", bbox_inches="tight")

### 2020-03-30 tex/ms.tex
added fig

@@
 % Title
-\title{Analytic Light Curves in Reflected Light}
+\title{Occultation Light Curves in Reflected Light}
 
@@
 \section{Introduction}
+\label{sec:intro}
 %
-This is an extension of \citep{Luger2019}.
+This is an extension of \citet{Luger2019}.
+
+\pagebreak
 
 %
-\begin{figure}[h!]
+\section{The Problem}
+\label{sec:the-problem}
+
+As in \citet{Luger2019}, we compute the instantaneous visible flux $f$ from
+a spherical body whose surface intensity is described by the spherical harmonic
+coefficient vector $\mathbf{y}$ as
+%
+\begin{align}
+    \label{eq:sTARRy}
+    f = \bvec{s}^\top \bvec{A} \bvec{R}' \bvec{R} \bvec{y}
+    \quad,
+\end{align}
+%
+where $\bvec{R}$ and $\bvec{R}'$ are spherical harmonic rotation matrices,
+$\bvec{A}$ is a change-of-basis matrix to a basis $\tilde{\bvec{g}}$,
+and $\bvec{s}^\top$ is the \emph{solution vector}, the integral of each
+of the basis functions in $\tilde{\bvec{g}}$ over
+the projected visible disk of the body (which may be partially occulted by
+another spherical body).
+For more information on these terms, the reader is referred to
+\citet{Luger2019}.
+
+\begin{figure}[t!]
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/speed.pdf}
-        \oscaption{speed}{%
-            Evaluation time for the starry algorithm.
-            \label{fig:speed}
+        \includegraphics[width=0.35\linewidth]{figures/illum.pdf}
+        \oscaption{illum}{%
+            Illumination geometry.
+            \label{fig:illum}
         }
@@
 
-\begin{figure}[h!]
+The derivations in \citet{Luger2019} assume that the coefficient vector
+$\mathbf{y}$ describes the \emph{emissivity} of the body, which (in the
+absence of limb darkening) is assumed to be Lambertian, i.e., all points on the
+surface emit equally in all directions.
+Here, we derive the solution to the occultation problem for Lambertian
+reflectance, in which case the vector $\mathbf{y}$ describes the
+surface \emph{reflectivity} (or \emph{Bond albedo}). Specifically, we assume
+the body is illuminated by a point-like source and the radiance at any point
+is proportional to the cosine of the angle between the incident light
+and the surface normal. Points for which this angle is greater than
+$\frac{\pi}{2}$ are unilluminated and therefore have radiance of zero;
+see Figure~\ref{fig:illum}.
+
+% case 1: 0
+% case 2: sTr
+% case 3: sTe * I + ~sTr
+% case 4: sTe * I
+% case 5: sTr - sT0 * I
+% case 6: (sTe + sT0) * I + ~sTr
+% case 7: (sTe - sT0) * I
+% case 8: sT0 * I
+
+\begin{figure}[t!]
     \begin{centering}
@@
 
-\begin{figure}[h!]
+\section{Cases 1--4}
+\label{sec:cases-1-4}
+TODO.
+
+\section{Cases 5--8}
+\label{sec:cases-5-8}
+
+\begin{figure}[t!]
     \begin{centering}
@@
     \label{eq:s}
-    \mathbf{s}_{n(\mu,\nu)} = \oint \mathbf{G}_{\mu,\nu} \cdot \dd\mathbf{r}
+    s_{n(\mu,\nu)} = \oint \mathbf{G}_{\mu,\nu} \cdot \dd\mathbf{r}
 \end{align}
@@
 configuration in Figure~\ref{fig:geometry}.
+
+\section{Performance}
+\label{sec:performance}
+
+%
+\begin{figure}[h!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/speed.pdf}
+        \oscaption{speed}{%
+            Evaluation time for the starry algorithm.
+            \label{fig:speed}
+        }
+    \end{centering}
+\end{figure}
 

### 2020-03-30 tex/figures/illum.py

@@ -1,0 +1,74 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.patches import Arc
+
+fig, ax = plt.subplots(1, figsize=(6, 6))
+ax.set_aspect(1)
+ax.set_xlim(-1.1, 1.1)
+ax.set_ylim(-1.1, 1.1)
+ax.axis("off")
+b = 0.25
+theta = np.pi / 3
+
+# Illumination
+x0, y0 = np.meshgrid(np.linspace(-1, 1, 3000), np.linspace(-1, 1, 3000))
+
+x = x0 * np.cos(theta) + y0 * np.sin(theta)
+y = -x0 * np.sin(theta) + y0 * np.cos(theta)
+z = np.sqrt(1 - x ** 2 - y ** 2)
+I = np.sqrt(1 - b ** 2) * y - b * z
+I[I < 0] = 0
+cmap = plt.get_cmap("Greys_r")
+ax.imshow(
+    I, extent=(-1, 1, -1, 1), origin="lower", vmin=1e-8, vmax=np.nanmax(I), cmap=cmap
+)
+
+# Planet
+x = np.linspace(-1, 1, 1000)
+yp = np.sqrt(1 - x ** 2)
+ax.plot(x, yp, "k-", lw=1, zorder=99)
+ax.plot(x, -yp, "k-", lw=1, zorder=99)
+
+# Terminator
+x0 = np.linspace(-1, 1, 1000)
+y0 = b * np.sqrt(1 - x0 ** 2)
+x = x0 * np.cos(theta) - y0 * np.sin(theta)
+y = x0 * np.sin(theta) + y0 * np.cos(theta)
+plt.plot(x, y, "r-", lw=1)
+
+ax.plot([0, -b * np.sin(theta)], [0, b * np.cos(theta)], "w--", lw=1)
+ax.plot([0, np.cos(theta)], [0, np.sin(theta)], "w--", lw=1)
+ax.plot([0, 1], [0, 0], "w--", lw=1)
+ax.annotate(
+    r"$b$",
+    xy=(0.45, 0.57),
+    xycoords="axes fraction",
+    ha="left",
+    va="center",
+    color="w",
+    fontsize=18,
+)
+ax.annotate(
+    r"$1$",
+    xy=(0.58, 0.73),
+    xycoords="axes fraction",
+    ha="left",
+    va="center",
+    color="w",
+    fontsize=18,
+)
+ax.annotate(
[…]

### 2020-03-31 tex/ms.tex
more text

@@
 \label{sec:the-problem}
-
+%
 As in \citet{Luger2019}, we compute the instantaneous visible flux $f$ from
@@
 %
-where $\bvec{R}$ and $\bvec{R}'$ are spherical harmonic rotation matrices,
-$\bvec{A}$ is a change-of-basis matrix to a basis $\tilde{\bvec{g}}$,
+where $\bvec{R}$ and $\bvec{R}'$ are spherical harmonic rotation matrices
+\citep[\S3.3 of][]{Luger2019},
+$\bvec{A}$ is the change-of-basis matrix from spherical harmonics
+to a basis $\tilde{\bvec{g}}$ \citep[Equation B13 in][]{Luger2019},
 and $\bvec{s}^\top$ is the \emph{solution vector}, the integral of each
@@
 another spherical body).
-For more information on these terms, the reader is referred to
+%
+The basis $\tilde{\bvec{g}}$ is called the \emph{Green's basis}; its name
+stems from the fact that its components have a structure that makes integration
+by Green's theorem convenient. Its components were defined in
+Equation~11 of \citet{Luger2019b}:
+%
+\begin{proof}{bg}
+    \tilde{g}_{l,m} &=
+    \begin{dcases}
+        %
+        \frac{\mu+2}{2}x^\frac{\mu}{2} y^\frac{\nu}{2}
+         & \qquad \mu, \nu \, \mathrm{even}
+        \\[1em]
+        %
+        z(x, y)
+         & \qquad \mu = \nu = 1
+        \\[1em]
+        %
+        3x^{l-2}yz(x, y)
+         & \qquad \nu \, \mathrm{odd}, \,
+        \mu = 1, \,
+        \frac{\mu + \nu}{2} \, \mathrm{even}
+        \\[1em]
+        %
+        z(x, y)
+        \bigg(
+        -x^{l-3} + x^{l-1} + 4x^{l-3}y^2
+        \bigg)
+         & \qquad \nu \, \mathrm{odd}, \,
+        \mu = 1, \,
+        \, \mathrm{odd}
+        \\[1em]
+        %
+        z(x, y)
+        \bigg(
+        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu-1}{2}
+        \ - \
+        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu+3}{2}
+        \\
+        \qquad\qquad \ - \
+        \frac{\mu+3}{2} x^\frac{\mu-1}{2} y^\frac{\nu-1}{2}
+        \bigg)
+         & \qquad \mathrm{otherwise}
+        \quad,
+    \end{dcases}
+    \label{eq:bg}
+\end{proof}
+%
+where $x$ and $y$ are the Cartesian components on the surface
+of the projected
+disk of the body, with $z(x, y) = \sqrt{1 - x^2 - y^2}$, and
+%
+\begin{align}
+    \mu & = l - m
+    \nonumber     \\
+    \nu & = l + m
+    \quad.
+\end{align}
+%
+The vector $\tilde{\bvec{g}}$ is structured such that
+the component at index $n$ is $\tilde{g}_{l,m}$ with
+\begin{align}
+    \label{eq:lm}
+    l & = \floor*{\sqrt{n}} \nonumber \\
+    m & = n - l^2 - l
+    \quad.
+\end{align}
+\xxx{The rotation matrices do the following...}
+For more information on all of these terms, the reader is referred to
 \citet{Luger2019}.
@@
         \oscaption{illum}{%
-            Illumination geometry.
+            Illumination geometry for the unocculted case.
+            A point source at Cartesian coordinates
+            $(0, y_s, z_s)$ illuminates a uniform,
+            Lambertian, spherical body of radius unity. The observed
+            radiance falls off as the cosine of the angle $\phi$ between the
+            source and the surface normal. Beyond the terminator
+            (defined by $\phi = \frac{\pi}{2}$), the radiance is zero. In
+            projection, the terminator is a segment of an ellipse of semi-major
+            axis unity and semi-minor axis
+            $b = -\nicefrac{z_s}{\sqrt{y_s^2 + z_s^2}}$.
             \label{fig:illum}
@@
 the body is illuminated by a point-like source and the radiance at any point
-is proportional to the cosine of the angle between the incident light
-and the surface normal. Points for which this angle is greater than
-$\frac{\pi}{2}$ are unilluminated and therefore have radiance of zero;
-see Figure~\ref{fig:illum}.
+is proportional to the cosine of the angle $\phi$ between the incident light
+and the surface normal. Points for which $\phi \ge \frac{\pi}{2}$ are
+unilluminated and therefore have radiance of zero; see Figure~\ref{fig:illum}.
 
+In \citet{Luger2019}, the crux of the problem was to compute the terms in the
+vector $\bvec{s}^\top$, which are surface integrals over
+the region of the occulted body that is visible to
+the observer (Figure 2 in that paper). Here, these integrals are significantly
+more difficult, because they involve not only the intersection of the
+limbs of the two bodies, but also intersections with the elliptical
+day/night terminator of the occulted body. Figure~\ref{fig:cases} shows the
+eight families of cases involving an occultation of an illuminated body by
+a spherical occultor. Each of these cases correspond to distinct ways in
+which the limb of the occultor can intersect with the limb of the occulted
+body and its terminator; together, these cases encompass all possible
+occultation configurations, for any illumination angle, occultor size, and
+occultor position. In the next three sections, we present the solution for the
+$\bvec{s}^\top$, and hence for the total visible flux, for each of these cases.
+
+% case 0: sTr
 % case 1: 0
@@
 
-\section{Cases 1--4}
+\section{The Solution: Case 0}
+\label{sec:cases-0}
+%
+Before we tackle configurations involving occultations, we must address the
+simpler problem of computing the total visible flux from an unocculted
+body in reflected light (see Figure~\ref{fig:illum}). This problem was
+originally solved by \citet{Haggard2018} and subsequently adapted to the
+\starry formalism in \citet{Luger2019b}, but for completeness we present
+the detailed solution below.
+
+Our task is to compute the solution vector for this
+configuration, which we will denote $\bvec{s}^\top_0$.  When no occultor
+is present (as in this case), it is
+more convenient to perform the integration in the \emph{polynomial basis}
+$\tilde{\bvec{p}}$ \citep[Equation 7 in][]{Luger2019}:
+%
+\begin{align}
+    \tilde{p}_{l,m}(x, y) & =
+    \begin{dcases}
+        x^\frac{\mu}{2} y^\frac{\nu}{2}
+         & \qquad \mu, \nu \, \mathrm{even}
+        \\[1em]
+        x^\frac{\mu-1}{2} y^\frac{\nu-1}{2} z(x, y)
+         & \qquad \mathrm{otherwise} \quad,
+    \end{dcases}
+\end{align}
+%
+where \xxx{we unroll p as before...}
+The solution vector is then given by
+%
+\begin{align}
+    \label{eq:sTref}
+    \bvec{s}^\top_0 & = \bvec{r}^\top \bvec{A_1} \bvec{R} \bvec{A}^{-1}
+    \quad,
+\end{align}
+%
+where $\bvec{r}^\top$ is the solution vector in the polynomial basis,
+$\bvec{A_1}$ is the change-of-basis matrix between the polynomial basis
+and the spherical harmonic basis, $\bvec{R}$ is a spherical harmonic rotation
+matrix, and $\bvec{A}$ is the change-of basis matrix between the spherical
+harmonic basis and the Green's basis.
+\xxx{In words, the equation above reads...}
+
+\xxx{...} In this frame, the body sits at the origin and is illuminated by a point
+source in the
+$y-z$ plane at coordinates $(0, y_s, z_s)$. It is straightforward to show
+that the illumination at a point $(x, y)$ on the projected disk is
+given by
+%
+\begin{proof}{illum}
+    \Psi(b; x, y) & =
+    \begin{dcases}
+        b_cy - bz(x, y) &
+        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
+        y \geq b \sqrt{1 - x^2}
+        \\
+        0               &
+        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
+        \mathrm{otherwise}
+    \end{dcases}
+    \quad ,
+    \label{eq:illum}
+\end{proof}
+%
+where $b_c = \sqrt{1 - b^2}$.
+%
+\xxx{The solution vector may then be computed as...}
+%
+\begin{align}
+    \label{eq:rT}
+    r_{n(\mu,\nu)} & =
+    \int_{-1}^{1}
+    \int_{b\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
+    \tilde{p}_{n(\mu,\nu)}(x, y)
+    \Psi(b; x, y)
+    \ \dd y \ \dd x
+    \quad.
+\end{align}
+%
+Equation~(\ref{eq:rT}) may be solved analytically in terms of purely
+trigonometric and algebraic functions of $b$:
+%
+\begin{proof}{rT}
+    \label{eq:rTsoln}
+    r_{n(\mu,\nu)} & =
+    \begin{cases}
+        \frac{b_c\left(1 - b^{\frac{\nu + 4}{2}}\right)}{2}
+        J_{\frac{\mu}{2}, \frac{\nu + 2}{2}} -
+        b I_\frac{\nu}{2}(b) K_{\frac{\mu}{2}, \frac{\nu}{2}}
+        %
+         &
+        %
+        \qquad
+        \mu, \nu \ \mathrm{even}
+        %
+        \\[1em]
+        %
+        b_c
+        I_{\frac{\nu + 1}{2}}(b) K_{\frac{\mu - 1}{2}, \frac{\nu + 1}{2}}
+        %
+        \\[0.5em]
+        \qquad
+        %
+        - \frac{b}{2} \bigg\{
+        \left(1 - b^{\frac{\nu + 1}{2}}\right)
+        \left(
+        J_{\frac{\mu - 1}{2}, \frac{\nu - 1}{2}} -
+        J_{\frac{\mu + 3}{2}, \frac{\nu - 1}{2}}
+        \right)
+        \\[0.5em]
+        \qquad\qquad
+        -
+        \left(1 - b^{\frac{\nu + 5}{2}}\right)
+        J_{\frac{\mu - 1}{2}, \frac{\nu + 3}{2}}
+        \bigg\}
+        %
+         &
+        %
+        \qquad
+        \mathrm{otherwise}
+        %
+    \end{cases}
+\end{proof}
+%
+where
+%
+\begin{proof}{rT}
+    \label{eq:IJK}
+    I_{j}(b) &= \int_b^1 a^j \sqrt{1 - a^2} \dd a
+    \nonumber \\
+    %
+    J_{i,j} &=
+    \frac{
+        \Gamma\left(\frac{i + 1}{2}\right)
+        \Gamma\left(\frac{j + 1}{2}\right)
+    }
+    {
+        \Gamma\left(\frac{i + j + 4}{2}\right)
+    }
+    %
+    \nonumber \\
+    %
+    K_{i,j} &=
+    \frac{
+        \Gamma\left(\frac{i + 1}{2}\right)
+        \Gamma\left(\frac{j + 4}{2}\right)
+    }
+    {
+        \Gamma\left(\frac{i + j + 5}{2}\right)
+    }
+    \quad.
+\end{proof}
+%
+Given initial conditions
+%
+\\[1em]
+\begin{minipage}{.33\linewidth}
+    \begin{proof}{rT}
+        I_{0}(b) &= \frac{\arccos(b) - bb_c}{2}
+        %
+        \nonumber \\
+        %
+        I_{1}(b) &= \frac{b_c^3}{3}
+        %
+        \nonumber
+    \end{proof}
+\end{minipage}%
+\begin{minipage}{.32\linewidth}
+    \begin{proof}{rT}
+        J_{0,0} &= \pi
+        %
+        \nonumber \\
+        %
+        J_{0,1} &= \frac{4}{3}
+        %
+        \nonumber
+    \end{proof}
+\end{minipage}%
+\begin{minipage}{.33\linewidth}
+    \begin{proof}{rT}
+        \label{eq:IJK0}
+        K_{0,0} &= \frac{4}{3}
+        %
+        \nonumber \\
+        K_{0,1} &= \frac{3\pi}{8}
+    \end{proof}
+\end{minipage}
+\\[1em]
+%
+we may compute all higher order terms from the recurrence relations
+%
+\begin{proof}{rT}
+    \label{eq:IJKrec}
+    I_{j}(b) &= \frac{b^n b_c^3 + (j - 1) I_{j - 2}(b)}{j + 2}
+    %
+    \nonumber \\
+    %
+    J_{0,j} &= \left(\frac{j - 1}{j + 2}\right) J_{0,j-2}
+    %
+    \nonumber \\
+    %
+    K_{0,j} &= \left(\frac{j + 2}{j + 3}\right) K_{0,j-2}
+    %
+    \nonumber \\
+    %
+    J_{i,j} &= \left(\frac{i - 1}{i + j + 2}\right) J_{i-2,j}
+    %
+    \nonumber \\
+    %
+    K_{i,j} &= \left(\frac{i - 1}{i + j + 3}\right) K_{i-2,j}
+    \quad.
+\end{proof}
+%
+
+\section{The Solution: Cases 1--4}
 \label{sec:cases-1-4}
-TODO.
+Cases 1--4 (see Figure~\ref{fig:cases}) involve configurations in which the
+occultor does not intersect with
+the terminator of the occulted body, and are therefore significantly easier to
+solve.
 
-\section{Cases 5--8}
+\section{The Solution: Cases 5--8}
 \label{sec:cases-5-8}
+Cases 5--8 (see Figure~\ref{fig:cases}).
 

### 2020-03-31 tex/figures/cases.py

@@ -2,12 +2,21 @@ from code import *
 import numpy as np
 import matplotlib.pyplot as plt
 
-
 # Setup figure
 fig, ax = plt.subplots(2, 4, figsize=(12, 5))
 ax = ax.flatten()
 
-# Labels
+# Cases
+visualize_simple(ax[0], 0.5, 75 * np.pi / 180, 0, 1.1)
+visualize_simple(ax[1], 0.5, 75 * np.pi / 180, 0, 0.25)
+visualize_simple(ax[2], 0.25, 10 * np.pi / 180, 0.8, 0.3)
+visualize_simple(ax[3], -0.25, np.pi, 0.15, 1.05)
+visualize_simple(ax[4], 0.5, 75 * np.pi / 180, 0.5, 0.7)
+visualize_simple(ax[5], 0.5, -10 * np.pi / 180, 0.5, 0.7)
+visualize_simple(ax[6], 0.5, np.pi, 4.65, 5.0)
+visualize_simple(ax[7], -0.5, 0, 4.65, 5.0)
+
+# Appearance
 for i, axis in enumerate(ax):
     axis.axis("off")
     axis.annotate(
@@ -20,14 +29,6 @@ for i, axis in enumerate(ax):
         va="top",
         fontsize=10,
     )
+    axis.set_rasterization_zorder(0)
 
-visualize_simple(ax[0], 0.5, 75 * np.pi / 180, 0, 1.1)
-visualize_simple(ax[1], 0.5, 75 * np.pi / 180, 0, 0.25)
-visualize_simple(ax[2], 0.25, 10 * np.pi / 180, 0.8, 0.3)
-visualize_simple(ax[3], -0.25, np.pi, 0.15, 1.05)
-visualize_simple(ax[4], 0.5, 75 * np.pi / 180, 0.5, 0.7)
-visualize_simple(ax[5], 0.5, -10 * np.pi / 180, 0.5, 0.7)
-visualize_simple(ax[6], 0.5, np.pi, 4.65, 5.0)
-visualize_simple(ax[7], -0.5, 0, 4.65, 5.0)
-
-fig.savefig("cases.pdf", bbox_inches="tight")
+fig.savefig("cases.pdf", bbox_inches="tight", dpi=300)

### 2020-03-31 tex/figures/code/viz.py

@@ -16,7 +16,6 @@ def visualize_simple(ax, b, theta, bo, ro, res=4999):
     if code == FLUX_NIGHT_VIS or code == FLUX_DAY_VIS:
         phi = phi[::-1]
 
-    color_day = (0.122, 0.467, 0.706, 0.33)
     color_night = (0, 0, 0, 0.75)
     color_day_occ = (0, 0, 0, 0.25)
     color_night_occ = (0, 0, 0, 0.5)
@@ -39,10 +38,15 @@ def visualize_simple(ax, b, theta, bo, ro, res=4999):
     img_day_occ[cond1 & cond2 & cond3] = 1
     img_night_occ = np.zeros_like(xpt)
     img_night_occ[cond1 & cond2 & ~cond3] = 1
-    img_day = np.zeros_like(xpt)
-    img_day[~cond1 & cond2 & cond3] = 1
     img_night = np.zeros_like(xpt)
     img_night[~cond1 & cond2 & ~cond3] = 1
+    x0, y0 = np.meshgrid(np.linspace(-1, 1, res), np.linspace(-1, 1, res))
+    x = x0 * np.cos(theta) + y0 * np.sin(theta)
+    y = -x0 * np.sin(theta) + y0 * np.cos(theta)
+    z = np.sqrt(1 - x ** 2 - y ** 2)
+    img_day = np.sqrt(1 - b ** 2) * y - b * z
+    img_day[img_day < 0] = np.nan
+    img_day[cond1] = np.nan
 
     # Draw basic shapes
     ax.axis("off")
@@ -60,6 +64,8 @@ def visualize_simple(ax, b, theta, bo, ro, res=4999):
         cmap=LinearSegmentedColormap.from_list(
             "cmap1", [(0, 0, 0, 0), color_day_occ], 2
         ),
+        interpolation="none",
+        zorder=-1,
     )
     ax.imshow(
         img_night_occ,
@@ -69,13 +75,27 @@ def visualize_simple(ax, b, theta, bo, ro, res=4999):
         cmap=LinearSegmentedColormap.from_list(
             "cmap1", [(0, 0, 0, 0), color_night_occ], 2
         ),
+        interpolation="none",
+        zorder=-1,
     )
     ax.imshow(
         img_day,
         origin="lower",
         extent=(-1, 1, -1, 1),
         alpha=1,
[…]

### 2020-03-31 tex/figures/illum.py

@@ -1,6 +1,7 @@
 import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib.patches import Arc
+from matplotlib.colors import LinearSegmentedColormap
 
 fig, ax = plt.subplots(1, figsize=(6, 6))
 ax.set_aspect(1)
@@ -8,67 +9,110 @@ ax.set_xlim(-1.1, 1.1)
 ax.set_ylim(-1.1, 1.1)
 ax.axis("off")
 b = 0.25
-theta = np.pi / 3
+theta = 0
 
 # Illumination
+cdict = {
+    "red": [[0.0, 0.0, 0.122], [1.0, 1.0, 1.0]],
+    "green": [[0.0, 0.0, 0.467], [1.0, 1.0, 1.0]],
+    "blue": [[0.0, 0.0, 0.706], [1.0, 1.0, 1.0]],
+}
+cmap = LinearSegmentedColormap("testCmap", segmentdata=cdict, N=256)
+cmap.set_under("k")
 x0, y0 = np.meshgrid(np.linspace(-1, 1, 3000), np.linspace(-1, 1, 3000))
-
 x = x0 * np.cos(theta) + y0 * np.sin(theta)
 y = -x0 * np.sin(theta) + y0 * np.cos(theta)
 z = np.sqrt(1 - x ** 2 - y ** 2)
 I = np.sqrt(1 - b ** 2) * y - b * z
 I[I < 0] = 0
-cmap = plt.get_cmap("Greys_r")
 ax.imshow(
-    I, extent=(-1, 1, -1, 1), origin="lower", vmin=1e-8, vmax=np.nanmax(I), cmap=cmap
+    I,
+    extent=(-1, 1, -1, 1),
+    origin="lower",
+    vmin=1e-8,
+    vmax=1,
+    cmap=cmap,
+    alpha=0.75,
+    zorder=-1,
 )
 
 # Planet
 x = np.linspace(-1, 1, 1000)
 yp = np.sqrt(1 - x ** 2)
-ax.plot(x, yp, "k-", lw=1, zorder=99)
-ax.plot(x, -yp, "k-", lw=1, zorder=99)
+ax.plot(x, yp, "k-", lw=1.5, zorder=98)
+ax.plot(x, -yp, "k-", lw=1.5, zorder=98)
 
 # Terminator
 x0 = np.linspace(-1, 1, 1000)
 y0 = b * np.sqrt(1 - x0 ** 2)
[…]

### 2020-04-01 tex/ms.tex
tweaks

@@
 a spherical body whose surface intensity is described by the spherical harmonic
-coefficient vector $\mathbf{y}$ as
+coefficient vector $\mathbf{y}$ in some static frame $\mathcal{F}$ as
 %
@@
 %
-where $x$ and $y$ are the Cartesian components on the surface
+where $x$ and $y$ are the Cartesian coordinates on the surface
 of the projected
@@
 \begin{align}
+    \label{eq:munu}
     \mu & = l - m
@@
 %
-The vector $\tilde{\bvec{g}}$ is structured such that
-the component at index $n$ is $\tilde{g}_{l,m}$ with
+The vector $\tilde{\bvec{g}}$ is ordered such that
+the component at index $n$ is $\tilde{g}_{l,m}$, with
 \begin{align}
@@
 \end{align}
-\xxx{The rotation matrices do the following...}
+Finally, the rotation matrix $\bvec{R} = \bvec{R}(i, \lambda, \theta)$
+rotates the body to the correct orientation on the sky given its
+inclination $i$, obliquity $\lambda$, and rotational phase $\theta$,
+while $\bvec{R}'$ rotates the body on the plane
+of the sky into the frame $\mathcal{F}'$ in which the integration is
+actually performed, with the occultor along the $+y$-axis.
 For more information on all of these terms, the reader is referred to
@@
 Our task is to compute the solution vector for this
-configuration, which we will denote $\bvec{s}^\top_0$.  When no occultor
-is present (as in this case), it is
-more convenient to perform the integration in the \emph{polynomial basis}
-$\tilde{\bvec{p}}$ \citep[Equation 7 in][]{Luger2019}:
+configuration, which we will denote $\bvec{s}^\top_0$.
+Since in this case there is no occultor, it is
+more convenient to perform the integration in a frame $\mathcal{F}''$ where the
+semi-major axis of the terminator is aligned with the $x$-axis
+(see Figure~\ref{fig:illum}); let us denote the matrix that rotates us
+from $\mathcal{F}'$ to $\mathcal{F}''$ as $\bvec{R}''$.
+It is also far easier to perform the integration
+in the \emph{polynomial basis} $\tilde{\bvec{p}}$
+\citep[Equation 7 in][]{Luger2019}:
 %
@@
 %
-where \xxx{we unroll p as before...}
-The solution vector is then given by
+where $\tilde{\bvec{p}}$ is again ordered such that the component at
+index $n$ is $\tilde{p}_{l,m}$, with $l$ and $m$ given by
+Equation~(\ref{eq:lm}).
+Now, if $\bvec{r}^\top$ is the solution to the surface integrals in the
+polynomial basis in $\mathcal{F}''$,
+we may compute the desired solution vector in the Green's basis from
 %
@@
     \label{eq:sTref}
-    \bvec{s}^\top_0 & = \bvec{r}^\top \bvec{A_1} \bvec{R} \bvec{A}^{-1}
+    \bvec{s}^\top_0 & = \bvec{r}^\top \bvec{A_1} \bvec{R}'' \bvec{A}^{-1}
     \quad,
@@
 %
-where $\bvec{r}^\top$ is the solution vector in the polynomial basis,
-$\bvec{A_1}$ is the change-of-basis matrix between the polynomial basis
-and the spherical harmonic basis, $\bvec{R}$ is a spherical harmonic rotation
-matrix, and $\bvec{A}$ is the change-of basis matrix between the spherical
-harmonic basis and the Green's basis.
-\xxx{In words, the equation above reads...}
+where $\bvec{A_1}$ \citep[Equation B11 in][]{Luger2019}
+transforms the solution into the spherical harmonic basis so it can
+be rotated out of the integration frame $\mathcal{F}''$ via $\bvec{R}''$, and
+$\bvec{A}^{-1}$ \citep[Equation B13 in][]{Luger2019} transforms the
+result into the Green's basis (in which $\bvec{s}^\top$ is defined).
 
-\xxx{...} In this frame, the body sits at the origin and is illuminated by a point
-source in the
-$y-z$ plane at coordinates $(0, y_s, z_s)$. It is straightforward to show
+Our task is thus to compute $\bvec{r}^\top$.
+In frame $\mathcal{F}''$, the body sits at the origin and is
+illuminated by a point source in the
+$y-z$ plane at coordinates $(0, y_s, z_s)$ as in Figure~\ref{fig:illum}.
+The day/night terminator is a half-ellipse whose semi-major axis
+is unity and is aligned with the $x$-axis. The semi-minor axis is given
+by $b = -\nicefrac{z_s}{\sqrt{y_s^2 + z_s^2}}$, where $b > 0$ corresponds to
+a half-ellipse that is concave down and $b < 0$ to one that is concave up.
+It is straightforward to show
 that the illumination at a point $(x, y)$ on the projected disk is
@@
 %
-\xxx{The solution vector may then be computed as...}
+The elements of the solution vector may then be computed from
 %
@@
     \label{eq:rT}
-    r_{n(\mu,\nu)} & =
+    r_{l, m}(b) & =
     \int_{-1}^{1}
@@
 %
+This is the integral of the illumination-weighted intensity of each
+term in the polynomial basis over the projected visible dayside of the
+body.
+%
 Equation~(\ref{eq:rT}) may be solved analytically in terms of purely
@@
     \label{eq:rTsoln}
-    r_{n(\mu,\nu)} & =
+    r_{l, m}(b) & =
     \begin{cases}

### 2020-04-01 tex/figures/code/viz.py

@@ -187,10 +187,9 @@ def visualize(b, theta, bo, ro, res=4999):
     kappa, lam, xi, code = get_angles(b, theta, np.cos(theta), np.sin(theta), bo, ro)
     phi = kappa - np.pi / 2
 
-    color_day = (1, 1, 1, 1)
     color_night = (0, 0, 0, 0.75)
-    color_day_occ = (0.122, 0.467, 0.706, 0.33)
-    color_night_occ = (0, 0, 0, 0.25)
+    color_day_occ = (0, 0, 0, 0.25)
+    color_night_occ = (0, 0, 0, 0.5)
 
     # Equation of half-ellipse
     x = np.linspace(-1, 1, 1000)
@@ -210,23 +209,28 @@ def visualize(b, theta, bo, ro, res=4999):
     img_day_occ[cond1 & cond2 & cond3] = 1
     img_night_occ = np.zeros_like(xpt)
     img_night_occ[cond1 & cond2 & ~cond3] = 1
-    img_day = np.zeros_like(xpt)
-    img_day[~cond1 & cond2 & cond3] = 1
     img_night = np.zeros_like(xpt)
     img_night[~cond1 & cond2 & ~cond3] = 1
+    x0, y0 = np.meshgrid(np.linspace(-1, 1, res), np.linspace(-1, 1, res))
+    x = x0 * np.cos(theta) + y0 * np.sin(theta)
+    y = -x0 * np.sin(theta) + y0 * np.cos(theta)
+    z = np.sqrt(1 - x ** 2 - y ** 2)
+    img_day = np.sqrt(1 - b ** 2) * y - b * z
+    img_day[img_day < 0] = np.nan
+    img_day[cond1] = np.nan
 
     # Plot
     if len(lam):
         fig, ax = plt.subplots(1, 3, figsize=(14, 5))
         fig.subplots_adjust(left=0.025, right=0.975, bottom=0.05, top=0.825)
-        ax[1].set_title("T", color="r")
-        ax[0].set_title("P", color="r")
-        ax[2].set_title("Q", color="r")
+        ax[1].set_title(r"$\mathcal{T}$", color="C1", fontsize=24)
+        ax[0].set_title(r"$\mathcal{P}$", color="C1", fontsize=24)
+        ax[2].set_title(r"$\mathcal{Q}$", color="C1", fontsize=24)
     else:
         fig, ax = plt.subplots(1, 2, figsize=(9, 5))
[…]

### 2020-04-01 tex/figures/geometry.py

@@ -8,4 +8,6 @@ theta = 75 * np.pi / 180
 bo = 0.5
 ro = 0.7
 fig, ax = visualize(b, theta, bo, ro)
+for axis in ax:
+    axis.set_rasterization_zorder(0)
 fig.savefig("geometry.pdf", bbox_inches="tight")

### 2020-04-01 tex/ms.tex
frames fig

@@
 \usepackage{xifthen}
+\newcommand{\BF}[1]{\ensuremath{\mathbf{#1}}}
+\newcommand{\BS}[1]{\ensuremath{\boldsymbol{#1}}}
 \newcommand{\dd}{\ensuremath{\mathrm{d}}}
 \newcommand{\STARRYQUADPOINTS}{100\xspace}
-\newcommand{\bkappa}{\boldsymbol{\kappa}}
-\newcommand{\blambda}{\boldsymbol{\lambda}}
-\newcommand{\bxi}{\boldsymbol{\xi}}
+\newcommand{\bkappa}{\BS{\kappa}}
+\newcommand{\blambda}{\BS{\lambda}}
+\newcommand{\bxi}{\BS{\xi}}
 \newcommand{\vmax}{{v_\mathrm{max}}}
@@
 }}
-\newcommand{\DE}{\Delta \boldsymbol{E}(k^2, \bkappa)}
-\newcommand{\DF}{\Delta \boldsymbol{F}(k^2, \bkappa)}
+\newcommand{\DE}{\Delta \BS{E}(k^2, \bkappa)}
+\newcommand{\DF}{\Delta \BS{F}(k^2, \bkappa)}
 \newcommand{\sgn}{{\mathrm{sgn}}}
@@
 \newcommand{\zhat}{\ensuremath{\mathbf{\hat{z}}}\xspace}
+\newcommand{\sT}{\ensuremath{\BF{s}^\top}}
+\newcommand{\bg}{\ensuremath{\tilde{\BF{g}}}}
+\newcommand{\bp}{\ensuremath{\tilde{\BF{p}}}}
 
@@
 
-\pagebreak
-
 %
@@
 %
-As in \citet{Luger2019}, we compute the instantaneous visible flux $f$ from
-a spherical body whose surface intensity is described by the spherical harmonic
-coefficient vector $\mathbf{y}$ in some static frame $\mathcal{F}$ as
+\subsection{Overview}
+\label{sec:overview}
+%
+Without loss of generality, assume the body whose flux we wish to compute
+has radius unity and sits at the origin of a right-handed Cartesian coordinate
+system with the $x$-axis pointing to the right on the sky, the $y$-axis
+pointing up on the sky, and the $z$-axis pointing out of the sky
+toward the observer; denote this frame by $\mathcal{F}_0$. In $\mathcal{F}_0$,
+the surface intensity field of the body is described by the spherical harmonic
+coefficient vector $\mathbf{y}$. Following \citet{Luger2019}, we may compute
+the total visible flux $f$ from this body as
 %
@@
     \label{eq:sTARRy}
-    f = \bvec{s}^\top \bvec{A} \bvec{R}' \bvec{R} \bvec{y}
+    f = \sT \BF{A} \BF{R}' \BF{R} \BF{y}
     \quad,
@@
 %
-where $\bvec{R}$ and $\bvec{R}'$ are spherical harmonic rotation matrices
-\citep[\S3.3 of][]{Luger2019},
-$\bvec{A}$ is the change-of-basis matrix from spherical harmonics
-to a basis $\tilde{\bvec{g}}$ \citep[Equation B13 in][]{Luger2019},
-and $\bvec{s}^\top$ is the \emph{solution vector}, the integral of each
-of the basis functions in $\tilde{\bvec{g}}$ over
+where, from right to left, $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
+is a Wigner rotation matrix that
+rotates $\bvec{y}$ to the sky frame $\mathcal{F}_\mathrm{sky}$
+given the body's inclination $i$, obliquity $\lambda$, and
+rotational phase $\vartheta$,
+%
+$\BF{R}'$ rotates the body on the plane
+of the sky into the frame $\mathcal{F}_\mathrm{int}$ in which the
+integration is actually performed,
+%
+$\BF{A}$ is the change-of-basis matrix from spherical harmonics
+to the basis in which the integrals are computed
+%,
+and $\sT$ is the \emph{solution vector}, the integral of each
+of the basis functions over
 the projected visible disk of the body (which may be partially occulted by
-another spherical body).
-%
-The basis $\tilde{\bvec{g}}$ is called the \emph{Green's basis}; its name
-stems from the fact that its components have a structure that makes integration
-by Green's theorem convenient. Its components were defined in
-Equation~11 of \citet{Luger2019b}:
-%
-\begin{proof}{bg}
-    \tilde{g}_{l,m} &=
-    \begin{dcases}
-        %
-        \frac{\mu+2}{2}x^\frac{\mu}{2} y^\frac{\nu}{2}
-         & \qquad \mu, \nu \, \mathrm{even}
-        \\[1em]
-        %
-        z(x, y)
-         & \qquad \mu = \nu = 1
-        \\[1em]
-        %
-        3x^{l-2}yz(x, y)
-         & \qquad \nu \, \mathrm{odd}, \,
-        \mu = 1, \,
-        \frac{\mu + \nu}{2} \, \mathrm{even}
-        \\[1em]
-        %
-        z(x, y)
-        \bigg(
-        -x^{l-3} + x^{l-1} + 4x^{l-3}y^2
-        \bigg)
-         & \qquad \nu \, \mathrm{odd}, \,
-        \mu = 1, \,
-        \, \mathrm{odd}
-        \\[1em]
-        %
-        z(x, y)
-        \bigg(
-        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu-1}{2}
-        \ - \
-        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu+3}{2}
-        \\
-        \qquad\qquad \ - \
-        \frac{\mu+3}{2} x^\frac{\mu-1}{2} y^\frac{\nu-1}{2}
-        \bigg)
-         & \qquad \mathrm{otherwise}
-        \quad,
-    \end{dcases}
-    \label{eq:bg}
-\end{proof}
-%
-where $x$ and $y$ are the Cartesian coordinates on the surface
-of the projected
-disk of the body, with $z(x, y) = \sqrt{1 - x^2 - y^2}$, and
-%
-\begin{align}
-    \label{eq:munu}
-    \mu & = l - m
-    \nonumber     \\
-    \nu & = l + m
-    \quad.
-\end{align}
-%
-The vector $\tilde{\bvec{g}}$ is ordered such that
-the component at index $n$ is $\tilde{g}_{l,m}$, with
-\begin{align}
-    \label{eq:lm}
-    l & = \floor*{\sqrt{n}} \nonumber \\
-    m & = n - l^2 - l
-    \quad.
-\end{align}
-Finally, the rotation matrix $\bvec{R} = \bvec{R}(i, \lambda, \theta)$
-rotates the body to the correct orientation on the sky given its
-inclination $i$, obliquity $\lambda$, and rotational phase $\theta$,
-while $\bvec{R}'$ rotates the body on the plane
-of the sky into the frame $\mathcal{F}'$ in which the integration is
-actually performed, with the occultor along the $+y$-axis.
-For more information on all of these terms, the reader is referred to
-\citet{Luger2019}.
+another spherical body). For more details, see Appendix~\ref{app:starry}.
 
@@
 In \citet{Luger2019}, the crux of the problem was to compute the terms in the
-vector $\bvec{s}^\top$, which are surface integrals over
+vector $\sT$, which are surface integrals over
 the region of the occulted body that is visible to
@@
 limbs of the two bodies, but also intersections with the elliptical
-day/night terminator of the occulted body. Figure~\ref{fig:cases} shows the
+day/night terminator of the occulted body.
+
+\begin{figure}[t!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/cases.pdf}
+        \oscaption{cases}{%
+            The eight families of cases of occultations in reflected light.
+            In these figures, the body with the solid outline
+            is the one whose flux we are interested in, and the body with the
+            dashed outline is the occultor.
+            The night side of the occulted body is colored
+            black (dark grey if occulted), and the dayside is colored blue
+            (light grey if occulted).
+            The cases in the top row involve
+            configurations in which the limb of the occultor does not intersect
+            with the terminator at any point, so the visible flux may be
+            computed in terms of classical \starry integrals. The remaining
+            cases require integration along the red boundary (the curves
+            $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$ of
+            \S\ref{sec:cases-5-8}), which
+            include the terminator. These involve the evaluation of incomplete
+            elliptic integrals and are derived below.
+            \label{fig:cases}
+        }
+    \end{centering}
+\end{figure}
+
+%
+
+\subsection{Problem Setup}
+\label{sec:setup}
+%
+
+Figure~\ref{fig:cases} shows the
 eight families of cases involving an occultation of an illuminated body by
@@
 occultor position. In the next three sections, we present the solution for the
-$\bvec{s}^\top$, and hence for the total visible flux, for each of these cases.
-
-% case 0: sTr
-% case 1: 0
-% case 2: sTr
-% case 3: sTe * I + ~sTr
-% case 4: sTe * I
-% case 5: sTr - sT0 * I
-% case 6: (sTe + sT0) * I + ~sTr
-% case 7: (sTe - sT0) * I
-% case 8: sT0 * I
-
-\begin{figure}[t!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/cases.pdf}
-        \oscaption{cases}{%
-            The eight families of cases of occultations in reflected light.
-            In these figures, the night side of the occulted body is colored
-            black (dark grey if occulted), and the dayside is colored blue
-            (light grey if occulted). The cases in the top row involve
-            configurations in which the limb of the occultor does not intersect
-            with the terminator at any point, so the visible flux may be
-            computed in terms of classical \starry integrals. The remaining
-            cases require integration along the red boundary (the curves
-            $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$ of
-            \S\ref{sec:integration}), which
-            include the terminator. These involve the evaluation of incomplete
-            elliptic integrals and are derived below.
-            \label{fig:cases}
-        }
-    \end{centering}
-\end{figure}
-
-\section{The Solution: Case 0}
-\label{sec:cases-0}
+$\sT$, and hence for the total visible flux, for each of these cases.
+
+\section{The Solution}
+\label{sec:solution}
+%
+\subsection{Case 0}
+\label{sec:case-0}
 %
@@
 \starry formalism in \citet{Luger2019b}, but for completeness we present
-the detailed solution below.
-
+the detailed solution in Appendix~\ref{app:case0}. We will refer to the
+solution vector for this case as $\sT_0$ (Equation~\ref{eq:sT0}).
+
+\subsection{Cases 1--4}
+\label{sec:cases-1-4}
+%
+Cases 1--4 (see Figure~\ref{fig:cases}) involve configurations in which the
+occultor does not intersect with
+the terminator of the occulted body, and are therefore fairly
+straightforward to solve.
+%
+Case 1 corresponds to any complete occultation of the body, so its
+solution vector is trivial:
+%
+\begin{align}
+    \label{eq:sT1}
+    \sT_1 = \BS{0}
+    \quad.
+\end{align}
+%
+Case 2 involves any occultation in which the occultor blocks \emph{only} the
+night side of the body (regardless of whether or not it intersects with the
+limb of the body). Since the night side intensity is zero everywhere, this case
+is also trivial, as the integration is the same as in case 0:
+%
+\begin{align}
+    \label{eq:sT2}
+    \sT_2 = \sT_0(b, \theta)
+    \quad.
+\end{align}
+%
+Case 3 corresponds to occultations in which the occultor blocks \emph{all} of
+the night side of the body and \emph{some} of the day side. In this
+configuration, the unocculted part of the disk consists only of dayside.
+Since we have no intersections with the terminator to worry about,
+we may compute the total flux using the \starry formalism from
+\citet{Luger2019}, provided we weight the intensity map by the illumination
+field:
+%
+\begin{align}
+    \label{eq:sT3}
+    \sT_3 = \sT_\star(b_o, r_o) \BS{\Psi}(b, \theta, d_s)
+    \quad,
+\end{align}
+%
+where $\sT_\star$ is the usual \starry solution vector
+\citep[Equation~26 in][]{Luger2019} and $\BS{\Psi}$ is an illumination
+matrix (Appendix~\ref{app:case3}).
+%
+Finally, case 4 involves any occultation in which the occultor blocks
+\emph{only} the day side of the body (regardless of whether or not it
+intersects with the limb).
+%
+\begin{align}
+    \label{eq:sT4}
+    \sT_4 = \sT_\star(b_o, r_o) + \sT_0(-b, \theta + \pi)
+    \quad.
+\end{align}
+%
+
+% case 1: 0
+% case 2: s0
+% case 3: sTe * I
+% case 4: sTe * I + ~sT0
+
+\subsection{Cases 5--8}
+\label{sec:cases-5-8}
+%
+Cases 5--8 (see Figure~\ref{fig:cases}, Figure~\ref{fig:geometry}).
+
+% case 5: sT0 - sT0 * I
+% case 6: (sTe + sT0) * I + ~sT0
+% case 7: (sTe - sT0) * I
+% case 8: sT0 * I
+
+\begin{figure}[t!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/geometry.pdf}
+        \oscaption{geometry}{%
+            Geometry of an occultation in reflected light, corresponding
+            to case 5 in Figure~\ref{fig:cases}. The surface integral over
+            the blue region is computed from the antiderivatives of the
+            surface intensity map counter-clockwise along the boundary curves
+            $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$.
+            \label{fig:geometry}
+        }
+    \end{centering}
+\end{figure}
+
+\section{Performance}
+\label{sec:performance}
+%
+See Figure~\ref{fig:speed}.
+%
+\begin{figure}[h!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/speed.pdf}
+        \oscaption{speed}{%
+            Evaluation time for the starry algorithm.
+            \label{fig:speed}
+        }
+    \end{centering}
+\end{figure}
+
+\appendix
+
+\section{The \starry formalism}
+\label{app:starry}
+%
+The basis $\bg$ is called the \emph{Green's basis}; its name
+stems from the fact that its components have a structure that makes integration
+by Green's theorem convenient. Its components were defined in
+Equation~11 of \citet{Luger2019b}:
+%
+\begin{proof}{bg}
+    \tilde{g}_{l,m} &=
+    \begin{dcases}
+        %
+        \frac{\mu+2}{2}x^\frac{\mu}{2} y^\frac{\nu}{2}
+         & \qquad \mu, \nu \, \mathrm{even}
+        \\[1em]
+        %
+        z(x, y)
+         & \qquad \mu = \nu = 1
+        \\[1em]
+        %
+        3x^{l-2}yz(x, y)
+         & \qquad \nu \, \mathrm{odd}, \,
+        \mu = 1, \,
+        \frac{\mu + \nu}{2} \, \mathrm{even}
+        \\[1em]
+        %
+        z(x, y)
+        \bigg(
+        -x^{l-3} + x^{l-1} + 4x^{l-3}y^2
+        \bigg)
+         & \qquad \nu \, \mathrm{odd}, \,
+        \mu = 1, \,
+        \, \mathrm{odd}
+        \\[1em]
+        %
+        z(x, y)
+        \bigg(
+        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu-1}{2}
+        \ - \
+        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu+3}{2}
+        \\
+        \qquad\qquad \ - \
+        \frac{\mu+3}{2} x^\frac{\mu-1}{2} y^\frac{\nu-1}{2}
+        \bigg)
+         & \qquad \mathrm{otherwise}
+        \quad,
+    \end{dcases}
+    \label{eq:bg}
+\end{proof}
+%
+where $x$ and $y$ are the Cartesian coordinates on the surface
+of the projected
+disk of the body, with $z(x, y) = \sqrt{1 - x^2 - y^2}$, and
+%
+\begin{align}
+    \label{eq:munu}
+    \mu & = l - m
+    \nonumber     \\
+    \nu & = l + m
+    \quad.
+\end{align}
+%
+The vector $\bg$ is ordered such that
+the component at index $n$ is $\tilde{g}_{l,m}$, with
+%
+\begin{align}
+    \label{eq:lm}
+    l & = \floor*{\sqrt{n}} \nonumber \\
+    m & = n - l^2 - l
+    \quad.
+\end{align}
+%
+Finally, the rotation matrix $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
+rotates the body to the correct orientation on the sky given its
+inclination $i$, obliquity $\lambda$, and rotational phase $\vartheta$,
+while $\BF{R}'$ rotates the body on the plane
+of the sky into the frame $\mathcal{F}'$ in which the integration is
+actually performed, with the occultor along the $+y$-axis.
+For more information on all of these terms, the reader is referred to
+\citet{Luger2019}.
+
+\section{Case 0}
+\label{app:case0}
+%
 Our task is to compute the solution vector for this
-configuration, which we will denote $\bvec{s}^\top_0$.
+configuration, which we will denote $\BF{s}^\top_0$.
 Since in this case there is no occultor, it is
@@
 (see Figure~\ref{fig:illum}); let us denote the matrix that rotates us
-from $\mathcal{F}'$ to $\mathcal{F}''$ as $\bvec{R}''$.
+from $\mathcal{F}'$ to $\mathcal{F}''$ as $\BF{R}''$.
 It is also far easier to perform the integration
-in the \emph{polynomial basis} $\tilde{\bvec{p}}$
+in the \emph{polynomial basis} $\bp$
 \citep[Equation 7 in][]{Luger2019}:
@@
 %
-where $\tilde{\bvec{p}}$ is again ordered such that the component at
+where $\bp$ is again ordered such that the component at
 index $n$ is $\tilde{p}_{l,m}$, with $l$ and $m$ given by
 Equation~(\ref{eq:lm}).
-Now, if $\bvec{r}^\top$ is the solution to the surface integrals in the
+Now, if $\BF{r}^\top$ is the solution to the surface integrals in the
 polynomial basis in $\mathcal{F}''$,
@@
 \begin{align}
-    \label{eq:sTref}
-    \bvec{s}^\top_0 & = \bvec{r}^\top \bvec{A_1} \bvec{R}'' \bvec{A}^{-1}
+    \label{eq:sT0}
+    \BF{s}^\top_0 & = \BF{r}^\top \BF{A_1} \BF{R}'' \BF{A}^{-1}
     \quad,
@@
 %
-where $\bvec{A_1}$ \citep[Equation B11 in][]{Luger2019}
+where $\BF{A_1}$ \citep[Equation B11 in][]{Luger2019}
 transforms the solution into the spherical harmonic basis so it can
-be rotated out of the integration frame $\mathcal{F}''$ via $\bvec{R}''$, and
-$\bvec{A}^{-1}$ \citep[Equation B13 in][]{Luger2019} transforms the
-result into the Green's basis (in which $\bvec{s}^\top$ is defined).
-
-Our task is thus to compute $\bvec{r}^\top$.
+be rotated out of the integration frame $\mathcal{F}''$ via $\BF{R}''$, and
+$\BF{A}^{-1}$ \citep[Equation B13 in][]{Luger2019} transforms the
+result into the Green's basis (in which $\sT$ is defined).
+
+Our task is thus to compute $\BF{r}^\top$.
 In frame $\mathcal{F}''$, the body sits at the origin and is
@@
 %
-\begin{proof}{illum}
+\begin{proof}{}
     \Psi(b; x, y) & =
@@
 %
-\begin{proof}{rT}
+\begin{proof}{}
     \label{eq:rTsoln}
@@
 %
-\begin{proof}{rT}
+\begin{proof}{}
     \label{eq:IJK}
@@
 \begin{minipage}{.33\linewidth}
-    \begin{proof}{rT}
-        I_{0}(b) &= \frac{\arccos(b) - bb_c}{2}
-        %
-        \nonumber \\
-        %
-        I_{1}(b) &= \frac{b_c^3}{3}
+    \begin{align}
+        I_{0}(b) & = \frac{\arccos(b) - bb_c}{2}
+        %
+        \nonumber                                \\
+        %
+        I_{1}(b) & = \frac{b_c^3}{3}
         %
         \nonumber
-    \end{proof}
+    \end{align}
 \end{minipage}%
 \begin{minipage}{.32\linewidth}
-    \begin{proof}{rT}
-        J_{0,0} &= \pi
-        %
-        \nonumber \\
-        %
-        J_{0,1} &= \frac{4}{3}
+    \begin{align}
+        J_{0,0} & = \pi
+        %
+        \nonumber               \\
+        %
+        J_{0,1} & = \frac{4}{3}
         %
         \nonumber
-    \end{proof}
+    \end{align}
 \end{minipage}%
 \begin{minipage}{.33\linewidth}
-    \begin{proof}{rT}
+    \begin{proof}{}
         \label{eq:IJK0}
@@
 %
-\begin{proof}{rT}
+\begin{proof}{}
     \label{eq:IJKrec}
@@
 \end{proof}
-%
-
-\section{The Solution: Cases 1--4}
-\label{sec:cases-1-4}
-Cases 1--4 (see Figure~\ref{fig:cases}) involve configurations in which the
-occultor does not intersect with
-the terminator of the occulted body, and are therefore significantly easier to
-solve.
-
-\section{The Solution: Cases 5--8}
-\label{sec:cases-5-8}
-Cases 5--8 (see Figure~\ref{fig:cases}).
-
-\begin{figure}[t!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/geometry.pdf}
-        \oscaption{geometry}{%
-            Geometry of an occultation in reflected light, corresponding
-            to case 5 in Figure~\ref{fig:cases}. The surface integral over
-            the blue region is computed from the antiderivatives of the
-            surface intensity map counter-clockwise along the boundary curves
-            $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$.
-            \label{fig:geometry}
-        }
-    \end{centering}
-\end{figure}
+
+\section{Case 3}
+\label{app:case3}
+Hello.
+
+\section{Case 4}
+\label{app:case4}
+Hello.
+
+\section{Cases 5--8}
+\label{app:cases-5-8}
+Hello.
 
@@
     \label{eq:G}
-    \bvec{G}_{\mu,\nu} (x, y) & =
+    \BF{G}_{\mu,\nu} (x, y) & =
     \begin{dcases}
@@
 \begin{align}
-    \dd \bvec{r} & = -r \sin\varphi \, \dd \varphi \, \xhat +
+    \dd \BF{r} & = -r \sin\varphi \, \dd \varphi \, \xhat +
     r \cos\varphi \, \dd \varphi \, \yhat
@@
 closed surface of integration, which we will denote $\mathcal{P}$,
-$\mathcal{Q}$, and $\mathcal{T}$. These are shown for a typical occultor-occulted
-configuration in Figure~\ref{fig:geometry}.
-
-\section{Performance}
-\label{sec:performance}
-
-%
-\begin{figure}[h!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/speed.pdf}
-        \oscaption{speed}{%
-            Evaluation time for the starry algorithm.
-            \label{fig:speed}
-        }
-    \end{centering}
-\end{figure}
-
-\section{Integration}
-\label{sec:integration}
+$\mathcal{Q}$, and $\mathcal{T}$. These are shown for a typical
+occultor-occulted configuration in Figure~\ref{fig:geometry}.
 
@@
     \label{eq:pairdiff}
-    \Delta \boldsymbol{v} \equiv \sum_{i=0}^{\frac{N - 1}{2}}
+    \Delta \BS{v} \equiv \sum_{i=0}^{\frac{N - 1}{2}}
     \left( v_{2i + 1} - v_{2i} \right)
@@
 which sums the difference of successive pairs of values in
-an array $\boldsymbol{v} = \{ v_0, v_1, v_2, v_3, {\cdot\cdot\cdot}, v_N\}$.
+an array $\BS{v} = \{ v_0, v_1, v_2, v_3, {\cdot\cdot\cdot}, v_N\}$.
 
@@
     \label{eq:q}
-    \boldsymbol{q}(k^2, \bkappa) = \sqrt{1 - \frac{\sinhalfkap[2]}{k^2}}
+    \BS{q}(k^2, \bkappa) = \sqrt{1 - \frac{\sinhalfkap[2]}{k^2}}
     \quad.
@@
 
-\begin{proof}{T2}
-    \mathcal{T}_{2}(b, \bxi) &= -\sgn(b) \Delta \boldsymbol{f}(b, \bxi)
+\begin{proof}{}
+    \mathcal{T}_{2}(b, \bxi) &= -\sgn(b) \Delta \BS{f}(b, \bxi)
 \end{proof}
@@
 %
-\begin{proof}{T2}
+\begin{proof}{}
     \begin{split}
@@
 %
-\begin{proof}{T2}
+\begin{proof}{}
     \phi(b, \xi_i) & =
@@
 where the last expression is valid for all $v > 0$. We find that this algorithm
-is generally stable, except when $\sin\left(\frac{\bkappa}{2}\right)$ is small. In
-that limit, we evaluate $\mathcal{I}_N(\bkappa)$ by numerical integration of
+is generally stable, except when $\sin\left(\frac{\bkappa}{2}\right)$ is small.
+In that limit, we evaluate $\mathcal{I}_N(\bkappa)$ by numerical integration of
 Equation~(\ref{eq:I}) using Gauss-Legendre quadrature with \STARRYQUADPOINTS
@@
     \left(\frac{1}{k^2} - 1\right) \DF +
-    \Delta \boldsymbol{z}_0(k^2, \bkappa)
+    \Delta \BS{z}_0(k^2, \bkappa)
     \bigg)
@@
     \left(3 k^2 - 7 + \frac{4}{k^2}\right) \DF +
-    \Delta \boldsymbol{z}_1(k^2, \bkappa)
+    \Delta \BS{z}_1(k^2, \bkappa)
     \bigg)
@@
     (2v - 3) k^2 \mathcal{J}_{v - 2}
-    + \Delta \boldsymbol{z}_v(k^2, \bkappa)
+    + \Delta \BS{z}_v(k^2, \bkappa)
     \bigg)
@@
     \label{eq:Jrec_z}
-    \boldsymbol{z}_0(k^2, \boldsymbol{\kappa}) & =
+    \BS{z}_0(k^2, \BS{\kappa}) & =
     \frac{
@@
         \coshalfkap
-        \boldsymbol{q}(k^2, \bkappa)
+        \BS{q}(k^2, \bkappa)
     }{
@@
     %
-    \boldsymbol{z}_1(k^2, \boldsymbol{\kappa}) & =
+    \BS{z}_1(k^2, \BS{\kappa}) & =
     \left(\left(3 \sinhalfkap[2] + 4\right) - 6k^2\right)
-    \boldsymbol{z}_0(k^2, \boldsymbol{\kappa})
+    \BS{z}_0(k^2, \BS{\kappa})
     %
@@
     %
-    \boldsymbol{z}_v(k^2, \boldsymbol{\kappa}) & =
+    \BS{z}_v(k^2, \BS{\kappa}) & =
     k^2
@@
     \coshalfkap
-    \boldsymbol{q}(k^2, \boldsymbol{\kappa})^5
+    \BS{q}(k^2, \BS{\kappa})^5
     \quad.
@@
     \frac{
-            \boldsymbol{z}_v(k^2, \boldsymbol{\kappa})
+            \BS{z}_v(k^2, \BS{\kappa})
         }{
@@
 %
-\begin{align}
+\begin{proof}{}
     \label{eq:Wsol}
@@
     \right)
-\end{align}
+\end{proof}
 %

### 2020-04-01 tex/figures/cases.py

@@ -9,8 +9,8 @@ ax = ax.flatten()
 # Cases
 visualize_simple(ax[0], 0.5, 75 * np.pi / 180, 0, 1.1)
 visualize_simple(ax[1], 0.5, 75 * np.pi / 180, 0, 0.25)
-visualize_simple(ax[2], 0.25, 10 * np.pi / 180, 0.8, 0.3)
-visualize_simple(ax[3], -0.25, np.pi, 0.15, 1.05)
+visualize_simple(ax[2], -0.25, np.pi, 0.15, 1.05)
+visualize_simple(ax[3], 0.25, 10 * np.pi / 180, 0.8, 0.3)
 visualize_simple(ax[4], 0.5, 75 * np.pi / 180, 0.5, 0.7)
 visualize_simple(ax[5], 0.5, -10 * np.pi / 180, 0.5, 0.7)
 visualize_simple(ax[6], 0.5, np.pi, 4.65, 5.0)

### 2020-04-01 tex/figures/code/viz.py

@@ -50,7 +50,7 @@ def visualize_simple(ax, b, theta, bo, ro, res=4999):
 
     # Draw basic shapes
     ax.axis("off")
-    ax.add_artist(plt.Circle((0, bo), ro, fill=False))
+    ax.add_artist(plt.Circle((0, bo), ro, fill=False, ls="--", lw=1.5))
     ax.add_artist(plt.Circle((0, 0), 1, fill=False))
     ax.plot(x_t, y_t, "k-", lw=1)
     ax.set_xlim(-1.25, 1.25)

### 2020-04-01 tex/figures/frames.py

@@ -1,0 +1,495 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import starry
+from starry._plotting import get_ortho_latitude_lines, get_ortho_longitude_lines
+from matplotlib.colors import LinearSegmentedColormap
+from matplotlib.patches import FancyArrowPatch
+
+
+# Config
+starry.config.lazy = False
+starry.config.quiet = True
+
+
+def plot_grid(ax, inc, obl, theta):
+    inc *= np.pi / 180
+    obl *= np.pi / 180
+    theta *= np.pi / 180
+    x = np.linspace(-1, 1, 10000)
+    y = np.sqrt(1 - x ** 2)
+    borders = [None, None]
+    (borders[0],) = ax.plot(x, y, "k-", alpha=1, lw=1)
+    (borders[1],) = ax.plot(x, -y, "k-", alpha=1, lw=1)
+    lats = get_ortho_latitude_lines(inc=inc, obl=obl)
+    latlines = [None for n in lats]
+    for n, l in enumerate(lats):
+        (latlines[n],) = ax.plot(l[0], l[1], "k-", lw=0.5, alpha=0.5, zorder=99)
+    lons = get_ortho_longitude_lines(inc=inc, obl=obl, theta=theta)
+    lonlines = [None for n in lons]
+    for n, l in enumerate(lons):
+        (lonlines[n],) = ax.plot(l[0], l[1], "k-", lw=0.5, alpha=0.5, zorder=99)
+
+
+# Params
+ydeg = 30
+res = 300
+inc = 60
+obl = 23.5
+theta = 60
+xs = -1
+ys = 1
+zs = 0.5
+xo = 0.4
+yo = 0.5
+ro = 0.5
+
+# Rotated params
+obl_int = obl + np.arctan(ys / xs) * 180 / np.pi
+xs_int = 0
+ys_int = np.sqrt(ys ** 2 + xs ** 2)
+obl_greens = obl + np.arctan(xo / yo) * 180 / np.pi
+t = np.arctan(xo / yo)
+xs_greens = xs * np.cos(t) - ys * np.sin(t)
+ys_greens = xs * np.sin(t) + ys * np.cos(t)
+bo = np.sqrt(xo ** 2 + yo ** 2)
+t = np.arctan(ys / xs)
+xo_int = xo * np.cos(t) - yo * np.sin(t)
+yo_int = xo * np.sin(t) + yo * np.cos(t)
+
+# Load the Earth map
+mape = starry.Map(ydeg)
[…]

### 2020-04-02 tex/ms.tex
better problem setup

@@
 \newcommand{\sT}{\ensuremath{\BF{s}^\top}}
+\newcommand{\rT}{\ensuremath{\BF{r}^\top}}
 \newcommand{\bg}{\ensuremath{\tilde{\BF{g}}}}
 \newcommand{\bp}{\ensuremath{\tilde{\BF{p}}}}
+\newcommand{\by}{\ensuremath{\tilde{\BF{y}}}}
 
@@
 % Title
-\title{Occultation Light Curves in Reflected Light}
+\title{Analytic Occultation Light Curves in Reflected Light}
 
@@
 %
-\subsection{Overview}
-\label{sec:overview}
+\subsection{Review of the \starry algorithm in emitted light}
+\label{sec:starry-review}
 %
@@
 toward the observer; denote this frame by $\mathcal{F}_0$. In $\mathcal{F}_0$,
-the surface intensity field of the body is described by the spherical harmonic
-coefficient vector $\mathbf{y}$. Following \citet{Luger2019}, we may compute
-the total visible flux $f$ from this body as
+the surface (emitted) intensity field of the body is described by the
+spherical harmonic coefficient vector $\mathbf{y}$. Following
+\citet{Luger2019}, when no occultor is present, we may compute the total
+visible flux $f$ from this body as
+%
+\begin{align}
+    \label{eq:rTA1Ry}
+    f = \rT \BF{A_1} \BF{R} \BF{y}
+    \quad,
+\end{align}
+%
+where, from right to left, $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
+is a Wigner rotation matrix that rotates $\bvec{y}$ to the sky frame
+$\mathcal{F}_\mathrm{sky}$ given the body's inclination $i$, obliquity
+$\lambda$, and rotational phase $\vartheta$,
+%
+$\BF{A_1}$ is the change-of-basis matrix from the spherical harmonic
+basis $\by$ to the \emph{polynomial basis} $\bp$ in which the integrals
+are computed,
+%
+and $\rT$ is the vector of solutions to the integral over
+the projected visible disk of the body for each term in $\bp$.
+%
+If an occultor is present, we instead compute the visible flux from
 %
@@
 %
-where, from right to left, $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
-is a Wigner rotation matrix that
-rotates $\bvec{y}$ to the sky frame $\mathcal{F}_\mathrm{sky}$
-given the body's inclination $i$, obliquity $\lambda$, and
-rotational phase $\vartheta$,
+where, as before, $\BF{R}$ rotates the body from $\mathcal{F}_0$
+to $\mathcal{F}_\mathrm{sky}$,
 %
 $\BF{R}'$ rotates the body on the plane
-of the sky into the frame $\mathcal{F}_\mathrm{int}$ in which the
+of the sky into the frame $\mathcal{F}_\mathrm{greens}$ in which the
 integration is actually performed,
 %
-$\BF{A}$ is the change-of-basis matrix from spherical harmonics
-to the basis in which the integrals are computed
-%,
-and $\sT$ is the \emph{solution vector}, the integral of each
-of the basis functions over
-the projected visible disk of the body (which may be partially occulted by
-another spherical body). For more details, see Appendix~\ref{app:starry}.
+$\BF{A}$ is the change-of-basis matrix from $\by$
+to the \emph{Green's basis} $\bg$ in which the integrals are computed,
+%
+and $\sT$ is the vector of solutions to the integral over
+the projected visible disk of the body for each term in $\bg$.
+For more details, see Appendix~\ref{app:starry} and \citet{Luger2019}.
+
+\subsection{Adapting the algorithm to the reflected light case}
+\label{sec:starry-review}
+%
+In order to compute light curves in reflected light, we must make two
+modifications to the \starry algorithm. First,
+the expressions above assume that the coefficient vector
+$\mathbf{y}$ describes the \emph{emissivity} of the body, which (in the
+absence of limb darkening) is assumed to be Lambertian, i.e., all points on the
+surface emit equally in all directions.
+Here, we wish to derive the solution for the flux in the case of Lambertian
+reflectance, in which case the vector $\mathbf{y}$ is taken to describe the
+surface \emph{reflectivity} (or \emph{Bond albedo}).
+
+Second, we must explicitly model the illumination of the body. We assume the
+body is illuminated by a point-like source, in which case the radiance at any
+point on the surface is proportional to the cosine of the angle $\phi$ between
+the incident light and the surface normal. Points for which
+$\phi \ge \frac{\pi}{2}$ are unilluminated and therefore have radiance of zero.
+%
+If the point-like illumination source is placed at sky coordinates
+$(x_s, y_s, z_s)$, the day/night terminator on the body is a half-ellipse
+of semi-major axis unity that is fully described by its semi-minor axis,
+%
+\begin{proof}{}
+    \label{eq:b}
+    b = -\frac{z_s}{\sqrt{x_s^2 + y_s^2 + z_s^2}}
+    \quad,
+\end{proof}
+%
+and the angle by which its semi-major axis is rotated away from the
+$+x$-axis,
+%
+\begin{proof}{}
+    \label{eq:theta}
+    \theta = \mathrm{arctan2}(y_s, x_s)
+    \quad.
+\end{proof}
+%
+Given this formulation, and assuming that
+$x_s^2 + y_s^2 + z_s^2 \gg 1$,
+it is straightforward to show that the illumination
+$I$ at a point $(x, y)$ on the projected disk of the body is given by
+the polynomial
+%
+\begin{proof}{}
+    \frac{I(b, \theta; x, y)}{I_0} &=
+    -b_c\sin\theta x + b_c\cos\theta y - bz(x, y)
+\end{proof}
+%
+where $b_c = \sqrt{1 - b^2}$, $z(x, y) = \sqrt{1 - x^2 - y^2}$, and
+%
+\begin{proof}{}
+    I_0 = \frac{L}{4\pi\left(x_s^2 + y_s^2 + z_s^2\right)}
+\end{proof}
+%
+is the peak illumination (at the substellar point,
+assuming the illumination source is a star), with $L$ equal to the luminosity
+of the source.
+%
+Since the illumination is just a polynomial in $x$, $y$, and $z(x, y)$, we
+can express it as a vector $\BF{i}(b, \theta)$ in the polynomial basis $\bp$.
+Recalling the structure of the basis (c.f. Appendix~\ref{app:starry}),
+%
+\begin{align}
+    \bp & =
+    \begin{pmatrix}
+        1   &
+        x   & z  & y  &
+        x^2 & xz & xy & yz & y^2 &
+        \cdot\cdot\cdot
+    \end{pmatrix}^\mathsf{T}
+    \quad,
+\end{align}
+%
+we may write
+%
+\begin{proof}{}
+    \BF{i}(b, \theta) & =
+    I_0
+    \begin{pmatrix}
+        0              \\
+        -b_c\sin\theta \\
+        -b             \\
+        b_c\cos\theta
+    \end{pmatrix}
+    \quad.
+\end{proof}
+%
+This fact allows us to construct a linear operator $\BF{I}$ to weight a map
+vector in the polynomial basis by the illumination profile.
+If we think about how each of the terms in $\bp$ transforms under $\BF{I}$,
+%
+\\[1em]
+%
+\begin{minipage}{0.22\linewidth}
+    \begin{align}
+        \begin{pmatrix}
+            1 \\
+            0 \\
+            0 \\
+            0
+        \end{pmatrix}
+         & \BS{\rightarrow}
+        \begin{pmatrix}
+            \bvec{i}_0 \\ %1
+            \bvec{i}_1 \\ %x
+            \bvec{i}_2 \\ %z
+            \bvec{i}_3 \\ %y
+            0          \\ %x^2
+            0          \\ %xz
+            0          \\ %xy
+            0          \\ %yz
+            0             %y^2
+        \end{pmatrix}
+        \nonumber
+    \end{align}
+\end{minipage}
+%
+\begin{minipage}{0.22\linewidth}
+    \begin{align}
+        \begin{pmatrix}
+            0 \\
+            1 \\
+            0 \\
+            0
+        \end{pmatrix}
+         & \BS{\rightarrow}
+        \begin{pmatrix}
+            0          \\ %1
+            \bvec{i}_0 \\ %x
+            0          \\ %z
+            0          \\ %y
+            \bvec{i}_1 \\ %x^2
+            \bvec{i}_2 \\ %xz
+            \bvec{i}_3 \\ %xy
+            0          \\ %yz
+            0    %y^2
+        \end{pmatrix}
+        \nonumber
+    \end{align}
+\end{minipage}
+%
+\begin{minipage}{0.22\linewidth}
+    \begin{align}
+        \begin{pmatrix}
+            0 \\
+            0 \\
+            1 \\
+            0
+        \end{pmatrix}
+         & \BS{\rightarrow}
+        \begin{pmatrix}
+            \bvec{i}_2  \\ %1
+            0           \\ %x
+            \bvec{i}_0  \\ %z
+            0           \\ %y
+            -\bvec{i}_2 \\ %x^2
+            \bvec{i}_1  \\ %xz
+            0           \\ %xy
+            \bvec{i}_3  \\ %yz
+            -\bvec{i}_2    %y^2
+        \end{pmatrix}
+        \nonumber
+    \end{align}
+\end{minipage}
+%
+\begin{minipage}{0.22\linewidth}
+    \begin{align}
+        \begin{pmatrix}
+            0 \\
+            0 \\
+            0 \\
+            1
+        \end{pmatrix}
+         & \BS{\rightarrow}
+        \begin{pmatrix}
+            0          \\ %1
+            0          \\ %x
+            0          \\ %z
+            \bvec{i}_0 \\ %y
+            0          \\ %x^2
+            0          \\ %xz
+            \bvec{i}_1 \\ %xy
+            \bvec{i}_2 \\ %yz
+            \bvec{i}_3    %y^2
+        \end{pmatrix}
+        \nonumber
+    \end{align}
+\end{minipage}
+\begin{minipage}{0.05\linewidth}
+    \begin{align}
+    \end{align}
+\end{minipage}
+%
+\\[1em]
+%
+we can compose $\BF{I}$ out of these column vectors:
+%
+\begin{proof}{}
+    \BF{I}(b, \theta) & =
+    I_0
+    \begin{pmatrix}
+        0              & 0              & -b             & 0              & \cdots \\
+        -b_c\sin\theta & 0              & 0              & 0              & \cdots \\
+        -b             & 0              & 0              & 0              & \cdots \\
+        b_c\cos\theta  & 0              & 0              & 0              & \cdots \\
+        0              & -b_c\sin\theta & b              & 0              & \cdots \\
+        0              & -b             & -b_c\sin\theta & 0              & \cdots \\
+        0              & b_c\cos\theta  & 0              & -b_c\sin\theta & \cdots \\
+        0              & 0              & b_c\cos\theta  & -b             & \cdots \\
+        0              & 0              & b              & b_c\cos\theta  & \cdots \\
+        \vdots         & \vdots         & \vdots         & \vdots         & \ddots
+    \end{pmatrix}
+\end{proof}
+%
+where the dimensions of the matrix are $\big((l + 2)^2, (l + 1)^2\big)$, where
+$l$ is the spherical harmonic degree of the map (this operator raises the
+degree of the map by one).
 
@@
     \begin{centering}
-        \includegraphics[width=0.35\linewidth]{figures/illum.pdf}
-        \oscaption{illum}{%
-            Illumination geometry for the unocculted case.
-            A point source at Cartesian coordinates
-            $(0, y_s, z_s)$ illuminates a uniform,
-            Lambertian, spherical body of radius unity. The observed
-            radiance falls off as the cosine of the angle $\phi$ between the
-            source and the surface normal. Beyond the terminator
-            (defined by $\phi = \frac{\pi}{2}$), the radiance is zero. In
-            projection, the terminator is a segment of an ellipse of semi-major
-            axis unity and semi-minor axis
-            $b = -\nicefrac{z_s}{\sqrt{y_s^2 + z_s^2}}$.
-            \label{fig:illum}
+        \includegraphics[width=\linewidth]{figures/frames.pdf}
+        \oscaption{frames}{%
+            How \starry computes the flux from a body in reflected light,
+            tracking each of the linear transformations from the input map
+            (far right) to the output (far left). The label below each map
+            denotes the reference frame, while the label above
+            each map denotes the basis in which the map is represented.
+            Arrows indicate linear operations and are labeled accordingly.
+            The upper branch corresponds to the unocculted case, while the
+            lower branch corresponds to the case where an occultor is present.
+            See text for details.
+            \label{fig:frames}
         }
@@
 
-The derivations in \citet{Luger2019} assume that the coefficient vector
-$\mathbf{y}$ describes the \emph{emissivity} of the body, which (in the
-absence of limb darkening) is assumed to be Lambertian, i.e., all points on the
-surface emit equally in all directions.
-Here, we derive the solution to the occultation problem for Lambertian
-reflectance, in which case the vector $\mathbf{y}$ describes the
-surface \emph{reflectivity} (or \emph{Bond albedo}). Specifically, we assume
-the body is illuminated by a point-like source and the radiance at any point
-is proportional to the cosine of the angle $\phi$ between the incident light
-and the surface normal. Points for which $\phi \ge \frac{\pi}{2}$ are
-unilluminated and therefore have radiance of zero; see Figure~\ref{fig:illum}.
+We may now re-write Equations~(\ref{eq:rTA1Ry}) and (\ref{eq:sTARRy}) to
+account for this illumination transformation. The flux outside of occultation
+is now given by
+%
+\begin{align}
+    \label{eq:rTIA1RRy}
+    f = \rT \BF{I} \BF{A_1} \BF{R}'' \BF{R} \BF{y}
+    \quad,
+\end{align}
+%
+and the flux during an occultation by
+%
+\begin{align}
+    \label{eq:sTA2IA1RRy}
+    f = \sT \BF{A_2} \BF{I} \BF{A_1} \BF{R}' \BF{R} \BF{y}
+    \quad.
+\end{align}
+%
+Two notes about these equations. First, we introduced a new rotation matrix
+$\BF{R}''$ in Equation~(\ref{eq:rTIA1RRy}), which rotates the problem so that
+the semi-major axis of the terminator is aligned with the $x$-axis; as will
+become clear in \S\ref{sec:case-0} below, this greatly simplifies the
+integration step. Second, in the derivation of Equation~(\ref{eq:sTA2IA1RRy})
+we used the fact that $\BF{A} = \BF{A_2} \BF{A_1}$
+\citep[c.f. Equation~14 in][]{Luger2019}, where $\BF{A_1}$ transforms from
+the spherical harmonic basis $\by$ to the polynomial basis $\bp$, and
+$\BF{A_2}$ transforms from $\bp$ to the Green's basis $\bg$.
+
+Figure~\ref{fig:frames} summarizes the transformations involved in the two
+equations above. Starting on the right with a map vector $\BF{y}$ in
+the spherical harmonic basis $\by$, defined in some observer-independent frame
+$\mathcal{F}_0$, we first rotate it via $\BF{R}$ to the sky frame
+$\mathcal{F}_\mathrm{sky}$, in which orientation the body is viewed by the
+observer. If there is no occultation (upper branch of the figure), we then
+rotate the map once more via $\BF{R}''$ to the integration frame
+$\mathcal{F}_\mathrm{int}$, in which the terminator is parallel to the
+$x$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$, apply the
+illumination transform $\BF{I}$, and finally dot in the solutions to the
+surface integrals $\rT$. If, on the other hand, an occultor is present,
+we rotate the map from $\mathcal{F}_\mathrm{sky}$ via $\BF{R}'$ to the frame
+$\mathcal{F}_\mathrm{greens}$, in which the occultor lies along the
+$+y$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$ and $\BF{I}$
+to weight the map by the illumination as above. Finally, we change basis
+via $\BF{A_2}$ to the Green's basis, in which we compute and dot the
+integrals $\sT$.
 
 In \citet{Luger2019}, the crux of the problem was to compute the terms in the
-vector $\sT$, which are surface integrals over
-the region of the occulted body that is visible to
-the observer (Figure 2 in that paper). Here, these integrals are significantly
-more difficult, because they involve not only the intersection of the
-limbs of the two bodies, but also intersections with the elliptical
-day/night terminator of the occulted body.
+vectors $\sT$ and $\rT$, which are surface integrals over
+the region of the body that is visible to the observer
+(see Figure 2 in that paper). Here, these integrals are significantly
+more difficult, because they involve not only integration along the
+limb of the body and of a possible occultor, but also along the
+elliptical day/night terminator.
 

### 2020-04-02 tex/figures/frames.py

@@ -226,7 +226,7 @@ ax = plt.subplot2grid((3, 7), (0, 4))
 ax.imshow(imgint, **img_kw)
 plot_grid(ax, inc, obl_int, theta)
 add_basis(ax, r"$\tilde{y}$")
-add_frame(ax, r"$\mathcal{F}_\mathrm{int}$")
+add_frame(ax, r"$\mathcal{F}_\mathrm{poly}$")
 add_terminator(ax, b, 0)
 axes.append(ax)
 
@@ -234,7 +234,7 @@ ax = plt.subplot2grid((3, 7), (0, 3))
 ax.imshow(imgint, **img_kw)
 plot_grid(ax, inc, obl_int, theta)
 add_basis(ax, r"$\tilde{p}$")
-add_frame(ax, r"$\mathcal{F}_\mathrm{int}$")
+add_frame(ax, r"$\mathcal{F}_\mathrm{poly}$")
 add_terminator(ax, b, 0)
 axes.append(ax)
 
@@ -242,8 +242,8 @@ ax = plt.subplot2grid((3, 7), (0, 2))
 ax.imshow(imgint, **img_kw)
 ax.imshow(fint, **flt_kw)
 plot_grid(ax, inc, obl_int, theta)
-add_basis(ax, r"$\tilde{y}$")
-add_frame(ax, r"$\mathcal{F}_\mathrm{int}$")
+add_basis(ax, r"$\tilde{p}$")
+add_frame(ax, r"$\mathcal{F}_\mathrm{poly}$")
 add_terminator(ax, b, 0)
 axes.append(ax)
 

### 2020-04-02 tex/ms.tex
more texts

@@
 \newcommand{\zhat}{\ensuremath{\mathbf{\hat{z}}}\xspace}
-\newcommand{\sT}{\ensuremath{\BF{s}^\top}}
-\newcommand{\rT}{\ensuremath{\BF{r}^\top}}
+\newcommand{\sT}{\ensuremath{\mathfrak{s}^\top}}
+\newcommand{\rT}{\ensuremath{\mathfrak{r}^\top}}
+\newcommand{\sTe}{\ensuremath{\BF{s}^\top}}
+\newcommand{\rTe}{\ensuremath{\BF{r}^\top}}
+%
 \newcommand{\bg}{\ensuremath{\tilde{\BF{g}}}}
@@
 \citet{Luger2019}, when no occultor is present, we may compute the total
-visible flux $f$ from this body as
+visible flux $f_0$ from this body as
 %
@@
     \label{eq:rTA1Ry}
-    f = \rT \BF{A_1} \BF{R} \BF{y}
+    f_0 = \rTe \BF{A_1} \BF{R} \BF{y}
     \quad,
@@
 $\mathcal{F}_\mathrm{sky}$ given the body's inclination $i$, obliquity
-$\lambda$, and rotational phase $\vartheta$,
+$\lambda$, and rotational phase $\vartheta$ (Equation~\ref{eq:R}),
 %
@@
 basis $\by$ to the \emph{polynomial basis} $\bp$ in which the integrals
-are computed,
-%
-and $\rT$ is the vector of solutions to the integral over
-the projected visible disk of the body for each term in $\bp$.
-%
-If an occultor is present, we instead compute the visible flux from
+are computed (Equation~\ref{eq:A1}),
+%
+and $\rTe$ is the vector of solutions to the integral over
+the projected visible disk of the body for each term in $\bp$
+(Equation~\ref{eq:rTe}).
+%
+If instead an occultor of radius $r_o$ is located at position $(x_o, y_o)$,
+we instead compute the visible flux $f$ from
 %
@@
     \label{eq:sTARRy}
-    f = \sT \BF{A} \BF{R}' \BF{R} \BF{y}
+    f = \sTe \BF{A} \BF{R}' \BF{R} \BF{y}
     \quad,
@@
 %
-$\BF{R}'$ rotates the body on the plane
-of the sky into the frame $\mathcal{F}_\mathrm{greens}$ in which the
-integration is actually performed,
+$\BF{R}' = \BF{R}'(\omega)$ rotates the body on the plane
+of the sky by an angle
+$\omega = \nicefrac{\pi}{2} - \mathrm{arctan2}(y_o, x_o)$
+into a frame $\mathcal{F}_\mathrm{greens}$ in which the
+occultor lies along the $+y$-axis (Equation~\ref{eq:R'}),
 %
 $\BF{A}$ is the change-of-basis matrix from $\by$
-to the \emph{Green's basis} $\bg$ in which the integrals are computed,
-%
-and $\sT$ is the vector of solutions to the integral over
-the projected visible disk of the body for each term in $\bg$.
+to the \emph{Green's basis} $\bg$ in which the integrals are computed
+(Equation~\ref{eq:A}),
+%
+and $\sTe = \sTe(b_o, r_o)$ is the vector of solutions to the integral over
+the projected visible disk of the body for each term in $\bg$
+(Equation~\ref{eq:sTe}), with $b_o = \sqrt{x_o^2 + y_o^2}$.
 For more details, see Appendix~\ref{app:starry} and \citet{Luger2019}.
@@
 Second, we must explicitly model the illumination of the body. We assume the
-body is illuminated by a point-like source, in which case the radiance at any
+body is illuminated by a point-like source of unit luminosity, in which case
+the radiance at any
 point on the surface is proportional to the cosine of the angle $\phi$ between
@@
 $(x_s, y_s, z_s)$, the day/night terminator on the body is a half-ellipse
-of semi-major axis unity that is fully described by its semi-minor axis,
+of semi-major axis unity that is fully described by its (signed) semi-minor
+axis,
 %
@@
     \label{eq:b}
-    b = -\frac{z_s}{\sqrt{x_s^2 + y_s^2 + z_s^2}}
+    b = -\frac{z_s}{r_s}
     \quad,
 \end{proof}
+%
+where $r_s = \sqrt{x_s^2 + y_s^2 + z_s^2}$ is the distance to the source,
 %
@@
 Given this formulation, and assuming that
-$x_s^2 + y_s^2 + z_s^2 \gg 1$,
+$r_s \gg 1$,
 it is straightforward to show that the illumination
-$I$ at a point $(x, y)$ on the projected disk of the body is given by
-the polynomial
-%
-\begin{proof}{}
-    \frac{I(b, \theta; x, y)}{I_0} &=
+$\mathfrak{I}$ at a point $(x, y)$ on the projected disk of the body is given
+by the function
+%
+\begin{proof}{}
+    \label{eq:Psi}
+    \mathfrak{I}(b, \theta, r_s; x, y)&=
+    \mathrm{max}\bigg( 0, I(b, \theta, r_s; x, y) \bigg)
+\end{proof}
+%
+where
+%
+\begin{proof}{}
+    I(b, \theta, r_s; x, y) &= \frac{1}{4\pi r_s^2}
+    \bigg(
     -b_c\sin\theta x + b_c\cos\theta y - bz(x, y)
-\end{proof}
-%
-where $b_c = \sqrt{1 - b^2}$, $z(x, y) = \sqrt{1 - x^2 - y^2}$, and
-%
-\begin{proof}{}
-    I_0 = \frac{L}{4\pi\left(x_s^2 + y_s^2 + z_s^2\right)}
-\end{proof}
-%
-is the peak illumination (at the substellar point,
-assuming the illumination source is a star), with $L$ equal to the luminosity
-of the source.
-%
-Since the illumination is just a polynomial in $x$, $y$, and $z(x, y)$, we
+    \bigg)
+\end{proof}
+%
+with $b_c = \sqrt{1 - b^2}$ and $z(x, y) = \sqrt{1 - x^2 - y^2}$.
+%
+Since $I$ is just a polynomial in $x$, $y$, and $z(x, y)$, we
 can express it as a vector $\BF{i}(b, \theta)$ in the polynomial basis $\bp$.
-Recalling the structure of the basis (c.f. Appendix~\ref{app:starry}),
+Recalling the structure of the basis (Equation~\ref{eq:p}),
 %
@@
 \begin{proof}{}
-    \BF{i}(b, \theta) & =
-    I_0
+    \BF{i}(b, \theta, r_s) & =
+    \frac{1}{4\pi r_s^2}
     \begin{pmatrix}
@@
 \begin{proof}{}
-    \BF{I}(b, \theta) & =
-    I_0
+    \BF{I}(b, \theta, r_s) & =
+    \frac{1}{4\pi r_s^2}
     \begin{pmatrix}
@@
 degree of the map by one).
+%
+Note, importantly, that this weighting is valid only on the dayside
+hemisphere (see Equation~\ref{eq:Psi}), as the operator $\BF{I}$ weights
+points on the nightside by a \emph{negative} amount, which is clearly
+unphysical. As we will see momentarily, we account for this by excluding the
+nightside from the integration region in our flux integrals.
 
@@
     \label{eq:rTIA1RRy}
-    f = \rT \BF{I} \BF{A_1} \BF{R}'' \BF{R} \BF{y}
+    f_0 & =
+    \mathfrak{r}^\top(b)
+    \BF{I}(b, 0, r_s)
+    \BF{A_1}
+    \BF{R}'(-\theta)
+    \BF{R}(i, \lambda, \vartheta)
+    \BF{y}
     \quad,
@@
     \label{eq:sTA2IA1RRy}
-    f = \sT \BF{A_2} \BF{I} \BF{A_1} \BF{R}' \BF{R} \BF{y}
-    \quad.
-\end{align}
-%
-Two notes about these equations. First, we introduced a new rotation matrix
-$\BF{R}''$ in Equation~(\ref{eq:rTIA1RRy}), which rotates the problem so that
-the semi-major axis of the terminator is aligned with the $x$-axis; as will
-become clear in \S\ref{sec:case-0} below, this greatly simplifies the
-integration step. Second, in the derivation of Equation~(\ref{eq:sTA2IA1RRy})
+    f & =
+    \mathfrak{s}^\top(b, \theta, b_o, r_o)
+    \BF{A_2}
+    \BF{I}(b, \theta, r_s)
+    \BF{A_1}
+    \BF{R}'(\omega)
+    \BF{R}(i, \lambda, \vartheta)
+    \BF{y}
+    \quad.
+\end{align}
+%
+A few notes about these equations are in order.
+First, we now apply a rotation matrix $\BF{R}'(-\theta)$
+(Equation~\ref{eq:R'}) to the unocculted case,
+which rotates the body so the semi-major axis of the terminator is aligned
+with the $x$-axis; as will become clear in \S\ref{sec:solution-no-occ} below,
+this greatly simplifies the integration step. Note the corresponding change
+in $\BF{I}$, which we call with $\theta = 0$.
+%
+Second, in the derivation of Equation~(\ref{eq:sTA2IA1RRy})
 we used the fact that $\BF{A} = \BF{A_2} \BF{A_1}$
-\citep[c.f. Equation~14 in][]{Luger2019}, where $\BF{A_1}$ transforms from
+(Equation~\ref{eq:A}), where $\BF{A_1}$ transforms from
 the spherical harmonic basis $\by$ to the polynomial basis $\bp$, and
 $\BF{A_2}$ transforms from $\bp$ to the Green's basis $\bg$.
+Finally, note that we replaced the integral vectors
+$\rTe$ and $\sTe(b_o, r_o)$
+with the vectors
+$\mathfrak{r}^\top(b)$ and $\mathfrak{s}^\top(b, \theta, b_o, r_o)$,
+respectively.
+As we mentioned above, we must modify the integration limits to exclude the
+nightside, where the weighting by $\BF{I}$ is unphysical.
+The vectors $\mathfrak{r}^\top$ and $\mathfrak{s}^\top$ correspond to these
+modified integrals, which we devote the rest of this paper to
+computing.
 
@@
 observer. If there is no occultation (upper branch of the figure), we then
-rotate the map once more via $\BF{R}''$ to the integration frame
+rotate the map once more via $\BF{R}'$ to the integration frame
 $\mathcal{F}_\mathrm{int}$, in which the terminator is parallel to the
@@
 
-In \citet{Luger2019}, the crux of the problem was to compute the terms in the
-vectors $\sT$ and $\rT$, which are surface integrals over
-the region of the body that is visible to the observer
-(see Figure 2 in that paper). Here, these integrals are significantly
-more difficult, because they involve not only integration along the
-limb of the body and of a possible occultor, but also along the
-elliptical day/night terminator.
+%
+
+\section{The Solution: No Occultation}
+\label{sec:solution-no-occ}
+%
+Before we tackle configurations involving occultations, we must address the
+simpler problem of computing the total visible flux from an unocculted
+body in reflected light (Equation~\ref{eq:rTIA1RRy}). This problem was
+originally solved by \citet{Haggard2018} and subsequently by
+\citet{Luger2019b}, but for completeness we present the detailed
+derivation in the \starry formalism here.
+
+As we discussed above, we perform the integration in a frame
+$\mathcal{F}_\mathrm{int}$
+in which the semi-major axis of the terminator is aligned with the
+$x$-axis, with the illumination source at $y \ge 0$.
+The solution vector may then be computed from
+%
+\begin{align}
+    \label{eq:rT}
+    \rT(b) & =
+    \int_{-1}^{1}
+    \int_{b\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
+    \bp(x, y)
+    \ \dd y \ \dd x
+    \quad,
+\end{align}
+%
+which is identical to Equation~(20) in \citet{Luger2019} except for the
+lower integration limit of the inner integral. The lower limit is now
+the equation describing the terminator, which ensures we always exclude the
+nightside from the integration region.
+%
+For computational efficiency, in practice we compute the integral of the
+intensity-weighted basis directly,
+%
+\begin{align}
+    \label{eq:rTI}
+    \BS{\rho}^\top(b, r_s) & \equiv
+    \rT(b) \mathbf{I}(b, 0, r_s)
+    \nonumber                       \\
+                           & =
+    \int_{-1}^{1}
+    \int_{b\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
+    \bp(x, y)
+    \mathbf{I}(b, 0, r_s)
+    \ \dd y \ \dd x
+    \quad,
+\end{align}
+%
+recalling that in frame $\mathcal{F}_\mathrm{int}$, $\theta = 0$ by
+definition.
+%
+Equation~(\ref{eq:rTI}) may be solved analytically in terms of purely
+trigonometric and algebraic functions of $b$. The component of $\BS{\rho}^\top$
+at index $n$ is given by
+%
+\begin{proof}{}
+    \label{eq:rTsoln}
+    \rho_n(b, r_s) & =
+    \frac{1}{4\pi r_s^2}
+    \begin{cases}
+        \frac{b_c\left(1 - b^{\frac{\nu + 4}{2}}\right)}{2}
+        J_{\frac{\mu}{2}, \frac{\nu + 2}{2}} -
+        b I_\frac{\nu}{2}(b) K_{\frac{\mu}{2}, \frac{\nu}{2}}
+        %
+         &
+        %
+        \qquad
+        \mu, \nu \ \mathrm{even}
+        %
+        \\[1em]
+        %
+        b_c
+        I_{\frac{\nu + 1}{2}}(b) K_{\frac{\mu - 1}{2}, \frac{\nu + 1}{2}}
+        %
+        \\[0.5em]
+        \qquad
+        %
+        - \frac{b}{2} \bigg\{
+        \left(1 - b^{\frac{\nu + 1}{2}}\right)
+        \left(
+        J_{\frac{\mu - 1}{2}, \frac{\nu - 1}{2}} -
+        J_{\frac{\mu + 3}{2}, \frac{\nu - 1}{2}}
+        \right)
+        \\[0.5em]
+        \qquad\qquad
+        -
+        \left(1 - b^{\frac{\nu + 5}{2}}\right)
+        J_{\frac{\mu - 1}{2}, \frac{\nu + 3}{2}}
+        \bigg\}
+        %
+         &
+        %
+        \qquad
+        \mathrm{otherwise}
+        %
+    \end{cases}
+\end{proof}
+%
+where we make use of the indices
+%
+\begin{align}
+    \label{eq:l-m-mu-nu}
+    \mu & = l - m
+    \nonumber                 \\
+    \nu & = l + m
+    \nonumber                 \\
+    l   & = \floor*{\sqrt{n}}
+    \nonumber                 \\
+    m   & = n - l^2 - l
+\end{align}
+%
+as in \citet{Luger2019} and we define the helper functions
+%
+\begin{proof}{}
+    \label{eq:HJK}
+    H_{j}(b) &= \int_b^1 a^j \sqrt{1 - a^2} \dd a
+    \nonumber \\
+    %
+    J_{i,j} &=
+    \frac{
+        \Gamma\left(\frac{i + 1}{2}\right)
+        \Gamma\left(\frac{j + 1}{2}\right)
+    }
+    {
+        \Gamma\left(\frac{i + j + 4}{2}\right)
+    }
+    %
+    \nonumber \\
+    %
+    K_{i,j} &=
+    \frac{
+        \Gamma\left(\frac{i + 1}{2}\right)
+        \Gamma\left(\frac{j + 4}{2}\right)
+    }
+    {
+        \Gamma\left(\frac{i + j + 5}{2}\right)
+    }
+    \quad.
+\end{proof}
+%
+Given initial conditions
+%
+\\[1em]
+\begin{minipage}{.33\linewidth}
+    \begin{align}
+        H_{0}(b) & = \frac{\arccos(b) - bb_c}{2}
+        %
+        \nonumber                                \\
+        %
+        H_{1}(b) & = \frac{b_c^3}{3}
+        %
+        \nonumber
+    \end{align}
+\end{minipage}%
+\begin{minipage}{.32\linewidth}
+    \begin{align}
+        J_{0,0} & = \pi
+        %
+        \nonumber               \\
+        %
+        J_{0,1} & = \frac{4}{3}
+        %
+        \nonumber
+    \end{align}
+\end{minipage}%
+\begin{minipage}{.33\linewidth}
+    \begin{proof}{}
+        \label{eq:IJK0}
+        K_{0,0} &= \frac{4}{3}
+        %
+        \nonumber \\
+        K_{0,1} &= \frac{3\pi}{8}
+    \end{proof}
+\end{minipage}
+\\[1em]
+%
+we may compute all higher order terms from the recurrence relations
+%
+\begin{proof}{}
+    \label{eq:IJKrec}
+    H_{j}(b) &= \frac{b^n b_c^3 + (j - 1) H_{j - 2}(b)}{j + 2}
+    %
+    \nonumber \\
+    %
+    J_{0,j} &= \left(\frac{j - 1}{j + 2}\right) J_{0,j-2}
+    %
+    \nonumber \\
+    %
+    K_{0,j} &= \left(\frac{j + 2}{j + 3}\right) K_{0,j-2}
+    %
+    \nonumber \\
+    %
+    J_{i,j} &= \left(\frac{i - 1}{i + j + 2}\right) J_{i-2,j}
+    %
+    \nonumber \\
+    %
+    K_{i,j} &= \left(\frac{i - 1}{i + j + 3}\right) K_{i-2,j}
+    \quad.
+\end{proof}
+%
+Once $\BS{\rho}^\top$ is known, the observed flux is computed from
+(c.f. Equation~\ref{eq:rTIA1RRy})
+%
+\begin{proof}{}
+    \label{eq:f0}
+    f_0 & =
+    \BS{\rho}^\top(b, r_s)
+    \BF{A_1}
+    \BF{R}'(-\theta)
+    \BF{R}(i, \lambda, \vartheta)
+    \BF{y}
+    \quad.
+\end{proof}
+%
+
+\section{The Solution: Occultation}
+\label{sec:solution-occ}
 
@@
 
-%
-
-\subsection{Problem Setup}
-\label{sec:setup}
-%
-
 Figure~\ref{fig:cases} shows the
@@
 occultation configurations, for any illumination angle, occultor size, and
-occultor position. In the next three sections, we present the solution for the
+occultor position. In the following sections, we present the solution for the
 $\sT$, and hence for the total visible flux, for each of these cases.
 
-\section{The Solution}
-\label{sec:solution}
-%
-\subsection{Case 0}
-\label{sec:case-0}
-%
-Before we tackle configurations involving occultations, we must address the
-simpler problem of computing the total visible flux from an unocculted
-body in reflected light (see Figure~\ref{fig:illum}). This problem was
-originally solved by \citet{Haggard2018} and subsequently adapted to the
-\starry formalism in \citet{Luger2019b}, but for completeness we present
-the detailed solution in Appendix~\ref{app:case0}. We will refer to the
-solution vector for this case as $\sT_0$ (Equation~\ref{eq:sT0}).
+\xxx{How do we determine which case we're modeling?}
 
@@
 %
-Case 1 corresponds to any complete occultation of the body, so its
-solution vector is trivial:
+Case 1 corresponds to any complete occultation of the body, so the
+solution for the flux is trivial:
 %
@@
     \label{eq:sT1}
-    \sT_1 = \BS{0}
+    f_1 = 0
     \quad.
@@
 limb of the body). Since the night side intensity is zero everywhere, this case
-is also trivial, as the integration is the same as in case 0:
+is also trivial, as the flux is equal to the flux in the no occultation case
+(Equation~\ref{eq:f0}):
 %
@@
     \label{eq:sT2}
-    \sT_2 = \sT_0(b, \theta)
+    f_2 = f_0
     \quad.
@@
 %
-\begin{align}
-    \label{eq:sT3}
-    \sT_3 = \sT_\star(b_o, r_o) \BS{\Psi}(b, \theta, d_s)
-    \quad,
-\end{align}
-%
-where $\sT_\star$ is the usual \starry solution vector
-\citep[Equation~26 in][]{Luger2019} and $\BS{\Psi}$ is an illumination
-matrix (Appendix~\ref{app:case3}).
+\begin{proof}{}
+    \label{eq:f3}
+    f_3 = \sTe(b_o, r_o)
+    \BF{A_2}
+    \BF{I}(b, \theta, r_s)
+    \BF{A_1}
+    \BF{R}'(\omega)
+    \BF{R}(i, \lambda, \vartheta)
+    \BF{y}
+    \quad.
+\end{proof}
 %
@@
 \emph{only} the day side of the body (regardless of whether or not it
-intersects with the limb).
-%
-\begin{align}
+intersects with the limb):
+%
+\begin{proof}{}
     \label{eq:sT4}
-    \sT_4 = \sT_\star(b_o, r_o) + \sT_0(-b, \theta + \pi)
-    \quad.
-\end{align}
-%
-
-% case 1: 0
-% case 2: s0
-% case 3: sTe * I
-% case 4: sTe * I + ~sT0
+    f_4 = f_3 + \hat{f}_0
+    \quad,
+\end{proof}
+%
+where we define
+%
+\begin{proof}{}
+    \label{eq:f0hat}
+    \hat{f}_0 & =
+    \BS{\rho}^\top(-b, r_s)
+    \BF{A_1}
+    \BF{R}'(-\theta - \pi)
+    \BF{R}(i, \lambda, \vartheta)
+    \BF{y}
+    \quad.
+\end{proof}
+
+%
 
@@
 %
-Cases 5--8 (see Figure~\ref{fig:cases}, Figure~\ref{fig:geometry}).
+\xxx{Cases 5--8} (see Figure~\ref{fig:cases}, Figure~\ref{fig:geometry}).
 
@@
 %
-See Figure~\ref{fig:speed}.
+\xxx{Performance!} See Figure~\ref{fig:speed}.
 %
@@
 \appendix
+
+\xxx{Work in progress below here.}
 
@@
 
-\section{Case 0}
-\label{app:case0}
-%
-Our task is to compute the solution vector for this
-configuration, which we will denote $\BF{s}^\top_0$.
-Since in this case there is no occultor, it is
-more convenient to perform the integration in a frame $\mathcal{F}''$ where the
-semi-major axis of the terminator is aligned with the $x$-axis
-(see Figure~\ref{fig:illum}); let us denote the matrix that rotates us
-from $\mathcal{F}'$ to $\mathcal{F}''$ as $\BF{R}''$.
-It is also far easier to perform the integration
-in the \emph{polynomial basis} $\bp$
+The \emph{polynomial basis} $\bp$
 \citep[Equation 7 in][]{Luger2019}:
@@
 Equation~(\ref{eq:lm}).
-Now, if $\BF{r}^\top$ is the solution to the surface integrals in the
-polynomial basis in $\mathcal{F}''$,
-we may compute the desired solution vector in the Green's basis from
-%
-\begin{align}
-    \label{eq:sT0}
-    \BF{s}^\top_0 & = \BF{r}^\top \BF{A_1} \BF{R}'' \BF{A}^{-1}
-    \quad,
-\end{align}
-%
-where $\BF{A_1}$ \citep[Equation B11 in][]{Luger2019}
-transforms the solution into the spherical harmonic basis so it can
-be rotated out of the integration frame $\mathcal{F}''$ via $\BF{R}''$, and
-$\BF{A}^{-1}$ \citep[Equation B13 in][]{Luger2019} transforms the
-result into the Green's basis (in which $\sT$ is defined).
-
-Our task is thus to compute $\BF{r}^\top$.
-In frame $\mathcal{F}''$, the body sits at the origin and is
-illuminated by a point source in the
-$y-z$ plane at coordinates $(0, y_s, z_s)$ as in Figure~\ref{fig:illum}.
-The day/night terminator is a half-ellipse whose semi-major axis
-is unity and is aligned with the $x$-axis. The semi-minor axis is given
-by $b = -\nicefrac{z_s}{\sqrt{y_s^2 + z_s^2}}$, where $b > 0$ corresponds to
-a half-ellipse that is concave down and $b < 0$ to one that is concave up.
-It is straightforward to show
-that the illumination at a point $(x, y)$ on the projected disk is
-given by
-%
-\begin{proof}{}
-    \Psi(b; x, y) & =
-    \begin{dcases}
-        b_cy - bz(x, y) &
-        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
-        y \geq b \sqrt{1 - x^2}
-        \\
-        0               &
-        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
-        \mathrm{otherwise}
-    \end{dcases}
-    \quad ,
-    \label{eq:illum}
-\end{proof}
-%
-where $b_c = \sqrt{1 - b^2}$.
-%
-The elements of the solution vector may then be computed from
-%
-\begin{align}
-    \label{eq:rT}
-    r_{l, m}(b) & =
-    \int_{-1}^{1}
-    \int_{b\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
-    \tilde{p}_{n(\mu,\nu)}(x, y)
-    \Psi(b; x, y)
-    \ \dd y \ \dd x
-    \quad.
-\end{align}
-%
-This is the integral of the illumination-weighted intensity of each
-term in the polynomial basis over the projected visible dayside of the
-body.
-%
-Equation~(\ref{eq:rT}) may be solved analytically in terms of purely
-trigonometric and algebraic functions of $b$:
-%
-\begin{proof}{}
-    \label{eq:rTsoln}
-    r_{l, m}(b) & =
-    \begin{cases}
-        \frac{b_c\left(1 - b^{\frac{\nu + 4}{2}}\right)}{2}
-        J_{\frac{\mu}{2}, \frac{\nu + 2}{2}} -
-        b I_\frac{\nu}{2}(b) K_{\frac{\mu}{2}, \frac{\nu}{2}}
-        %
-         &
-        %
-        \qquad
-        \mu, \nu \ \mathrm{even}
-        %
-        \\[1em]
-        %
-        b_c
-        I_{\frac{\nu + 1}{2}}(b) K_{\frac{\mu - 1}{2}, \frac{\nu + 1}{2}}
-        %
-        \\[0.5em]
-        \qquad
-        %
-        - \frac{b}{2} \bigg\{
-        \left(1 - b^{\frac{\nu + 1}{2}}\right)
-        \left(
-        J_{\frac{\mu - 1}{2}, \frac{\nu - 1}{2}} -
-        J_{\frac{\mu + 3}{2}, \frac{\nu - 1}{2}}
-        \right)
-        \\[0.5em]
-        \qquad\qquad
-        -
-        \left(1 - b^{\frac{\nu + 5}{2}}\right)
-        J_{\frac{\mu - 1}{2}, \frac{\nu + 3}{2}}
-        \bigg\}
-        %
-         &
-        %
-        \qquad
-        \mathrm{otherwise}
-        %
-    \end{cases}
-\end{proof}
-%
-where
-%
-\begin{proof}{}
-    \label{eq:IJK}
-    I_{j}(b) &= \int_b^1 a^j \sqrt{1 - a^2} \dd a
-    \nonumber \\
-    %
-    J_{i,j} &=
-    \frac{
-        \Gamma\left(\frac{i + 1}{2}\right)
-        \Gamma\left(\frac{j + 1}{2}\right)
-    }
-    {
-        \Gamma\left(\frac{i + j + 4}{2}\right)
-    }
-    %
-    \nonumber \\
-    %
-    K_{i,j} &=
-    \frac{
-        \Gamma\left(\frac{i + 1}{2}\right)
-        \Gamma\left(\frac{j + 4}{2}\right)
-    }
-    {
-        \Gamma\left(\frac{i + j + 5}{2}\right)
-    }
-    \quad.
-\end{proof}
-%
-Given initial conditions
-%
-\\[1em]
-\begin{minipage}{.33\linewidth}
-    \begin{align}
-        I_{0}(b) & = \frac{\arccos(b) - bb_c}{2}
-        %
-        \nonumber                                \\
-        %
-        I_{1}(b) & = \frac{b_c^3}{3}
-        %
-        \nonumber
-    \end{align}
-\end{minipage}%
-\begin{minipage}{.32\linewidth}
-    \begin{align}
-        J_{0,0} & = \pi
-        %
-        \nonumber               \\
-        %
-        J_{0,1} & = \frac{4}{3}
-        %
-        \nonumber
-    \end{align}
-\end{minipage}%
-\begin{minipage}{.33\linewidth}
-    \begin{proof}{}
-        \label{eq:IJK0}
-        K_{0,0} &= \frac{4}{3}
-        %
-        \nonumber \\
-        K_{0,1} &= \frac{3\pi}{8}
-    \end{proof}
-\end{minipage}
-\\[1em]
-%
-we may compute all higher order terms from the recurrence relations
-%
-\begin{proof}{}
-    \label{eq:IJKrec}
-    I_{j}(b) &= \frac{b^n b_c^3 + (j - 1) I_{j - 2}(b)}{j + 2}
-    %
-    \nonumber \\
-    %
-    J_{0,j} &= \left(\frac{j - 1}{j + 2}\right) J_{0,j-2}
-    %
-    \nonumber \\
-    %
-    K_{0,j} &= \left(\frac{j + 2}{j + 3}\right) K_{0,j-2}
-    %
-    \nonumber \\
-    %
-    J_{i,j} &= \left(\frac{i - 1}{i + j + 2}\right) J_{i-2,j}
-    %
-    \nonumber \\
-    %
-    K_{i,j} &= \left(\frac{i - 1}{i + j + 3}\right) K_{i-2,j}
-    \quad.
-\end{proof}
-
-\section{Case 3}
-\label{app:case3}
-Hello.
-
-\section{Case 4}
-\label{app:case4}
-Hello.
-
-\section{Cases 5--8}
-\label{app:cases-5-8}
-Hello.
 

### 2020-04-02 tex/figures/frames.py

@@ -302,15 +302,15 @@ axes.append(ax)
 
 # Indicate the transformations between each image
 add_arrow(axes[0], axes[1], r"$\mathbf{R}$")
-add_arrow(axes[1], axes[2], r"$\mathbf{R}''$", kind="bar_up")
+add_arrow(axes[1], axes[2], r"$\mathbf{R}'$", kind="bar_up")
 add_arrow(axes[2], axes[3], r"$\mathbf{A_1}$")
 add_arrow(axes[3], axes[4], r"$\mathbf{I}$")
-add_arrow(axes[4], axes[5], r"$\mathbf{r}^\top$", eps=0.2)
+add_arrow(axes[4], axes[5], r"$\mathfrak{r}^\top$", eps=0.2)
 add_arrow(axes[1], axes[6], r"$\mathbf{R}'$", kind="bar_down")
 add_arrow(axes[6], axes[7], r"$\mathbf{A_1}$")
 add_arrow(axes[7], axes[8], r"$\mathbf{I}$")
 add_arrow(axes[8], axes[9], r"$\mathbf{A_2}$")
-add_arrow(axes[9], axes[10], r"$\mathbf{s}^\top$", eps=0.2)
+add_arrow(axes[9], axes[10], r"$\mathfrak{s}^\top$", eps=0.2)
 
 # Appearance
 for ax in axes:

### 2020-04-03 tex/ms.tex
more text, but frame notation is messed up

@@
 %
+\textbf{Note:}
+This section closely follows the
+notation and formalism introduced in \citet{Luger2019}. While we
+include all of the relevant equations and definitions in
+Appendix~\ref{app:starry}, the reader is strongly encouraged to
+review \S2--3 of \citet{Luger2019} before proceeding.
+
 \subsection{Review of the \starry algorithm in emitted light}
@@
 basis $\by$ to the \emph{polynomial basis} $\bp$ in which the integrals
-are computed (Equation~\ref{eq:A1}),
+are computed (Equations~\ref{eq:by}, \ref{eq:bp}, and \ref{eq:A1}),
 %
@@
 of the sky by an angle
-$\omega = \nicefrac{\pi}{2} - \mathrm{arctan2}(y_o, x_o)$
+$\omega = \mathrm{arctan2}(x_o, y_o)$
 into a frame $\mathcal{F}_\mathrm{greens}$ in which the
@@
 and the angle by which its semi-major axis is rotated away from the
-$+x$-axis,
+$+x$-axis \xxx{CHECK ME},
 %
@@
     \label{eq:theta}
-    \theta = \mathrm{arctan2}(y_s, x_s)
-    \quad.
+    \theta &=
+    \begin{cases}
+        -\mathrm{arctan2}(x_s, y_s)
+         & \qquad \mathcal{F} = \mathcal{F}_\mathrm{term}   \\
+        \omega - \mathrm{arctan2}(x_s, y_s)
+         & \qquad \mathcal{F} = \mathcal{F}_\mathrm{greens}
+        \quad.
+    \end{cases}
 \end{proof}
@@
 can express it as a vector $\BF{i}(b, \theta)$ in the polynomial basis $\bp$.
-Recalling the structure of the basis (Equation~\ref{eq:p}),
-%
-\begin{align}
-    \bp & =
-    \begin{pmatrix}
-        1   &
-        x   & z  & y  &
-        x^2 & xz & xy & yz & y^2 &
-        \cdot\cdot\cdot
-    \end{pmatrix}^\mathsf{T}
-    \quad,
-\end{align}
-%
+Recalling the structure of the basis (Equation~\ref{eq:bp}),
 we may write
@@
 rotate the map once more via $\BF{R}'$ to the integration frame
-$\mathcal{F}_\mathrm{int}$, in which the terminator is parallel to the
+$\mathcal{F}_\mathrm{term}$, in which the terminator is parallel to the
 $x$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$, apply the
@@
 As we discussed above, we perform the integration in a frame
-$\mathcal{F}_\mathrm{int}$
+$\mathcal{F}_\mathrm{term}$
 in which the semi-major axis of the terminator is aligned with the
@@
 %
-recalling that in frame $\mathcal{F}_\mathrm{int}$, $\theta = 0$ by
+recalling that in frame $\mathcal{F}_\mathrm{term}$, $\theta = 0$ by
 definition.
@@
 
-Figure~\ref{fig:cases} shows the
-eight families of cases involving an occultation of an illuminated body by
-a spherical occultor. Each of these cases correspond to distinct ways in
-which the limb of the occultor can intersect with the limb of the occulted
-body and its terminator; together, these cases encompass all possible
+The integration in the unocculted case presented above is relatively
+straightforward, since
+the boundaries of integration are always the half-ellipse defining the
+terminator and the half-circle defining the upper limb of the body
+(Equation~\ref{eq:rT}). When an occultor is present, however, the
+integration boundaries are far less trivial, since they may or may not
+include sections of the terminator, sections of the limb of the body,
+and sections of the limb of the occultor. There are in total eight families of
+configurations, each defined by a distinct combination of integration
+boundaries; these are shown in Figure~\ref{fig:cases}.
+Together, these cases encompass all possible
 occultation configurations, for any illumination angle, occultor size, and
-occultor position. In the following sections, we present the solution for the
-$\sT$, and hence for the total visible flux, for each of these cases.
-
-\xxx{How do we determine which case we're modeling?}
+occultor position.
+
+Before we discuss how to compute the occultation integrals, we must first
+develop a procedure to identify the relevant case given the occultor
+position $(x_o, y_o)$ and radius $r_o$ and the terminator semi-minor
+axis $b$ and angle $\theta$. Then, once the case is determined, we must
+identify the relevant integration boundaries, which depend on the points
+of intesection between the limb of the body, the limb of the occultor, and
+the terminator. We do so in the following section.
+
+\subsection{Case determination and integration boundaries}
+\label{sec:which-case}
+%
+The key to identifying the case corresponding to a given configuration is
+to determine whether or not the limb of the occultor intersects the terminator
+of the body, and if so, the points of intersection.
+Switching momentarily to the frame $\mathcal{F}_\mathrm{term}$,
+the equations defining the
+\begin{align}
+    y_1(x) & = b \sqrt{1 - x^2}
+    \nonumber                                       \\
+    y_2(x) & = y'_o \pm \sqrt{r_o^2 - (x - x'_o)^2}
+\end{align}
+%
+where $x'_o = $ and $y'_o = $ are the coordinates of the occultor in
+$\mathcal{F}_\mathrm{term}$.
+
+Recall that we perform the integration in frame
+$\mathcal{F}_\mathrm{greens}$, in which the occultor lies along the $+y$-axis
+at $(0, b_o)$, with $b_o = \sqrt{x_o^2 + y_o^2}$. In this frame, the
+semi-major axis of the terminator is at an angle $\theta$ with respect to the
+$+x$-axis (Equation~\ref{eq:theta}).
 
@@
 \label{app:starry}
+%
+Equations:
+%
+\begin{align}
+    \label{eq:R}
+    \BF{R} = ?
+\end{align}
+%
+\begin{align}
+    \label{eq:by}
+    \by = ?
+\end{align}
+%
+\begin{align}
+    \label{eq:bp}
+    \bp & =
+    \begin{pmatrix}
+        1   &
+        x   & z  & y  &
+        x^2 & xz & xy & yz & y^2 &
+        \cdot\cdot\cdot
+    \end{pmatrix}^\mathsf{T}
+    \quad,
+\end{align}
+%
+\begin{align}
+    \label{eq:A1}
+    \BF{A_1} = ?
+\end{align}
+%
+\begin{align}
+    \label{eq:rTe}
+    \rTe = ?
+\end{align}
+%
+\begin{align}
+    \label{eq:R'}
+    \BF{R}' = ?
+\end{align}
+%
+\begin{align}
+    \label{eq:A}
+    \BF{A} = ?
+\end{align}
+%
+\begin{align}
+    \label{eq:sTe}
+    \sTe = ?
+\end{align}
 %

### 2020-04-03 tex/ms.tex
better notation

@@
 #1
-\dd\varphi
 }
@@
 include all of the relevant equations and definitions in
-Appendix~\ref{app:starry}, the reader is strongly encouraged to
+Appendix~\ref{app:starry}, the reader is encouraged to
 review \S2--3 of \citet{Luger2019} before proceeding.
+
+\xxx{Unprimed = sky. Prime = greens. Double prime = term.}
+\xxx{Emphasize why we can't just analytically weight the nightside by
+    zero and integrate as before.}
 
@@
 has radius unity and sits at the origin of a right-handed Cartesian coordinate
-system with the $x$-axis pointing to the right on the sky, the $y$-axis
-pointing up on the sky, and the $z$-axis pointing out of the sky
-toward the observer; denote this frame by $\mathcal{F}_0$. In $\mathcal{F}_0$,
+system in some frame $\mathcal{F}_0$. In this frame,
 the surface (emitted) intensity field of the body is described by the
-spherical harmonic coefficient vector $\mathbf{y}$. Following
-\citet{Luger2019}, when no occultor is present, we may compute the total
+spherical harmonic coefficient vector $\mathbf{y}$.
+An observer views the body from a large distance in the sky frame
+$\mathcal{F}$, in which the $x$-axis points to the right,
+the $y$-axis points up, and the $z$-axis points out of the sky
+toward the observer. Following \citet{Luger2019}, if
+an occultor of radius $r_o$ is located at sky position $(x_o, y_o)$,
+we compute the visible flux $f$ from
+%
+\begin{align}
+    \label{eq:sTARRy}
+    f = \sTe \BF{A} \BF{R}' \BF{R} \BF{y}
+    \quad,
+\end{align}
+%
+where, from right to left, $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
+is a Wigner rotation matrix that rotates $\bvec{y}$ from $\mathcal{F}_0$
+to the sky frame $\mathcal{F}$
+given the body's inclination $i$, obliquity
+$\lambda$, and rotational phase $\vartheta$ (Equation~\ref{eq:R}),
+%
+$\BF{R}' = \BF{R}'(x_o, y_o)$ rotates the body on the plane
+of the sky into the integration frame $\mathcal{F}'$, in which the
+occultor lies along the $+y'$-axis (Equation~\ref{eq:R'}),
+%
+$\BF{A}$ is the change-of-basis matrix from $\by$
+to the \emph{Green's basis} $\bg$ in which the integrals are computed
+(Equations~\ref{eq:by}, \ref{eq:bg}, and \ref{eq:A}),
+%
+and $\sTe = \sTe(b_o, r_o)$ is the vector of solutions to the integral over
+the projected visible disk of the body for each term in $\bg$
+(Equation~\ref{eq:sTe}), with $b_o = \sqrt{x_o^2 + y_o^2}$.
+%
+If instead no occultor is present, we compute the total
 visible flux $f_0$ from this body as
@@
     \label{eq:rTA1Ry}
-    f_0 = \rTe \BF{A_1} \BF{R} \BF{y}
+    f_0 = \rTe \BF{A_1} \BF{R}'' \BF{R} \BF{y}
     \quad,
@@
 %
-where, from right to left, $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
-is a Wigner rotation matrix that rotates $\bvec{y}$ to the sky frame
-$\mathcal{F}_\mathrm{sky}$ given the body's inclination $i$, obliquity
-$\lambda$, and rotational phase $\vartheta$ (Equation~\ref{eq:R}),
+where, as before, $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
+rotates the body from $\mathcal{F}_0$
+to the sky frame $\mathcal{F}$,
+%
+$\BF{R}''$ rotates the body on the plane
+of the sky into the integration frame
+$\mathcal{F}''$ (Equation~\ref{eq:R''})%
+\footnote{%
+    In \citet{Luger2019}, $\mathcal{F}'' = \mathcal{F}'$, so
+    this rotation is trivial: $\BF{R}''$ is just the identity matrix.
+},
 %
@@
 basis $\by$ to the \emph{polynomial basis} $\bp$ in which the integrals
-are computed (Equations~\ref{eq:by}, \ref{eq:bp}, and \ref{eq:A1}),
+are computed (Equations~\ref{eq:bp} and \ref{eq:A1}),
 %
@@
 %
-If instead an occultor of radius $r_o$ is located at position $(x_o, y_o)$,
-we instead compute the visible flux $f$ from
-%
-\begin{align}
-    \label{eq:sTARRy}
-    f = \sTe \BF{A} \BF{R}' \BF{R} \BF{y}
-    \quad,
-\end{align}
-%
-where, as before, $\BF{R}$ rotates the body from $\mathcal{F}_0$
-to $\mathcal{F}_\mathrm{sky}$,
-%
-$\BF{R}' = \BF{R}'(\omega)$ rotates the body on the plane
-of the sky by an angle
-$\omega = \mathrm{arctan2}(x_o, y_o)$
-into a frame $\mathcal{F}_\mathrm{greens}$ in which the
-occultor lies along the $+y$-axis (Equation~\ref{eq:R'}),
-%
-$\BF{A}$ is the change-of-basis matrix from $\by$
-to the \emph{Green's basis} $\bg$ in which the integrals are computed
-(Equation~\ref{eq:A}),
-%
-and $\sTe = \sTe(b_o, r_o)$ is the vector of solutions to the integral over
-the projected visible disk of the body for each term in $\bg$
-(Equation~\ref{eq:sTe}), with $b_o = \sqrt{x_o^2 + y_o^2}$.
 For more details, see Appendix~\ref{app:starry} and \citet{Luger2019}.
@@
 the radiance at any
-point on the surface is proportional to the cosine of the angle $\phi$ between
+point on the surface is proportional to the cosine of the angle between
 the incident light and the surface normal. Points for which
-$\phi \ge \frac{\pi}{2}$ are unilluminated and therefore have radiance of zero.
+this angle is greater than $\nicefrac{\pi}{2}$ are unilluminated and
+therefore have radiance of zero.
 %
@@
 %
-and the angle by which its semi-major axis is rotated away from the
-$+x$-axis \xxx{CHECK ME},
-%
-\begin{proof}{}
-    \label{eq:theta}
-    \theta &=
-    \begin{cases}
-        -\mathrm{arctan2}(x_s, y_s)
-         & \qquad \mathcal{F} = \mathcal{F}_\mathrm{term}   \\
-        \omega - \mathrm{arctan2}(x_s, y_s)
-         & \qquad \mathcal{F} = \mathcal{F}_\mathrm{greens}
-        \quad.
-    \end{cases}
-\end{proof}
-%
+and the angle $\theta$ by which its semi-major axis is rotated away from the
+$+x$-axis (defined \xxx{below}).
 Given this formulation, and assuming that
@@
 \begin{proof}{}
-    \label{eq:Psi}
+    \label{eq:illum}
     \mathfrak{I}(b, \theta, r_s; x, y)&=
@@
 Note, importantly, that this weighting is valid only on the dayside
-hemisphere (see Equation~\ref{eq:Psi}), as the operator $\BF{I}$ weights
+hemisphere (see Equation~\ref{eq:illum}), as the operator $\BF{I}$ weights
 points on the nightside by a \emph{negative} amount, which is clearly
@@
             Arrows indicate linear operations and are labeled accordingly.
-            The upper branch corresponds to the unocculted case, while the
-            lower branch corresponds to the case where an occultor is present.
+            The upper branch corresponds to the occulted case
+            (Equation~\ref{eq:sTA2IA1RRy}), while the
+            lower branch corresponds to the case where the body
+            is unocculted (Equation~\ref{eq:rTIA1RRy}).
             See text for details.
@@
 
-We may now re-write Equations~(\ref{eq:rTA1Ry}) and (\ref{eq:sTARRy}) to
-account for this illumination transformation. The flux outside of occultation
+We may now re-write Equations~(\ref{eq:sTARRy}) and (\ref{eq:rTA1Ry}) to
+account for this illumination transformation. The flux during an occultation
 is now given by
+%
+\begin{align}
+    \label{eq:sTA2IA1RRy}
+    f & =
+    \mathfrak{s}^\top(b, \theta', b_o, r_o)
+    \BF{A_2}
+    \BF{I}(b, \theta', r_s)
+    \BF{A_1}
+    \BF{R}'(x_o, y_o)
+    \BF{R}(i, \lambda, \vartheta)
+    \BF{y}
+    \quad,
+\end{align}
+%
+where
+%
+\begin{align}
+    \label{eq:theta'}
+    \theta' = \mathrm{arctan2}(x_o, y_o) - \mathrm{arctan2}(x_s, y_s)
+\end{align}
+%
+is the angle of the terminator in the frame $\mathcal{F}'$.
+Note that we made use of the fact that
+$\BF{A} = \BF{A_2} \BF{A_1}$
+(Equation~\ref{eq:A}), where $\BF{A_1}$ transforms from
+the spherical harmonic basis $\by$ to the polynomial basis $\bp$, and
+$\BF{A_2}$ transforms from $\bp$ to the Green's basis $\bg$.
+
+Similarly, the flux outside of an occultation is now given by
 %
@@
     \mathfrak{r}^\top(b)
-    \BF{I}(b, 0, r_s)
+    \BF{I}(b, \theta'', r_s)
     \BF{A_1}
-    \BF{R}'(-\theta)
+    \BF{R}''(x_s, y_s)
     \BF{R}(i, \lambda, \vartheta)
@@
 %
-and the flux during an occultation by
-%
-\begin{align}
-    \label{eq:sTA2IA1RRy}
-    f & =
-    \mathfrak{s}^\top(b, \theta, b_o, r_o)
-    \BF{A_2}
-    \BF{I}(b, \theta, r_s)
-    \BF{A_1}
-    \BF{R}'(\omega)
-    \BF{R}(i, \lambda, \vartheta)
-    \BF{y}
-    \quad.
-\end{align}
-%
-A few notes about these equations are in order.
-First, we now apply a rotation matrix $\BF{R}'(-\theta)$
-(Equation~\ref{eq:R'}) to the unocculted case,
-which rotates the body so the semi-major axis of the terminator is aligned
-with the $x$-axis; as will become clear in \S\ref{sec:solution-no-occ} below,
-this greatly simplifies the integration step. Note the corresponding change
-in $\BF{I}$, which we call with $\theta = 0$.
-%
-Second, in the derivation of Equation~(\ref{eq:sTA2IA1RRy})
-we used the fact that $\BF{A} = \BF{A_2} \BF{A_1}$
-(Equation~\ref{eq:A}), where $\BF{A_1}$ transforms from
-the spherical harmonic basis $\by$ to the polynomial basis $\bp$, and
-$\BF{A_2}$ transforms from $\bp$ to the Green's basis $\bg$.
-Finally, note that we replaced the integral vectors
+where
+%
+\begin{align}
+    \label{eq:theta''}
+    \theta'' = 0
+\end{align}
+%
+is the angle of the terminator in the frame $\mathcal{F}''$, by
+construction. The transformation
+$\BF{R}'' = \BF{R}''(x_s, y_s)$ (Equation~\ref{eq:R''}) rotates
+the body so the semi-major axis of the terminator is aligned
+with the $x''$-axis; as will become clear in \S\ref{sec:solution-no-occ} below,
+this greatly simplifies the integration step.
+
+Note that in both equations we replaced the integral vectors
 $\rTe$ and $\sTe(b_o, r_o)$
 with the vectors
-$\mathfrak{r}^\top(b)$ and $\mathfrak{s}^\top(b, \theta, b_o, r_o)$,
+$\mathfrak{r}^\top(b)$ and $\mathfrak{s}^\top(b, \theta', b_o, r_o)$,
 respectively.
@@
 $\mathcal{F}_0$, we first rotate it via $\BF{R}$ to the sky frame
-$\mathcal{F}_\mathrm{sky}$, in which orientation the body is viewed by the
-observer. If there is no occultation (upper branch of the figure), we then
-rotate the map once more via $\BF{R}'$ to the integration frame
-$\mathcal{F}_\mathrm{term}$, in which the terminator is parallel to the
-$x$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$, apply the
-illumination transform $\BF{I}$, and finally dot in the solutions to the
-surface integrals $\rT$. If, on the other hand, an occultor is present,
-we rotate the map from $\mathcal{F}_\mathrm{sky}$ via $\BF{R}'$ to the frame
-$\mathcal{F}_\mathrm{greens}$, in which the occultor lies along the
-$+y$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$ and $\BF{I}$
-to weight the map by the illumination as above. Finally, we change basis
+$\mathcal{F}$, in which the body is viewed by the
+observer. If an occultor is present (upper branch of the figure),
+we rotate the map from $\mathcal{F}$ via $\BF{R}'$ to the frame
+$\mathcal{F}'$, in which the occultor lies along the
+$+y'$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$ and $\BF{I}$
+to weight the map by the illumination. Finally, we change basis
 via $\BF{A_2}$ to the Green's basis, in which we compute and dot the
 integrals $\sT$.
+If, on the other hand, there is no occultation (lower branch of the figure),
+we instead rotate the map via $\BF{R}''$ to the integration frame
+$\mathcal{F}''$, in which the terminator is parallel to the
+$x''$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$, apply the
+illumination transform $\BF{I}$, and finally dot in the solutions to the
+surface integrals $\rT$.
 
@@
 As we discussed above, we perform the integration in a frame
-$\mathcal{F}_\mathrm{term}$
+$\mathcal{F}''$
 in which the semi-major axis of the terminator is aligned with the
-$x$-axis, with the illumination source at $y \ge 0$.
+$x''$-axis, with the illumination source at $y'' \ge 0$.
 The solution vector may then be computed from
@@
     \int_{-1}^{1}
-    \int_{b\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
-    \bp(x, y)
-    \ \dd y \ \dd x
+    \int_{b\sqrt{1 - x''^2}}^{\sqrt{1 - x''^2}}
+    \bp(x'', y'')
+    \ \dd y'' \ \dd x''
     \quad,
@@
     \int_{-1}^{1}
-    \int_{b\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
-    \bp(x, y)
+    \int_{b\sqrt{1 - x''^2}}^{\sqrt{1 - x''^2}}
+    \bp(x'', y'')
     \mathbf{I}(b, 0, r_s)
-    \ \dd y \ \dd x
+    \ \dd y'' \ \dd x''
     \quad,
@@
 %
-recalling that in frame $\mathcal{F}_\mathrm{term}$, $\theta = 0$ by
+recalling that in frame $\mathcal{F}''$, $\theta'' = 0$ by
 definition.
@@
     \BF{A_1}
-    \BF{R}'(-\theta)
+    \BF{R}''(x_s, y_s)
     \BF{R}(i, \lambda, \vartheta)
@@
 develop a procedure to identify the relevant case given the occultor
-position $(x_o, y_o)$ and radius $r_o$ and the terminator semi-minor
-axis $b$ and angle $\theta$. Then, once the case is determined, we must
+impact parameter $b_o$ and radius $r_o$ and the terminator semi-minor
+axis $b$ and angle $\theta'$ in the frame $\mathcal{F}'$.
+Then, once the case is determined, we must
 identify the relevant integration boundaries, which depend on the points
@@
 of the body, and if so, the points of intersection.
-Switching momentarily to the frame $\mathcal{F}_\mathrm{term}$,
-the equations defining the
-\begin{align}
-    y_1(x) & = b \sqrt{1 - x^2}
-    \nonumber                                       \\
-    y_2(x) & = y'_o \pm \sqrt{r_o^2 - (x - x'_o)^2}
-\end{align}
-%
-where $x'_o = $ and $y'_o = $ are the coordinates of the occultor in
-$\mathcal{F}_\mathrm{term}$.
-
-Recall that we perform the integration in frame
-$\mathcal{F}_\mathrm{greens}$, in which the occultor lies along the $+y$-axis
-at $(0, b_o)$, with $b_o = \sqrt{x_o^2 + y_o^2}$. In this frame, the
-semi-major axis of the terminator is at an angle $\theta$ with respect to the
-$+x$-axis (Equation~\ref{eq:theta}).
+While we perform the integration in frame $\mathcal{F}'$, finding the points
+of intersection with the terminator is easier if we temporarily switch to
+the frame $\mathcal{F}''$ (via Equation~\ref{eq:R''}) in which the terminator
+is parallel to the $x''$-axis.
+In this frame, the equations defining the terminator and the limb of the
+occultor are, respectively,
+%
+\begin{proof}{}
+    y''_1(x'') & = b \sqrt{1 - x''^2}
+    \nonumber                                               \\
+    y''_2(x'') & = y''_o \pm \sqrt{r_o^2 - (x'' - x''_o)^2}
+\end{proof}
+%
+where
+%
+\begin{proof}{}
+    x''_o = b_o\sin\theta'
+    \nonumber \\
+    y''_o = b_o\cos\theta'
+\end{proof}
+%
+are the coordinates of the occultor in $\mathcal{F}''$.
+%
+We wish to find the set of $N$ points
+$\{{x''}_n~\big|~0~\le~n~<~N\}$
+for which
+$y''_1(x_n'') - y''_2(x_n'') = 0$. Following \citet{Luger2017}, we may
+express this condition as the quartic equation
+%
+\begin{proof}{}
+    \label{eq:quartic}
+    A {x''}^4 + B {x''}^3 + C {x''}^2 + D {x''} + E = 0
+\end{proof}
+%
+with coefficients
+%
+\begin{proof}{}
+    \label{eq:quartic-coeffs}
+    A &= (1 - b^2)^2
+    \nonumber \\
+    B &= -4 x''_o (1 - b^2)
+    \nonumber \\
+    C &= -2 \bigg(
+    b^4
+    + r_o^2
+    - 3 {x''_o}^2
+    - {y''_o}^2
+    - b^2 \big(1 + r_o^2 - {x''_o}^2 + {y''_o}^2\big)
+    \bigg)
+    \nonumber \\
+    D &= -4 x''_o (b^2 - r_o^2 + {x''_o}^2 + {y''_o}^2)
+    \nonumber \\
+    E &=
+    b^4
+    - 2 b^2 \big(r_o^2 - {x''_o}^2 + {y''_o}^2\big)
+    + \big(r_o^2 - {x''_o}^2 - {y''_o}^2\big)^2
+    \quad.
+\end{proof}
+%
+Although closed-form solutions to quartic equations exist
+\citep[see, e.g.,][who solve for the area of overlap between two ellipses
+    analytically]{Hughes2011}, they are prone to significant numerical
+instabilities. Instead, we solve for the roots of the quartic
+numerically by casting it
+as an eigenvalue problem \citep[e.g.,][]{Edelman1995} and polish the
+results with a few iterations of Newton's method. We find that this is
+reasonably computationally efficient and
+yields roots with precision within a couple orders of magnitude of machine
+epsilon (see \S\ref{sec:performance}).
+
+In general, the quartic defined by Equation~(\ref{eq:quartic}) has
+$N=4$ (potentially degenerate) roots, some of which may be complex, and some
+of which correspond to intersections with the wrong half of the
+terminator ellipse (i.e., the section of the terminator on the far side
+of the body). After excluding the unphysical solutions, we are still left with
+anywhere between zero and four roots.
+
+\xxx{More here...}
 
@@
 %
+\xxx{This section needs to be revised.}
 Cases 1--4 (see Figure~\ref{fig:cases}) involve configurations in which the
@@
 \begin{align}
+    \label{eq:R''}
+    \BF{R}'' = ?
+\end{align}
+%
+\begin{align}
     \label{eq:A}
@@
 of the sky into the frame $\mathcal{F}'$ in which the integration is
-actually performed, with the occultor along the $+y$-axis.
+actually performed, with the occultor along the $+y'$-axis.
 For more information on all of these terms, the reader is referred to

### 2020-04-03 tex/figures/frames.py

@@ -217,83 +217,83 @@ ax = plt.subplot2grid((3, 7), (1, 5))
 ax.imshow(imgsky, **img_kw)
 plot_grid(ax, inc, obl, theta)
 add_basis(ax, r"$\tilde{y}$")
-add_frame(ax, r"$\mathcal{F}_\mathrm{sky}$")
+add_frame(ax, r"$\mathcal{F}$")
 add_terminator(ax, b, -np.arctan(ys / xs) * 180 / np.pi)
-axes.append(ax)
-
-# Top row
-ax = plt.subplot2grid((3, 7), (0, 4))
-ax.imshow(imgint, **img_kw)
-plot_grid(ax, inc, obl_int, theta)
-add_basis(ax, r"$\tilde{y}$")
-add_frame(ax, r"$\mathcal{F}_\mathrm{poly}$")
-add_terminator(ax, b, 0)
-axes.append(ax)
-
-ax = plt.subplot2grid((3, 7), (0, 3))
-ax.imshow(imgint, **img_kw)
-plot_grid(ax, inc, obl_int, theta)
-add_basis(ax, r"$\tilde{p}$")
-add_frame(ax, r"$\mathcal{F}_\mathrm{poly}$")
-add_terminator(ax, b, 0)
-axes.append(ax)
-
-ax = plt.subplot2grid((3, 7), (0, 2))
-ax.imshow(imgint, **img_kw)
-ax.imshow(fint, **flt_kw)
-plot_grid(ax, inc, obl_int, theta)
-add_basis(ax, r"$\tilde{p}$")
-add_frame(ax, r"$\mathcal{F}_\mathrm{poly}$")
-add_terminator(ax, b, 0)
-axes.append(ax)
-
-ax = plt.subplot2grid((3, 7), (0, 1))
-ax.text(
-    0.65, 0.5, r"$f$", transform=ax.transAxes, size=14, ha="center", va="center",
-)
-ax.imshow(imgint, alpha=0, **img_kw)
 axes.append(ax)
 
 # Bottom row
 ax = plt.subplot2grid((3, 7), (2, 4))
-ax.imshow(imggreens, **img_kw)
-plot_grid(ax, inc, obl_greens, theta)
+ax.imshow(imgint, **img_kw)
+plot_grid(ax, inc, obl_int, theta)
 add_basis(ax, r"$\tilde{y}$")
-add_frame(ax, r"$\mathcal{F}_\mathrm{greens}$")
[…]

### 2020-04-03 tex/figures/geometry.py

@@ -2,6 +2,17 @@ from code import visualize
 import numpy as np
 import matplotlib.pyplot as plt
 
+# DEBUG
+plt.switch_backend("MacOSX")
+b, theta, bo, ro = (
+    0.5488316824842527,
+    4.03591586925189,
+    0.34988513192814663,
+    0.7753986686719786,
+)
+fig, ax = visualize(b, theta, bo, ro)
+plt.show()
+quit()
 
 b = 0.5
 theta = 75 * np.pi / 180

### 2020-04-04 tex/ms.tex
slow progress

@@
 \begin{proof}{}
+    \label{eq:illum_poly}
     I(b, \theta, r_s; x, y) &= \frac{1}{4\pi r_s^2}
@@
         J_{\frac{\mu}{2}, \frac{\nu + 2}{2}} -
-        b I_\frac{\nu}{2}(b) K_{\frac{\mu}{2}, \frac{\nu}{2}}
+        b H_\frac{\nu}{2}(b) K_{\frac{\mu}{2}, \frac{\nu}{2}}
         %
@@
         b_c
-        I_{\frac{\nu + 1}{2}}(b) K_{\frac{\mu - 1}{2}, \frac{\nu + 1}{2}}
+        H_{\frac{\nu + 1}{2}}(b) K_{\frac{\mu - 1}{2}, \frac{\nu + 1}{2}}
         %
@@
 \label{sec:solution-occ}
+%
+The integration in the unocculted case presented above is relatively
+straightforward, since
+the boundaries of integration are always the half-ellipse defining the
+terminator and the half-circle defining the upper limb of the body
+(Equation~\ref{eq:rT}). When an occultor is present, however, the
+integration boundaries are far less trivial, since they may or may not
+include sections of the terminator, sections of the limb of the body,
+and sections of the limb of the occultor. There are in total eight families of
+configurations, each defined by a distinct combination of integration
+boundaries; these are shown in Figure~\ref{fig:cases}.
+Together, these cases encompass all possible
+occultation configurations, for any illumination angle, occultor size, and
+occultor position.
+
+Before we discuss how to compute the occultation integrals, we must first
+develop a procedure to identify the relevant case given the occultor
+impact parameter $b_o = \sqrt{x_o^2 + y_o^2}$ and radius $r_o$ and
+the terminator semi-minor
+axis $b$ and angle $\theta'$ in the frame $\mathcal{F}'$.
+Then, once the case is determined, we must
+identify the relevant integration boundaries, which depend on the points
+of intesection between the limb of the body, the limb of the occultor, and
+the terminator. We do so in the following sections.
+
+%
+
+\subsection{Case determination}
+\label{sec:which-case}
 
@@
             computed in terms of classical \starry integrals. The remaining
-            cases require integration along the red boundary (the curves
-            $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$ of
+            cases require integration along the orange boundary (the curves
+            $P$, $T$, and $Q$ of
             \S\ref{sec:cases-5-8}), which
@@
 
-The integration in the unocculted case presented above is relatively
-straightforward, since
-the boundaries of integration are always the half-ellipse defining the
-terminator and the half-circle defining the upper limb of the body
-(Equation~\ref{eq:rT}). When an occultor is present, however, the
-integration boundaries are far less trivial, since they may or may not
-include sections of the terminator, sections of the limb of the body,
-and sections of the limb of the occultor. There are in total eight families of
-configurations, each defined by a distinct combination of integration
-boundaries; these are shown in Figure~\ref{fig:cases}.
-Together, these cases encompass all possible
-occultation configurations, for any illumination angle, occultor size, and
-occultor position.
-
-Before we discuss how to compute the occultation integrals, we must first
-develop a procedure to identify the relevant case given the occultor
-impact parameter $b_o$ and radius $r_o$ and the terminator semi-minor
-axis $b$ and angle $\theta'$ in the frame $\mathcal{F}'$.
-Then, once the case is determined, we must
-identify the relevant integration boundaries, which depend on the points
-of intesection between the limb of the body, the limb of the occultor, and
-the terminator. We do so in the following section.
-
-\subsection{Case determination and integration boundaries}
-\label{sec:which-case}
-%
 The key to identifying the case corresponding to a given configuration is
@@
 We wish to find the set of $N$ points
-$\{{x''}_n~\big|~0~\le~n~<~N\}$
+$\{x_n''~\big|~0~\le~n~<~N\}$
 for which
@@
 
-\xxx{More here...}
+Cases with zero roots (case 1 -- case 4) are treated in \S\ref{sec:cases-1-4},
+while cases with one or two roots (case 5 -- case 8) are treated in
+\S\ref{sec:cases-5-8}. Cases with three or four roots
+(case 9 -- case 10) are rarely encountered
+in practice, but are possible for some pathological configurations; these are
+treated in \S\ref{sec:cases-9-10}.
+
+%
 
@@
 %
-\xxx{This section needs to be revised.}
 Cases 1--4 (see Figure~\ref{fig:cases}) involve configurations in which the
@@
 \begin{align}
-    \label{eq:sT1}
+    \label{eq:f1}
     f_1 = 0
@@
 \begin{align}
-    \label{eq:sT2}
+    \label{eq:f2}
     f_2 = f_0
@@
     \BF{A_2}
-    \BF{I}(b, \theta, r_s)
+    \BF{I}(b, \theta', r_s)
     \BF{A_1}
-    \BF{R}'(\omega)
+    \BF{R}'(x_o, y_o)
     \BF{R}(i, \lambda, \vartheta)
@@
 \emph{only} the day side of the body (regardless of whether or not it
-intersects with the limb):
-%
-\begin{proof}{}
-    \label{eq:sT4}
-    f_4 = f_3 + \hat{f}_0
-    \quad,
-\end{proof}
-%
-where we define
+intersects with the limb). We compute this by first weighting the solution
+for the occultation in emitted light by the intensity profile as in
+case 3. The flux $f_3$ obtained in this fashion contains the contribution
+from the entire nightside, which as we discuss above is unphysically weighted
+by the negative part of Equation~(\ref{eq:illum_poly}). We can compute what
+this contribution is from the complement of case 0:
 %
@@
     \hat{f}_0 & =
-    \BS{\rho}^\top(-b, r_s)
+    -\BS{\rho}^\top(-b, r_s)
     \BF{A_1}
-    \BF{R}'(-\theta - \pi)
+    \BF{R}''(-x_s, -y_s)
     \BF{R}(i, \lambda, \vartheta)
     \BF{y}
+    \quad,
+\end{proof}
+%
+i.e., the flux we would get if we placed a negative illumination source
+at the antipode $(-x_s, -y_s, -z_s)$ of the true source.
+The total flux in this case is thus
+%
+\begin{proof}{}
+    \label{eq:f4}
+    f_4 = f_3 - \hat{f}_0
     \quad.
@@
 %
-\xxx{Cases 5--8} (see Figure~\ref{fig:cases}, Figure~\ref{fig:geometry}).
-
-% case 5: sT0 - sT0 * I
-% case 6: (sTe + sT0) * I + ~sT0
-% case 7: (sTe - sT0) * I
-% case 8: sT0 * I
 
@@
             to case 5 in Figure~\ref{fig:cases}. The surface integral over
-            the blue region is computed from the antiderivatives of the
-            surface intensity map counter-clockwise along the boundary curves
-            $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$.
+            the occulted portion of the dayside (light gray region)
+            is computed from the line integrals of the antiderivatives of the
+            surface intensity map along the boundary curves
+            $P$, $T$, and $Q$. See text for details.
             \label{fig:geometry}
@@
 \end{figure}
+
+Cases 5--8 (see Figure~\ref{fig:cases}) correspond to configurations in which
+the limb of the occultor intersects with the terminator at either one point
+(case 5) or two points (cases 6, 7, and 8). Because of these intersections, we
+cannot simply re-weight the emitted light solution, as the integration
+boundaries are now different. In general, we may compute the flux by
+integrating the components of the Green's basis $\bg$
+over the region $S$ bounded by three curves, which we denote
+$P$, $T$, and $Q$. These are shown in orange
+in Figure~\ref{fig:cases} and presented in more detail in
+Figure~\ref{fig:geometry}.
+Curve $P$ is a segment of the limb of
+the occultor, parametrized by the angle $\phi \in [\phi_1, \phi_2]$;
+curve $T$ is a segment of the terminator,
+parametrized by the angle $\xi \in [\xi_1, \xi_2]$;
+and curve $Q$ is a segment of the limb of the occulted body,
+parametrized by the angle $\lambda \in [\lambda_1, \lambda_2]$.
+The endpoints $\phi_1, \phi_2, \xi_1, \xi_2, \lambda_1,$ and
+$\lambda_2$ are functions of the solutions to the quartic from
+\S\ref{sec:which-case} and will be presented below.
+
+As in \citet{Luger2019}, the approach to computing the surface integrals
+of each of the terms in $\bg$ over $S$
+is to use Green's theorem to transform them into line integrals along the
+curves $P$, $T$, and $Q$. Let $\mathfrak{p}^\top$,
+$\mathfrak{t}^\top$, and $\mathfrak{q}^\top$ denote the vectors
+corresponding to the line integrals
+along the curves $P$, $T$, and $Q$, respectively, for each of the terms in
+$\bg$. The integration is performed in the frame $\mathcal{F}'$,
+in a counter-clockwise direction relative to the center
+of the integration region $S$.
+Then the integral of $\bg$ over $S$ is%
+\footnote{%
+    The components of the vectors $\mathfrak{p}^\top$ and
+    $\mathfrak{q}^\top$ are analogous to the ``primitive integrals''
+    $\mathcal{P}$ and $\mathcal{Q}$
+    defined in Equations~(30)--(32) in \citet{Luger2019}, although the
+    integration limits of both and the sense of integration of $\mathcal{P}$
+    are different.
+}
+%
+\begin{align}
+    \label{eq:sT}
+    \sT & =
+    \mathfrak{p}^\top + \mathfrak{t}^\top + \mathfrak{q}^\top
+    \quad,
+\end{align}
+%
+where the dependence on $b, \theta', b_o,$ and $r_o$ is implicit.
+%
+We defer the solution to Equation~(\ref{eq:sT}) to \S\ref{sec:sT} below,
+as it is quite lengthy. Given $\sT$, the flux $f_S$ over the integration
+region $S$ is computed from Equation~(\ref{eq:sTA2IA1RRy}):
+%
+\begin{align}
+    f_S & =
+    \mathfrak{s}^\top(b, \theta', b_o, r_o)
+    \BF{A_2}
+    \BF{I}(b, \theta', r_s)
+    \BF{A_1}
+    \BF{R}'(x_o, y_o)
+    \BF{R}(i, \lambda, \vartheta)
+    \BF{y}
+    \quad.
+\end{align}
+%
+Note that this is not necessarily the \emph{observed} flux, which we must
+compute on a case-by-case basis below.
+
+Case 5 corresponds to configurations in which the limb of the occultor
+intersects the terminator at a single point. The integration region
+(see Figures~\ref{fig:cases} and \ref{fig:geometry}) is the occulted
+portion of the dayside, which is bounded by all three curves $P$, $Q$, and $T$.
+The total flux may
+be computed by subtracting the occulted flux $f_S$ from the total dayside
+flux $f_0$:
+%
+\begin{proof}{}
+    \label{eq:f5}
+    f_5 = f_0 - f_S
+    \quad.
+\end{proof}
+%
+Cases 6--8 involve two points of intersection between the occultor limb and
+the terminator. Case 6 corresponds to occultors that block some of the
+nightside and some of the dayside, regardless of whether the occultor
+is fully within the disk of the occulted body. We begin by computing the
+flux over the unocculted region, $f_3$, which includes the spurious
+nightside contribution. We then remove this contribution by noting that it
+is equal to the total nightside contribution, $\hat{f}_0$, minus the
+occulted nightside flux, $f_S$:
+%
+\begin{proof}{}
+    \label{eq:f6}
+    f_6 = f_3 - (\hat{f}_0 - f_S)
+    \quad.
+\end{proof}
+%
+Case 7 corresponds to occultors that \xxx{what?}
+%
+\begin{proof}{}
+    \label{eq:7}
+    f_7 = f_3 - f_S
+    \quad.
+\end{proof}
+%
+Finally, case 8 corresponds to occultors that \xxx{what?}
+%
+\begin{proof}{}
+    \label{eq:f8}
+    f_8 = f_S
+    \quad.
+\end{proof}
+%
+
+\subsection{Cases 9--10}
+\label{sec:cases-9-10}
+%
+Pathological cases with 3 or 4 roots here.
+
+%
+
+\subsection{Computing the integrals $\sT$}
+\label{sec:sT}
+\xxx{This is going to be be painful.}
 

### 2020-04-04 tex/figures/code/viz.py

@@ -223,14 +223,14 @@ def visualize(b, theta, bo, ro, res=4999):
     if len(lam):
         fig, ax = plt.subplots(1, 3, figsize=(14, 5))
         fig.subplots_adjust(left=0.025, right=0.975, bottom=0.05, top=0.825)
-        ax[1].set_title(r"$\mathcal{T}$", color="C1", fontsize=24)
-        ax[0].set_title(r"$\mathcal{P}$", color="C1", fontsize=24)
-        ax[2].set_title(r"$\mathcal{Q}$", color="C1", fontsize=24)
+        ax[1].set_title(r"$T$", color="C1", fontsize=24)
+        ax[0].set_title(r"$P$", color="C1", fontsize=24)
+        ax[2].set_title(r"$Q$", color="C1", fontsize=24)
     else:
         fig, ax = plt.subplots(1, 2, figsize=(9, 5))
         fig.subplots_adjust(left=0.025, right=0.975, bottom=0.05, top=0.825)
-        ax[1].set_title(r"$\mathcal{T}$", color="C1", fontsize=24)
-        ax[0].set_title(r"$\mathcal{P}$", color="C1", fontsize=24)
+        ax[1].set_title(r"$T$", color="C1", fontsize=24)
+        ax[0].set_title(r"$P$", color="C1", fontsize=24)
 
     # Labels
     for i in range(len(phi)):
@@ -266,7 +266,7 @@ def visualize(b, theta, bo, ro, res=4999):
     # Draw basic shapes
     for axis in ax:
         axis.axis("off")
-        axis.add_artist(plt.Circle((0, bo), ro, fill=False))
+        axis.add_artist(plt.Circle((0, bo), ro, lw=1.5, ls="--", fill=False))
         axis.add_artist(plt.Circle((0, 0), 1, fill=False))
         axis.plot(x_t, y_t, "k-", lw=1)
         axis.set_xlim(-1.25, 1.25)

### 2020-04-04 tex/figures/geometry.py

@@ -2,17 +2,6 @@ from code import visualize
 import numpy as np
 import matplotlib.pyplot as plt
 
-# DEBUG
-plt.switch_backend("MacOSX")
-b, theta, bo, ro = (
-    0.5488316824842527,
-    4.03591586925189,
-    0.34988513192814663,
-    0.7753986686719786,
-)
-fig, ax = visualize(b, theta, bo, ro)
-plt.show()
-quit()
 
 b = 0.5
 theta = 75 * np.pi / 180

### 2020-04-05 tex/ms.tex
better

@@
 %
+Finally, for future reference, we can also compute what we will call the
+\emph{complement} of case 0:
+%
+\begin{proof}{}
+    \label{eq:f0hat}
+    \hat{f}_0 & =
+    -\BS{\rho}^\top(-b, r_s)
+    \BF{A_1}
+    \BF{R}''(-x_s, -y_s)
+    \BF{R}(i, \lambda, \vartheta)
+    \BF{y}
+    \quad,
+\end{proof}
+%
+This is the flux we would get if we placed a \emph{negative} illumination
+source at the antipode $(-x_s, -y_s, -z_s)$ of the true source, and
+will be useful in negating the unphysical negative contribution from our
+polynomial illumination function (Equation~\ref{eq:illum_poly}) in
+the following section.
 
@@
 the terminator of the occulted body, and are therefore fairly
-straightforward to solve.
-%
-Case 1 corresponds to any complete occultation of the body, so the
-solution for the flux is trivial:
-%
-\begin{align}
-    \label{eq:f1}
-    f_1 = 0
-    \quad.
-\end{align}
-%
-Case 2 involves any occultation in which the occultor blocks \emph{only} the
-night side of the body (regardless of whether or not it intersects with the
-limb of the body). Since the night side intensity is zero everywhere, this case
-is also trivial, as the flux is equal to the flux in the no occultation case
-(Equation~\ref{eq:f0}):
-%
-\begin{align}
-    \label{eq:f2}
-    f_2 = f_0
-    \quad.
-\end{align}
-%
-Case 3 corresponds to occultations in which the occultor blocks \emph{all} of
-the night side of the body and \emph{some} of the day side. In this
-configuration, the unocculted part of the disk consists only of dayside.
-Since we have no intersections with the terminator to worry about,
-we may compute the total flux using the \starry formalism from
-\citet{Luger2019}, provided we weight the intensity map by the illumination
-field:
-%
-\begin{proof}{}
-    \label{eq:f3}
-    f_3 = \sTe(b_o, r_o)
+straightforward to solve. In particular, we can use the original emitted
+light solution from \citet{Luger2019}, provided we weight the map by our
+polynomial illumination function:
+%
+\begin{proof}{}
+    \label{eq:fI}
+    f_I &=
+    \sTe(b_o, r_o)
     \BF{A_2}
@@
     \BF{y}
-    \quad.
+    \quad,
+\end{proof}
+%
+where $\sTe(b_o, r_o)$ is the emitted light solution vector
+\citep[Equation~26 in][]{Luger2019}. The flux $f_I$ is the flux one would
+measure from a body whose surface map is weighted by the illumination function
+$\BF{I}(b, \theta', r_s)$ during an occultation. Note that this is not
+necessarily the \emph{observed} flux, since this may include the unphysical
+negative contribution from the nightside. We must compute the actual
+observed flux on a case-by-case basis.
+
+Case 1 corresponds to any complete occultation of the body
+($b_o \le r_o - 1$), so the solution for the flux is trivial:
+%
+\begin{align}
+    \label{eq:f1}
+    f_1 = 0
+    \quad.
+\end{align}
+%
+Case 2 involves any occultation in which the occultor blocks \emph{only} the
+night side of the body (regardless of whether or not it intersects with the
+limb of the body). Since the night side intensity is zero everywhere, this case
+is also trivial, as the flux is equal to the flux in the no occultation case
+(Equation~\ref{eq:f0}):
+%
+\begin{align}
+    \label{eq:f2}
+    f_2 = f_0
+    \quad.
+\end{align}
+%
+Case 3 corresponds to occultations in which the occultor blocks \emph{all} of
+the night side of the body and \emph{some} of the day side. In this
+configuration, the unocculted part of the disk consists only of dayside, and
+we can simply use the weighted solution in emitted light
+(Equation~\ref{eq:fI}):
+%
+\begin{proof}{}
+    \label{eq:f3}
+    f_3 = f_\mathrm{I}
 \end{proof}
@@
 \emph{only} the day side of the body (regardless of whether or not it
-intersects with the limb). We compute this by first weighting the solution
-for the occultation in emitted light by the intensity profile as in
-case 3. The flux $f_3$ obtained in this fashion contains the contribution
-from the entire nightside, which as we discuss above is unphysically weighted
-by the negative part of Equation~(\ref{eq:illum_poly}). We can compute what
-this contribution is from the complement of case 0:
-%
-\begin{proof}{}
-    \label{eq:f0hat}
-    \hat{f}_0 & =
-    -\BS{\rho}^\top(-b, r_s)
-    \BF{A_1}
-    \BF{R}''(-x_s, -y_s)
-    \BF{R}(i, \lambda, \vartheta)
-    \BF{y}
-    \quad,
-\end{proof}
-%
-i.e., the flux we would get if we placed a negative illumination source
-at the antipode $(-x_s, -y_s, -z_s)$ of the true source.
-The total flux in this case is thus
+intersects with the limb). We first compute the illumination-weighted flux
+$f_I$ as above, then negate the unphysical nightside contribution
+using Equation~(\ref{eq:f0hat}):
 %
@@
     \label{eq:f4}
-    f_4 = f_3 - \hat{f}_0
+    f_4 = f_I - \hat{f}_0
     \quad.
@@
 \begin{align}
+    \label{eq:fS}
     f_S & =
@@
 %
-Note that this is not necessarily the \emph{observed} flux, which we must
+Note again that this is not necessarily the \emph{observed} flux, which we must
 compute on a case-by-case basis below.
@@
 the terminator. Case 6 corresponds to occultors that block some of the
-nightside and some of the dayside, regardless of whether the occultor
-is fully within the disk of the occulted body. We begin by computing the
+nightside and some of the dayside, but \emph{neither} of the extrema of the
+terminator ellipse. We begin by computing the
 flux over the unocculted region, $f_3$, which includes the spurious
@@
     \label{eq:f6}
-    f_6 = f_3 - (\hat{f}_0 - f_S)
-    \quad.
-\end{proof}
-%
-Case 7 corresponds to occultors that \xxx{what?}
+    f_6 = f_I - (\hat{f}_0 - f_S)
+    \quad.
+\end{proof}
+%
+Cases 7 and 8 correspond to occultors that also block some nightside and some
+dayside, along with \emph{both} of the extrema of the ellipse; these are
+therefore exclusively for large occultors ($r_o > 1$). Case 7
+involves occultations in which only a small lens-shaped region of the
+nightside is visible. The total flux is the visible dayside plus unphysical
+nightside contribution, $f_I$, minus the nightside contribution, which we
+compute from Equation~(\ref{eq:fS}):
 %
@@
     \label{eq:7}
-    f_7 = f_3 - f_S
-    \quad.
-\end{proof}
-%
-Finally, case 8 corresponds to occultors that \xxx{what?}
+    f_7 = f_I - f_S
+    \quad.
+\end{proof}
+%
+Conversely, case 8 involves occultations in which only a small lens-shaped
+region of the dayside is visible. In this case, we may compute the observed
+flux from Equation~(\ref{eq:fS}) directly:
 %
@@
 \label{sec:cases-9-10}
-%
-Pathological cases with 3 or 4 roots here.
+
+\begin{figure}[t!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/pathological.pdf}
+        \oscaption{pathological}{%
+            Two additional families of occultations in reflected light,
+            involving rare triple (case 9, left) and quadruple
+            (case 10, right) intersections between the limb of the
+            occultor and the terminator of the occulted body. Both cases
+            involve integration over two disjoint regions (bounded by
+            the orange curves in the figure). The insets next to each case
+            show a zoomed-in version of two such regions. See text for
+            more details.
+            \label{fig:pathological}
+        }
+    \end{centering}
+\end{figure}
+
+Pathological cases with 3 or 4 roots here (Figure~\ref{fig:pathological}).
 

### 2020-04-05 tex/figures/code/viz.py

@@ -13,7 +13,12 @@ def visualize_simple(ax, b, theta, bo, ro, res=4999):
     phi = kappa - np.pi / 2
 
     # HACK
-    if code == FLUX_NIGHT_VIS or code == FLUX_DAY_VIS:
+    if (
+        code == FLUX_NIGHT_VIS
+        or code == FLUX_DAY_VIS
+        or code == FLUX_QUAD_DAY_VIS
+        or code == FLUX_QUAD_NIGHT_VIS
+    ):
         phi = phi[::-1]
 
     color_night = (0, 0, 0, 0.75)
@@ -110,10 +115,21 @@ def visualize_simple(ax, b, theta, bo, ro, res=4999):
     # Draw integration paths
     # T
     if len(xi):
-        if code == FLUX_NIGHT_VIS or code == FLUX_DAY_VIS:
-            inds = x_t ** 2 + (y_t - bo) ** 2 > ro ** 2
+        if (
+            code == FLUX_NIGHT_VIS
+            or code == FLUX_DAY_VIS
+            or code == FLUX_QUAD_DAY_VIS
+            or code == FLUX_QUAD_NIGHT_VIS
+        ):
+            inds = np.where(x_t ** 2 + (y_t - bo) ** 2 > ro ** 2)[0]
+            if code == FLUX_QUAD_DAY_VIS or code == FLUX_QUAD_NIGHT_VIS:
+                midpt = np.arange(len(x_t))[inds[1:]][np.diff(inds) > 1][0]
+                x_t[midpt] = np.nan
         else:
-            inds = x_t ** 2 + (y_t - bo) ** 2 < ro ** 2
+            inds = np.where(x_t ** 2 + (y_t - bo) ** 2 < ro ** 2)[0]
+            if code == FLUX_TRIP_DAY_OCC or code == FLUX_TRIP_NIGHT_OCC:
+                midpt = np.arange(len(x_t))[inds[1:]][np.diff(inds) > 1][0]
+                x_t[midpt] = np.nan
         ax.plot(x_t[inds], y_t[inds], "C1-", lw=2)
 
     if len(phi):

### 2020-04-05 tex/figures/pathological.py

@@ -1,0 +1,66 @@
+from code import *
+import numpy as np
+import matplotlib.pyplot as plt
+
+# DEBUG
+plt.switch_backend("MacOSX")
+
+# Setup figure
+fig, ax = plt.subplots(1, 4, figsize=(12, 3))
+
+# Case 9
+visualize_simple(
+    ax[0], 0.5488316824842527, 4.03591586925189, 0.34988513192814663, 0.7753986686719786
+)
+axins0 = ax[0].inset_axes([1.15, 0.0, 1.0, 1.0])
+visualize_simple(
+    axins0,
+    0.5488316824842527,
+    4.03591586925189,
+    0.34988513192814663,
+    0.7753986686719786,
+)
+axins0.axis("on")
+ax[1].set_visible(False)
+x1, x2, y1, y2 = 0.6, 0.7, 0.7, 0.8
+axins0.set_xlim(x1, x2)
+axins0.set_ylim(y1, y2)
+axins0.set_xticks([])
+axins0.set_yticks([])
+rectangle_patch, connector_lines = ax[0].indicate_inset_zoom(axins0)
+rectangle_patch.set_ec("k")
+for line in connector_lines:
+    line.set_ec("k")
+
+# Case 10
+visualize_simple(ax[2], 0.5, np.pi, 0.99, 1.5)
+axins1 = ax[2].inset_axes([1.15, 0.0, 1.0, 1.0])
+visualize_simple(axins1, 0.5, np.pi, 0.99, 1.5)
+axins1.axis("on")
+ax[3].set_visible(False)
+x1, x2, y1, y2 = 0.25, 1.0, -0.625, 0.125
+axins1.set_xlim(x1, x2)
+axins1.set_ylim(y1, y2)
+axins1.set_xticks([])
+axins1.set_yticks([])
+rectangle_patch, connector_lines = ax[2].indicate_inset_zoom(axins1)
+rectangle_patch.set_ec("k")
+for line in connector_lines:
+    line.set_ec("k")
+
+# Appearance
+for i, axis in enumerate([ax[0], ax[2]]):
+    axis.axis("off")
+    axis.annotate(
+        "case {}".format(i + 9),
+        xy=(0.5, 0.0),
+        xycoords="axes fraction",
+        xytext=(0, 0),
+        textcoords="offset points",
+        ha="center",
+        va="top",
+        fontsize=10,
+    )
+    axis.set_rasterization_zorder(0)
+
+fig.savefig("pathological.pdf", bbox_inches="tight", dpi=300)

### 2020-04-06 tex/ms.tex
fix backend

@@
 include sections of the terminator, sections of the limb of the body,
-and sections of the limb of the occultor. There are in total eight families of
+and sections of the limb of the occultor. There are in total ten families of
 configurations, each defined by a distinct combination of integration
-boundaries; these are shown in Figure~\ref{fig:cases}.
+boundaries; these are shown in Figures~\ref{fig:cases} and
+\ref{fig:pathological}.
 Together, these cases encompass all possible
@@
 occultor position.
+
+\xxx{In general, we do not just integrate over the dayside.}
 
@@
         \oscaption{cases}{%
-            The eight families of cases of occultations in reflected light.
+            The eight principal families of cases of occultations in
+            reflected light.
             In these figures, the body with the solid outline
@@
 Cases 6--8 involve two points of intersection between the occultor limb and
-the terminator. Case 6 corresponds to occultors that block some of the
+the terminator. The region we integrate over is bounded only by the terminator
+and the limb of the occultor, so when computing $f_S$ below we set
+$\mathfrak{q}^\top = \boldsymbol{0}$.
+%
+Case 6 corresponds to occultors that block some of the
 nightside and some of the dayside, but \emph{neither} of the extrema of the
@@
 
-Pathological cases with 3 or 4 roots here (Figure~\ref{fig:pathological}).
+Finally, cases 9 and 10 correspond to (rare) configurations involving three
+or four roots to Equation~\ref{eq:quartic}, respectively, and are
+illustrated in Figure~\ref{fig:pathological}.
 

### 2020-04-06 tex/figures/pathological.py

@@ -2,9 +2,6 @@ from code import *
 import numpy as np
 import matplotlib.pyplot as plt
 
-# DEBUG
-plt.switch_backend("MacOSX")
-
 # Setup figure
 fig, ax = plt.subplots(1, 4, figsize=(12, 3))
 

### 2020-04-06 tex/ms.tex
finished casses

@@
 include sections of the terminator, sections of the limb of the body,
-and sections of the limb of the occultor. There are in total ten families of
+and sections of the limb of the occultor. There are in total 14 families of
 configurations, each defined by a distinct combination of integration
@@
         \oscaption{cases}{%
-            The eight principal families of cases of occultations in
+            The 10 principal families of cases of occultations in
             reflected light.
@@
             dashed outline is the occultor.
-            The night side of the occulted body is colored
+            The nightside of the occulted body is colored
             black (dark grey if occulted), and the dayside is colored blue
-            (light grey if occulted).
-            The cases in the top row involve
+            (bluish-grey if occulted).
+            Case 0 is the unocculted case (\S\ref{sec:solution-no-occ}),
+            while cases 1--5 involve
             configurations in which the limb of the occultor does not intersect
@@
             $P$, $T$, and $Q$ of
-            \S\ref{sec:cases-5-8}), which
+            \S\ref{sec:cases-hard}), which
             include the terminator. These involve the evaluation of incomplete
@@
 
-Cases with zero roots (case 1 -- case 4) are treated in \S\ref{sec:cases-1-4},
+Cases with zero roots (case 1 -- case 4) are treated in \S\ref{sec:cases-easy},
 while cases with one or two roots (case 5 -- case 8) are treated in
-\S\ref{sec:cases-5-8}. Cases with three or four roots
+\S\ref{sec:cases-hard}. Cases with three or four roots
 (case 9 -- case 10) are rarely encountered
 in practice, but are possible for some pathological configurations; these are
-treated in \S\ref{sec:cases-9-10}.
-
-%
-
-\subsection{Cases 1--4}
-\label{sec:cases-1-4}
-%
-Cases 1--4 (see Figure~\ref{fig:cases}) involve configurations in which the
+treated in \S\ref{sec:cases-pathological}.
+
+%
+
+\subsection{Cases 1--5}
+\label{sec:cases-easy}
+%
+Cases 1--5 (see Figure~\ref{fig:cases}) involve configurations in which the
 occultor does not intersect with
@@
 %
-Case 2 involves any occultation in which the occultor blocks \emph{only} the
-night side of the body (regardless of whether or not it intersects with the
-limb of the body). Since the night side intensity is zero everywhere, this case
+Case 2 corresponds to occultations in which the occultor blocks \emph{all} of
+the dayside of the body and \emph{some} of the nightside. In this
+configuration, the unocculted part of the disk consists only of nightside, so
+the solution is again trivial:
+%
+\begin{align}{}
+    \label{eq:f2}
+    f_2 = 0
+    \quad.
+\end{align}
+%
+Conversely, case 3 corresponds to occultations in which the occultor blocks
+\emph{all} of the nightside of the body and \emph{some} of the dayside.
+Since the visible portion of the disk consistss only of dayside, we can
+simply use the weighted solution in emitted light
+(Equation~\ref{eq:fI}):
+%
+\begin{proof}{}
+    \label{eq:f3}
+    f_3 = f_\mathrm{I}
+\end{proof}
+%
+Case 4 involves any occultation in which the occultor blocks \emph{only} the
+nightside of the body (regardless of whether or not it intersects with the
+limb of the body). Since the nightside intensity is zero everywhere, this case
 is also trivial, as the flux is equal to the flux in the no occultation case
@@
 \begin{align}
-    \label{eq:f2}
+    \label{eq:f4}
     f_2 = f_0
@@
 %
-Case 3 corresponds to occultations in which the occultor blocks \emph{all} of
-the night side of the body and \emph{some} of the day side. In this
-configuration, the unocculted part of the disk consists only of dayside, and
-we can simply use the weighted solution in emitted light
-(Equation~\ref{eq:fI}):
-%
-\begin{proof}{}
-    \label{eq:f3}
-    f_3 = f_\mathrm{I}
-\end{proof}
-%
-Finally, case 4 involves any occultation in which the occultor blocks
-\emph{only} the day side of the body (regardless of whether or not it
+Finally, case 5 involves any occultation in which the occultor blocks
+\emph{only} the dayside of the body (regardless of whether or not it
 intersects with the limb). We first compute the illumination-weighted flux
@@
 \begin{proof}{}
-    \label{eq:f4}
-    f_4 = f_I - \hat{f}_0
-    \quad.
-\end{proof}
-
-%
-
-\subsection{Cases 5--8}
-\label{sec:cases-5-8}
+    \label{eq:f5}
+    f_5 = f_I - \hat{f}_0
+    \quad.
+\end{proof}
+
+%
+
+\subsection{Cases 6--10}
+\label{sec:cases-hard}
 %
@@
             Geometry of an occultation in reflected light, corresponding
-            to case 5 in Figure~\ref{fig:cases}. The surface integral over
-            the occulted portion of the dayside (light gray region)
+            to case 6 in Figure~\ref{fig:cases}. The surface integral over
+            the occulted portion of the dayside (bluish-grey region)
             is computed from the line integrals of the antiderivatives of the
@@
 
-Cases 5--8 (see Figure~\ref{fig:cases}) correspond to configurations in which
+Cases 6--10 (see Figure~\ref{fig:cases}) correspond to configurations in which
 the limb of the occultor intersects with the terminator at either one point
-(case 5) or two points (cases 6, 7, and 8). Because of these intersections, we
+(case 6) or two points (cases 7--10). Because of these intersections, we
 cannot simply re-weight the emitted light solution, as the integration
@@
 corresponding to the line integrals
-along the curves $P$, $T$, and $Q$, respectively, for each of the terms in
-$\bg$. The integration is performed in the frame $\mathcal{F}'$,
+along the curves $P$, $T$, and $Q$, respectively, of the anti-exterior
+derivatives of each of the terms in
+$\bg$ (see Appendix~\ref{sec:sT}).
+The integration is performed in the frame $\mathcal{F}'$,
 in a counter-clockwise direction relative to the center
@@
     defined in Equations~(30)--(32) in \citet{Luger2019}, although the
-    integration limits of both and the sense of integration of $\mathcal{P}$
+    integration limits of both (and the sense of integration of $\mathcal{P}$)
     are different.
@@
 
-Case 5 corresponds to configurations in which the limb of the occultor
+Case 6 corresponds to configurations in which the limb of the occultor
 intersects the terminator at a single point. The integration region
@@
 \begin{proof}{}
-    \label{eq:f5}
-    f_5 = f_0 - f_S
-    \quad.
-\end{proof}
-%
-Cases 6--8 involve two points of intersection between the occultor limb and
+    \label{eq:f6}
+    f_6 = f_0 - f_S
+    \quad.
+\end{proof}
+%
+Cases 7--10 involve two points of intersection between the occultor limb and
 the terminator. The region we integrate over is bounded only by the terminator
@@
 %
-Case 6 corresponds to occultors that block some of the
+Cases 7 and 8 correspond to occultors that block some of the
 nightside and some of the dayside, but \emph{neither} of the extrema of the
-terminator ellipse. We begin by computing the
-flux over the unocculted region, $f_3$, which includes the spurious
+terminator ellipse. In case 7 a lens-shaped region is formed by the
+intersection of the occultor limb and the terminator on the
+\emph{nightside}, while in case 8 this region is formed on the \emph{dayside}.
+%
+In case 7, we begin by computing the
+flux over the unocculted region, $f_I$, which includes the spurious
 nightside contribution. We then remove this contribution by noting that it
@@
 \begin{proof}{}
-    \label{eq:f6}
-    f_6 = f_I - (\hat{f}_0 - f_S)
-    \quad.
-\end{proof}
-%
-Cases 7 and 8 correspond to occultors that also block some nightside and some
+    \label{eq:f7}
+    f_7 = f_I - (\hat{f}_0 - f_S)
+    \quad.
+\end{proof}
+%
+Case 8, on the other hand, is topologically equivalent to case 6, since
+the integration region consists of occulted dayside:
+%
+\begin{proof}{}
+    \label{eq:f8}
+    f_8 = f_0 - f_S
+    \quad.
+\end{proof}
+%
+Cases 9 and 10 correspond to occultors that also block some nightside and some
 dayside, along with \emph{both} of the extrema of the ellipse; these are
-therefore exclusively for large occultors ($r_o > 1$). Case 7
+therefore exclusively for large occultors ($r_o > 1$). Case 9
 involves occultations in which only a small lens-shaped region of the
@@
 \begin{proof}{}
-    \label{eq:7}
-    f_7 = f_I - f_S
-    \quad.
-\end{proof}
-%
-Conversely, case 8 involves occultations in which only a small lens-shaped
+    \label{eq:f9}
+    f_9 = f_I - f_S
+    \quad.
+\end{proof}
+%
+Conversely, case 10 involves occultations in which only a small lens-shaped
 region of the dayside is visible. In this case, we may compute the observed
@@
 \begin{proof}{}
-    \label{eq:f8}
-    f_8 = f_S
-    \quad.
-\end{proof}
-%
-
-\subsection{Cases 9--10}
-\label{sec:cases-9-10}
+    \label{eq:f10}
+    f_{10} = f_S
+    \quad.
+\end{proof}
+%
+
+\subsection{Cases 11--14}
+\label{sec:cases-pathological}
 
@@
         \oscaption{pathological}{%
-            Two additional families of occultations in reflected light,
-            involving rare triple (case 9, left) and quadruple
-            (case 10, right) intersections between the limb of the
-            occultor and the terminator of the occulted body. Both cases
+            Four additional families of occultations in reflected light,
+            involving rare triple (cases 11 and 12, top) and quadruple
+            (cases 13 and 14, bottom) intersections between the limb of the
+            occultor and the terminator of the occulted body. All four cases
             involve integration over two disjoint regions (bounded by
             the orange curves in the figure). The insets next to each case
-            show a zoomed-in version of two such regions. See text for
+            show a zoomed-in version of four such regions. See text for
             more details.
@@
 
-Finally, cases 9 and 10 correspond to (rare) configurations involving three
-or four roots to Equation~\ref{eq:quartic}, respectively, and are
-illustrated in Figure~\ref{fig:pathological}.
-
+Cases 11--14 correspond to (rare) configurations involving three
+or four roots to Equation~\ref{eq:quartic} and are
+illustrated in Figure~\ref{fig:pathological}. All four involve integration over
+two disjoint regions (see the figure).
+%
+Cases 11 and 12 involve three points of intersection between the terminator
+and the occultor limb. In case 11, the regions of integration $S_1$ and
+$S_2$ are the
+occulted portion of the dayside, so the solution is similar to
+that of cases 6 and 8:
+%
+\begin{proof}{}
+    \label{eq:f11}
+    f_{11} = f_0 - (f_{S_1} + f_{S_2})
+    \quad,
+\end{proof}
+%
+where $f_{S_1}$ and $f_{S_2}$ are computed from Equation~(\ref{eq:fS}) for
+each of the integration regions. Conversely, in case 12 the two regions
+are the occulted portion of the nightside, so the solution is similar to that
+of case 7:
+%
+\begin{proof}{}
+    \label{eq:f12}
+    f_{12} = f_I - \big(\hat{f}_0 - (f_{S_1} + f_{S_2})\big)
+    \quad,
+\end{proof}
+%
+Finally, cases 13 and 14 involve four points of intersection between the
+terminator and the occultor limb. The regions of integration in case 13 are
+the visible portion of the nightside, so this case is equivalent to case 9:
+%
+\begin{proof}{}
+    \label{eq:f13}
+    f_{13} = f_I - (f_{S_1} + f_{S_2})
+    \quad.
+\end{proof}
+%
+Conversely, the regions of integration in case 14 are the
+visible portion of the dayside, so this case is equivalent to case 10:
+%
+\begin{proof}{}
+    \label{eq:f14}
+    f_{14} = (f_{S_1} + f_{S_2})
+    \quad.
+\end{proof}
 %

### 2020-04-06 tex/figures/cases.py

@@ -3,32 +3,53 @@ import numpy as np
 import matplotlib.pyplot as plt
 
 # Setup figure
-fig, ax = plt.subplots(2, 4, figsize=(12, 5))
+fig, ax = plt.subplots(3, 4, figsize=(12, 8))
 ax = ax.flatten()
 
+# Legend
+ax[11].plot([0, 1], [0, 0], color="C0", lw=8, alpha=0.75, label="dayside")
+ax[11].plot(
+    [0, 1],
+    [0, 0],
+    color=(0.314, 0.431, 0.514),
+    lw=8,
+    alpha=0.5,
+    label="occulted dayside",
+)
+ax[11].plot([-1, 1], [0, 0], color="k", alpha=0.75, lw=8, label="nightside")
+ax[11].plot([0, 1], [0, 0], color="k", alpha=0.5, lw=8, label="occulted nightside")
+ax[11].plot([0, 1], [0, 0], color="k", lw=2, ls="--", label="occultor limb")
+ax[11].plot([0, 1], [0, 0], color="C1", lw=2, label="integration boundary")
+ax[11].set_ylim(1, 2)
+ax[11].legend(loc="center", fontsize=10, frameon=False)
+
 # Cases
-visualize_simple(ax[0], 0.5, 75 * np.pi / 180, 0, 1.1)
-visualize_simple(ax[1], 0.5, 75 * np.pi / 180, 0, 0.25)
-visualize_simple(ax[2], -0.25, np.pi, 0.15, 1.05)
-visualize_simple(ax[3], 0.25, 10 * np.pi / 180, 0.8, 0.3)
-visualize_simple(ax[4], 0.5, 75 * np.pi / 180, 0.5, 0.7)
-visualize_simple(ax[5], 0.5, -10 * np.pi / 180, 0.5, 0.7)
-visualize_simple(ax[6], 0.5, np.pi, 4.65, 5.0)
-visualize_simple(ax[7], -0.5, 0, 4.65, 5.0)
+visualize_simple(ax[0], 0.5, 75 * np.pi / 180, 0, 0.0)
+visualize_simple(ax[1], 0.5, 75 * np.pi / 180, 0, 1.1)
+visualize_simple(ax[2], -0.25, 0, 0.175, 1.05)
+visualize_simple(ax[3], 0.25, np.pi, 0.175, 1.05)
[…]

### 2020-04-06 tex/figures/code/viz.py

@@ -22,11 +22,11 @@ def visualize_simple(ax, b, theta, bo, ro, res=4999):
         phi = phi[::-1]
 
     color_night = (0, 0, 0, 0.75)
-    color_day_occ = (0, 0, 0, 0.25)
+    color_day_occ = (0.314, 0.431, 0.514, 0.5)
     color_night_occ = (0, 0, 0, 0.5)
 
     # Equation of half-ellipse
-    x = np.linspace(-1, 1, 1000)
+    x = np.linspace(-1, 1, 10000)
     y = b * np.sqrt(1 - x ** 2)
     x_t = x * np.cos(theta) - y * np.sin(theta)
     y_t = x * np.sin(theta) + y * np.cos(theta)
@@ -204,7 +204,7 @@ def visualize(b, theta, bo, ro, res=4999):
     phi = kappa - np.pi / 2
 
     color_night = (0, 0, 0, 0.75)
-    color_day_occ = (0, 0, 0, 0.25)
+    color_day_occ = (0.314, 0.431, 0.514, 0.5)
     color_night_occ = (0, 0, 0, 0.5)
 
     # Equation of half-ellipse

### 2020-04-06 tex/figures/pathological.py

@@ -3,9 +3,10 @@ import numpy as np
 import matplotlib.pyplot as plt
 
 # Setup figure
-fig, ax = plt.subplots(1, 4, figsize=(12, 3))
+fig, ax = plt.subplots(2, 4, figsize=(12, 6))
+ax = ax.flatten()
 
-# Case 9
+# Case 11
 visualize_simple(
     ax[0], 0.5488316824842527, 4.03591586925189, 0.34988513192814663, 0.7753986686719786
 )
@@ -29,13 +30,25 @@ rectangle_patch.set_ec("k")
 for line in connector_lines:
     line.set_ec("k")
 
-# Case 10
-visualize_simple(ax[2], 0.5, np.pi, 0.99, 1.5)
+# Case 12
+visualize_simple(
+    ax[2],
+    -0.5488316824842527,
+    4.03591586925189 - np.pi,
+    0.34988513192814663,
+    0.7753986686719786,
+)
 axins1 = ax[2].inset_axes([1.15, 0.0, 1.0, 1.0])
-visualize_simple(axins1, 0.5, np.pi, 0.99, 1.5)
+visualize_simple(
+    axins1,
+    -0.5488316824842527,
+    4.03591586925189 - np.pi,
+    0.34988513192814663,
+    0.7753986686719786,
+)
 axins1.axis("on")
 ax[3].set_visible(False)
-x1, x2, y1, y2 = 0.25, 1.0, -0.625, 0.125
+x1, x2, y1, y2 = 0.6, 0.7, 0.7, 0.8
 axins1.set_xlim(x1, x2)
 axins1.set_ylim(y1, y2)
 axins1.set_xticks([])
@@ -45,11 +58,43 @@ rectangle_patch.set_ec("k")
 for line in connector_lines:
     line.set_ec("k")
 
+# Case 13
+visualize_simple(ax[4], 0.5, np.pi, 0.99, 1.5)
+axins2 = ax[4].inset_axes([1.15, 0.0, 1.0, 1.0])
+visualize_simple(axins2, 0.5, np.pi, 0.99, 1.5)
+axins2.axis("on")
+ax[5].set_visible(False)
+x1, x2, y1, y2 = 0.25, 1.0, -0.625, 0.125
+axins2.set_xlim(x1, x2)
+axins2.set_ylim(y1, y2)
+axins2.set_xticks([])
+axins2.set_yticks([])
+rectangle_patch, connector_lines = ax[4].indicate_inset_zoom(axins2)
[…]

### 2020-04-06 tex/ms.tex
more text

@@
 
-Similarly, the flux outside of an occultation is now given by
+Similarly, the flux when there is no occultation is now given by
 %
@@
 $\lambda_2$ are functions of the solutions to the quartic from
-\S\ref{sec:which-case} and will be presented below.
-
-As in \citet{Luger2019}, the approach to computing the surface integrals
-of each of the terms in $\bg$ over $S$
-is to use Green's theorem to transform them into line integrals along the
-curves $P$, $T$, and $Q$. Let $\mathfrak{p}^\top$,
-$\mathfrak{t}^\top$, and $\mathfrak{q}^\top$ denote the vectors
-corresponding to the line integrals
-along the curves $P$, $T$, and $Q$, respectively, of the anti-exterior
-derivatives of each of the terms in
-$\bg$ (see Appendix~\ref{sec:sT}).
-The integration is performed in the frame $\mathcal{F}'$,
-in a counter-clockwise direction relative to the center
-of the integration region $S$.
-Then the integral of $\bg$ over $S$ is%
-\footnote{%
-    The components of the vectors $\mathfrak{p}^\top$ and
-    $\mathfrak{q}^\top$ are analogous to the ``primitive integrals''
-    $\mathcal{P}$ and $\mathcal{Q}$
-    defined in Equations~(30)--(32) in \citet{Luger2019}, although the
-    integration limits of both (and the sense of integration of $\mathcal{P}$)
-    are different.
-}
-%
-\begin{align}
-    \label{eq:sT}
-    \sT & =
-    \mathfrak{p}^\top + \mathfrak{t}^\top + \mathfrak{q}^\top
+\S\ref{sec:which-case} and will be presented in \S\ref{sec:sT}.
+
+Let $\sT$ be the integral of $\bg^\top$ over $S$:
+%
+\begin{align}
+    \label{eq:sTint}
+    \sT(b, \theta', b_o, r_o) & =
+    \iint\limits_{S(b, \theta', b_o, r_o)}
+    \bg^\top(x', y')
+    \ \dd x' \ \dd y'
     \quad,
@@
 %
-where the dependence on $b, \theta', b_o,$ and $r_o$ is implicit.
-%
-We defer the solution to Equation~(\ref{eq:sT}) to \S\ref{sec:sT} below,
+We defer the solution to Equation~(\ref{eq:sTint}) to \S\ref{sec:sT} below,
 as it is quite lengthy. Given $\sT$, the flux $f_S$ over the integration
@@
 Cases 7--10 involve two points of intersection between the occultor limb and
-the terminator. The region we integrate over is bounded only by the terminator
-and the limb of the occultor, so when computing $f_S$ below we set
-$\mathfrak{q}^\top = \boldsymbol{0}$.
+the terminator.
 %
@@
     \label{eq:f14}
-    f_{14} = (f_{S_1} + f_{S_2})
+    f_{14} = f_{S_1} + f_{S_2}
     \quad.
@@
 \label{sec:sT}
-\xxx{This is going to be be painful.}
+%
+In the previous sections, we discussed how to identify the case
+corresponding to a specific configuration of the occultor and the
+illumination source. We showed how in some cases
+(1--5; \S\ref{sec:cases-easy}) the total flux may be
+computed by exploiting the classical \starry integrals (Equation~\ref{eq:fI}).
+In all other cases (6--14; \S\ref{sec:cases-hard} and
+\S\ref{sec:cases-pathological}), however, the flux computation involves
+evaluation of
+Equation~(\ref{eq:fS}), where the solution vector $\mathfrak{s}^\top$
+is the vector of integrals of each of the terms in the Green's basis $\bg$
+over a region $S$ of the
+projected disk of the occultor (Equation~\ref{eq:sTint}).
+%
+As in \citet{Luger2019}, the approach to computing $\sT$
+is to use Green's theorem to transform the surface integrals into line
+integrals along the curves $P$, $T$, and $Q$
+(see Figure~\ref{fig:geometry}). Specifically, we write%
+\footnote{%
+    In this section, we deliberately drop the prime symbols from $x'$ and
+    $y'$ for clarity. We also drop the dependence of $\sT$ and the primitive
+    integrals on the geometrical parameters $b, \theta', b_o, r_o$.
+}
+%
+\begin{align}
+    \label{eq:greens}
+    \sT
+     & =
+    \iint\limits_{S}
+    \bg^\top(x, y)
+    \ \dd x \ \dd y
+    \nonumber \\[0.5em]
+     & =
+    \oint \bvec{G} (x, y) \cdot
+    \dd \bvec{r} (x, y)
+    \quad,
+\end{align}
+%
+where $\bvec{G} (x, y)$
+is an array of two-dimensional Cartesian vectors chosen such that its
+exterior derivative is $\bg$,
+%
+\begin{align}
+    \label{eq:DGg}
+    \frac{\dd \bvec{G}_{y}(x, y)}{\dd x}
+    - \frac{\dd \bvec{G}_{x}(x, y)}{\dd y} = \bg(x, y)
+    \quad,
+\end{align}
+%
+and
+%
+\begin{align}
+    \dd \BF{r} (x, y) & =
+    \left(\frac{\dd x}{\dd \varphi}\right) \dd \varphi \, \xhat +
+    \left(\frac{\dd y}{\dd \varphi}\right) \dd \varphi \, \yhat
+    \quad,
+\end{align}
+%
+where $\varphi$ is the parametrized angle along the integration path.
+%
+\citet{Luger2019} showed that one possible solution to
+Equation~(\ref{eq:DGg}) consists of the vector whose $n^\mathrm{th}$
+component is given by
+%
+\begin{align}
+    \label{eq:G}
+    \BF{G}_n (x, y) & =
+    \begin{dcases}
+        %
+        x^{\frac{\mu + 2}{2}}
+        y^{\frac{\nu}{2}}
+        \,\yhat
+         & \qquad \mu, \nu \, \mathrm{even}
+        \\[1em]
+        %
+        \frac{1-z(x, y)^3}{3(1-z(x, y)^2)}\bigg(-y \, \xhat + x \, \yhat\bigg)
+         & \qquad \mu = \nu = 1
+        \\[1em]
+        %
+        x^{l-2}
+        z(x, y)^3
+        \,\xhat
+         & \qquad \nu \, \mathrm{odd}, \,
+        \mu = 1, \,
+        \frac{\mu + \nu}{2} \, \mathrm{even}
+        \\[1em]
+        %
+        x^{l-3}
+        y
+        z(x, y)^3
+        \,\xhat
+         & \qquad \nu \, \mathrm{odd}, \,
+        \mu = 1, \,
+        \frac{\mu + \nu}{2} \, \mathrm{odd}
+        \\[1em]
+        %
+        x^{\frac{\mu-3}{2}}
+        y^{\frac{\nu-1}{2}}
+        z(x, y)^3
+        \,\yhat
+         & \qquad \mathrm{otherwise,}
+    \end{dcases}
+\end{align}
+%
+where the indices $l, m, \mu, \nu$ are given by Equation~(\ref{eq:l-m-mu-nu}).
+
+We showed in the previous sections that there are at most three curves
+$P$, $T$, and $Q$ bounding a given closed surface of integration
+(see Figure~\ref{fig:geometry}). We may therefore express
+Equation~(\ref{eq:greens}) as
+%
+\begin{align}
+    \label{eq:sT}
+    \sT & =
+    \mathfrak{p}^\top + \mathfrak{t}^\top + \mathfrak{q}^\top
+    \quad,
+\end{align}
+%
+where we define the primitive integrals
+%
+\begin{align}
+    \label{eq:pT}
+    \mathfrak{p}^\top
+     & =
+    \int\limits_{\phi_1}^{\phi_2}
+    \mathbf{G}(x_p, y_p)
+    \cdot \dd \mathbf{r}(x_p, y_p)
+    %
+    \\
+    %
+    \label{eq:tT}
+    \mathfrak{t}^\top
+     & =
+    \int\limits_{\xi_1}^{\xi_2}
+    \mathbf{G}(x_t, y_t)
+    \cdot \dd \mathbf{r}(x_t, y_t)
+    %
+    \\
+    %
+    \label{eq:qT}
+    \mathfrak{q}^\top
+     & =
+    \int\limits_{\lambda_1}^{\lambda_2}
+    \mathbf{G}(x_q, y_q)
+    \cdot \dd \mathbf{r}(x_q, y_q)
+\end{align}
+%
+to be the line integrals of $\mathbf{G}$ along each of the curves
+$P$, $T$, and $Q$, respectively, where the coordinates are parametrized
+in terms of $\varphi$ as follows:
+%
+\\[1em]
+%
+\begin{minipage}{0.31\linewidth}
+    \begin{align}
+        x_p & = r_o \cos\varphi
+        \nonumber                     \\
+        y_p & = b_o + r_o \sin\varphi
+        \nonumber
+    \end{align}
+\end{minipage}
+%
+\begin{minipage}{0.35\linewidth}
+    \begin{align}
+        x_t & = \cos\theta' \cos\varphi - b \sin\theta' \sin\varphi
+        \nonumber                                                   \\
+        y_t & = \sin\theta' \cos\varphi + b \cos\theta' \sin\varphi
+        \nonumber
+    \end{align}
+\end{minipage}
+%
+\begin{minipage}{0.31\linewidth}
+    \begin{align}
+        \label{eq:xy_pqt}
+        x_q & =\cos\varphi
+        \nonumber           \\
+        y_q & = \sin\varphi
+        \quad.
+    \end{align}
+\end{minipage}
+%
+\\[1em]
+
+\xxx{We perform the integration in a frame $\mathcal{F}'$
+    in which the occultor is aligned with the $+y'$-axis,
+    in a counter-clockwise direction relative to the center
+    of the integration region $S$.}
 

### 2020-04-06 tex/ms.tex
omg so much math

@@
 We wish to find the set of $N$ points
-$\{x_n''~\big|~0~\le~n~<~N\}$
+$\BS{x''} = \{x_n''~\big|~0~\le~n~<~N\}$
 for which
@@
 Curve $P$ is a segment of the limb of
-the occultor, parametrized by the angle $\phi \in [\phi_1, \phi_2]$;
+the occultor, parametrized by the angle $\phi \in [\phi_0, \phi_1]$;
 curve $T$ is a segment of the terminator,
-parametrized by the angle $\xi \in [\xi_1, \xi_2]$;
+parametrized by the angle $\xi \in [\xi_0, \xi_1]$;
 and curve $Q$ is a segment of the limb of the occulted body,
-parametrized by the angle $\lambda \in [\lambda_1, \lambda_2]$.
-The endpoints $\phi_1, \phi_2, \xi_1, \xi_2, \lambda_1,$ and
-$\lambda_2$ are functions of the solutions to the quartic from
+parametrized by the angle $\lambda \in [\lambda_0, \lambda_1]$.
+The endpoints $\phi_0, \phi_1, \xi_0, \xi_1, \lambda_0,$ and
+$\lambda_1$ are functions of the solutions to the quartic from
 \S\ref{sec:which-case} and will be presented in \S\ref{sec:sT}.
@@
 Equation~(\ref{eq:fS}), where the solution vector $\mathfrak{s}^\top$
-is the vector of integrals of each of the terms in the Green's basis $\bg$
+is the vector of integrals (in the frame $\mathcal{F}'$)
+of each of the terms in the Green's basis $\bg$
 over a region $S$ of the
@@
 \footnote{%
-    In this section, we deliberately drop the prime symbols from $x'$ and
-    $y'$ for clarity. We also drop the dependence of $\sT$ and the primitive
-    integrals on the geometrical parameters $b, \theta', b_o, r_o$.
+    In this section, we deliberately drop the dependence of $\sT$ and
+    the primitive
+    integrals on the geometrical parameters $b, \theta', b_o, r_o$
+    for clarity.
 }
@@
     \iint\limits_{S}
-    \bg^\top(x, y)
-    \ \dd x \ \dd y
+    \bg^\top(x', y')
+    \ \dd x' \ \dd y'
     \nonumber \\[0.5em]
      & =
-    \oint \bvec{G} (x, y) \cdot
-    \dd \bvec{r} (x, y)
+    \oint \bvec{G}^\top (x', y') \cdot
+    \dd \bvec{r} (x', y')
     \quad,
@@
 %
-where $\bvec{G} (x, y)$
+where $\bvec{G} (x', y')$
 is an array of two-dimensional Cartesian vectors chosen such that its
@@
     \label{eq:DGg}
-    \frac{\dd \bvec{G}_{y}(x, y)}{\dd x}
-    - \frac{\dd \bvec{G}_{x}(x, y)}{\dd y} = \bg(x, y)
+    \frac{\dd \bvec{G}_{y'}(x', y')}{\dd x'}
+    - \frac{\dd \bvec{G}_{x'}(x', y')}{\dd y'} = \bg(x', y')
     \quad,
@@
 \begin{align}
-    \dd \BF{r} (x, y) & =
-    \left(\frac{\dd x}{\dd \varphi}\right) \dd \varphi \, \xhat +
-    \left(\frac{\dd y}{\dd \varphi}\right) \dd \varphi \, \yhat
+    \dd \BF{r} (x', y') & =
+    \left(\frac{\dd x'}{\dd \varphi}\right) \dd \varphi \, \xhat' +
+    \left(\frac{\dd y'}{\dd \varphi}\right) \dd \varphi \, \yhat'
     \quad,
@@
 %
-where $\varphi$ is the parametrized angle along the integration path.
+where $\varphi$ is the parametrized angle along the integration path
+and the integral is taken in a counter-clockwise direction relative to
+the center of the integration region.
 %
@@
         %
-        x^{\frac{\mu + 2}{2}}
-        y^{\frac{\nu}{2}}
-        \,\yhat
+        x'^{\frac{\mu + 2}{2}}
+        y'^{\frac{\nu}{2}}
+        \,\yhat'
          & \qquad \mu, \nu \, \mathrm{even}
@@
         %
-        \frac{1-z(x, y)^3}{3(1-z(x, y)^2)}\bigg(-y \, \xhat + x \, \yhat\bigg)
+        \frac{1-z(x', y')^3}{3(1-z(x', y')^2)}\bigg(-y' \, \xhat' + x' \, \yhat'\bigg)
          & \qquad \mu = \nu = 1
@@
         %
-        x^{l-2}
-        z(x, y)^3
+        x'^{l-2}
+        z(x', y')^3
         \,\xhat
@@
         %
-        x^{l-3}
-        y
-        z(x, y)^3
+        x'^{l-3}
+        y'
+        z(x', y')^3
         \,\xhat
@@
         %
-        x^{\frac{\mu-3}{2}}
-        y^{\frac{\nu-1}{2}}
-        z(x, y)^3
+        x'^{\frac{\mu-3}{2}}
+        y'^{\frac{\nu-1}{2}}
+        z(x', y')^3
         \,\yhat
@@
 %
-\begin{align}
+\begin{proof}{}
     \label{eq:sT}
@@
     \quad,
-\end{align}
-%
-where we define the primitive integrals
-%
-\begin{align}
+\end{proof}
+%
+where we define the primitive integrals%
+\footnote{%
+    The components of the vectors $\mathfrak{p}^\top$ and
+    $\mathfrak{q}^\top$ are analogous to the primitive integrals
+    $\mathcal{P}$ and $\mathcal{Q}$
+    defined in Equations~(30)--(32) in \citet{Luger2019}, although the
+    integration limits of both and the sense of integration of $\mathcal{P}$
+    are different.
+}
+%
+\begin{proof}{}
     \label{eq:pT}
@@
     & =
-    \int\limits_{\phi_1}^{\phi_2}
-    \mathbf{G}(x_p, y_p)
-    \cdot \dd \mathbf{r}(x_p, y_p)
+    \int\limits_{\BS{\phi}}
+    \mathbf{G}^\top(x'_p, y'_p)
+    \cdot \dd \mathbf{r}(x'_p, y'_p)
     %
@@
     & =
-    \int\limits_{\xi_1}^{\xi_2}
-    \mathbf{G}(x_t, y_t)
-    \cdot \dd \mathbf{r}(x_t, y_t)
+    \int\limits_{\BS{\xi}}
+    \mathbf{G}^\top(x'_t, y'_t)
+    \cdot \dd \mathbf{r}(x'_t, y'_t)
     %
@@
     & =
-    \int\limits_{\lambda_1}^{\lambda_2}
-    \mathbf{G}(x_q, y_q)
-    \cdot \dd \mathbf{r}(x_q, y_q)
-\end{align}
+    \int\limits_{\BS{\lambda}}
+    \mathbf{G}^\top(x'_q, y'_q)
+    \cdot \dd \mathbf{r}(x'_q, y'_q)
+\end{proof}
 %
 to be the line integrals of $\mathbf{G}$ along each of the curves
-$P$, $T$, and $Q$, respectively, where the coordinates are parametrized
+$P$, $T$, and $Q$, respectively, where the coordinates along each
+curve are parametrized
 in terms of $\varphi$ as follows:
@@
     \begin{align}
-        x_p & = r_o \cos\varphi
-        \nonumber                     \\
-        y_p & = b_o + r_o \sin\varphi
+        x'_p & = r_o \cos\varphi
+        \nonumber                      \\
+        y'_p & = b_o + r_o \sin\varphi
         \nonumber
@@
     \begin{align}
-        x_t & = \cos\theta' \cos\varphi - b \sin\theta' \sin\varphi
-        \nonumber                                                   \\
-        y_t & = \sin\theta' \cos\varphi + b \cos\theta' \sin\varphi
+        x'_t & = \cos\theta' \cos\varphi - b \sin\theta' \sin\varphi
+        \nonumber                                                    \\
+        y'_t & = \sin\theta' \cos\varphi + b \cos\theta' \sin\varphi
         \nonumber
@@
 \begin{minipage}{0.31\linewidth}
-    \begin{align}
+    \begin{proof}{}
         \label{eq:xy_pqt}
-        x_q & =\cos\varphi
-        \nonumber           \\
-        y_q & = \sin\varphi
-        \quad.
-    \end{align}
+        x'_q & =\cos\varphi
+        \nonumber           \\
+        y'_q & = \sin\varphi
+        \quad,
+    \end{proof}
 \end{minipage}
@@
 \\[1em]
-
-\xxx{We perform the integration in a frame $\mathcal{F}'$
-    in which the occultor is aligned with the $+y'$-axis,
-    in a counter-clockwise direction relative to the center
-    of the integration region $S$.}
+%
+and we define
+%
+\begin{align}
+    \int\limits_{\BS{\varphi}} & \equiv
+    %
+    \int\limits_{\varphi_{0}}^{\varphi_{1}}
+    +
+    \int\limits_{\varphi_{2}}^{\varphi_{3}}
+    +
+    \cdots
+    +
+    \int\limits_{\varphi_{N - 2}}^{\varphi_{N - 1}}
+    %
+    \nonumber                           \\
+                               & \equiv
+    \sum_{i = 0}^{\frac{N - 1}{2}}
+    \int\limits_{\varphi_{2i}}^{\varphi_{2i+1}}
+\end{align}
+%
+to be the sum of definite integrals between pairs of limits $\varphi_i$
+arranged in an array $\BS{\varphi}$ of length $N$.
+For cases involving integration over a single closed region, this
+corresponds to a single integral. For cases 11--14, this corresponds to
+the sum of two integrals, one for each of the two disjoint regions.
+In the next three sections, we derive the solutions to each of these
+primitive integrals.
+
+\subsection{The integral along the occultor limb, $\mathfrak{p}^\top$}
+\label{sec:pT}
+%
+In this section we present a solution to Equation~(\ref{eq:pT}). The first
+order of business is to derive expressions for the integration limits
+$\BS{\phi}$. Depending on the integration case, these limits will correspond
+to the point of intersection between the limb of the occultor and the
+limb of the occulted body and/or the point of intersection between the limb
+of the occultor and the terminator of the occulted body.
+The former is given by
+\citep[c.f. Equation~24 in][]{Luger2019}
+%
+\begin{align}
+    \phi_l & = \frac{\pi}{2} \pm \left(\arcsin\left(\frac{1 - r_o ^ 2 - b_o ^ 2}{2 b_o r_o}\right) - \frac{\pi}{2}\right)
+    \quad,
+\end{align}
+%
+where the sign is chosen such that the point
+$(r_o\cos\phi_l, b_o + r_o\sin\phi_l)$ is on the dayside of the occulted body,
+and the latter (of which there may be multiple) is given by
+%
+% Introduce the function
+% %
+% \begin{proof}{}
+%     \textrm{\faAdjust}(x, y) &=
+%     \begin{cases}
+%         \textrm{\faCircleO} & \qquad -x \sin\theta' + y\cos\theta' \ge b \sqrt{1 - (x\cos\theta' + y\sin\theta') ^ 2}
+%         \\
+%         \textrm{\faCircle}  & \qquad \mathrm{otherwise}
+%     \end{cases}
+% \end{proof}
+% %
+% which returns \faCircleO\ if point $(x, y)$ is on the dayside of the body and
+% \faCircle\ if it is on the nightside.
+%
+%
+\begin{align}
+    \BS{\phi_t} & =
+    \theta' + \mathrm{arctan2}\left(b\sqrt{1 - \BS{x''}^2 - y''_o}, \BS{x''} - x''_o\right)
+    \quad
+\end{align}
+%
+where $\BS{x''}$ are the roots of the quartic (Equation~\ref{eq:quartic}).
+These angles are then sorted and placed in the array $\BS{\phi}$ such that
+the integration is always performed in a counter-clockwise sense about
+the center of the integration region.
+%
+The left panel in Figure~\ref{fig:geometry} shows a configuration in which
+the lower integration limit $\phi_0 = 158.2^\circ$ corresponds to the
+point of intersection between the limbs of the two bodies and the upper
+integration limit $\phi_1 = 223.3^\circ$ corresponds to the
+limb-terminator intersection. Both angles are measured counter-clockwise
+from the $x'$-axis.
+
+\xxx{OK, now solve the integral.}
+
+Let
+%
+\begin{align}
+    \BS{\kappa} = \BS{\phi} + \frac{\pi}{2}
+\end{align}
 

### 2020-04-06 tex/figures/code/viz.py

@@ -251,7 +251,7 @@ def visualize(b, theta, bo, ro, res=4999):
     # Labels
     for i in range(len(phi)):
         ax[1].annotate(
-            r"$\xi_{} = {:.1f}^\circ$".format(i + 1, xi[i] * 180 / np.pi),
+            r"$\xi_{} = {:.1f}^\circ$".format(i, xi[i] * 180 / np.pi),
             xy=(0, 0),
             xycoords="axes fraction",
             xytext=(5, 25 - i * 20),
@@ -260,7 +260,7 @@ def visualize(b, theta, bo, ro, res=4999):
             color="k",
         )
         ax[0].annotate(
-            r"$\phi_{} = {:.1f}^\circ$".format(i + 1, phi[i] * 180 / np.pi),
+            r"$\phi_{} = {:.1f}^\circ$".format(i, phi[i] * 180 / np.pi),
             xy=(0, 0),
             xycoords="axes fraction",
             xytext=(5, 25 - i * 20),
@@ -270,7 +270,7 @@ def visualize(b, theta, bo, ro, res=4999):
         )
     for i in range(len(lam)):
         ax[2].annotate(
-            r"$\lambda_{} = {:.1f}^\circ$".format(i + 1, lam[i] * 180 / np.pi),
+            r"$\lambda_{} = {:.1f}^\circ$".format(i, lam[i] * 180 / np.pi),
             xy=(0, 0),
             xycoords="axes fraction",
             xytext=(5, 25 - i * 20),
@@ -459,7 +459,7 @@ def visualize(b, theta, bo, ro, res=4999):
             ax[1].add_patch(arc)
 
             ax[1].annotate(
-                r"$\xi_{}$".format(i + 1),
+                r"$\xi_{}$".format(i),
                 xy=(
                     0.5 * sz[i] * np.cos(0.5 * np.sign(b) * xi_i + theta),
                     0.5 * sz[i] * np.sin(0.5 * np.sign(b) * xi_i + theta),
@@ -522,7 +522,7 @@ def visualize(b, theta, bo, ro, res=4999):
         )
         ax[0].add_patch(arc)
         ax[0].annotate(
-            r"${}\phi_{}$".format("-" if phi_i < 0 else "", i + 1),
+            r"${}\phi_{}$".format("-" if phi_i < 0 else "", i),
             xy=(
[…]

### 2020-04-08 tex/ms.tex
still going
better notation

@@
 \input{cortex}
+
+\usepackage{amsmath}
+\usepackage{fontspec}
+\usepackage{unicode-math}
 
@@
 \newcommand{\BF}[1]{\ensuremath{\mathbf{#1}}}
-\newcommand{\BS}[1]{\ensuremath{\boldsymbol{#1}}}
-\newcommand{\dd}{\ensuremath{\mathrm{d}}}
+\newcommand{\BS}[1]{\ensuremath{\pmb{#1}}}
+\newcommand{\dd}{\ensuremath{\text{d}}}
 \newcommand{\STARRYQUADPOINTS}{100\xspace}
@@
 \newcommand{\bxi}{\BS{\xi}}
-\newcommand{\vmax}{{v_\mathrm{max}}}
-\newcommand{\kapint}[1]{%
-\sum_{i = 0}^{\frac{N - 1}{2}}
-\int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
-#1
-\dd\varphi
-}
-\newcommand{\lamint}[1]{%
-\sum_{i = 0}^{\frac{N - 1}{2}}
-\int\limits_{\frac{1}{2}\lambda_{2i}}^{\frac{1}{2}\lambda_{2i+1}}
-#1
-}
+\newcommand{\vmax}{{v_\text{max}}}
 \newcommand{\coshalfkap}[1][]{%
@@
 \newcommand{\DF}{\Delta \BS{F}(k^2, \bkappa)}
-\newcommand{\sgn}{{\mathrm{sgn}}}
-\newcommand{\xhat}{\ensuremath{\mathbf{\hat{x}}}\xspace}
-\newcommand{\yhat}{\ensuremath{\mathbf{\hat{y}}}\xspace}
-\newcommand{\zhat}{\ensuremath{\mathbf{\hat{z}}}\xspace}
-\newcommand{\sT}{\ensuremath{\mathfrak{s}^\top}}
-\newcommand{\rT}{\ensuremath{\mathfrak{r}^\top}}
+\newcommand{\sgn}{{\text{sgn}}}
+\newcommand{\xhat}{\ensuremath{\pmb{\hat{x}}}\xspace}
+\newcommand{\yhat}{\ensuremath{\pmb{\hat{y}}}\xspace}
+\newcommand{\zhat}{\ensuremath{\pmb{\hat{z}}}\xspace}
+\newcommand{\sT}{\ensuremath{\mathbbb{s}^\top}}
+\newcommand{\rT}{\ensuremath{\mathbbb{r}^\top}}
+\newcommand{\pT}{\ensuremath{\mathbbb{p}^\top}}
+\newcommand{\tT}{\ensuremath{\mathbbb{t}^\top}}
+\newcommand{\qT}{\ensuremath{\mathbbb{q}^\top}}
 \newcommand{\sTe}{\ensuremath{\BF{s}^\top}}
 \newcommand{\rTe}{\ensuremath{\BF{r}^\top}}
-%
 \newcommand{\bg}{\ensuremath{\tilde{\BF{g}}}}
@@
 \newcommand{\by}{\ensuremath{\tilde{\BF{y}}}}
+\newcommand{\iI}{\ensuremath{\mathbbb{i}}}
+\newcommand{\iJ}{\ensuremath{\mathbbb{j}}}
+\newcommand{\iU}{\ensuremath{\mathbbb{u}}}
+\newcommand{\iW}{\ensuremath{\mathbbb{w}}}
+\newcommand{\vint}[2]{%
+\int\limits_{#1}
+#2
+\dd\varphi
+}
+
+% REMOVE
+\newcommand{\kapint}[1]{%
+\sum_{i = 0}^{\frac{N - 1}{2}}
+\int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
+#1
+\dd\varphi
+}
+\newcommand{\lamint}[1]{%
+\sum_{i = 0}^{\frac{N - 1}{2}}
+\int\limits_{\frac{1}{2}\lambda_{2i}}^{\frac{1}{2}\lambda_{2i+1}}
+#1
+}
 
@@
 it is straightforward to show that the illumination
-$\mathfrak{I}$ at a point $(x, y)$ on the projected disk of the body is given
+$\mathcal{I}$ at a point $(x, y)$ on the projected disk of the body is given
 by the function
@@
     \label{eq:illum}
-    \mathfrak{I}(b, \theta, r_s; x, y)&=
-    \mathrm{max}\bigg( 0, I(b, \theta, r_s; x, y) \bigg)
+    \mathcal{I}(b, \theta, r_s; x, y)&=
+    \text{max}\bigg( 0, I(b, \theta, r_s; x, y) \bigg)
 \end{proof}
@@
     f & =
-    \mathfrak{s}^\top(b, \theta', b_o, r_o)
+    \sT(b, \theta', b_o, r_o)
     \BF{A_2}
@@
     \label{eq:theta'}
-    \theta' = \mathrm{arctan2}(x_o, y_o) - \mathrm{arctan2}(x_s, y_s)
+    \theta' = \text{arctan2}(x_o, y_o) - \text{arctan2}(x_s, y_s)
 \end{align}
@@
     f_0 & =
-    \mathfrak{r}^\top(b)
+    \rT(b)
     \BF{I}(b, \theta'', r_s)
@@
 with the vectors
-$\mathfrak{r}^\top(b)$ and $\mathfrak{s}^\top(b, \theta', b_o, r_o)$,
+$\rT(b)$ and $\sT(b, \theta', b_o, r_o)$,
 respectively.
@@
 nightside, where the weighting by $\BF{I}$ is unphysical.
-The vectors $\mathfrak{r}^\top$ and $\mathfrak{s}^\top$ correspond to these
+The vectors $\rT$ and $\sT$ correspond to these
 modified integrals, which we devote the rest of this paper to
@@
         \qquad
-        \mu, \nu \ \mathrm{even}
+        \mu, \nu \ \text{even}
         %
@@
         \qquad
-        \mathrm{otherwise}
+        \text{otherwise}
         %
@@
 
-\xxx{In general, we do not just integrate over the dayside.}
+\xxx{In general, we do not just integrate over the dayside. We integrate over
+    the simplest region -- usually the one with the fewest boundaries --
+    and combine it with the formalism from \S\ref{sec:solution-no-occ} to
+    compute the visible flux.}
 
@@
     \label{eq:f3}
-    f_3 = f_\mathrm{I}
+    f_3 = f_I
 \end{proof}
@@
     f_S & =
-    \mathfrak{s}^\top(b, \theta', b_o, r_o)
+    \sT(b, \theta', b_o, r_o)
     \BF{A_2}
@@
 evaluation of
-Equation~(\ref{eq:fS}), where the solution vector $\mathfrak{s}^\top$
+Equation~(\ref{eq:fS}), where the solution vector $\sT$
 is the vector of integrals (in the frame $\mathcal{F}'$)
@@
 \citet{Luger2019} showed that one possible solution to
-Equation~(\ref{eq:DGg}) consists of the vector whose $n^\mathrm{th}$
+Equation~(\ref{eq:DGg}) consists of the vector whose $n^\text{th}$
 component is given by
@@
         \,\yhat'
-         & \qquad \mu, \nu \, \mathrm{even}
+         & \qquad \mu, \nu \, \text{even}
         \\[1em]
@@
         \,\xhat
-         & \qquad \nu \, \mathrm{odd}, \,
+         & \qquad \nu \, \text{odd}, \,
         \mu = 1, \,
-        \frac{\mu + \nu}{2} \, \mathrm{even}
+        l \, \text{even}
         \\[1em]
@@
         \,\xhat
-         & \qquad \nu \, \mathrm{odd}, \,
+         & \qquad \nu \, \text{odd}, \,
         \mu = 1, \,
-        \frac{\mu + \nu}{2} \, \mathrm{odd}
+        l \, \text{odd}
         \\[1em]
@@
         \,\yhat
-         & \qquad \mathrm{otherwise,}
+         & \qquad \text{otherwise,}
     \end{dcases}
@@
     \sT & =
-    \mathfrak{p}^\top + \mathfrak{t}^\top + \mathfrak{q}^\top
+    \pT + \tT + \qT
     \quad,
@@
 \footnote{%
-    The components of the vectors $\mathfrak{p}^\top$ and
-    $\mathfrak{q}^\top$ are analogous to the primitive integrals
+    The components of the vectors $\pT$ and
+    $\qT$ are analogous to the primitive integrals
     $\mathcal{P}$ and $\mathcal{Q}$
@@
     \label{eq:pT}
-    \mathfrak{p}^\top
+    \pT
     & =
@@
     \label{eq:tT}
-    \mathfrak{t}^\top
+    \tT
     & =
@@
     \label{eq:qT}
-    \mathfrak{q}^\top
+    \qT
     & =
@@
 %
-\begin{minipage}{0.31\linewidth}
+\begin{minipage}{0.3\linewidth}
     \begin{align}
@@
 %
-\begin{minipage}{0.35\linewidth}
+\begin{minipage}{0.34\linewidth}
     \begin{align}
@@
 %
-\begin{minipage}{0.31\linewidth}
+\begin{minipage}{0.3\linewidth}
     \begin{proof}{}
@@
 
-\subsection{The integral along the occultor limb, $\mathfrak{p}^\top$}
+\xxx{It is useful to} define the pairwise difference operator
+%
+\begin{align}
+    \label{eq:pairdiff}
+    \Delta \BS{v} \equiv \sum_{i=0}^{\frac{N - 1}{2}}
+    \left( v_{2i + 1} - v_{2i} \right)
+\end{align}
+%
+which sums the difference of successive pairs of values in
+an array $\BS{v} = \{ v_0, v_1, v_2, v_3, {\cdot\cdot\cdot}, v_N\}$.
+
+\subsection{The integral along the occultor limb, $\pT$}
 \label{sec:pT}
@@
 %         \\
-%         \textrm{\faCircle}  & \qquad \mathrm{otherwise}
+%         \textrm{\faCircle}  & \qquad \text{otherwise}
 %     \end{cases}
@@
     \BS{\phi_t} & =
-    \theta' + \mathrm{arctan2}\left(b\sqrt{1 - \BS{x''}^2 - y''_o}, \BS{x''} - x''_o\right)
+    \theta' + \text{arctan2}\left(b\sqrt{1 - \BS{x''}^2 - y''_o}, \BS{x''} - x''_o\right)
     \quad
@@
 
-\xxx{OK, now solve the integral.}
-
-Let
+In order to evaluate the integral in Equation~(\ref{eq:pT}),
+we follow the reparametrization tricks of \S{D.2.3} in \citet{Luger2019}.
+The algebra is long and tedious, so we merely present the result
+(alongside the usual validation links). The $n^\text{th}$ component
+of $\pT$ is
+%
+\begin{proof}{}
+    \label{eq:pTsoln}
+    \mathbb{p}_n &=
+    \begin{dcases}
+        %
+        %
+        2(2r_o)^{l+2}
+        \mathbb{V}
+        \left(
+        \frac{\mu+4}{4},
+        \frac{\nu}{2},
+        0;
+        \iI
+        \right)
+        %
+         & \qquad \frac{\mu}{2} \, \text{even}
+        \\[1em]
+        %
+        %
+        \mathbb{p}_2
+        %
+         & \qquad \mu = \nu = 1
+        \\[1em]
+        %
+        %
+        (2r_o)^{l-1} \beta
+        \left\{
+        \mathbb{V}
+        \left(
+        \frac{l-2}{2},
+        0,
+        0;
+        \iJ
+        \right) -
+        2
+        \mathbb{V}
+        \left(
+        \frac{l-2}{2},
+        0,
+        1;
+        \iJ
+        \right)
+        \right\}
+        %
+         & \qquad \mu = 1, \,
+        l \, \text{even}
+        \\[1em]
+        %
+        %
+        (2r_o)^{l-1} \beta
+        \left\{
+        \mathbb{V}
+        \left(
+        \frac{l-3}{2},
+        1,
+        0;
+        \iJ
+        \right) -
+        \mathbb{V}
+        \left(
+        \frac{l-3}{2},
+        1,
+        1;
+        \iJ
+        \right)
+        \right\}
+        %
+         & \qquad \mu = 1, \, l \ne 1, \,
+        l \, \text{odd}
+        \\[1em]
+        %
+        %
+        2(2r_o)^{l-1} \beta\,
+        \mathbb{V}
+        \left(
+        \frac{\mu-1}{4},
+        \frac{\nu-1}{2},
+        0;
+        \iJ
+        \right)
+        %
+         & \qquad \frac{\mu-1}{2} \, \text{even}, \, l \ne 1
+        \\[1em]
+        %
+        %
+        2(2r_o)^{l+2}
+        \mathbb{V}
+        \left(
+        \Big\lfloor\frac{\mu + 4}{4}\Big\rfloor,
+        \frac{\nu}{2},
+        0;
+        \iU
+        \right)
+        %
+         & \qquad \mu, \nu \, \text{even}
+        \\[1em]
+        %
+        %
+        (2r_o)^{l-1} \beta\,
+        \mathbb{V}
+        \left(
+        \frac{\mu-1}{4},
+        \frac{\nu-1}{2},
+        0;
+        \iW
+        \right)
+         & \qquad \mu, \nu \, \text{odd}
+        \quad,
+        %
+        %
+    \end{dcases}
+    %
+\end{proof}
+%
+where $\beta = \left(1 - (b_o - r_o)^2\right)^\frac{3}{2}$
+and we define the Vieta operator
+%
+\begin{align}
+    \mathbb{V}\left(u, v, w; \mathbbb{x}\right) \equiv
+    \sum_{i=0}^{u + v}
+    \mathcal{A}_{u, v, i}
+    \mathbb{x}_{u + w + i}
+\end{align}
+%
+as the dot product of a vector $\mathbbb{x}$ and
+the vector of Vieta's theorem coefficients $\BS{\mathcal{A}}_{u, v}$, where
+\citep[c.f. Equation~D34 in][]{Luger2019}
+%
+\begin{align}
+    \label{eq:vieta}
+    \mathcal{A}_{u,v,i} & =
+    \sum_{j=\text{max}(0,u-i)}^{\text{min}(u+v-i,u)}
+    \binom{u}{j}
+    \binom{v}{u+v-i-j}
+    (-1)^{u+j}\left(\frac{b_o-r_o}{2r_o}\right)^{u+v-i-j}
+    \quad.
+\end{align}
+%
+The vectors $\iI$, $\iJ$,
+$\iU$, and $\iW$ are solutions
+to specific integrals, which we compute recursively below. As in
+\citet{Luger2019} the $n = 2$ term of $\mathbb{p}$ (second case in the
+equation above) is handled separately; we also compute this below.
+
+%
+
+\subsubsection{The vector $\iI$}
+\label{sec:i}
+%
+The components of the vector $\iI$ are given by the integral
+%
+\begin{align}
+    \label{eq:I}
+    \mathbb{i}_v(\bkappa) & =
+    \vint{\bkappa}{\sinhalfkap[2v]}
+    \quad,
+\end{align}
+%
+for $v \in [0, \vmax]$,
+where we define the helper angle
 %
@@
     \BS{\kappa} = \BS{\phi} + \frac{\pi}{2}
+    \quad.
+\end{align}
+%
+The integral in the expression above is the same as that in Equation (D38)
+of \citet{Luger2019}, except for a change in the limits of integration.
+As in \citet{Luger2019}, we can compute the vector $\iI$ recursively given
+a trivial lower boundary condition:
+%
+\begin{proof}{I}
+    \label{eq:Irec}
+    \mathbb{i}_0(\bkappa) &=
+    \frac{\Delta \bkappa}{2}
+    %
+    \nonumber \\
+    %
+    \mathbb{i}_v(\bkappa) &=
+    \frac{1}{2v}
+    \bigg(
+    (2v - 1) \mathbb{i}_{v-1}(\bkappa) -
+    \Delta \left(\sinhalfkap[2v - 1]\coshalfkap\right)
+    \bigg)
+\end{proof}
+%
+where the last expression is valid for all $v > 0$. We find that this algorithm
+is generally stable, except when
+$\sin\left(\nicefrac{\bkappa}{2}\right)$ is small.
+In that limit, we evaluate $\mathbb{i}_\vmax(\bkappa)$
+by numerical integration of
+Equation~(\ref{eq:I}) using Gauss-Legendre quadrature with \STARRYQUADPOINTS
+points. We then recurse downward by substituting $v \rightarrow v + 1$ in
+Equation~(\ref{eq:Irec}) and solving for $\mathbb{i}_v(\bkappa)$.
+
+\xxx{Work in progress below here.}
+
+\subsubsection{The vector $\mathbbb{j}$}
+\label{sec:j}
+%
+Define the quantity
+%
+\begin{align}
+    \label{eq:q}
+    \BS{q}(k^2, \bkappa) = \sqrt{1 - \frac{\sinhalfkap[2]}{k^2}}
+    \quad.
 \end{align}
@@
         \cdot\cdot\cdot
-    \end{pmatrix}^\mathsf{T}
+    \end{pmatrix}^\top
     \quad,
@@
         \frac{\mu+2}{2}x^\frac{\mu}{2} y^\frac{\nu}{2}
-         & \qquad \mu, \nu \, \mathrm{even}
+         & \qquad \mu, \nu \, \text{even}
         \\[1em]
@@
         3x^{l-2}yz(x, y)
-         & \qquad \nu \, \mathrm{odd}, \,
+         & \qquad \nu \, \text{odd}, \,
         \mu = 1, \,
-        \frac{\mu + \nu}{2} \, \mathrm{even}
+        \frac{\mu + \nu}{2} \, \text{even}
         \\[1em]
@@
         \bigg)
-         & \qquad \nu \, \mathrm{odd}, \,
+         & \qquad \nu \, \text{odd}, \,
         \mu = 1, \,
-        \, \mathrm{odd}
+        \, \text{odd}
         \\[1em]
@@
         \bigg)
-         & \qquad \mathrm{otherwise}
+         & \qquad \text{otherwise}
         \quad,
@@
         x^\frac{\mu}{2} y^\frac{\nu}{2}
-         & \qquad \mu, \nu \, \mathrm{even}
+         & \qquad \mu, \nu \, \text{even}
         \\[1em]
         x^\frac{\mu-1}{2} y^\frac{\nu-1}{2} z(x, y)
-         & \qquad \mathrm{otherwise} \quad,
+         & \qquad \text{otherwise} \quad,
     \end{dcases}
@@
         \,\yhat
-         & \qquad \mu, \nu \, \mathrm{even}
+         & \qquad \mu, \nu \, \text{even}
         \\[1em]
@@
         \,\xhat
-         & \qquad \nu \, \mathrm{odd}, \,
+         & \qquad \nu \, \text{odd}, \,
         \mu = 1, \,
-        \frac{\mu + \nu}{2} \, \mathrm{even}
+        \frac{\mu + \nu}{2} \, \text{even}
         \\[1em]
@@
         \,\xhat
-         & \qquad \nu \, \mathrm{odd}, \,
+         & \qquad \nu \, \text{odd}, \,
         \mu = 1, \,
-        \frac{\mu + \nu}{2} \, \mathrm{odd}
+        \frac{\mu + \nu}{2} \, \text{odd}
         \\[1em]
@@
 occultor-occulted configuration in Figure~\ref{fig:geometry}.
-
-\subsection{Definitions}
-%
-Define the pairwise difference operator
-%
-\begin{align}
-    \label{eq:pairdiff}
-    \Delta \BS{v} \equiv \sum_{i=0}^{\frac{N - 1}{2}}
-    \left( v_{2i + 1} - v_{2i} \right)
-\end{align}
-%
-which sums the difference of successive pairs of values in
-an array $\BS{v} = \{ v_0, v_1, v_2, v_3, {\cdot\cdot\cdot}, v_N\}$.
-
-Define the quantity
-%
-\begin{align}
-    \label{eq:q}
-    \BS{q}(k^2, \bkappa) = \sqrt{1 - \frac{\sinhalfkap[2]}{k^2}}
-    \quad.
-\end{align}
 
@@
 %
-
-\subsection{$\mathcal{I}_v$}
-%
-The function $\mathcal{I}_v$ is given by
-%
-\begin{align}
-    \label{eq:I}
-    \mathcal{I}_v(\bkappa) & =
-    \kapint{\sinhalfkap[2v]}
-    \quad.
-\end{align}
-%
-The integral in this expression is the same as that in Equation (D38)
-of \citet{Luger2019}, except for a change in the limits of integration.
-As in \citet{Luger2019}, we can compute this integral recursively given
-a trivial lower boundary condition:
-%
-\begin{proof}{I}
-    \label{eq:Irec}
-    \mathcal{I}_0(\bkappa) &=
-    \frac{\Delta \bkappa}{2}
-    %
-    \nonumber \\
-    %
-    \mathcal{I}_v(\bkappa) &=
-    \frac{1}{2v}
-    \bigg(
-    (2v - 1) \mathcal{I}_{v-1}(\bkappa) -
-    \Delta \left(\sinhalfkap[2v - 1]\coshalfkap\right)
-    \bigg)
-\end{proof}
-%
-where the last expression is valid for all $v > 0$. We find that this algorithm
-is generally stable, except when $\sin\left(\frac{\bkappa}{2}\right)$ is small.
-In that limit, we evaluate $\mathcal{I}_N(\bkappa)$ by numerical integration of
-Equation~(\ref{eq:I}) using Gauss-Legendre quadrature with \STARRYQUADPOINTS
-points. We then recurse downward by substituting $v \rightarrow v + 1$ in
-Equation~(\ref{eq:Irec}) and solving for $\mathcal{I}_v(\bkappa)$.
 

### 2020-04-09 tex/ms.tex
reorg

@@
 
-\usepackage{amsmath}
-\usepackage{fontspec}
-\usepackage{unicode-math}
-
-% Shorthand for this paper
-\usepackage{xifthen}
-\newcommand{\BF}[1]{\ensuremath{\mathbf{#1}}}
-\newcommand{\BS}[1]{\ensuremath{\pmb{#1}}}
-\newcommand{\dd}{\ensuremath{\text{d}}}
-\newcommand{\STARRYQUADPOINTS}{100\xspace}
-\newcommand{\bkappa}{\BS{\kappa}}
-\newcommand{\blambda}{\BS{\lambda}}
-\newcommand{\bxi}{\BS{\xi}}
-\newcommand{\vmax}{{v_\text{max}}}
-\newcommand{\coshalfkap}[1][]{%
-\ifthenelse{%
-    \equal{#1}{}
-}{
-    \cos\left(\frac{\bkappa}{2}\right)
-}{
-    \cos^{#1}\left(\frac{\bkappa}{2}\right)
-}}
-\newcommand{\sinhalfkap}[1][]{%
-\ifthenelse{%
-    \equal{#1}{}
-}{
-    \sin\left(\frac{\bkappa}{2}\right)
-}{
-    \sin^{#1}\left(\frac{\bkappa}{2}\right)
-}}
-\newcommand{\DE}{\Delta \BS{E}(k^2, \bkappa)}
-\newcommand{\DF}{\Delta \BS{F}(k^2, \bkappa)}
-\newcommand{\sgn}{{\text{sgn}}}
-\newcommand{\xhat}{\ensuremath{\pmb{\hat{x}}}\xspace}
-\newcommand{\yhat}{\ensuremath{\pmb{\hat{y}}}\xspace}
-\newcommand{\zhat}{\ensuremath{\pmb{\hat{z}}}\xspace}
-\newcommand{\sT}{\ensuremath{\mathbbb{s}^\top}}
-\newcommand{\rT}{\ensuremath{\mathbbb{r}^\top}}
-\newcommand{\pT}{\ensuremath{\mathbbb{p}^\top}}
-\newcommand{\tT}{\ensuremath{\mathbbb{t}^\top}}
-\newcommand{\qT}{\ensuremath{\mathbbb{q}^\top}}
-\newcommand{\sTe}{\ensuremath{\BF{s}^\top}}
-\newcommand{\rTe}{\ensuremath{\BF{r}^\top}}
-\newcommand{\bg}{\ensuremath{\tilde{\BF{g}}}}
-\newcommand{\bp}{\ensuremath{\tilde{\BF{p}}}}
-\newcommand{\by}{\ensuremath{\tilde{\BF{y}}}}
-\newcommand{\iI}{\ensuremath{\mathbbb{i}}}
-\newcommand{\iJ}{\ensuremath{\mathbbb{j}}}
-\newcommand{\iU}{\ensuremath{\mathbbb{u}}}
-\newcommand{\iW}{\ensuremath{\mathbbb{w}}}
-\newcommand{\vint}[2]{%
-\int\limits_{#1}
-#2
-\dd\varphi
-}
-
-% REMOVE
-\newcommand{\kapint}[1]{%
-\sum_{i = 0}^{\frac{N - 1}{2}}
-\int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
-#1
-\dd\varphi
-}
-\newcommand{\lamint}[1]{%
-\sum_{i = 0}^{\frac{N - 1}{2}}
-\int\limits_{\frac{1}{2}\lambda_{2i}}^{\frac{1}{2}\lambda_{2i+1}}
-#1
-}
-
-% Bibliography stuff
+% Load custom style
+\input{style}
+
+% Bibliography
 \bibliographystyle{aasjournal}
@@
 This is an extension of \citet{Luger2019}.
+\xxx{
+    \textbf{To do list:}
+    \begin{itemize}
+        \item Make our frame convention explicit.
+              Unprimed = sky. Prime = greens. Double prime = term.
+        \item Emphasize why we can't just analytically weight the nightside by
+              zero and integrate as before.
+        \item Add a table clarifying the notation.
+    \end{itemize}
+}
 
@@
 %
-\textbf{Note:}
-This section closely follows the
+This paper closely follows the
 notation and formalism introduced in \citet{Luger2019}. While we
-include all of the relevant equations and definitions in
-Appendix~\ref{app:starry}, the reader is encouraged to
-review \S2--3 of \citet{Luger2019} before proceeding.
-
-\xxx{Unprimed = sky. Prime = greens. Double prime = term.}
-\xxx{Emphasize why we can't just analytically weight the nightside by
-    zero and integrate as before.}
+include all of the relevant equations and definitions below,
+the reader is encouraged to
+review \citet{Luger2019} before proceeding.
 
@@
 %
+\xxx{Add equations for the rotation and change of basis matrices below.}
 Without loss of generality, assume the body whose flux we wish to compute
@@
 system in some frame $\mathcal{F}_0$. In this frame,
-the surface (emitted) intensity field of the body is described by the
-spherical harmonic coefficient vector $\mathbf{y}$.
+the surface (emitted) intensity field of the body is described by a
+vector $\mathbf{y}$ of coefficients in the spherical harmonic
+basis $\by$:
+%
+\begin{align}
+    \label{eq:by}
+    \by & =
+    \begin{pmatrix}
+        Y_{0, 0}  &
+        Y_{1, -1} & Y_{1, 0}  & Y_{1, 1} &
+        Y_{2, -2} & Y_{2, -1} & Y_{2, 0} & Y_{2, 1} & Y_{2, 2} &
+        \cdot\cdot\cdot
+    \end{pmatrix}^\top
+    \quad,
+\end{align}
+%
+where the component at index $n$ is $Y_{l,m}$ with
+%
+\begin{align}
+    \label{eq:l-m}
+    l & = \floor*{\sqrt{n}}
+    \nonumber               \\
+    m & = n - l^2 - l
+    \quad.
+\end{align}
+%
 An observer views the body from a large distance in the sky frame
@@
     \label{eq:sTARRy}
-    f = \sTe \BF{A} \BF{R}' \BF{R} \BF{y}
-    \quad,
-\end{align}
-%
-where, from right to left, $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
+    f = \sTe \mathbf{A} \mathbf{R}' \mathbf{R} \mathbf{y}
+    \quad,
+\end{align}
+%
+where, from right to left, $\mathbf{R} = \mathbf{R}(i, \lambda, \vartheta)$
 is a Wigner rotation matrix that rotates $\bvec{y}$ from $\mathcal{F}_0$
@@
 %
-$\BF{R}' = \BF{R}'(x_o, y_o)$ rotates the body on the plane
+$\mathbf{R}' = \mathbf{R}'(x_o, y_o)$ rotates the body on the plane
 of the sky into the integration frame $\mathcal{F}'$, in which the
@@
 %
-$\BF{A}$ is the change-of-basis matrix from $\by$
-to the \emph{Green's basis} $\bg$ in which the integrals are computed
-(Equations~\ref{eq:by}, \ref{eq:bg}, and \ref{eq:A}),
+$\mathbf{A}$ is the change-of-basis matrix from $\by$
+to the \emph{Green's basis} $\bg$ in which the integrals are computed,
+whose component at index $n$ is
+%
+\begin{align}
+    \label{eq:bg}
+    \tilde{g}_{n}(x, y) & =
+    \begin{dcases}
+        %
+        \frac{\mu+2}{2}x^\frac{\mu}{2} y^\frac{\nu}{2}
+         & \qquad \mu, \nu \, \text{even}
+        \\[1em]
+        %
+        z(x, y)
+         & \qquad \mu = \nu = 1
+        \\[1em]
+        %
+        3x^{l-2}yz(x, y)
+         & \qquad \nu \, \text{odd}, \,
+        \mu = 1, \,
+        \frac{\mu + \nu}{2} \, \text{even}
+        \\[1em]
+        %
+        z(x, y)
+        \bigg(
+        -x^{l-3} + x^{l-1} + 4x^{l-3}y^2
+        \bigg)
+         & \qquad \nu \, \text{odd}, \,
+        \mu = 1, \,
+        \, \text{odd}
+        \\[1em]
+        %
+        z(x, y)
+        \bigg(
+        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu-1}{2}
+        \ - \
+        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu+3}{2}
+        \\
+        \qquad\qquad \ - \
+        \frac{\mu+3}{2} x^\frac{\mu-1}{2} y^\frac{\nu-1}{2}
+        \bigg)
+         & \qquad \text{otherwise}
+        \quad,
+    \end{dcases}
+\end{align}
+%
+with
+%
+\begin{align}
+    \label{eq:mu-nu}
+    \mu & \equiv l - m
+    \nonumber          \\
+    \nu & \equiv l + m
+\end{align}
+%
+and
+%
+\begin{align}
+    z(x, y) \equiv \sqrt{1 - x^2 - y^2}
+    \quad,
+\end{align}
 %
@@
 the projected visible disk of the body for each term in $\bg$
-(Equation~\ref{eq:sTe}), with $b_o = \sqrt{x_o^2 + y_o^2}$.
-%
+\citep[Equation~26 in][]{Luger2019}, with $b_o = \sqrt{x_o^2 + y_o^2}$.
+
 If instead no occultor is present, we compute the total
@@
     \label{eq:rTA1Ry}
-    f_0 = \rTe \BF{A_1} \BF{R}'' \BF{R} \BF{y}
-    \quad,
-\end{align}
-%
-where, as before, $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
+    f_0 = \rTe \mathbf{A_1} \mathbf{R}'' \mathbf{R} \mathbf{y}
+    \quad,
+\end{align}
+%
+where, as before, $\mathbf{R} = \mathbf{R}(i, \lambda, \vartheta)$
 rotates the body from $\mathcal{F}_0$
@@
 %
-$\BF{R}''$ rotates the body on the plane
+$\mathbf{R}''$ rotates the body on the plane
 of the sky into the integration frame
@@
     In \citet{Luger2019}, $\mathcal{F}'' = \mathcal{F}'$, so
-    this rotation is trivial: $\BF{R}''$ is just the identity matrix.
+    this rotation is trivial: $\mathbf{R}''$ is just the identity matrix.
 },
 %
-$\BF{A_1}$ is the change-of-basis matrix from the spherical harmonic
+$\mathbf{A_1}$ is the change-of-basis matrix from the spherical harmonic
 basis $\by$ to the \emph{polynomial basis} $\bp$ in which the integrals
-are computed (Equations~\ref{eq:bp} and \ref{eq:A1}),
+are computed, whose component at index $n$ is
+%
+\begin{align}
+    \tilde{p}_n(x, y) & =
+    \begin{dcases}
+        x^\frac{\mu}{2} y^\frac{\nu}{2}
+         & \qquad \mu, \nu \, \text{even}
+        \\[1em]
+        x^\frac{\mu-1}{2} y^\frac{\nu-1}{2} z(x, y)
+         & \qquad \text{otherwise}
+        \quad,
+    \end{dcases}
+\end{align}
 %
@@
 the projected visible disk of the body for each term in $\bp$
-(Equation~\ref{eq:rTe}).
-%
-For more details, see Appendix~\ref{app:starry} and \citet{Luger2019}.
+\citep[Equation~19 in][]{Luger2019}.
 
@@
 Since $I$ is just a polynomial in $x$, $y$, and $z(x, y)$, we
-can express it as a vector $\BF{i}(b, \theta)$ in the polynomial basis $\bp$.
+can express it as a vector $\mathbf{i}(b, \theta)$ in the polynomial basis $\bp$.
 Recalling the structure of the basis (Equation~\ref{eq:bp}),
@@
 \begin{proof}{}
-    \BF{i}(b, \theta, r_s) & =
+    \mathbf{i}(b, \theta, r_s) & =
     \frac{1}{4\pi r_s^2}
@@
 %
-This fact allows us to construct a linear operator $\BF{I}$ to weight a map
+This fact allows us to construct a linear operator $\mathbf{I}$ to weight a map
 vector in the polynomial basis by the illumination profile.
-If we think about how each of the terms in $\bp$ transforms under $\BF{I}$,
+If we think about how each of the terms in $\bp$ transforms under $\mathbf{I}$,
 %
@@
         \end{pmatrix}
-         & \BS{\rightarrow}
+         & \pmb{\rightarrow}
         \begin{pmatrix}
@@
 %
-we can compose $\BF{I}$ out of these column vectors:
-%
-\begin{proof}{}
-    \BF{I}(b, \theta, r_s) & =
+we can compose $\mathbf{I}$ out of these column vectors:
+%
+\begin{proof}{}
+    \mathbf{I}(b, \theta, r_s) & =
     \frac{1}{4\pi r_s^2}
@@
 Note, importantly, that this weighting is valid only on the dayside
-hemisphere (see Equation~\ref{eq:illum}), as the operator $\BF{I}$ weights
+hemisphere (see Equation~\ref{eq:illum}), as the operator $\mathbf{I}$ weights
 points on the nightside by a \emph{negative} amount, which is clearly
@@
     \sT(b, \theta', b_o, r_o)
-    \BF{A_2}
-    \BF{I}(b, \theta', r_s)
-    \BF{A_1}
-    \BF{R}'(x_o, y_o)
-    \BF{R}(i, \lambda, \vartheta)
-    \BF{y}
+    \mathbf{A_2}
+    \mathbf{I}(b, \theta', r_s)
+    \mathbf{A_1}
+    \mathbf{R}'(x_o, y_o)
+    \mathbf{R}(i, \lambda, \vartheta)
+    \mathbf{y}
     \quad,
@@
     \label{eq:theta'}
-    \theta' = \text{arctan2}(x_o, y_o) - \text{arctan2}(x_s, y_s)
+    \theta' = \atantwo(x_o, y_o) - \atantwo(x_s, y_s)
 \end{align}
@@
 Note that we made use of the fact that
-$\BF{A} = \BF{A_2} \BF{A_1}$
-(Equation~\ref{eq:A}), where $\BF{A_1}$ transforms from
+$\mathbf{A} = \mathbf{A_2} \mathbf{A_1}$
+(Equation~\ref{eq:A}), where $\mathbf{A_1}$ transforms from
 the spherical harmonic basis $\by$ to the polynomial basis $\bp$, and
-$\BF{A_2}$ transforms from $\bp$ to the Green's basis $\bg$.
+$\mathbf{A_2}$ transforms from $\bp$ to the Green's basis $\bg$.
 
@@
     \rT(b)
-    \BF{I}(b, \theta'', r_s)
-    \BF{A_1}
-    \BF{R}''(x_s, y_s)
-    \BF{R}(i, \lambda, \vartheta)
-    \BF{y}
+    \mathbf{I}(b, \theta'', r_s)
+    \mathbf{A_1}
+    \mathbf{R}''(x_s, y_s)
+    \mathbf{R}(i, \lambda, \vartheta)
+    \mathbf{y}
     \quad,
@@
 construction. The transformation
-$\BF{R}'' = \BF{R}''(x_s, y_s)$ (Equation~\ref{eq:R''}) rotates
+$\mathbf{R}'' = \mathbf{R}''(x_s, y_s)$ (Equation~\ref{eq:R''}) rotates
 the body so the semi-major axis of the terminator is aligned
@@
 As we mentioned above, we must modify the integration limits to exclude the
-nightside, where the weighting by $\BF{I}$ is unphysical.
+nightside, where the weighting by $\mathbf{I}$ is unphysical.
 The vectors $\rT$ and $\sT$ correspond to these
@@
 Figure~\ref{fig:frames} summarizes the transformations involved in the two
-equations above. Starting on the right with a map vector $\BF{y}$ in
+equations above. Starting on the right with a map vector $\mathbf{y}$ in
 the spherical harmonic basis $\by$, defined in some observer-independent frame
-$\mathcal{F}_0$, we first rotate it via $\BF{R}$ to the sky frame
+$\mathcal{F}_0$, we first rotate it via $\mathbf{R}$ to the sky frame
 $\mathcal{F}$, in which the body is viewed by the
 observer. If an occultor is present (upper branch of the figure),
-we rotate the map from $\mathcal{F}$ via $\BF{R}'$ to the frame
+we rotate the map from $\mathcal{F}$ via $\mathbf{R}'$ to the frame
 $\mathcal{F}'$, in which the occultor lies along the
-$+y'$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$ and $\BF{I}$
+$+y'$-axis. We then apply $\mathbf{A_1}$ to change basis to $\bp$ and $\mathbf{I}$
 to weight the map by the illumination. Finally, we change basis
-via $\BF{A_2}$ to the Green's basis, in which we compute and dot the
+via $\mathbf{A_2}$ to the Green's basis, in which we compute and dot the
 integrals $\sT$.
 If, on the other hand, there is no occultation (lower branch of the figure),
-we instead rotate the map via $\BF{R}''$ to the integration frame
+we instead rotate the map via $\mathbf{R}''$ to the integration frame
 $\mathcal{F}''$, in which the terminator is parallel to the
-$x''$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$, apply the
-illumination transform $\BF{I}$, and finally dot in the solutions to the
+$x''$-axis. We then apply $\mathbf{A_1}$ to change basis to $\bp$, apply the
+illumination transform $\mathbf{I}$, and finally dot in the solutions to the
 surface integrals $\rT$.
@@
     \label{eq:rTI}
-    \BS{\rho}^\top(b, r_s) & \equiv
+    \pmb{\rho}^\top(b, r_s) & \equiv
     \rT(b) \mathbf{I}(b, 0, r_s)
@@
 Equation~(\ref{eq:rTI}) may be solved analytically in terms of purely
-trigonometric and algebraic functions of $b$. The component of $\BS{\rho}^\top$
+trigonometric and algebraic functions of $b$. The component of $\pmb{\rho}^\top$
 at index $n$ is given by
@@
 %
-Once $\BS{\rho}^\top$ is known, the observed flux is computed from
+Once $\pmb{\rho}^\top$ is known, the observed flux is computed from
 (c.f. Equation~\ref{eq:rTIA1RRy})
@@
     f_0 & =
-    \BS{\rho}^\top(b, r_s)
-    \BF{A_1}
-    \BF{R}''(x_s, y_s)
-    \BF{R}(i, \lambda, \vartheta)
-    \BF{y}
+    \pmb{\rho}^\top(b, r_s)
+    \mathbf{A_1}
+    \mathbf{R}''(x_s, y_s)
+    \mathbf{R}(i, \lambda, \vartheta)
+    \mathbf{y}
     \quad.
@@
     \hat{f}_0 & =
-    -\BS{\rho}^\top(-b, r_s)
-    \BF{A_1}
-    \BF{R}''(-x_s, -y_s)
-    \BF{R}(i, \lambda, \vartheta)
-    \BF{y}
+    -\pmb{\rho}^\top(-b, r_s)
+    \mathbf{A_1}
+    \mathbf{R}''(-x_s, -y_s)
+    \mathbf{R}(i, \lambda, \vartheta)
+    \mathbf{y}
     \quad,
@@
 include sections of the terminator, sections of the limb of the body,
-and sections of the limb of the occultor. There are in total 14 families of
-configurations, each defined by a distinct combination of integration
+and sections of the limb of the occultor. The integration regions may also
+be disjoint; for instance, in case 7 of Figure~\ref{fig:cases}, the
+portion of the dayside that is unocculted consists of two separate
+regions.
+
+Whereas in \citet{Luger2019} we compute the observed flux by always
+integrating over the unocculted portion of the disk, here we find that
+it is often easier and more computationally efficient to compute the
+integral of the intensity over the
+\emph{simplest} region -- meaning the one with the fewest boundaries --
+and combine it with the formalism from \S\ref{sec:solution-no-occ} to
+compute the visible flux. These integrals may be over the unocculted dayside,
+the occulted dayside, the unocculted nightside, or the occulted nightside;
+in the case of the latter three, a bit of algebra
+(\S\ref{sec:cases-pathological}--\S\ref{sec:cases-pathological}) is needed
+to relate these to the observed flux. Additionally, in some cases we can
+avoid computing new integrals entirely, as the solution can be obtained from
+a combination of the classical \starry solution vector $\sT$ and the
+formalism from the unocculted case (\S\ref{sec:solution-no-occ}).
+
+After exhaustive experimentation, we identified in total 14 families of
+geometrical configurations for the occultation problem,
+each defined by a distinct combination of integration
 boundaries; these are shown in Figures~\ref{fig:cases} and
@@
 occultor position.
-
-\xxx{In general, we do not just integrate over the dayside. We integrate over
-    the simplest region -- usually the one with the fewest boundaries --
-    and combine it with the formalism from \S\ref{sec:solution-no-occ} to
-    compute the visible flux.}
 
@@
             cases require integration along the orange boundary (the curves
-            $P$, $T$, and $Q$ of
+            $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$ of
             \S\ref{sec:cases-hard}), which
@@
 %
-We wish to find the set of $N$ points
-$\BS{x''} = \{x_n''~\big|~0~\le~n~<~N\}$
+We wish to find the vector of $N$ points
+$\mathbf{x''} = \left(x_0, x_1, {\cdot\cdot\cdot}, x_{N-1}\right)^\top$
 for which
@@
     \sTe(b_o, r_o)
-    \BF{A_2}
-    \BF{I}(b, \theta', r_s)
-    \BF{A_1}
-    \BF{R}'(x_o, y_o)
-    \BF{R}(i, \lambda, \vartheta)
-    \BF{y}
+    \mathbf{A_2}
+    \mathbf{I}(b, \theta', r_s)
+    \mathbf{A_1}
+    \mathbf{R}'(x_o, y_o)
+    \mathbf{R}(i, \lambda, \vartheta)
+    \mathbf{y}
     \quad,
@@
 measure from a body whose surface map is weighted by the illumination function
-$\BF{I}(b, \theta', r_s)$ during an occultation. Note that this is not
+$\mathbf{I}(b, \theta', r_s)$ during an occultation. Note that this is not
 necessarily the \emph{observed} flux, since this may include the unphysical
@@
             surface intensity map along the boundary curves
-            $P$, $T$, and $Q$. See text for details.
+            $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$. See text for details.
             \label{fig:geometry}
@@
 over the region $S$ bounded by three curves, which we denote
-$P$, $T$, and $Q$. These are shown in orange
+$\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$. These are shown in orange
 in Figure~\ref{fig:cases} and presented in more detail in
 Figure~\ref{fig:geometry}.
-Curve $P$ is a segment of the limb of
+Curve $\mathcal{P}$ is a segment of the limb of
 the occultor, parametrized by the angle $\phi \in [\phi_0, \phi_1]$;
-curve $T$ is a segment of the terminator,
+curve $\mathcal{T}$ is a segment of the terminator,
 parametrized by the angle $\xi \in [\xi_0, \xi_1]$;
-and curve $Q$ is a segment of the limb of the occulted body,
+and curve $\mathcal{Q}$ is a segment of the limb of the occulted body,
 parametrized by the angle $\lambda \in [\lambda_0, \lambda_1]$.
@@
     \sT(b, \theta', b_o, r_o)
-    \BF{A_2}
-    \BF{I}(b, \theta', r_s)
-    \BF{A_1}
-    \BF{R}'(x_o, y_o)
-    \BF{R}(i, \lambda, \vartheta)
-    \BF{y}
+    \mathbf{A_2}
+    \mathbf{I}(b, \theta', r_s)
+    \mathbf{A_1}
+    \mathbf{R}'(x_o, y_o)
+    \mathbf{R}(i, \lambda, \vartheta)
+    \mathbf{y}
     \quad.
@@
 (see Figures~\ref{fig:cases} and \ref{fig:geometry}) is the occulted
-portion of the dayside, which is bounded by all three curves $P$, $Q$, and $T$.
+portion of the dayside, which is bounded by all three curves $\mathcal{P}$, $\mathcal{Q}$, and $\mathcal{T}$.
 The total flux may
@@
 is to use Green's theorem to transform the surface integrals into line
-integrals along the curves $P$, $T$, and $Q$
+integrals along the curves $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$
 (see Figure~\ref{fig:geometry}). Specifically, we write%
@@
 where $\bvec{G} (x', y')$
-is an array of two-dimensional Cartesian vectors chosen such that its
+is a vector of two-dimensional Cartesian vectors chosen such that its
 exterior derivative is $\bg$,
@@
 \begin{align}
-    \dd \BF{r} (x', y') & =
+    \dd \mathbf{r} (x', y') & =
     \left(\frac{\dd x'}{\dd \varphi}\right) \dd \varphi \, \xhat' +
@@
     \label{eq:G}
-    \BF{G}_n (x, y) & =
+    \mathbf{G}_n (x, y) & =
     \begin{dcases}
@@
 We showed in the previous sections that there are at most three curves
-$P$, $T$, and $Q$ bounding a given closed surface of integration
+$\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$ bounding a given closed surface of integration
 (see Figure~\ref{fig:geometry}). We may therefore express
@@
     & =
-    \int\limits_{\BS{\phi}}
+    \int\limits_{\pmb{\phi}}
     \mathbf{G}^\top(x'_p, y'_p)
@@
     & =
-    \int\limits_{\BS{\xi}}
+    \int\limits_{\pmb{\xi}}
     \mathbf{G}^\top(x'_t, y'_t)
@@
     & =
-    \int\limits_{\BS{\lambda}}
+    \int\limits_{\pmb{\lambda}}
     \mathbf{G}^\top(x'_q, y'_q)
@@
 to be the line integrals of $\mathbf{G}$ along each of the curves
-$P$, $T$, and $Q$, respectively, where the coordinates along each
+$\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$, respectively, where the coordinates along each
 curve are parametrized
@@
 \begin{align}
-    \int\limits_{\BS{\varphi}} & \equiv
+    \label{eq:vint}
+    \int\limits_{\pmb{\varphi}} & \equiv
     %
@@
 to be the sum of definite integrals between pairs of limits $\varphi_i$
-arranged in an array $\BS{\varphi}$ of length $N$.
-For cases involving integration over a single closed region, this
-corresponds to a single integral. For cases 11--14, this corresponds to
-the sum of two integrals, one for each of the two disjoint regions.
-In the next three sections, we derive the solutions to each of these
-primitive integrals.
-
-\xxx{It is useful to} define the pairwise difference operator
+arranged in a vector $\pmb{\varphi}$ of length $N$.
+%
+For future reference, it will also be useful to define the operator
 %
@@
     \label{eq:pairdiff}
-    \Delta \BS{v} \equiv \sum_{i=0}^{\frac{N - 1}{2}}
-    \left( v_{2i + 1} - v_{2i} \right)
+    \Delta \mathbf{x} \equiv \sum_{i=0}^{\frac{N - 1}{2}}
+    \left( x_{2i + 1} - x_{2i} \right)
+    \quad,
 \end{align}
@@
 which sums the difference of successive pairs of values in
-an array $\BS{v} = \{ v_0, v_1, v_2, v_3, {\cdot\cdot\cdot}, v_N\}$.
+a vector
+$\mathbf{x} = \left( x_0, x_1, x_2, x_3, {\cdot\cdot\cdot}, x_{N - 1} \right)^\top$.
+This will come in handy when computing definite integrals. Specifically,
+if $F$ is the antiderivative of some function $f$, we may use the
+fundamental theorem of calculus to compute the integral of
+$f$ over the interval(s) given
+by the vector of limit pairs $\pmb{\varphi}$:
+%
+\begin{align}
+    \vint{\pmb{\varphi}}{f(\varphi)}
+     & = \int\limits_{\varphi_{0}}^{\varphi_{1}} f(\varphi) \dd\varphi
+    +
+    \int\limits_{\varphi_{2}}^{\varphi_{3}} f(\varphi) \dd\varphi
+    +
+    {\cdot\cdot\cdot}
+    +
+    \int\limits_{\varphi_{N - 2}}^{\varphi_{N - 1}} f(\varphi) \dd\varphi
+    \nonumber                                                          \\
+     & = \Delta \mathbf{F}(\pmb{\varphi})
+\end{align}
+%
+where $\mathbf{F}$ is the vector given by
+%
+\begin{align}
+    \mathbf{F}(\pmb{\varphi}) =
+    \bigg( F(\varphi_0), F(\varphi_1), F(\varphi_2), F(\varphi_3),
+    {\cdot\cdot\cdot}, F(\varphi_{N - 2}), F(\varphi_{N - 1}) \bigg)^\top
+    \quad.
+\end{align}
+%
+Note that most of the cases (1--10) involve integration over a single closed
+region, so Equations~(\ref{eq:vint}) and (\ref{eq:pairdiff}) reduce to
+%
+\begin{align}
+    \int\limits_{\pmb{\varphi}} & \equiv
+    %
+    \int\limits_{\varphi_{0}}^{\varphi_{1}}
+\end{align}
+%
+and
+%
+\begin{align}
+    \Delta \mathbf{x} \equiv x_1 - x_0
+    \quad.
+\end{align}
+%
+For cases 11--14, we must integrate over two disjoint regions, so we
+sum over two pairs of limits.
+%
+In the next three sections, we derive the solutions to each of the
+primitive integrals $\pT$, $\tT$, and $\qT$.
 
@@
 order of business is to derive expressions for the integration limits
-$\BS{\phi}$. Depending on the integration case, these limits will correspond
+$\pmb{\phi}$. Depending on the integration case, these limits will correspond
 to the point of intersection between the limb of the occultor and the
@@
 \begin{align}
-    \BS{\phi_t} & =
-    \theta' + \text{arctan2}\left(b\sqrt{1 - \BS{x''}^2 - y''_o}, \BS{x''} - x''_o\right)
+    \pmb{\phi_t} & =
+    \theta' +
+    \atantwo
+    \left(b\sqrt{1 - {\mathbf{x''}}^2 - y''_o}, \mathbf{x''} - x''_o\right)
     \quad
@@
 %
-where $\BS{x''}$ are the roots of the quartic (Equation~\ref{eq:quartic}).
-These angles are then sorted and placed in the array $\BS{\phi}$ such that
+where $\mathbf{x''}$ are the roots of the quartic (Equation~\ref{eq:quartic}).
+These angles are then sorted and placed in the vector $\pmb{\phi}$ such that
 the integration is always performed in a counter-clockwise sense about
@@
         2(2r_o)^{l+2}
-        \mathbb{V}
+        V
         \left(
@@
         0;
-        \iI
+        \viI
         \right)
@@
         \left\{
-        \mathbb{V}
+        V
         \left(
@@
         0;
-        \iJ
+        \viJ
         \right) -
         2
-        \mathbb{V}
+        V
         \left(
@@
         1;
-        \iJ
+        \viJ
         \right)
@@
         0;
-        \iJ
+        \viJ
         \right) -
-        \mathbb{V}
+        V
         \left(
@@
         2(2r_o)^{l-1} \beta\,
-        \mathbb{V}
+        V
         \left(
@@
         0;
-        \iJ
+        \viJ
         \right)
@@
         0;
-        \iU
+        \viU
         \right)
@@
         (2r_o)^{l-1} \beta\,
-        \mathbb{V}
+        V
         \left(
@@
         0;
-        \iW
+        \viW
         \right)
@@
 \begin{align}
-    \mathbb{V}\left(u, v, w; \mathbbb{x}\right) \equiv
+    V\left(u, v, w; \mathbf{x}\right) \equiv
     \sum_{i=0}^{u + v}
     \mathcal{A}_{u, v, i}
-    \mathbb{x}_{u + w + i}
-\end{align}
-%
-as the dot product of a vector $\mathbbb{x}$ and
-the vector of Vieta's theorem coefficients $\BS{\mathcal{A}}_{u, v}$, where
+    \mathbf{x}_{u + w + i}
+\end{align}
+%
+as the dot product of a vector $\mathbf{x}$ and
+the vector of Vieta's theorem coefficients, where
 \citep[c.f. Equation~D34 in][]{Luger2019}
@@
 %
-The vectors $\iI$, $\iJ$,
-$\iU$, and $\iW$ are solutions
+The vectors $\viI$, $\viJ$,
+$\viU$, and $\viW$ are solutions
 to specific integrals, which we compute recursively below. As in
-\citet{Luger2019} the $n = 2$ term of $\mathbb{p}$ (second case in the
+\citet{Luger2019} the $n = 2$ term of $\pT$ (second case in the
 equation above) is handled separately; we also compute this below.
@@
 
-\subsubsection{The vector $\iI$}
-\label{sec:i}
-%
-The components of the vector $\iI$ are given by the integral
+\subsubsection{The vector $\viI$}
+\label{sec:I}
+%
+The components of the vector $\viI$ are given by the integral
 %
@@
     \label{eq:I}
-    \mathbb{i}_v(\bkappa) & =
-    \vint{\bkappa}{\sinhalfkap[2v]}
+    \iI_v(\vkappa) & =
+    \vint{\vkappa}{\sinhalfkap[2v]}
     \quad,
@@
 \begin{align}
-    \BS{\kappa} = \BS{\phi} + \frac{\pi}{2}
+    \pmb{\kappa} = \pmb{\phi} + \frac{\pi}{2}
     \quad.
@@
 of \citet{Luger2019}, except for a change in the limits of integration.
-As in \citet{Luger2019}, we can compute the vector $\iI$ recursively given
+As in \citet{Luger2019}, we can compute the vector $\viI$ recursively given
 a trivial lower boundary condition:
@@
     \label{eq:Irec}
-    \mathbb{i}_0(\bkappa) &=
-    \frac{\Delta \bkappa}{2}
-    %
-    \nonumber \\
-    %
-    \mathbb{i}_v(\bkappa) &=
+    \iI_0(\vkappa) &=
+    \frac{\Delta \vkappa}{2}
+    %
+    \nonumber \\
+    %
+    \iI_v(\vkappa) &=
     \frac{1}{2v}
     \bigg(
-    (2v - 1) \mathbb{i}_{v-1}(\bkappa) -
+    (2v - 1) \iI_{v-1}(\vkappa) -
     \Delta \left(\sinhalfkap[2v - 1]\coshalfkap\right)
@@
 is generally stable, except when
-$\sin\left(\nicefrac{\bkappa}{2}\right)$ is small.
-In that limit, we evaluate $\mathbb{i}_\vmax(\bkappa)$
+$\sin\left(\nicefrac{\vkappa}{2}\right)$ is small.
+In that limit, we evaluate $\iI_\vmax(\vkappa)$
 by numerical integration of
@@
 points. We then recurse downward by substituting $v \rightarrow v + 1$ in
-Equation~(\ref{eq:Irec}) and solving for $\mathbb{i}_v(\bkappa)$.
-
-\xxx{Work in progress below here.}
-
-\subsubsection{The vector $\mathbbb{j}$}
-\label{sec:j}
-%
-Define the quantity
-%
-\begin{align}
-    \label{eq:q}
-    \BS{q}(k^2, \bkappa) = \sqrt{1 - \frac{\sinhalfkap[2]}{k^2}}
-    \quad.
-\end{align}
-
-\section{Performance}
-\label{sec:performance}
-%
-\xxx{Performance!} See Figure~\ref{fig:speed}.
-%
-\begin{figure}[h!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/speed.pdf}
-        \oscaption{speed}{%
-            Evaluation time for the starry algorithm.
-            \label{fig:speed}
-        }
-    \end{centering}
-\end{figure}
-
-\appendix
-
-\xxx{Work in progress below here.}
-
-\section{The \starry formalism}
-\label{app:starry}
-%
-Equations:
-%
-\begin{align}
-    \label{eq:R}
-    \BF{R} = ?
-\end{align}
-%
-\begin{align}
-    \label{eq:by}
-    \by = ?
-\end{align}
-%
-\begin{align}
-    \label{eq:bp}
-    \bp & =
-    \begin{pmatrix}
-        1   &
-        x   & z  & y  &
-        x^2 & xz & xy & yz & y^2 &
-        \cdot\cdot\cdot
-    \end{pmatrix}^\top
-    \quad,
-\end{align}
-%
-\begin{align}
-    \label{eq:A1}
-    \BF{A_1} = ?
-\end{align}
-%
-\begin{align}
-    \label{eq:rTe}
-    \rTe = ?
-\end{align}
-%
-\begin{align}
-    \label{eq:R'}
-    \BF{R}' = ?
-\end{align}
-%
-\begin{align}
-    \label{eq:R''}
-    \BF{R}'' = ?
-\end{align}
-%
-\begin{align}
-    \label{eq:A}
-    \BF{A} = ?
-\end{align}
-%
-\begin{align}
-    \label{eq:sTe}
-    \sTe = ?
-\end{align}
-%
-The basis $\bg$ is called the \emph{Green's basis}; its name
-stems from the fact that its components have a structure that makes integration
-by Green's theorem convenient. Its components were defined in
-Equation~11 of \citet{Luger2019b}:
-%
-\begin{proof}{bg}
-    \tilde{g}_{l,m} &=
-    \begin{dcases}
-        %
-        \frac{\mu+2}{2}x^\frac{\mu}{2} y^\frac{\nu}{2}
-         & \qquad \mu, \nu \, \text{even}
-        \\[1em]
-        %
-        z(x, y)
-         & \qquad \mu = \nu = 1
-        \\[1em]
-        %
-        3x^{l-2}yz(x, y)
-         & \qquad \nu \, \text{odd}, \,
-        \mu = 1, \,
-        \frac{\mu + \nu}{2} \, \text{even}
-        \\[1em]
-        %
-        z(x, y)
-        \bigg(
-        -x^{l-3} + x^{l-1} + 4x^{l-3}y^2
-        \bigg)
-         & \qquad \nu \, \text{odd}, \,
-        \mu = 1, \,
-        \, \text{odd}
-        \\[1em]
-        %
-        z(x, y)
-        \bigg(
-        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu-1}{2}
-        \ - \
-        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu+3}{2}
-        \\
-        \qquad\qquad \ - \
-        \frac{\mu+3}{2} x^\frac{\mu-1}{2} y^\frac{\nu-1}{2}
-        \bigg)
-         & \qquad \text{otherwise}
-        \quad,
-    \end{dcases}
-    \label{eq:bg}
-\end{proof}
-%
-where $x$ and $y$ are the Cartesian coordinates on the surface
-of the projected
-disk of the body, with $z(x, y) = \sqrt{1 - x^2 - y^2}$, and
-%
-\begin{align}
-    \label{eq:munu}
-    \mu & = l - m
-    \nonumber     \\
-    \nu & = l + m
-    \quad.
-\end{align}
-%
-The vector $\bg$ is ordered such that
-the component at index $n$ is $\tilde{g}_{l,m}$, with
-%
-\begin{align}
-    \label{eq:lm}
-    l & = \floor*{\sqrt{n}} \nonumber \\
-    m & = n - l^2 - l
-    \quad.
-\end{align}
-%
-Finally, the rotation matrix $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
-rotates the body to the correct orientation on the sky given its
-inclination $i$, obliquity $\lambda$, and rotational phase $\vartheta$,
-while $\BF{R}'$ rotates the body on the plane
-of the sky into the frame $\mathcal{F}'$ in which the integration is
-actually performed, with the occultor along the $+y'$-axis.
-For more information on all of these terms, the reader is referred to
-\citet{Luger2019}.
-
-The \emph{polynomial basis} $\bp$
-\citep[Equation 7 in][]{Luger2019}:
-%
-\begin{align}
-    \tilde{p}_{l,m}(x, y) & =
-    \begin{dcases}
-        x^\frac{\mu}{2} y^\frac{\nu}{2}
-         & \qquad \mu, \nu \, \text{even}
-        \\[1em]
-        x^\frac{\mu-1}{2} y^\frac{\nu-1}{2} z(x, y)
-         & \qquad \text{otherwise} \quad,
-    \end{dcases}
-\end{align}
-%
-where $\bp$ is again ordered such that the component at
-index $n$ is $\tilde{p}_{l,m}$, with $l$ and $m$ given by
-Equation~(\ref{eq:lm}).
-
-As in \citet{Luger2019}, the elements of the solution vector $\mathbf{s}^\top$
-are given by the line integral
-%
-\begin{align}
-    \label{eq:s}
-    s_{n(\mu,\nu)} = \oint \mathbf{G}_{\mu,\nu} \cdot \dd\mathbf{r}
-\end{align}
-%
-where
-%
-\begin{align}
-    \label{eq:G}
-    \BF{G}_{\mu,\nu} (x, y) & =
-    \begin{dcases}
-        %
-        x^{\frac{\mu + 2}{2}}
-        y^{\frac{\nu}{2}}
-        \,\yhat
-         & \qquad \mu, \nu \, \text{even}
-        \\[1em]
-        %
-        \frac{1-z(x, y)^3}{3(1-z(x, y)^2)}\bigg(-y \, \xhat + x \, \yhat\bigg)
-         & \qquad \mu = \nu = 1
-        \\[1em]
-        %
-        x^{l-2}
-        z(x, y)^3
-        \,\xhat
-         & \qquad \nu \, \text{odd}, \,
-        \mu = 1, \,
-        \frac{\mu + \nu}{2} \, \text{even}
-        \\[1em]
-        %
-        x^{l-3}
-        y
-        z(x, y)^3
-        \,\xhat
-         & \qquad \nu \, \text{odd}, \,
-        \mu = 1, \,
-        \frac{\mu + \nu}{2} \, \text{odd}
-        \\[1em]
-        %
-        x^{\frac{\mu-3}{2}}
-        y^{\frac{\nu-1}{2}}
-        z(x, y)^3
-        \,\yhat
-         & \qquad \text{otherwise,}
-    \end{dcases}
-\end{align}
-%
-and
-%
-\begin{align}
-    \dd \BF{r} & = -r \sin\varphi \, \dd \varphi \, \xhat +
-    r \cos\varphi \, \dd \varphi \, \yhat
-    \quad,
-\end{align}
-%
-where $\varphi = \varphi(x, y)$ is the parametrized angle along the
-arc of integration. Generally, there are at most three arcs bounding a given
-closed surface of integration, which we will denote $\mathcal{P}$,
-$\mathcal{Q}$, and $\mathcal{T}$. These are shown for a typical
-occultor-occulted configuration in Figure~\ref{fig:geometry}.
-
-\subsection{$\mathcal{H}_{u,v}$}
-%
-The function $\mathcal{H}_{u,v}$ is given by
-%
-\begin{align}
-    \label{eq:H}
-    \mathcal{H}_{u,v}(\blambda) & =
-    \lamint{
-        \cos^u\varphi
-        \sin^v\varphi
-    }
-    \quad.
-\end{align}
-%
-The integral in this expression is the same as that in Equation (D27)
-of \citet{Luger2019}, except for a change in the limits of integration.
-We can compute this integral recursively given four lower boundary conditions:
-%
-\begin{proof}{H}
-    \label{eq:Hlower}
-    \mathcal{H}_{0,0}(\blambda) &= \Delta \blambda
-    %
-    \nonumber \\
-    %
-    \mathcal{H}_{1,0}(\blambda) &= \Delta \sin\blambda
-    %
-    \nonumber \\
-    %
-    \mathcal{H}_{0,1}(\blambda) &= -\Delta \cos\blambda
-    %
-    \nonumber \\
-    %
-    \mathcal{H}_{1,1}(\blambda) &= -\frac{\Delta\cos^2\blambda}{2}
-    %
-    \quad.
-\end{proof}
-%
-The remaining terms may be computed by upward recursion using the
-relations
-%
-\begin{proof}{H}
-    \label{eq:Hrec1}
-    \mathcal{H}_{u,v}(\blambda) &=
-    \frac{
-        -\Delta \left(
-        \cos^{u + 1} \blambda
-        \sin^{v - 1} \blambda
-        \right)
-        +(v - 1)\mathcal{H}_{u,v - 2}(\blambda)
-    }{u + v}
-\end{proof}
-%
-for $u < 2, v \ge 2$ and
-%
-\begin{proof}{H}
-    \label{eq:Hrec2}
-    \mathcal{H}_{u,v}(\blambda) &=
-    \frac{
-        \Delta \left(
-        \cos^{u - 1} \blambda
-        \sin^{v + 1} \blambda
-        \right)
-        + (u - 1)\mathcal{H}_{u - 2,v}(\blambda)
-    }{u + v}
-\end{proof}
-%
-for all remaining terms.
-
-\subsection{$\mathcal{T}_{2}$}
-%
-The function $\mathcal{T}_{2}$ is given by
-%
-\begin{align}
-    \label{eq:T2}
-    \mathcal{T}_{2}(b, \bxi) & = ?
-    \quad.
-\end{align}
-
-\begin{proof}{}
-    \mathcal{T}_{2}(b, \bxi) &= -\sgn(b) \Delta \BS{f}(b, \bxi)
-\end{proof}
-%
-where
-%
-\begin{proof}{}
-    \begin{split}
-        f_i(b, \xi_i) =
-        \frac{1}{3}\scalebox{1.4}{\Bigg(}
-        &\arctan\left( \frac{|b|\sin\xi_i}{\cos\xi_i} \right)
-        %
-        \\
-        %
-        &- \sgn\left({\sin\xi_i}\right)
-        \left(
-        \arctan
-        \left(
-            \frac{
-                \left(\frac{\sin\xi_i}{1 + \cos\xi_i}\right)^2 + 2 b^2 - 1
-            }{2 |b| \sqrt{1 - b^2}}
-            \right)
-        + |b| \sqrt{1 - b^2} \cos\xi_i
-        \right)
-        %
-        \\
-        %
-        &+ \phi(b, \xi_i)
-        \scalebox{1.4}{\Bigg)}
-    \end{split}
-\end{proof}
-%
-and
-%
-\begin{proof}{}
-    \phi(b, \xi_i) & =
-    \begin{cases}
-        0                          & \qquad 0 \leq \xi_i < \frac{\pi}{2}     \\
-        \pi                        & \qquad \frac{\pi}{2} \leq \xi_i < \pi   \\
-        2 |b| \sqrt{1 - b^2}       & \qquad \pi < \xi_i \leq \frac{3\pi}{2}  \\
-        \pi + 2 |b| \sqrt{1 - b^2} & \qquad \frac{3\pi}{2} \leq \xi_i < 2\pi
-        \quad.
-    \end{cases}
-\end{proof}
-
-\subsection{$\mathcal{U}_v$}
-%
-The function $\mathcal{U}_v$ is given by
-%
-\begin{align}
-    \label{eq:U}
-    \mathcal{U}_v(\bkappa) =
-    \kapint{\cos\varphi\sin^{2v}\varphi}
-    \quad.
-\end{align}
-%
-This integral has an analytic solution for all $v$:
-%
-\begin{proof}{U}
-    \label{eq:Usol}
-    \mathcal{U}_v(\bkappa) &= \frac{\Delta \sinhalfkap[v+1]}{v + 1}
-    \quad.
-\end{proof}
-%
-
-\subsection{$\mathcal{J}_v$}
-%
-The function $\mathcal{J}_v$ is given by
+Equation~(\ref{eq:Irec}) and solving for $\iI_v(\vkappa)$.
+
+%
+
+\subsubsection{The vector $\viJ$}
+\label{sec:J}
+%
+The components of the vector $\viJ$ are given by the integral
 %
@@
     \label{eq:J}
-    \mathcal{J}_v(k^2, \bkappa) =
-    \kapint{
+    \iJ_v(k^2, \vkappa) =
+    \vint{\vkappa}{
         \sin^{2v}\varphi
@@
 In that paper, we computed all terms
-$\{ \mathcal{J}_0, {\cdot\cdot\cdot}, \mathcal{J}_\vmax \}$ from a three-term
+$\{ \iJ_0, {\cdot\cdot\cdot}, \iJ_\vmax \}$ from a three-term
 recurrence relation and two boundary conditions. In the case of upward
-recursion, the boundary conditions $\mathcal{J}_0$ and $\mathcal{J}_1$ were
+recursion, the boundary conditions $\iJ_0$ and $\iJ_1$ were
 computed analytically from the complete elliptic integrals $K(k^2)$
 and $E(k^2)$. In cases where upward recursion was not numerically stable, we
-evaluated $\mathcal{J}_\vmax$ and $\mathcal{J}_{\vmax-1}$
+evaluated $\iJ_\vmax$ and $\iJ_{\vmax-1}$
 via a quickly convergent series expansion and recursed downward.
@@
 boundary conditions \citep[Equation D46 in ][]{Luger2019} with the
-incomplete elliptic integrals $F(k^2, \kappa)$ and $E(k^2, \kappa)$,
+incomplete elliptic integrals $\mathbf{F}(k^2, \vkappa)$ and
+$\mathbf{E}(k^2, \vkappa)$,
 then use the same upward
-recursion relation to obtain analytic solutions for all $\mathcal{J}_v$:
+recursion relation to obtain analytic solutions for all $\iJ_v$:
 %
@@
     \label{eq:Jrec}
-    \mathcal{J}_0(k^2, \bkappa) &=
+    \iJ_0(k^2, \vkappa) &=
     \frac{1}{3} \bigg(
@@
     \left(\frac{1}{k^2} - 1\right) \DF +
-    \Delta \BS{z}_0(k^2, \bkappa)
+    \Delta \mathbf{z}_0(k^2, \vkappa)
     \bigg)
@@
     %
-    \mathcal{J}_1(k^2, \bkappa) &=
+    \iJ_1(k^2, \vkappa) &=
     \frac{1}{15} \bigg(
     \left(-3 k^2 + 13 - \frac{8}{k^2}\right) \DE +
+    \nonumber \\
+    &\qquad\quad\quad\quad\quad\quad\quad\quad\quad
     \left(3 k^2 - 7 + \frac{4}{k^2}\right) \DF +
-    \Delta \BS{z}_1(k^2, \bkappa)
+    \Delta \mathbf{z}_1(k^2, \vkappa)
     \bigg)
@@
     %
-    \mathcal{J}_v(k^2, \bkappa) &=
+    \iJ_v(k^2, \vkappa) &=
     \frac{1}{2v + 3}
     \bigg(
-    2 \left( v + 1 + (v - 1) k^2 \right) \mathcal{J}_{v - 1} -
-    (2v - 3) k^2 \mathcal{J}_{v - 2}
-    + \Delta \BS{z}_v(k^2, \bkappa)
+    2 \left( v + 1 + (v - 1) k^2 \right) \iJ_{v - 1} -
+    (2v - 3) k^2 \iJ_{v - 2}
+    + \Delta \mathbf{z}_v(k^2, \vkappa)
     \bigg)
@@
     \label{eq:Jrec_z}
-    \BS{z}_0(k^2, \BS{\kappa}) & =
+    \mathbf{z}_0(k^2, \pmb{\kappa}) & =
     \frac{
@@
         \coshalfkap
-        \BS{q}(k^2, \bkappa)
+        \mathbf{q}(k^2, \vkappa)
     }{
@@
     %
-    \BS{z}_1(k^2, \BS{\kappa}) & =
+    \mathbf{z}_1(k^2, \pmb{\kappa}) & =
     \left(\left(3 \sinhalfkap[2] + 4\right) - 6k^2\right)
-    \BS{z}_0(k^2, \BS{\kappa})
+    \mathbf{z}_0(k^2, \pmb{\kappa})
     %
@@
     %
-    \BS{z}_v(k^2, \BS{\kappa}) & =
+    \mathbf{z}_v(k^2, \pmb{\kappa}) & =
     k^2
@@
     \coshalfkap
-    \BS{q}(k^2, \BS{\kappa})^5
-    \quad.
-\end{proof}
+    \mathbf{q}(k^2, \pmb{\kappa})^5
+    \quad,
+\end{proof}
+%
+with
+%
+\begin{align}
+    \label{eq:q}
+    \mathbf{q}(k^2, \vkappa) = \sqrt{1 - \frac{\sinhalfkap[2]}{k^2}}
+    \quad.
+\end{align}
 %
@@
 To address this, we express the recurrence structure of the problem as
-a tridiagonal system with one lower boundary condition $\mathcal{J}_0$
-and one upper boundary condition $\mathcal{J}_\vmax$:
+a tridiagonal system with one lower boundary condition $\iJ_0$
+and one upper boundary condition $\iJ_\vmax$:
 %
@@
     \begin{pmatrix}
-        \mathcal{J}_1   \\
-        \mathcal{J}_2   \\
-        \mathcal{J}_3   \\
-        \mathcal{J}_4   \\
+        \iJ_1           \\
+        \iJ_2           \\
+        \iJ_3           \\
+        \iJ_4           \\
         \cdot\cdot\cdot \\
-        \mathcal{J}_{\vmax-1}
+        \iJ_{\vmax-1}
     \end{pmatrix}
@@
     \begin{pmatrix}
-        c_0 - b_0 \mathcal{J}_0 \\
+        c_0 - b_0 \iJ_0 \\
         c_1             \\
@@
         \cdot\cdot\cdot \\
-        c_\vmax - \mathcal{J}_\vmax
+        c_\vmax - \iJ_\vmax
     \end{pmatrix}
@@
     b_v(k) &= \frac{(2v - 3) k^2}{2v + 3} \nonumber \\
-    c_v(k^2, \bkappa) &= \Delta
+    c_v(k^2, \vkappa) &= \Delta
     \bigg(
     \frac{
-            \BS{z}_v(k^2, \BS{\kappa})
+            \mathbf{z}_v(k^2, \pmb{\kappa})
         }{
@@
 Solving this matrix system yields values for all
-intermediate $\{ \mathcal{J}_1, {\cdot\cdot\cdot}, \mathcal{J}_{\vmax - 1} \}$.
+intermediate $\{ \iJ_1, {\cdot\cdot\cdot}, \iJ_{\vmax - 1} \}$.
 While efficient algorithms exist for solving tridiagonal problems, we obtain
@@
 
-We evaluate the upper boundary condition $\mathcal{J}_{\vmax}$ by numerical
+We evaluate the upper boundary condition $\iJ_{\vmax}$ by numerical
 integration of Equation~(\ref{eq:J}) via Gauss-Legendre quadrature with
@@
 
-\subsection{$\mathcal{W}_n$}
-%
-The function $\mathcal{W}_n$ is given by
+%
+
+\subsubsection{The vector $\viU$}
+\label{sec:U}
+%
+The components of the vector $\viU$ are given by the integral
+%
+\begin{align}
+    \label{eq:U}
+    \iU_v(\vkappa) =
+    \vint{\vkappa}{\cos\varphi\sin^{2v}\varphi}
+    \quad.
+\end{align}
+%
+This integral has an analytic solution for all $v$:
+%
+\begin{proof}{U}
+    \label{eq:Usol}
+    \iU_v(\vkappa) &= \frac{\Delta \sinhalfkap[v+1]}{v + 1}
+    \quad.
+\end{proof}
+
+%
+
+\subsubsection{The vector $\viW$}
+\label{sec:W}
+%
+The components of the vector $\viW$ are given by the integral
 %
@@
     \label{eq:W}
-    % TODO
-    \mathcal{W}_n = \int
-\end{align}
-%
-This integral has a closed-form solution:
+    \iW_v(\vkappa) = ???
+    \quad.
+\end{align}
+%
+This integral also has a closed-form solution:
 %
@@
     \label{eq:Wsol}
-    \mathcal{W}_n =
-    \frac{\sin^{2n + 2}\left(\frac{\bkappa}{2}\right)}{2n + 5}
+    \iW_n =
+    \frac{\sin^{2n + 2}\left(\frac{\vkappa}{2}\right)}{2n + 5}
     \left(
@@
     \right)
+    \quad,
 \end{proof}
@@
 where ${_2F_1}(a, b; c; z)$ is the Gauss hypergeometric function.
-
-% by either upward recursion (stable for |1 - q^2| > 1/2) or downward
-% recursion (always stable).
+%
+\xxx{Figure out the integral form, and write up the recursion relations.}
+
+%
+% DEBUG
+\vfill
+\pagebreak
+%
+
+\section{Performance}
+\label{sec:performance}
+%
+\xxx{Performance!} See Figure~\ref{fig:speed}.
+%
+\begin{figure}[h!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/speed.pdf}
+        \oscaption{speed}{%
+            Evaluation time for the starry algorithm.
+            \label{fig:speed}
+        }
+    \end{centering}
+\end{figure}
+
+\appendix
+
+\xxx{Migrate this up.}
+
+%
+The function $\mathcal{H}_{u,v}$ is given by
+%
+\begin{align}
+    \label{eq:H}
+    \mathcal{H}_{u,v}(\vlambda) & =
+    \vint{\vlambda}{
+        \cos^u\varphi
+        \sin^v\varphi
+    }
+    \quad.
+\end{align}
+%
+The integral in this expression is the same as that in Equation (D27)
+of \citet{Luger2019}, except for a change in the limits of integration.
+We can compute this integral recursively given four lower boundary conditions:
+%
+\begin{proof}{H}
+    \label{eq:Hlower}
+    \mathcal{H}_{0,0}(\vlambda) &= \Delta \vlambda
+    %
+    \nonumber \\
+    %
+    \mathcal{H}_{1,0}(\vlambda) &= \Delta \sin\vlambda
+    %
+    \nonumber \\
+    %
+    \mathcal{H}_{0,1}(\vlambda) &= -\Delta \cos\vlambda
+    %
+    \nonumber \\
+    %
+    \mathcal{H}_{1,1}(\vlambda) &= -\frac{\Delta\cos^2\vlambda}{2}
+    %
+    \quad.
+\end{proof}
+%
+The remaining terms may be computed by upward recursion using the
+relations
+%
+\begin{proof}{H}
+    \label{eq:Hrec1}
+    \mathcal{H}_{u,v}(\vlambda) &=
+    \frac{
+        -\Delta \left(
+        \cos^{u + 1} \vlambda
+        \sin^{v - 1} \vlambda
+        \right)
+        +(v - 1)\mathcal{H}_{u,v - 2}(\vlambda)
+    }{u + v}
+\end{proof}
+%
+for $u < 2, v \ge 2$ and
+%
+\begin{proof}{H}
+    \label{eq:Hrec2}
+    \mathcal{H}_{u,v}(\vlambda) &=
+    \frac{
+        \Delta \left(
+        \cos^{u - 1} \vlambda
+        \sin^{v + 1} \vlambda
+        \right)
+        + (u - 1)\mathcal{H}_{u - 2,v}(\vlambda)
+    }{u + v}
+\end{proof}
+%
+for all remaining terms.
+
+\subsection{$\mathcal{\mathcal{T}}_{2}$}
+%
+The function $\mathcal{\mathcal{T}}_{2}$ is given by
+%
+\begin{align}
+    \label{eq:T2}
+    \mathcal{\mathcal{T}}_{2}(b, \vxi) & = ?
+    \quad.
+\end{align}
+
+\begin{proof}{}
+    \mathcal{\mathcal{T}}_{2}(b, \vxi) &= -\sgn(b) \Delta \mathbf{F}(b, \vxi)
+\end{proof}
+%
+where
+%
+\begin{proof}{}
+    \begin{split}
+        f_i(b, \xi_i) =
+        \frac{1}{3}\scalebox{1.4}{\Bigg(}
+        &\arctan\left( \frac{|b|\sin\xi_i}{\cos\xi_i} \right)
+        %
+        \\
+        %
+        &- \sgn\left({\sin\xi_i}\right)
+        \left(
+        \arctan
+        \left(
+            \frac{
+                \left(\frac{\sin\xi_i}{1 + \cos\xi_i}\right)^2 + 2 b^2 - 1
+            }{2 |b| \sqrt{1 - b^2}}
+            \right)
+        + |b| \sqrt{1 - b^2} \cos\xi_i
+        \right)
+        %
+        \\
+        %
+        &+ \phi(b, \xi_i)
+        \scalebox{1.4}{\Bigg)}
+    \end{split}
+\end{proof}
+%
+and
+%
+\begin{proof}{}
+    \phi(b, \xi_i) & =
+    \begin{cases}
+        0                          & \qquad 0 \leq \xi_i < \frac{\pi}{2}     \\
+        \pi                        & \qquad \frac{\pi}{2} \leq \xi_i < \pi   \\
+        2 |b| \sqrt{1 - b^2}       & \qquad \pi < \xi_i \leq \frac{3\pi}{2}  \\
+        \pi + 2 |b| \sqrt{1 - b^2} & \qquad \frac{3\pi}{2} \leq \xi_i < 2\pi
+        \quad.
+    \end{cases}
+\end{proof}
 

### 2020-04-09 tex/figures/code/viz.py

@@ -239,14 +239,14 @@ def visualize(b, theta, bo, ro, res=4999):
     if len(lam):
         fig, ax = plt.subplots(1, 3, figsize=(14, 5))
         fig.subplots_adjust(left=0.025, right=0.975, bottom=0.05, top=0.825)
-        ax[1].set_title(r"$T$", color="C1", fontsize=24)
-        ax[0].set_title(r"$P$", color="C1", fontsize=24)
-        ax[2].set_title(r"$Q$", color="C1", fontsize=24)
+        ax[1].set_title(r"$\mathcal{T}$", color="C1", fontsize=24)
+        ax[0].set_title(r"$\mathcal{P}$", color="C1", fontsize=24)
+        ax[2].set_title(r"$\mathcal{Q}$", color="C1", fontsize=24)
     else:
         fig, ax = plt.subplots(1, 2, figsize=(9, 5))
         fig.subplots_adjust(left=0.025, right=0.975, bottom=0.05, top=0.825)
-        ax[1].set_title(r"$T$", color="C1", fontsize=24)
-        ax[0].set_title(r"$P$", color="C1", fontsize=24)
+        ax[1].set_title(r"$\mathcal{T}$", color="C1", fontsize=24)
+        ax[0].set_title(r"$\mathcal{P}$", color="C1", fontsize=24)
 
     # Labels
     for i in range(len(phi)):

### 2020-04-10 tex/ms.tex
more text

@@
 %
-\xxx{Add equations for the rotation and change of basis matrices below.}
 Without loss of generality, assume the body whose flux we wish to compute
@@
 given the body's inclination $i$, obliquity
-$\lambda$, and rotational phase $\vartheta$ (Equation~\ref{eq:R}),
+$\lambda$, and rotational phase $\vartheta$
+\citep[Appendix C in][]{Luger2019},
 %
@@
 of the sky into the integration frame $\mathcal{F}'$, in which the
-occultor lies along the $+y'$-axis (Equation~\ref{eq:R'}),
-%
-$\mathbf{A}$ is the change-of-basis matrix from $\by$
+occultor lies along the $+y'$-axis,
+%
+$\mathbf{A}$
+\citep[Equation~B13 in][]{Luger2019}
+is the change-of-basis matrix from $\by$
 to the \emph{Green's basis} $\bg$ in which the integrals are computed,
@@
 of the sky into the integration frame
-$\mathcal{F}''$ (Equation~\ref{eq:R''})%
+$\mathcal{F}''$%
 \footnote{%
@@
 %
-$\mathbf{A_1}$ is the change-of-basis matrix from the spherical harmonic
+$\mathbf{A_1}$
+\citep[Equation~B11 in][]{Luger2019}
+is the change-of-basis matrix from the spherical harmonic
 basis $\by$ to the \emph{polynomial basis} $\bp$ in which the integrals
@@
 \begin{align}
+    \label{eq:bp}
     \tilde{p}_n(x, y) & =
@@
 and the angle $\theta$ by which its semi-major axis is rotated away from the
-$+x$-axis (defined \xxx{below}).
+$+x$-axis (a frame-dependent quantity, defined below).
 Given this formulation, and assuming that
@@
 $\mathbf{A} = \mathbf{A_2} \mathbf{A_1}$
-(Equation~\ref{eq:A}), where $\mathbf{A_1}$ transforms from
+\citep[Equation~14 in][]{Luger2019}, where $\mathbf{A_1}$ transforms from
 the spherical harmonic basis $\by$ to the polynomial basis $\bp$, and
@@
 construction. The transformation
-$\mathbf{R}'' = \mathbf{R}''(x_s, y_s)$ (Equation~\ref{eq:R''}) rotates
-the body so the semi-major axis of the terminator is aligned
+$\mathbf{R}'' = \mathbf{R}''(x_s, y_s)$ rotates
+the body
+through an angle $\atantwo(x_s, y_s)$
+so the semi-major axis of the terminator is aligned
 with the $x''$-axis; as will become clear in \S\ref{sec:solution-no-occ} below,
@@
     \label{eq:pTsoln}
-    \mathbb{p}_n &=
-    \begin{dcases}
-        %
+    \mathbb{p}_n & =
+    \resizebox{.8\hsize}{!}{$
+            \begin{cases}
                 %
                 2(2r_o)^{l+2}
+                %
+                \begin{cases}
+                    %
                     V
@@
                     %
-         & \qquad \frac{\mu}{2} \, \text{even}
-        \\[1em]
-        %
+                     & \qquad \qquad \qquad \qquad \qquad
+                    \qquad \qquad \qquad \quad
+                    \frac{\mu}{2} \, \text{even}
+                    \\[0.5em]
+                    %    
+                    V
+                    \left(
+                    \frac{\mu + 2}{2},
+                    \frac{\nu}{2},
+                    0;
+                    \viU
+                    \right)
+                    %
+                     & \qquad \qquad \qquad \qquad \qquad
+                    \qquad \qquad \qquad \quad
+                    \frac{\mu}{2} \, \text{odd}
+                    %
+                \end{cases}
+                %
+                 & \qquad
+                \mu, \nu \, \text{even}
+                %
+                \\[2em]
                 %
@@
                 %
-         & \qquad \mu = \nu = 1
-        \\[1em]
-        %
-        %
-        (2r_o)^{l-1} \beta
-        \left\{
+                 & \qquad
+                \mu = \nu = 1
+                %
+                \\[1.5em]
+                %
+                \beta (2r_o)^{l-1}
+                %
+                \begin{cases}
+                    %
+                    \begin{cases}
+                        %
                         V
@@
                         \right)
-        \right\}
-        %
-         & \qquad \mu = 1, \,
+                        %
+                         & \qquad \quad
                         l \, \text{even}
+                        %
                         \\[1em]
                         %
-        %
-        (2r_o)^{l-1} \beta
-        \left\{
                         V
@@
                         \right) -
-        V
+                        2V
                         \left(
@@
                         \right)
-        \right\}
-        %
-         & \qquad \mu = 1, \, l \ne 1, \,
-        l \, \text{odd}
-        \\[1em]
-        %
-        %
-        2(2r_o)^{l-1} \beta\,
+                        %
+                         & \qquad \quad
+                        l \, \text{odd} \ne 1
+                        %
+                    \end{cases}
+                    %
+                     & \qquad
+                    \mu = 1
+                    %
+                    \\[3em]
+                    %
+                    \begin{cases}
+                        %
+                        2
                         V
@@
                         %
-         & \qquad \frac{\mu-1}{2} \, \text{even}, \, l \ne 1
+                         & \qquad \qquad \qquad \qquad
+                        \frac{\mu - 1}{2} \, \text{even}
+                        %
                         \\[1em]
                         %
-        %
-        2(2r_o)^{l+2}
-        V
-        \left(
-        \Big\lfloor\frac{\mu + 4}{4}\Big\rfloor,
-        \frac{\nu}{2},
-        0;
-        \viU
-        \right)
-        %
-         & \qquad \mu, \nu \, \text{even}
-        \\[1em]
-        %
-        %
-        (2r_o)^{l-1} \beta\,
+                        2
                         V
@@
                         \right)
-         & \qquad \mu, \nu \, \text{odd}
-        \quad,
-        %
-        %
-    \end{dcases}
-    %
+                        %
+                         & \qquad \qquad \qquad \qquad
+                        \frac{\mu - 1}{2} \, \text{odd}
+                        %
+                    \end{cases}
+                    %
+                     & \qquad
+                    \mu > 1
+                    %
+                \end{cases}
+                %
+                 & \qquad
+                \mu, \nu \, \text{odd}
+                %
+            \end{cases}
+        $}
 \end{proof}
@@
 to specific integrals, which we compute recursively below. As in
-\citet{Luger2019} the $n = 2$ term of $\pT$ (second case in the
-equation above) is handled separately; we also compute this below.
+\citet{Luger2019} the $n = 2$ term of $\pT$, $\mathbb{p}_2$,
+is handled separately; we also compute this below.
+
+Note that several of the cases in Equation~(\ref{eq:pTsoln}) are
+identical to those in Equation~(D35) of \citet{Luger2019}, provided
+we replace their integrals $\mathcal{I}$ and $\mathcal{J}$ with our
+integrals $\viI$ and $\viJ$, respectively. The integrals themselves
+are similar, except for a change in the limits of integration, which
+are no longer symmetric about zero. As we will see, this leads to the
+dependence of these expressions on \emph{incomplete} elliptic integrals.
+Note also that the integrals $\viU$ and $\viW$ are new, as certain
+cancellations in \citet{Luger2019} resulted in the corresponding cases
+contributing zero net flux \citep[last case in Equation~D35 of][]{Luger2019}.
 
@@
 \end{proof}
-
 %
@@
     \label{eq:W}
-    \iW_v(\vkappa) = ???
-    \quad.
-\end{align}
-%
-This integral also has a closed-form solution:
+    \iW_v(k^2, \vkappa) =
+    \vint{\vkappa}{
+        \cos\varphi\sin^{2v + 1}\varphi
+        \left(1 - \frac{\sin^2\varphi}{k^2}\right)^\frac{3}{2}
+    }
+    \quad.
+\end{align}
+%
+We may compute it by either upward or downward recursion. In the upward
+case, we start with the lower boundary condition
+%
+\begin{proof}{}
+    \iW_0 &= \Delta
+    \Bigg\{
+    \frac{\sinhalfkap[2]}{5}
+    \left(
+    \frac{1 - \mathbf{q}(k^2, \vkappa)^2}{1 - \mathbf{q}(k^2, \vkappa)^3}
+    +
+    \mathbf{q}(k^2, \vkappa)^3
+    \right)
+    \Bigg\}
+    \quad.
+\end{proof}
+%
+Defining
+%
+\begin{align}
+    \mathbf{c}_0(k^2, \vkappa) & =
+    \sinhalfkap[4]
+    \frac{\mathbf{q}(k^2, \vkappa)^5}{1 - \mathbf{q}(k^2, \vkappa)^2}
+    \quad,
+\end{align}
+%
+we may recurse upward in $\iW$ and $\mathbf{c}$ simultaneously:
+%
+\begin{proof}{}
+    \label{eq:Wv}
+    \iW_v                      & =
+    \frac{\Delta}{2v + 5}
+    \left(
+    \frac{2 v \sinhalfkap[2]}{1 - \mathbf{q}(k^2, \vkappa)^2}
+    \iW_{v - 1}
+    - \mathbf{c}_{v - 1}(k^2, \vkappa)
+    \right)
+    \nonumber
+    \\
+    \mathbf{c}_v(k^2, \vkappa) & =
+    \sinhalfkap[2] \mathbf{c}_{v - 1}(k^2, \vkappa)
+\end{proof}
+%
+for $v > 0$.
+%
+In the case of downward recursion, we start with the upper boundary
+condition for $v = \vmax$,
 %
@@
     \label{eq:Wsol}
-    \iW_n =
-    \frac{\sin^{2n + 2}\left(\frac{\vkappa}{2}\right)}{2n + 5}
+    \iW_\vmax &=
+    \frac{\sin^{2\vmax + 2}\left(\frac{\vkappa}{2}\right)}{\vmax + \frac{5}{2}}
     \left(
-    \frac{3}{n+1}
-        {_2F_1}\left(-\frac{1}{2}, n + 1; n + 2; 1 - q^2\right) + 2 q^3
+    \mathbf{f}_\vmax(k^2, \vkappa)
+    + 2 \mathbf{q}(k^2, \vkappa)^3
     \right)
@@
 %
-where ${_2F_1}(a, b; c; z)$ is the Gauss hypergeometric function.
-%
-\xxx{Figure out the integral form, and write up the recursion relations.}
+where
+%
+\begin{proof}{}
+    \mathbf{f}_v(k^2, \vkappa)
+    &\equiv
+    \frac{3}{v+1}
+    \,
+    {_2\mathbf{F}_1}\left(
+    -\frac{1}{2},
+    v + 1;
+    v + 2;
+    1 - \mathbf{q}(k^2, \vkappa)^2
+    \right)
+\end{proof}
+%
+and ${_2\mathbf{F}_1}(a, b; c; \mathbf{z})$ is the Gauss
+hypergeometric function.
+We then recurse downward \xxx{...}
+\xxx{TODO: Check these expressions.}
 

### 2020-04-10 tex/figures/pathological.py

@@ -105,4 +105,7 @@ for i, axis in enumerate([ax[0], ax[2], ax[4], ax[6]]):
     )
     axis.set_rasterization_zorder(0)
 
+for axis in [axins0, axins1, axins2, axins3]:
+    axis.set_rasterization_zorder(0)
+
 fig.savefig("pathological.pdf", bbox_inches="tight", dpi=300)

### 2020-04-13 tex/ms.tex
added W proof

@@
 %
-We may compute it by either upward or downward recursion. In the upward
-case, we start with the lower boundary condition
-%
-\begin{proof}{}
-    \iW_0 &= \Delta
-    \Bigg\{
+We may compute it by either upward or downward recursion. In both cases,
+we compute each of the $\iW_v$ from
+%
+\begin{proof}{W}
+    \iW_v(k^2, \vkappa) = \Delta \mathbf{b}_v(k^2, \vkappa)
+    \quad.
+\end{proof}
+%
+In the upward case, we start with the lower boundary conditions
+%
+\begin{proof}{W}
+    \mathbf{b}_0(k^2, \vkappa) &=
     \frac{\sinhalfkap[2]}{5}
     \left(
-    \frac{1 - \mathbf{q}(k^2, \vkappa)^2}{1 - \mathbf{q}(k^2, \vkappa)^3}
+    \frac{1 - \mathbf{q}(k^2, \vkappa)^3}{1 - \mathbf{q}(k^2, \vkappa)^2}
     +
@@
     \right)
-    \Bigg\}
-    \quad.
-\end{proof}
-%
-Defining
-%
-\begin{align}
+    \nonumber \\
     \mathbf{c}_0(k^2, \vkappa) & =
@@
     \quad,
-\end{align}
-%
-we may recurse upward in $\iW$ and $\mathbf{c}$ simultaneously:
-%
-\begin{proof}{}
-    \label{eq:Wv}
-    \iW_v                      & =
-    \frac{\Delta}{2v + 5}
+\end{proof}
+%
+and recurse upward in $\mathbf{b}$ and $\mathbf{c}$ simultaneously:
+%
+\begin{proof}{W}
+    \mathbf{b}_v(k^2, \vkappa) & =
+    \frac{1}{2v + 5}
     \left(
     \frac{2 v \sinhalfkap[2]}{1 - \mathbf{q}(k^2, \vkappa)^2}
-    \iW_{v - 1}
+    \mathbf{b}_{v - 1}(k^2, \vkappa)
     - \mathbf{c}_{v - 1}(k^2, \vkappa)
@@
 In the case of downward recursion, we start with the upper boundary
-condition for $v = \vmax$,
-%
-\begin{proof}{}
-    \label{eq:Wsol}
-    \iW_\vmax &=
-    \frac{\sin^{2\vmax + 2}\left(\frac{\vkappa}{2}\right)}{\vmax + \frac{5}{2}}
+conditions
+%
+\begin{proof}{W}
+    \mathbf{b}_\vmax &=
+    \frac{\sin^{2\vmax + 2}\left(\frac{\vkappa}{2}\right)}{4\vmax + 10}
     \left(
@@
     \right)
+    \nonumber \\
+    \mathbf{c}_\vmax &=
+    \frac{1}{2}
+    \mathbf{q}(k^2, \vkappa)^5
+    \sin^{2\vmax}\left(\frac{\vkappa}{2}\right)
     \quad,
@@
 %
-\begin{proof}{}
+\begin{proof}{W}
     \mathbf{f}_v(k^2, \vkappa)
@@
 hypergeometric function.
-We then recurse downward \xxx{...}
-\xxx{TODO: Check these expressions.}
+%
+We recurse downward in $\mathbf{b}$ and $\mathbf{c}$ simultaneously:
+%
+\begin{proof}{W}
+    \mathbf{b}_v(k^2, \vkappa) & =
+    \frac{1 - \mathbf{q}(k^2, \vkappa)^2}{\sinhalfkap[2]}
+    \left(1 + \frac{5}{2v + 2}\right)
+    \mathbf{b}_{v + 1}(k^2, \vkappa) +
+    \frac{\mathbf{c}_{v + 1}(k^2, \vkappa)}{v + 1}
+    \nonumber
+    \\
+    \mathbf{c}_v(k^2, \vkappa) & =
+    \frac{\mathbf{c}_{v + 1}(k^2, \vkappa)}{\sinhalfkap[2]}
+    \quad.
+\end{proof}
 

### 2020-04-13 tex/ms.tex
added integral t

@@
 \begin{align}
-    \phi_l & = \frac{\pi}{2} \pm \left(\arcsin\left(\frac{1 - r_o ^ 2 - b_o ^ 2}{2 b_o r_o}\right) - \frac{\pi}{2}\right)
+    \phi_0 & = \frac{\pi}{2} \pm \left(\arcsin\left(\frac{1 - r_o ^ 2 - b_o ^ 2}{2 b_o r_o}\right) - \frac{\pi}{2}\right)
     \quad,
@@
 \begin{align}
-    \pmb{\phi_t} & =
+    \pmb{\phi_1} & =
     \theta' +
@@
 boundary conditions \citep[Equation D46 in ][]{Luger2019} with the
-incomplete elliptic integrals $\mathbf{F}(k^2, \vkappa)$ and
-$\mathbf{E}(k^2, \vkappa)$,
+incomplete elliptic integrals $\mathbbb{F}(k^2, \vkappa)$ and
+$\mathbbb{E}(k^2, \vkappa)$,
 then use the same upward
@@
     \,
-    {_2\mathbf{F}_1}\left(
+    {_2\mathbbb{F}_1}\left(
     -\frac{1}{2},
@@
 %
-and ${_2\mathbf{F}_1}(a, b; c; \mathbf{z})$ is the Gauss
+and ${_2\mathbbb{F}_1}(a, b; c; \mathbf{z})$ is the Gauss
 hypergeometric function.
@@
 %
+
+\subsection{The integral along the terminator, $\tT$}
+%
+In this section we present a solution to Equation~(\ref{eq:tT}), the
+line integral along the day/night terminator of the occulted body. As
+before, the first thing we must do is derive expressions for the integration
+limits $\pmb{\xi}$.
+%
+Depending on the integration case, these limits
+will corresponds to the point of intersection between the terminator and
+the limb of the occultor and/or the point of intersection between the
+terminator and the limb of the occulted body. The former is given by
+%
+\begin{proof}{}
+    \pmb{\xi_0} &= \atantwo\left(\sqrt{1 - {\mathbf{x''}}^2}, \mathbf{x''} \right)
+\end{proof}
+%
+where $\mathbf{x''}$ are the roots of the quartic (Equation~\ref{eq:quartic}).
+The latter is given by
+%
+\begin{proof}{}
+    \xi_1 &=
+    \begin{cases}
+        0   & \qquad \qquad (1 - x_o'')^2 + {y_o''}^2 < r_o^2
+        \\
+        \pi & \qquad \qquad \text{otherwise}
+        \quad.
+    \end{cases}
+\end{proof}
+%
+As before, these angles are then sorted and placed in the vector
+$\pmb{\xi}$ such that the integration is performed counter-clockwise
+about the center of the integration region.
+%
+The middle panel of Figure~\ref{fig:geometry} shows a case where
+$\xi_0 = 96.5^\circ$ corresponds to the point of intersection between the occultor
+limb and the terminator and $\xi_1 = 0^\circ$ corresponds to the
+point where the terminator extends onto the backside of the body.
+%
+Note, importantly, that unlike $\pmb{\phi}$, the angle $\pmb{\xi}$ is not
+measured between the $x$-axis and a point on the curve of $\mathcal{T}$.
+Recall that $\pmb{\xi}$ is an angular parameter of the ellipse, so it is
+measured in the same way as the eccentric anomaly in a Keplerian orbit:
+it is the
+angle between the $x$-axis and the perpendicular
+projection of a point on the ellipse onto the unit circle
+(see Figure~\ref{fig:geometry}).
+
+\begin{align}
+    \mathbb{t}_n & =
+    \begin{cases}
+        %
+        %
+        b\cos\theta'
+        \sum\limits_{j=0}^{\frac{\nu}{2}}
+        \sum\limits_{k=0}^{\frac{\mu + 2}{2}}
+        {_1}Z^{\mu,\nu}_{j,k}(b, \theta')
+        \iH_{j + k + 1, l + 1 - j - k}(\pmb{\xi})
+        \\
+        \quad\quad\quad\quad
+        - \, \sin\theta'
+        \sum\limits_{j=0}^{\frac{\nu}{2}}
+        \sum\limits_{k=0}^{\frac{\mu + 2}{2}}
+        {_1}Z^{\mu,\nu}_{j,k}(b, \theta')
+        \iH_{j + k, l + 2 - j - k}(\pmb{\xi})
+        %
+         & \qquad \mu, \nu, \, \text{even}
+        %
+        %
+        \\[3em]
+        %
+        %
+        \frac{1}{3}
+        \Delta
+        \Bigg(
+        \arctan\left( \frac{|b|\sin\vxi}{\cos\vxi} \right)
+        \\
+        \qquad\quad\quad
+        - \, \sgn\left({\sin\vxi}\right)
+        \left(
+            \arctan
+            \left(
+                \frac{
+                    \left(\frac{\sin\vxi}{1 + \cos\vxi}\right)^2 + 2 b^2 - 1
+                }{2 |b| b_c}
+                \right)
+            + |b| b_c \cos\vxi
+            \right)
+        \\
+        \qquad\quad\quad
+        + \, \pmb{\phi}(b, \vxi)
+        \Bigg)
+        %
+         & \qquad \mu = \nu = 1
+        %
+        %
+        \\[3em]
+        %
+        %
+        -b\sin\theta'
+        \sum\limits_{j=0}^{l-2}
+        {_3}Z^{\mu,\nu}_{j}(b, \theta')
+        \iH_{j + 1, l + 1 - j}(\pmb{\xi})
+        \\
+        \quad\quad\quad\quad
+        - \, \cos\theta'
+        \sum\limits_{j=0}^{l-2}
+        {_3}Z^{\mu,\nu}_{j}(b, \theta')
+        \iH_{j, l + 2 - j}(\pmb{\xi})
+        %
+         & \qquad \nu \, \text{odd}, \mu = 1, l \, \text{even}
+        %
+        %
+        \\[3em]
+        %
+        %
+        -b\sin\theta'
+        \sum\limits_{j=0}^{l-3}
+        \bigg(
+        \sin\theta'{_4}Z^{\mu,\nu}_{j}(b, \theta')
+        \iH_{j + 2, l - j}(\pmb{\xi})
+        \\
+        \qquad\qquad\qquad
+        +
+        b\cos\theta'{_4}Z^{\mu,\nu}_{j}(b, \theta')
+        \iH_{j + 1, l + 1 - j}(\pmb{\xi})
+        \bigg)
+        \\
+        \quad\quad\quad\quad
+        - \, \cos\theta'
+        \sum\limits_{j=0}^{l-3}
+        \bigg(
+        \sin\theta'{_4}Z^{\mu,\nu}_{j}(b, \theta')
+        \iH_{j + 1, l + 1 - j}(\pmb{\xi})
+        \\
+        \qquad\qquad\qquad
+        +
+        b\cos\theta'{_4}Z^{\mu,\nu}_{j}(b, \theta')
+        \iH_{j, l + 2 - j}(\pmb{\xi})
+        \bigg)
+        %
+         & \qquad \nu \, \text{odd}, \mu = 1, l \, \text{odd}
+        %
+        %
+        \\[3em]
+        b\cos\theta'
+        \sum\limits_{j=0}^{\frac{\nu}{2}}
+        \sum\limits_{k=0}^{\frac{\mu + 2}{2}}
+        {_2}Z^{\mu,\nu}_{j,k}(b, \theta')
+        \iH_{j + k + 1, l + 1 - j - k}(\pmb{\xi})
+        \\
+        \quad\quad\quad\quad
+        - \, \sin\theta'
+        \sum\limits_{j=0}^{\frac{\nu}{2}}
+        \sum\limits_{k=0}^{\frac{\mu + 2}{2}}
+        {_2}Z^{\mu,\nu}_{j,k}(b, \theta')
+        \iH_{j + k, l + 2 - j - k}(\pmb{\xi})
+        %
+         & \qquad \text{otherwise}
+        %
+        %
+    \end{cases}
+\end{align}
+%
+where
+%
+\begin{align}
+    {_1}Z^{\mu,\nu}_{j,k}(b, \theta') & =
+    \binom{\frac{\nu}{2}}{j}
+    \binom{\frac{\mu + 2}{2}}{k}
+    (-1)^{\frac{\mu + 2 - 2k}{2}}
+    b^{l + 1 - j - k}
+    \sin^\frac{\mu + 2 + 2j - 2k}{2}\theta'
+    \cos^\frac{\nu - 2j + 2k}{2}\theta'
+    %
+    \nonumber                             \\
+    %
+    {_2}Z^{\mu,\nu}_{j,k}(b, \theta') & =
+    \binom{\frac{\nu - 1}{2}}{j}
+    \binom{\frac{\mu - 3}{2}}{k}
+    (-1)^{\frac{\mu - 3 - 2k}{2}}
+    b^{l - 2 - j - k}
+    b_c^3
+    \sin^\frac{\mu - 3 + 2j - 2k}{2}\theta'
+    \cos^\frac{\nu - 1 - 2j + 2k}{2}\theta'
+    %
+    \nonumber                             \\
+    %
+    {_3}Z^{\mu,\nu}_{j}(b, \theta')   & =
+    \binom{l - 2}{j}
+    (-1)^{l - 2 - j}
+    b^{l - 2 - j}
+    b_c^3
+    \sin^{l - 2 - j}\theta'
+    \cos^j\theta'
+    %
+    \nonumber                             \\
+    %
+    {_4}Z^{\mu,\nu}_{j}(b, \theta')   & =
+    \binom{l - 3}{j}
+    (-1)^{l - 3 - j}
+    b^{l - 3 - j}
+    b_c^3
+    \sin^{l - 3 - j}\theta'
+    \cos^j\theta'
+    %
+    \nonumber                             \\
+    %
+    \phi(b, \xi)                      & =
+    \begin{cases}
+        0               & \qquad 0 \leq \xi < \frac{\pi}{2}     \\
+        \pi             & \qquad \frac{\pi}{2} \leq \xi < \pi   \\
+        2 |b| b_c       & \qquad \pi < \xi \leq \frac{3\pi}{2}  \\
+        \pi + 2 |b| b_c & \qquad \frac{3\pi}{2} \leq \xi < 2\pi
+        \quad.
+    \end{cases}
+\end{align}
+
+%
 % DEBUG

### 2020-04-14 tex/ms.tex
finished qT

@@
 This will come in handy when computing definite integrals. Specifically,
-if $F$ is the antiderivative of some function $f$, we may use the
+if $g$ is the antiderivative of some function $f$, we may use the
 fundamental theorem of calculus to compute the integral of
@@
     \nonumber                                                          \\
-     & = \Delta \mathbf{F}(\pmb{\varphi})
-\end{align}
-%
-where $\mathbf{F}$ is the vector given by
-%
-\begin{align}
-    \mathbf{F}(\pmb{\varphi}) =
-    \bigg( F(\varphi_0), F(\varphi_1), F(\varphi_2), F(\varphi_3),
-    {\cdot\cdot\cdot}, F(\varphi_{N - 2}), F(\varphi_{N - 1}) \bigg)^\top
+     & = \Delta \mathbf{g}(\pmb{\varphi})
+\end{align}
+%
+where $\mathbf{g}$ is the vector given by
+%
+\begin{align}
+    \mathbf{g}(\pmb{\varphi}) =
+    \bigg( g(\varphi_0), g(\varphi_1), g(\varphi_2), g(\varphi_3),
+    {\cdot\cdot\cdot}, g(\varphi_{N - 2}), g(\varphi_{N - 1}) \bigg)^\top
     \quad.
@@
 \begin{align}
-    \phi_0 & = \frac{\pi}{2} \pm \left(\arcsin\left(\frac{1 - r_o ^ 2 - b_o ^ 2}{2 b_o r_o}\right) - \frac{\pi}{2}\right)
+    \phi_0 & =
+    \frac{\pi}{2} \pm \left(\arcsin\left(\frac{1 - r_o ^ 2 - b_o ^ 2}{2 b_o r_o}\right) - \frac{\pi}{2}\right)
     \quad,
@@
 where the sign is chosen such that the point
-$(r_o\cos\phi_l, b_o + r_o\sin\phi_l)$ is on the dayside of the occulted body,
+$(r_o\cos\phi_0, b_o + r_o\sin\phi_0)$ is on the dayside of the occulted body,
 and the latter (of which there may be multiple) is given by
@@
 where $\mathbf{x''}$ are the roots of the quartic (Equation~\ref{eq:quartic}).
-These angles are then sorted and placed in the vector $\pmb{\phi}$ such that
+These angles are then wrapped to the range $[0, 2\pi)$
+and sorted into the vector $\pmb{\phi}$ such that
 the integration is always performed in a counter-clockwise sense about
@@
 limb-terminator intersection. Both angles are measured counter-clockwise
-from the $x'$-axis.
+from the line $x' = b_o$.
 
@@
 \begin{proof}{}
-    \pmb{\xi_0} &= \atantwo\left(\sqrt{1 - {\mathbf{x''}}^2}, \mathbf{x''} \right)
+    \pmb{\xi_0} &=
+    \atantwo\left(\sqrt{1 - {\mathbf{x''}}^2}, \mathbf{x''} \right)
 \end{proof}
@@
 %
-As before, these angles are then sorted and placed in the vector
+As before, these angles are then
+wrapped to the range $[0, 2\pi)$ and
+sorted into the vector
 $\pmb{\xi}$ such that the integration is performed counter-clockwise
@@
 Note, importantly, that unlike $\pmb{\phi}$, the angle $\pmb{\xi}$ is not
-measured between the $x$-axis and a point on the curve of $\mathcal{T}$.
+measured between the horizontal and a point on the curve of $\mathcal{T}$.
 Recall that $\pmb{\xi}$ is an angular parameter of the ellipse, so it is
@@
 it is the
-angle between the $x$-axis and the perpendicular
+angle between the semi-major axis of the ellipse and the perpendicular
 projection of a point on the ellipse onto the unit circle
@@
 
-\begin{align}
+The solution to Equation~(\ref{eq:tT}) involves repeated application
+of the binomial theorem. As before, we simply present the result, with
+validation links:
+%
+\begin{proof}{}
     \mathbb{t}_n & =
@@
         \sum\limits_{k=0}^{\frac{\mu + 2}{2}}
-        {_1}Z^{\mu,\nu}_{j,k}(b, \theta')
+        Z^{\frac{\nu}{2}, \frac{\mu+2}{2}}_{j,k}
+        (b, \theta') \,
         \iH_{j + k + 1, l + 1 - j - k}(\pmb{\xi})
@@
         \sum\limits_{k=0}^{\frac{\mu + 2}{2}}
-        {_1}Z^{\mu,\nu}_{j,k}(b, \theta')
+        Z^{\frac{\nu}{2}, \frac{\mu+2}{2}}_{j,k}
+        (b, \theta') \,
         \iH_{j + k, l + 2 - j - k}(\pmb{\xi})
         %
-         & \qquad \mu, \nu, \, \text{even}
+         & \qquad
+        \mathrel{\raisebox{1.25em}{$\mu, \nu, \, \text{even}$}}
         %
@@
         \Delta
-        \Bigg(
+        \Big\{
         \arctan\left( \frac{|b|\sin\vxi}{\cos\vxi} \right)
@@
         \right)
+        %
+         & \qquad \mu = \nu = 1
+        %
         \\
@@
         + \, \pmb{\phi}(b, \vxi)
-        \Bigg)
-        %
-         & \qquad \mu = \nu = 1
-        %
+        \Big\}
         %
@@
         \sum\limits_{j=0}^{l-2}
-        {_3}Z^{\mu,\nu}_{j}(b, \theta')
+        Z^{0, l-2}_{0,k}
+        (b, \theta') \,
         \iH_{j + 1, l + 1 - j}(\pmb{\xi})
@@
         \sum\limits_{j=0}^{l-2}
-        {_3}Z^{\mu,\nu}_{j}(b, \theta')
+        Z^{0, l-2}_{0,k}
+        (b, \theta') \,
         \iH_{j, l + 2 - j}(\pmb{\xi})
         %
-         & \qquad \nu \, \text{odd}, \mu = 1, l \, \text{even}
+         & \qquad
+        \mathrel{\raisebox{1.25em}{$\nu \, \text{odd}, \mu = 1, l \, \text{even}$}}
         %
@@
         \bigg(
-        \sin\theta'{_4}Z^{\mu,\nu}_{j}(b, \theta')
+        \sin\theta'
+        Z^{0, l-3}_{0,k}
+        (b, \theta') \,
         \iH_{j + 2, l - j}(\pmb{\xi})
@@
         +
-        b\cos\theta'{_4}Z^{\mu,\nu}_{j}(b, \theta')
+        \, b\cos\theta'
+        Z^{0, l-3}_{0,k}
+        (b, \theta') \,
         \iH_{j + 1, l + 1 - j}(\pmb{\xi})
@@
         \bigg(
-        \sin\theta'{_4}Z^{\mu,\nu}_{j}(b, \theta')
+        \sin\theta'
+        Z^{0, l-3}_{0,k}
+        (b, \theta') \,
         \iH_{j + 1, l + 1 - j}(\pmb{\xi})
+        %
+         & \qquad
+        \mathrel{\raisebox{1.25em}{$\nu \, \text{odd}, \mu = 1, l \, \text{odd}$}}
+        %
         \\
@@
         +
-        b\cos\theta'{_4}Z^{\mu,\nu}_{j}(b, \theta')
+        \, b\cos\theta'
+        Z^{0, l-3}_{0,k}
+        (b, \theta') \,
         \iH_{j, l + 2 - j}(\pmb{\xi})
@@
         %
-         & \qquad \nu \, \text{odd}, \mu = 1, l \, \text{odd}
         %
@@
         \sum\limits_{k=0}^{\frac{\mu + 2}{2}}
-        {_2}Z^{\mu,\nu}_{j,k}(b, \theta')
+        Z^{\frac{\nu-1}{2}, \frac{\mu - 3}{2}}_{j,k}
+        (b, \theta') \,
         \iH_{j + k + 1, l + 1 - j - k}(\pmb{\xi})
@@
         \sum\limits_{k=0}^{\frac{\mu + 2}{2}}
-        {_2}Z^{\mu,\nu}_{j,k}(b, \theta')
+        Z^{\frac{\nu-1}{2}, \frac{\mu - 3}{2}}_{j,k}
+        (b, \theta') \,
         \iH_{j + k, l + 2 - j - k}(\pmb{\xi})
         %
-         & \qquad \text{otherwise}
+         & \qquad
+        \mathrel{\raisebox{1.25em}{$\text{otherwise}$}}
         %
@@
     \end{cases}
-\end{align}
-%
-where
-%
-\begin{align}
-    {_1}Z^{\mu,\nu}_{j,k}(b, \theta') & =
-    \binom{\frac{\nu}{2}}{j}
-    \binom{\frac{\mu + 2}{2}}{k}
-    (-1)^{\frac{\mu + 2 - 2k}{2}}
-    b^{l + 1 - j - k}
-    \sin^\frac{\mu + 2 + 2j - 2k}{2}\theta'
-    \cos^\frac{\nu - 2j + 2k}{2}\theta'
-    %
-    \nonumber                             \\
-    %
-    {_2}Z^{\mu,\nu}_{j,k}(b, \theta') & =
-    \binom{\frac{\nu - 1}{2}}{j}
-    \binom{\frac{\mu - 3}{2}}{k}
-    (-1)^{\frac{\mu - 3 - 2k}{2}}
-    b^{l - 2 - j - k}
-    b_c^3
-    \sin^\frac{\mu - 3 + 2j - 2k}{2}\theta'
-    \cos^\frac{\nu - 1 - 2j + 2k}{2}\theta'
-    %
-    \nonumber                             \\
-    %
-    {_3}Z^{\mu,\nu}_{j}(b, \theta')   & =
-    \binom{l - 2}{j}
-    (-1)^{l - 2 - j}
-    b^{l - 2 - j}
-    b_c^3
-    \sin^{l - 2 - j}\theta'
-    \cos^j\theta'
-    %
-    \nonumber                             \\
-    %
-    {_4}Z^{\mu,\nu}_{j}(b, \theta')   & =
-    \binom{l - 3}{j}
-    (-1)^{l - 3 - j}
-    b^{l - 3 - j}
-    b_c^3
-    \sin^{l - 3 - j}\theta'
-    \cos^j\theta'
-    %
-    \nonumber                             \\
-    %
+\end{proof}
+%
+where we define
+%
+\begin{proof}{}
+    Z^{u,v}_{j,k}(b, \theta') & =
+    \binom{u}{j}
+    \binom{v}{k}
+    (-1)^{v-k}
+    b^{u+v-j-k}
+    \sin^{v+j-k}\theta'
+    \cos^{u-j+k}\theta'
+\end{proof}
+%
+and
+%
+\begin{proof}{}
     \phi(b, \xi) & =
@@
     \end{cases}
-\end{align}
+\end{proof}
+%
+The components of the vector $\viH$ are given by the integral
+%
+\begin{align}
+    \label{eq:H}
+    \iH_{u,v}(\vxi) & =
+    \vint{\vxi}{
+        \cos^u\varphi
+        \sin^v\varphi
+    }
+    \quad.
+\end{align}
+%
+This integral is the same as that in Equation (D27)
+of \citet{Luger2019}, except for a change in the limits of integration.
+We can compute this integral recursively given four lower boundary conditions:
+%
+\begin{proof}{H}
+    \label{eq:Hlower}
+    \iH_{0,0}(\vxi) &= \Delta \vxi
+    %
+    \nonumber \\
+    %
+    \iH_{1,0}(\vxi) &= \Delta \sin\vxi
+    %
+    \nonumber \\
+    %
+    \iH_{0,1}(\vxi) &= -\Delta \cos\vxi
+    %
+    \nonumber \\
+    %
+    \iH_{1,1}(\vxi) &= -\frac{\Delta\cos^2\vxi}{2}
+    %
+    \quad.
+\end{proof}
+%
+The remaining terms may be computed by upward recursion using the
+relations
+%
+\begin{proof}{H}
+    \label{eq:Hrec1}
+    \iH_{u,v}(\vxi) &=
+    \frac{
+        -\Delta \left(
+        \cos^{u + 1} \vxi
+        \sin^{v - 1} \vxi
+        \right)
+        +(v - 1)\iH_{u,v - 2}(\vxi)
+    }{u + v}
+\end{proof}
+%
+for $u < 2, v \ge 2$ and
+%
+\begin{proof}{H}
+    \label{eq:Hrec2}
+    \iH_{u,v}(\vxi) &=
+    \frac{
+        \Delta \left(
+        \cos^{u - 1} \vxi
+        \sin^{v + 1} \vxi
+        \right)
+        + (u - 1)\iH_{u - 2,v}(\vxi)
+    }{u + v}
+\end{proof}
+%
+for all remaining terms.
+
+%
+
+\subsection{The integral along the occulted body limb, $\qT$}
+%
+The final line integral we must solve is the integral along the boundary
+of the occulted body,  Equation~(\ref{eq:qT}). Fortunately, this is
+also the easiest of the three.
+%
+The limits of integration $\vlambda$
+correspond to the point at which the terminator crosses from the dayside
+to the night side,
+%
+\begin{proof}{}
+    \lambda_0 &=
+    \begin{cases}
+        \theta'        & \qquad \qquad \cos^2\theta' + (\sin\theta' - b_o)^2 < r_o^2
+        \\
+        \theta ' + \pi & \qquad \qquad \text{otherwise}
+        \quad.
+    \end{cases}
+\end{proof}
+%
+and the point of intersection between the limb of the occultor
+and the limb of the occulted body,
+%
+\begin{proof}{}
+    \lambda_1 & =
+    \frac{\pi}{2} \pm \left(\arcsin\left(\frac{1 - r_o ^ 2 + b_o ^ 2}{2 b_o}\right) - \frac{\pi}{2}\right)
+    \quad,
+\end{proof}
+%
+where the sign is chosen such that the point
+$(\cos\lambda_1, \sin\lambda_1)$ is on the dayside of the occulted body.
+%
+As before, these angles are
+wrapped to the range $[0, 2\pi)$ and
+placed in the vector
+$\lambda$ such that the line integral is taken in the counter-clockwise
+direction about the center of the integration region. The right panel
+of Figure~\ref{fig:geometry} shows a case where
+$\lambda_0 = 75^\circ$ and $\lambda_1 = 130.5^\circ$. Both angles are
+measured counter-clockwise from the $x'$-axis.
+
+Given $\vlambda$, the solution to Equation~(\ref{eq:qT}) is straightforward:
+%
+\begin{proof}{}
+    \mathbb{q}_n &=
+    \begin{cases}
+        \iH_{\frac{\mu + 4}{2}, \frac{\nu}{2}}(\vlambda)
+                                  & \qquad \mu, \nu, \, \text{even}
+        \\[1em]
+        \frac{1}{3}\Delta\vlambda & \qquad \mu = \nu = 1
+        \\[1em]
+        0                         & \qquad \text{otherwise}
+        \quad,
+    \end{cases}
+\end{proof}
+%
+where the vector $\viH$ is given by Equation~(\ref{eq:H}).
 
@@
 
-\appendix
-
-\xxx{Migrate this up.}
-
-%
-The function $\mathcal{H}_{u,v}$ is given by
-%
-\begin{align}
-    \label{eq:H}
-    \mathcal{H}_{u,v}(\vlambda) & =
-    \vint{\vlambda}{
-        \cos^u\varphi
-        \sin^v\varphi
-    }
-    \quad.
-\end{align}
-%
-The integral in this expression is the same as that in Equation (D27)
-of \citet{Luger2019}, except for a change in the limits of integration.
-We can compute this integral recursively given four lower boundary conditions:
-%
-\begin{proof}{H}
-    \label{eq:Hlower}
-    \mathcal{H}_{0,0}(\vlambda) &= \Delta \vlambda
-    %
-    \nonumber \\
-    %
-    \mathcal{H}_{1,0}(\vlambda) &= \Delta \sin\vlambda
-    %
-    \nonumber \\
-    %
-    \mathcal{H}_{0,1}(\vlambda) &= -\Delta \cos\vlambda
-    %
-    \nonumber \\
-    %
-    \mathcal{H}_{1,1}(\vlambda) &= -\frac{\Delta\cos^2\vlambda}{2}
-    %
-    \quad.
-\end{proof}
-%
-The remaining terms may be computed by upward recursion using the
-relations
-%
-\begin{proof}{H}
-    \label{eq:Hrec1}
-    \mathcal{H}_{u,v}(\vlambda) &=
-    \frac{
-        -\Delta \left(
-        \cos^{u + 1} \vlambda
-        \sin^{v - 1} \vlambda
-        \right)
-        +(v - 1)\mathcal{H}_{u,v - 2}(\vlambda)
-    }{u + v}
-\end{proof}
-%
-for $u < 2, v \ge 2$ and
-%
-\begin{proof}{H}
-    \label{eq:Hrec2}
-    \mathcal{H}_{u,v}(\vlambda) &=
-    \frac{
-        \Delta \left(
-        \cos^{u - 1} \vlambda
-        \sin^{v + 1} \vlambda
-        \right)
-        + (u - 1)\mathcal{H}_{u - 2,v}(\vlambda)
-    }{u + v}
-\end{proof}
-%
-for all remaining terms.
-
-\subsection{$\mathcal{\mathcal{T}}_{2}$}
-%
-The function $\mathcal{\mathcal{T}}_{2}$ is given by
-%
-\begin{align}
-    \label{eq:T2}
-    \mathcal{\mathcal{T}}_{2}(b, \vxi) & = ?
-    \quad.
-\end{align}
-
-\begin{proof}{}
-    \mathcal{\mathcal{T}}_{2}(b, \vxi) &= -\sgn(b) \Delta \mathbf{F}(b, \vxi)
-\end{proof}
-%
-where
-%
-\begin{proof}{}
-    \begin{split}
-        f_i(b, \xi_i) =
-        \frac{1}{3}\scalebox{1.4}{\Bigg(}
-        &\arctan\left( \frac{|b|\sin\xi_i}{\cos\xi_i} \right)
-        %
-        \\
-        %
-        &- \sgn\left({\sin\xi_i}\right)
-        \left(
-        \arctan
-        \left(
-            \frac{
-                \left(\frac{\sin\xi_i}{1 + \cos\xi_i}\right)^2 + 2 b^2 - 1
-            }{2 |b| \sqrt{1 - b^2}}
-            \right)
-        + |b| \sqrt{1 - b^2} \cos\xi_i
-        \right)
-        %
-        \\
-        %
-        &+ \phi(b, \xi_i)
-        \scalebox{1.4}{\Bigg)}
-    \end{split}
-\end{proof}
-%
-and
-%
-\begin{proof}{}
-    \phi(b, \xi_i) & =
-    \begin{cases}
-        0                          & \qquad 0 \leq \xi_i < \frac{\pi}{2}     \\
-        \pi                        & \qquad \frac{\pi}{2} \leq \xi_i < \pi   \\
-        2 |b| \sqrt{1 - b^2}       & \qquad \pi < \xi_i \leq \frac{3\pi}{2}  \\
-        \pi + 2 |b| \sqrt{1 - b^2} & \qquad \frac{3\pi}{2} \leq \xi_i < 2\pi
-        \quad.
-    \end{cases}
-\end{proof}
-
 % Bibliography

### 2020-04-14 tex/ms.tex
working on p2

@@
 This is an extension of \citet{Luger2019}.
-\xxx{
-    \textbf{To do list:}
-    \begin{itemize}
-        \item Make our frame convention explicit.
-              Unprimed = sky. Prime = greens. Double prime = term.
-        \item Emphasize why we can't just analytically weight the nightside by
-              zero and integrate as before.
-        \item Add a table clarifying the notation.
-    \end{itemize}
+
+%
+
+\section{Performance}
+\label{sec:performance}
+%
+See Figure~\ref{fig:speed}.
+%
+\begin{figure}[h!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/speed.pdf}
+        \oscaption{speed}{%
+            Evaluation time (vertical axis)
+            and numerical precision (point size)
+            for a single flux evaluation as a function of spherical
+            harmonic degree for different methods.
+            In orange we show results for the emitted light
+            \starry algorithm from \citet{Luger2019} (solid: no gradient,
+            dashed: with gradient), and in blue we show results for
+            the reflected
+            light algorithm from this paper (solid: no gradient,
+            dashed: with gradient). For comparison, in purple we show
+            results for discrete integration on a grid (solid) and
+            numerical integration using two-dimensional Gaussian
+            quadrature (dashed); neither of these include gradient
+            evaluations. The reflected light algorithm is around one
+            order of magnitude slower and less precise than the emitted
+            light algorithm, but still ${\sim}4$ orders of magnitude faster
+            and ${\sim}10$ orders of magnitude more precise than numerical
+            integration.
+            \label{fig:speed}
         }
-
-%
+    \end{centering}
+\end{figure}
+
+% Bibliography
+\bibliography{bib}
+
+% APPENDIX
+\appendix
+
+%
+
 \section{The Problem}
@@
 with $b_c = \sqrt{1 - b^2}$ and $z(x, y) = \sqrt{1 - x^2 - y^2}$.
-%
-Since $I$ is just a polynomial in $x$, $y$, and $z(x, y)$, we
+
+In principle, our task is now straightforward: weight each of the
+terms in the Green's basis (Equation~\ref{eq:bg}) and integrate them
+over the visible portion of the body's disk to obtain the reflected
+light solution vector, $\sT$. Unfortunately, the piecewise nature
+of Equation~(\ref{eq:illum}) makes direct evaluation of these integrals
+extremely difficult in practice.
+%
+We find that it is more tractable to weight our basis terms by
+the function $I$ (Equation~\ref{eq:illum_poly}) and to modify the limits
+of integration to exclude the nightside of the body, where $I$ is
+(unphysically) negative.
+%
+In particular, since $I$ is just a polynomial in $x$, $y$, and $z(x, y)$, we
 can express it as a vector $\mathbf{i}(b, \theta)$ in the polynomial basis $\bp$.
@@
 %
-Note, importantly, that this weighting is valid only on the dayside
+Note, again, that this weighting is valid only on the dayside
 hemisphere (see Equation~\ref{eq:illum}), as the operator $\mathbf{I}$ weights
@@
 \begin{align}
+    \label{eq:kappa}
     \pmb{\kappa} = \pmb{\phi} + \frac{\pi}{2}
@@
 %
+\xxx{Define $k^2$.}
 The integral in this expression is again the same as that in Equation (D39)
@@
 boundary conditions \citep[Equation D46 in ][]{Luger2019} with the
-incomplete elliptic integrals $\mathbbb{F}(k^2, \vkappa)$ and
-$\mathbbb{E}(k^2, \vkappa)$,
+incomplete elliptic integrals
+%
+\begin{align}
+    \label{eq:F}
+    \mathbb{F}(k^2, \kappa) & = \int_0^{\kappa} \frac{\dd \varphi}{\sqrt{1 - k^2 \sin^2 \varphi}}
+    \\
+    \intertext{and}
+    \label{eq:E}
+    \mathbb{E}(k^2, \kappa) & = \int_0^{\kappa} \sqrt{1 - k^2 \sin^2 \varphi} \, \dd \varphi
+\end{align}
+%
 then use the same upward
@@
 
+\subsection{The term $\mathbb{p}_2$}
+\label{sec:p2}
+%
+The final integral we must solve is that corresponding to
+$\mathbb{p}_2$ ($\mu = \nu = 1$). As in \citet{Luger2019}, this is
+the integral of the linear limb darkening term,
+whose solution must be handled
+separately due to the fact that the corresponding antiderivative
+in Equation~(\ref{eq:G}) is not a polynomial in $x$, $y$, and $z(x, y)$.
+The integral we must solve is
+%
+\begin{align}
+    \mathbb{p}_2 & =
+    \vint{\pmb{\phi}}{
+        \left(
+        \frac{
+            1 - (1 - r_o^2 - b_o^2 - 2 b_o r_o \sin\varphi)^\frac{3}{2}
+        }{
+            r_o^2 + b_o^2 + 2 b_o r_o \sin\varphi
+        }
+        \right)
+        \left(r_o^2 + b_o r_o \sin\varphi\right)
+    }
+\end{align}
+%
+The solution is tricky, but fortunately a similar integral was solved in
+Equation~(34) of \citet{Pal2012}. Adapting their solution to our formalism,
+we obtain
+%
+\begin{proof}{}
+    \frac{1}{3}
+    \Big(
+    c_0 +
+    c_1 \Delta\mathbbb{F}(k^2, \vkappa) +
+    c_2 \Delta\mathbbb{E}(k^2, \vkappa) +
+    c_3 \Delta\mathbbb{P}(k^2, \vkappa)
+    \Big)
+\end{proof}
+%
+where
+%
+\begin{proof}{}
+    c_0 &=
+    \begin{cases}
+        ? & ?
+    \end{cases}
+    \nonumber \\
+    c_1 &= ?
+    \nonumber \\
+    c_2 &= -\frac{2}{3} \sqrt{k^2 b_o r_o} (4 - 7 r_o^2 - b_o^2)
+    \nonumber \\
+    c_3 &= \frac{1}{3} \sqrt{k^2 b_o r_o} \frac{b_o + r_o}{(b_o - r_o)^2}
+\end{proof}
+%
+\xxx{This section needs work!}
+
+%
+
 \subsection{The integral along the terminator, $\tT$}
+\label{sec:tT}
 %
@@
 \subsection{The integral along the occulted body limb, $\qT$}
+\label{sec:qT}
 %
@@
 
-%
-% DEBUG
+% TABLE
 \vfill
 \pagebreak
-%
-
-\section{Performance}
-\label{sec:performance}
-%
-\xxx{Performance!} See Figure~\ref{fig:speed}.
-%
-\begin{figure}[h!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/speed.pdf}
-        \oscaption{speed}{%
-            Evaluation time for the starry algorithm.
-            \label{fig:speed}
-        }
-    \end{centering}
-\end{figure}
-
-% Bibliography
-\bibliography{bib}
+\input{table}
 

### 2020-04-16 tex/ms.tex
fixed p2

@@
 \begin{align}
+    \label{eq:z}
     z(x, y) \equiv \sqrt{1 - x^2 - y^2}
@@
     \label{eq:G}
-    \mathbf{G}_n (x, y) & =
+    \mathbf{G}_n (x', y') & =
     \begin{dcases}
@@
     \label{eq:I}
-    \iI_v(\vkappa) & =
-    \vint{\vkappa}{\sinhalfkap[2v]}
+    \iI_v(\valpha) & =
+    \vint{\valpha}{\sin^{2v}\varphi}
     \quad,
@@
 \begin{align}
-    \label{eq:kappa}
-    \pmb{\kappa} = \pmb{\phi} + \frac{\pi}{2}
+    \label{eq:alpha}
+    \valpha \equiv \frac{\pmb{\phi}}{2} + \frac{\pi}{4}
     \quad.
@@
     \label{eq:Irec}
-    \iI_0(\vkappa) &=
-    \frac{\Delta \vkappa}{2}
-    %
-    \nonumber \\
-    %
-    \iI_v(\vkappa) &=
+    \iI_0(\valpha) &=
+    \Delta \valpha
+    %
+    \nonumber \\
+    %
+    \iI_v(\valpha) &=
     \frac{1}{2v}
     \bigg(
-    (2v - 1) \iI_{v-1}(\vkappa) -
-    \Delta \left(\sinhalfkap[2v - 1]\coshalfkap\right)
+    (2v - 1) \iI_{v-1}(\valpha) -
+    \Delta \left(\sin^{2v - 1}\valpha\cos^{2v -1}\valpha\right)
     \bigg)
@@
 is generally stable, except when
-$\sin\left(\nicefrac{\vkappa}{2}\right)$ is small.
-In that limit, we evaluate $\iI_\vmax(\vkappa)$
+$\sin\valpha$ is small.
+In that limit, we evaluate $\iI_\vmax(\valpha)$
 by numerical integration of
@@
 points. We then recurse downward by substituting $v \rightarrow v + 1$ in
-Equation~(\ref{eq:Irec}) and solving for $\iI_v(\vkappa)$.
+Equation~(\ref{eq:Irec}) and solving for $\iI_v(\valpha)$.
 
@@
     \label{eq:J}
-    \iJ_v(k^2, \vkappa) =
-    \vint{\vkappa}{
+    \iJ_v(k^2, \valpha) =
+    \vint{\valpha}{
         \sin^{2v}\varphi
@@
     }
-    \quad.
-\end{align}
-%
-\xxx{Define $k^2$.}
+    \quad,
+\end{align}
+%
+where
+%
+\begin{align}
+    \label{eq:k2}
+    k^2 & \equiv \frac{1 - r_o^2 - b_o^2 + 2 b_o r_o}{4 b_o r_o}
+    \quad.
+\end{align}
+%
 The integral in this expression is again the same as that in Equation (D39)
@@
     \label{eq:F}
-    \mathbb{F}(k^2, \kappa) & = \int_0^{\kappa} \frac{\dd \varphi}{\sqrt{1 - k^2 \sin^2 \varphi}}
+    \mathbb{F}(\psi \,|\, m) & \equiv \int_0^{\psi} \frac{\dd \varphi}{\sqrt{1 - m \sin^2 \varphi}}
     \\
@@
     \label{eq:E}
-    \mathbb{E}(k^2, \kappa) & = \int_0^{\kappa} \sqrt{1 - k^2 \sin^2 \varphi} \, \dd \varphi
-\end{align}
+    \mathbb{E}(\psi \,|\, m) & \equiv \int_0^{\psi} \sqrt{1 - m \sin^2 \varphi} \, \dd \varphi
+    \quad,
+\end{align}
+%
+which we compute from the $el\mathit{2}$ parametrization of
+\citet{Bulirsch1965},
 %
@@
     \label{eq:Jrec}
-    \iJ_0(k^2, \vkappa) &=
+    \iJ_0(k^2, \valpha) &=
     \frac{1}{3} \bigg(
@@
     \left(\frac{1}{k^2} - 1\right) \DF +
-    \Delta \mathbf{z}_0(k^2, \vkappa)
+    \Delta \mathbf{z}_0(k^2, \valpha)
     \bigg)
@@
     %
-    \iJ_1(k^2, \vkappa) &=
+    \iJ_1(k^2, \valpha) &=
     \frac{1}{15} \bigg(
-    \left(-3 k^2 + 13 - \frac{8}{k^2}\right) \DE +
+    \left(-3 k^2 + 13 - \frac{8}{k^2}\right) \DE
     \nonumber \\
     &\qquad\quad\quad\quad\quad\quad\quad\quad\quad
+    +
     \left(3 k^2 - 7 + \frac{4}{k^2}\right) \DF +
-    \Delta \mathbf{z}_1(k^2, \vkappa)
+    \Delta \mathbf{z}_1(k^2, \valpha)
     \bigg)
@@
     %
-    \iJ_v(k^2, \vkappa) &=
+    \iJ_v(k^2, \valpha) &=
     \frac{1}{2v + 3}
     \bigg(
-    2 \left( v + 1 + (v - 1) k^2 \right) \iJ_{v - 1} -
-    (2v - 3) k^2 \iJ_{v - 2}
-    + \Delta \mathbf{z}_v(k^2, \vkappa)
+    2 \left( v + 1 + (v - 1) k^2 \right) \iJ_{v - 1}(k^2, \valpha)
+    \nonumber \\
+    &\qquad\qquad\quad\quad\quad\quad
+    -
+    (2v - 3) k^2 \iJ_{v - 2}(k^2, \valpha)
+    + \Delta \mathbf{z}_v(k^2, \valpha)
     \bigg)
@@
     \label{eq:Jrec_z}
-    \mathbf{z}_0(k^2, \pmb{\kappa}) & =
+    \mathbf{z}_0(k^2, \valpha) & =
     \frac{
-        \sinhalfkap
-        \coshalfkap
-        \mathbf{q}(k^2, \vkappa)
+        \sin\valpha
+        \cos\valpha
+        \,
+        \mathbf{q}(k^2, \valpha)
     }{
@@
     %
-    \mathbf{z}_1(k^2, \pmb{\kappa}) & =
-    \left(\left(3 \sinhalfkap[2] + 4\right) - 6k^2\right)
-    \mathbf{z}_0(k^2, \pmb{\kappa})
+    \mathbf{z}_1(k^2, \valpha) & =
+    \left(3 \sin^2\valpha + 4 - 6k^2\right)
+    \mathbf{z}_0(k^2, \valpha)
     %
@@
     %
-    \mathbf{z}_v(k^2, \pmb{\kappa}) & =
+    \mathbf{z}_v(k^2, \valpha) & =
     k^2
-    \sinhalfkap[2v - 3]
-    \coshalfkap
-    \mathbf{q}(k^2, \pmb{\kappa})^5
+    \sin^{2v - 3}\valpha
+    \cos\valpha
+    \,
+    \mathbf{q}(k^2, \valpha)^5
     \quad,
@@
     \label{eq:q}
-    \mathbf{q}(k^2, \vkappa) = \sqrt{1 - \frac{\sinhalfkap[2]}{k^2}}
-    \quad.
-\end{align}
-%
-However, in practice we find that this procedure is even more numerically
+    \mathbf{q}(k^2, \valpha) = \sqrt{1 - \frac{\sin^2\valpha}{k^2}}
+    \quad.
+\end{align}
+%
+Note that when $k^2 < 1$ we use the reciprocal-modulus transformation
+to evaluate the elliptic integrals:
+%
+\begin{align}
+    \mathbb{F}\left(\psi \,\Big|\, \frac{1}{k^2}\right) & =
+    k \, \mathbb{F}(\beta \,|\, k^2)
+    \nonumber                                                                                        \\
+    \mathbb{E}\left(\psi \,\Big|\, \frac{1}{k^2}\right) & =
+    \frac{\mathbb{E}(\beta \,|\, k^2) - (1 - k^2) \mathbb{F}(\beta \,|\, k^2)}{k}
+    \\
+    \intertext{with}
+    \beta                                               & = \arcsin\left( \frac{\sin\psi}{k} \right)
+    \quad.
+\end{align}
+%
+
+In practice, however, we find that this procedure is even more numerically
 unstable than it was in \citet{Luger2019}.
@@
     b_v(k) &= \frac{(2v - 3) k^2}{2v + 3} \nonumber \\
-    c_v(k^2, \vkappa) &= \Delta
+    c_v(k^2, \valpha) &= \Delta
     \bigg(
     \frac{
-            \mathbf{z}_v(k^2, \pmb{\kappa})
+            \mathbf{z}_v(k^2, \valpha)
         }{
@@
     \label{eq:U}
-    \iU_v(\vkappa) =
-    \vint{\vkappa}{\cos\varphi\sin^{2v}\varphi}
+    \iU_v(\valpha) =
+    \vint{\valpha}{\cos\varphi\sin^{2v + 1}\varphi}
     \quad.
@@
     \label{eq:Usol}
-    \iU_v(\vkappa) &= \frac{\Delta \sinhalfkap[v+1]}{v + 1}
+    \iU_v(\valpha) &= \frac{\Delta \sin^{2v+2}\valpha}{2v + 2}
     \quad.
@@
     \label{eq:W}
-    \iW_v(k^2, \vkappa) =
-    \vint{\vkappa}{
+    \iW_v(k^2, \valpha) =
+    \vint{\valpha}{
         \cos\varphi\sin^{2v + 1}\varphi
@@
 \begin{proof}{W}
-    \iW_v(k^2, \vkappa) = \Delta \mathbf{b}_v(k^2, \vkappa)
+    \iW_v(k^2, \valpha) = \Delta \mathbf{b}_v(k^2, \valpha)
     \quad.
@@
 \begin{proof}{W}
-    \mathbf{b}_0(k^2, \vkappa) &=
-    \frac{\sinhalfkap[2]}{5}
+    \mathbf{b}_0(k^2, \valpha) &=
+    \frac{\sin^2\valpha}{5}
     \left(
-    \frac{1 - \mathbf{q}(k^2, \vkappa)^3}{1 - \mathbf{q}(k^2, \vkappa)^2}
+    \frac{1 - \mathbf{q}(k^2, \valpha)^3}{1 - \mathbf{q}(k^2, \valpha)^2}
     +
-    \mathbf{q}(k^2, \vkappa)^3
+    \mathbf{q}(k^2, \valpha)^3
     \right)
     \nonumber \\
-    \mathbf{c}_0(k^2, \vkappa) & =
-    \sinhalfkap[4]
-    \frac{\mathbf{q}(k^2, \vkappa)^5}{1 - \mathbf{q}(k^2, \vkappa)^2}
+    \mathbf{c}_0(k^2, \valpha) & =
+    \sin^4\valpha \,
+    \frac{\mathbf{q}(k^2, \valpha)^5}{1 - \mathbf{q}(k^2, \valpha)^2}
     \quad,
@@
 \begin{proof}{W}
-    \mathbf{b}_v(k^2, \vkappa) & =
+    \mathbf{b}_v(k^2, \valpha) & =
     \frac{1}{2v + 5}
     \left(
-    \frac{2 v \sinhalfkap[2]}{1 - \mathbf{q}(k^2, \vkappa)^2}
-    \mathbf{b}_{v - 1}(k^2, \vkappa)
-    - \mathbf{c}_{v - 1}(k^2, \vkappa)
+    \frac{2 v \sin^2\valpha}{1 - \mathbf{q}(k^2, \valpha)^2}
+    \mathbf{b}_{v - 1}(k^2, \valpha)
+    - \mathbf{c}_{v - 1}(k^2, \valpha)
     \right)
@@
     \\
-    \mathbf{c}_v(k^2, \vkappa) & =
-    \sinhalfkap[2] \mathbf{c}_{v - 1}(k^2, \vkappa)
+    \mathbf{c}_v(k^2, \valpha) & =
+    \sin^2\valpha \, \mathbf{c}_{v - 1}(k^2, \valpha)
 \end{proof}
@@
     \mathbf{b}_\vmax &=
-    \frac{\sin^{2\vmax + 2}\left(\frac{\vkappa}{2}\right)}{4\vmax + 10}
+    \frac{\sin^{2\vmax + 2}\valpha}{4\vmax + 10}
     \left(
-    \mathbf{f}_\vmax(k^2, \vkappa)
-    + 2 \mathbf{q}(k^2, \vkappa)^3
+    \mathbf{f}_\vmax(k^2, \valpha)
+    + 2 \mathbf{q}(k^2, \valpha)^3
     \right)
@@
     \frac{1}{2}
-    \mathbf{q}(k^2, \vkappa)^5
-    \sin^{2\vmax}\left(\frac{\vkappa}{2}\right)
+    \mathbf{q}(k^2, \valpha)^5
+    \sin^{2\vmax}\valpha
     \quad,
@@
 \begin{proof}{W}
-    \mathbf{f}_v(k^2, \vkappa)
+    \mathbf{f}_v(k^2, \valpha)
     &\equiv
@@
     v + 2;
-    1 - \mathbf{q}(k^2, \vkappa)^2
+    1 - \mathbf{q}(k^2, \valpha)^2
     \right)
@@
 and ${_2\mathbbb{F}_1}(a, b; c; \mathbf{z})$ is the Gauss
-hypergeometric function.
+hypergeometric function, which we compute via its series
+definition.
 %
@@
 \begin{proof}{W}
-    \mathbf{b}_v(k^2, \vkappa) & =
-    \frac{1 - \mathbf{q}(k^2, \vkappa)^2}{\sinhalfkap[2]}
+    \mathbf{b}_v(k^2, \valpha) & =
+    \frac{1 - \mathbf{q}(k^2, \valpha)^2}{\sin^2\valpha}
     \left(1 + \frac{5}{2v + 2}\right)
-    \mathbf{b}_{v + 1}(k^2, \vkappa) +
-    \frac{\mathbf{c}_{v + 1}(k^2, \vkappa)}{v + 1}
+    \mathbf{b}_{v + 1}(k^2, \valpha) +
+    \frac{\mathbf{c}_{v + 1}(k^2, \valpha)}{v + 1}
     \nonumber
     \\
-    \mathbf{c}_v(k^2, \vkappa) & =
-    \frac{\mathbf{c}_{v + 1}(k^2, \vkappa)}{\sinhalfkap[2]}
+    \mathbf{c}_v(k^2, \valpha) & =
+    \frac{\mathbf{c}_{v + 1}(k^2, \valpha)}{\sin^2\valpha}
     \quad.
@@
 \begin{align}
+    \label{eq:p2}
     \mathbb{p}_2 & =
     \vint{\pmb{\phi}}{
+        \frac{1}{3}
         \left(
         \frac{
-            1 - (1 - r_o^2 - b_o^2 - 2 b_o r_o \sin\varphi)^\frac{3}{2}
+            1 - z(r_o\cos\varphi, b_o + r_o\sin\varphi)^3
         }{
-            r_o^2 + b_o^2 + 2 b_o r_o \sin\varphi
+            1 - z(r_o\cos\varphi, b_o + r_o\sin\varphi)^2
         }
@@
     }
-\end{align}
-%
+    \quad,
+\end{align}
+%
+where $z$ is the usual Cartesian coordinate (Equation~\ref{eq:z}).
 The solution is tricky, but fortunately a similar integral was solved in
@@
 %
-\begin{proof}{}
+\begin{proof}{p2}
+    \label{eq:p2_soln}
+    \mathbb{p}_2 & =
     \frac{1}{3}
@@
     c_0 +
-    c_1 \Delta\mathbbb{F}(k^2, \vkappa) +
-    c_2 \Delta\mathbbb{E}(k^2, \vkappa) +
-    c_3 \Delta\mathbbb{P}(k^2, \vkappa)
+    c_1 \DF +
+    c_2 \DE +
+    c_3 \DPi
     \Big)
@@
 %
-\begin{proof}{}
+\begin{proof}{p2}
     c_0 &=
+    \Delta
+    \Bigg\{
+    -\atantwo\left(
+    -(b_o - r_o) \cos\valpha, (b_o + r_o) \sin\valpha
+    \right)
+    + \valpha
+    \nonumber \\
+    &\qquad\enspace\enspace
+    - \frac{4}{3} b_o r_o
+    \sin\valpha \cos\valpha
+    \sqrt{1 - (b_o - r_o)^2 - 4 b_o r_o \sin^2\alpha}
+    \nonumber \\
+    &\qquad\enspace\enspace
+    + \pmb{\delta}(b_o, r_o, \valpha)
+    \Bigg\}
+    \nonumber \\[0.5em]
+    c_1 &=
+    \frac{1 + b_o^4 - b_o^2(5 + 2 r_o^2) + r_o^4 + r_o^2}{3 \sqrt{1 - (b_o - r_o)^2}}
+    \nonumber \\[0.5em]
+    c_2 &= \frac{(b_o^2+7r_o^2-4)\sqrt{1 - (b_o - r_o)^2}}{3}
+    \nonumber \\[0.5em]
+    c_3 &= \frac{b_o + r_o}{(b_o - r_o)\sqrt{1 - (b_o - r_o)^2}}
+    \quad,
+    \\
+    \intertext{and}
+    %
+    \delta(b_o, r_o, \alpha) &=
     \begin{cases}
-        ? & ?
+        -2\pi
+         &
+        \qquad
+        \alpha > \frac{3\pi}{2} \,\, \text{and} \,\, b_o > r_o
+        \\
+        +2\pi
+         &
+        \qquad
+        \alpha > \frac{3\pi}{2} \,\, \text{and} \,\, b_o < r_o
+        \\
+        0
+         &
+        \qquad
+        \text{otherwise}
+        \quad.
     \end{cases}
-    \nonumber \\
-    c_1 &= ?
-    \nonumber \\
-    c_2 &= -\frac{2}{3} \sqrt{k^2 b_o r_o} (4 - 7 r_o^2 - b_o^2)
-    \nonumber \\
-    c_3 &= \frac{1}{3} \sqrt{k^2 b_o r_o} \frac{b_o + r_o}{(b_o - r_o)^2}
-\end{proof}
-%
-\xxx{This section needs work!}
-
-%
+\end{proof}
+%
+The quantities $\mathbbb{F}(\valpha \,|\, \nicefrac{1}{k^2})$ and
+$\mathbbb{E}(\valpha \,|\, \nicefrac{1}{k^2})$
+are the same incomplete elliptic integrals as those in
+\S\ref{sec:J}, while
+%
+\begin{align}
+    \label{eq:Pi}
+    \mathbb{\Pi}(n; \psi \,|\, m) & \equiv
+    \int_0^{\psi}
+    \frac{\dd \varphi}{(1 - n \sin^2\varphi)\sqrt{1 - m \sin^2 \varphi}}
+\end{align}
+%
+is the incomplete elliptic integral of the third
+kind, with
+%
+\begin{proof}{p2}
+    n & = -\frac{4 b_o r_o}{(r_o - b_o)^2}
+    \quad.
+\end{proof}
+%
+
+While stable algorithms exist to evaluate $\mathbb{\Pi}(n; \psi \,|\, m)$
+\citep[e.g.][]{Bulirsch1969}, we find that the parametrization above has
+poor numerical stability, particularly in the vicinity of the singular
+points $b_o = r_o$ and $b_o = 1 + r_o$. In practice, we find that
+numerical evaluation of Equation~(\ref{eq:p2}) via Gaussian quadrature
+is more numerically stable and just as computationally efficient as
+the procedure outlined above.
 
@@
         \qquad\quad\quad
-        + \, \pmb{\phi}(b, \vxi)
+        + \, \pmb{\delta}(b, \vxi)
         \Big\}
@@
 \begin{proof}{}
-    \phi(b, \xi) & =
+    \delta(b, \xi) & =
     \begin{cases}

### 2020-04-16 tex/ms.tex
woot

@@
 review \citet{Luger2019} before proceeding.
+To improve the readability of this paper,
+Tables~\ref{tab:symbols}--\ref{tab:matrices} at the end list the principal
+symbols and quantities used throughout the text, with links to the
+sections and equations in which they are defined.
 
@@
 %
-where, from right to left, $\mathbf{R} = \mathbf{R}(i, \lambda, \vartheta)$
+where, from right to left, $\mathbf{R} = \mathbf{R}(\text{I}, \Lambda, \Theta)$
 is a Wigner rotation matrix that rotates $\bvec{y}$ from $\mathcal{F}_0$
 to the sky frame $\mathcal{F}$
-given the body's inclination $i$, obliquity
-$\lambda$, and rotational phase $\vartheta$
+given the body's inclination $\text{I}$, obliquity
+$\Lambda$, and rotational phase $\Theta$
 \citep[Appendix C in][]{Luger2019},
@@
 %
-where, as before, $\mathbf{R} = \mathbf{R}(i, \lambda, \vartheta)$
+where, as before, $\mathbf{R} = \mathbf{R}(\text{I}, \Lambda, \Theta)$
 rotates the body from $\mathcal{F}_0$
@@
 \subsection{Adapting the algorithm to the reflected light case}
-\label{sec:starry-review}
+\label{sec:adapting-starry}
 %
@@
 %
-with $b_c = \sqrt{1 - b^2}$ and $z(x, y) = \sqrt{1 - x^2 - y^2}$.
+with $b_c \equiv \sqrt{1 - b^2}$ and $z(x, y) = \sqrt{1 - x^2 - y^2}$.
 
@@
 \begin{proof}{}
+    \label{eq:ivec}
     \mathbf{i}(b, \theta, r_s) & =
@@
 \begin{proof}{}
+    \label{eq:Imat}
     \mathbf{I}(b, \theta, r_s) & =
@@
     \mathbf{R}'(x_o, y_o)
-    \mathbf{R}(i, \lambda, \vartheta)
+    \mathbf{R}(\text{I}, \Lambda, \Theta)
     \mathbf{y}
@@
     \mathbf{R}''(x_s, y_s)
-    \mathbf{R}(i, \lambda, \vartheta)
+    \mathbf{R}(\text{I}, \Lambda, \Theta)
     \mathbf{y}
@@
     \label{eq:rTI}
-    \pmb{\rho}^\top(b, r_s) & \equiv
-    \rT(b) \mathbf{I}(b, 0, r_s)
+    \overset{\quad\pmb{\wedge}}{\mathbbb{r}}{^\top}(b, r_s) & \equiv
+    \rT(b) \mathbf{I}(b, \theta'', r_s)
     \nonumber                                                        \\
@@
 Equation~(\ref{eq:rTI}) may be solved analytically in terms of purely
-trigonometric and algebraic functions of $b$. The component of $\pmb{\rho}^\top$
+trigonometric and algebraic functions of $b$.
+The component of $\overset{\quad\pmb{\wedge}}{\mathbbb{r}}{^\top}$
 at index $n$ is given by
@@
     \label{eq:rTsoln}
-    \rho_n(b, r_s) & =
+    \overset{\quad\wedge}{\mathbb{r}}_n(b, r_s) & =
     \frac{1}{4\pi r_s^2}
@@
         \frac{b_c\left(1 - b^{\frac{\nu + 4}{2}}\right)}{2}
-        J_{\frac{\mu}{2}, \frac{\nu + 2}{2}} -
-        b H_\frac{\nu}{2}(b) K_{\frac{\mu}{2}, \frac{\nu}{2}}
+        \mathbb{L}_{\frac{\mu}{2}, \frac{\nu + 2}{2}} -
+        b \mathbb{k}_\frac{\nu}{2}(b) \mathbb{M}_{\frac{\mu}{2}, \frac{\nu}{2}}
         %
@@
         b_c
-        H_{\frac{\nu + 1}{2}}(b) K_{\frac{\mu - 1}{2}, \frac{\nu + 1}{2}}
+        \mathbb{k}_{\frac{\nu + 1}{2}}(b) \mathbb{M}_{\frac{\mu - 1}{2}, \frac{\nu + 1}{2}}
         %
@@
         \left(
-        J_{\frac{\mu - 1}{2}, \frac{\nu - 1}{2}} -
-        J_{\frac{\mu + 3}{2}, \frac{\nu - 1}{2}}
+        \mathbb{L}_{\frac{\mu - 1}{2}, \frac{\nu - 1}{2}} -
+        \mathbb{L}_{\frac{\mu + 3}{2}, \frac{\nu - 1}{2}}
         \right)
@@
         \left(1 - b^{\frac{\nu + 5}{2}}\right)
-        J_{\frac{\mu - 1}{2}, \frac{\nu + 3}{2}}
+        \mathbb{L}_{\frac{\mu - 1}{2}, \frac{\nu + 3}{2}}
         \bigg\}
@@
 %
-where we make use of the indices
-%
-\begin{align}
-    \label{eq:l-m-mu-nu}
-    \mu & = l - m
-    \nonumber                 \\
-    \nu & = l + m
-    \nonumber                 \\
-    l   & = \floor*{\sqrt{n}}
-    \nonumber                 \\
-    m   & = n - l^2 - l
-\end{align}
-%
-as in \citet{Luger2019} and we define the helper functions
+where the components of $\mathbbb{k}$, $\mathbbb{L}$, and $\mathbbb{M}$
+are given by
 %
@@
     \label{eq:HJK}
-    H_{j}(b) &= \int_b^1 a^j \sqrt{1 - a^2} \dd a
-    \nonumber \\
-    %
-    J_{i,j} &=
+    \mathbb{k}_{j}(b) &= \int_b^1 a^j \sqrt{1 - a^2} \dd a
+    \nonumber \\
+    %
+    \mathbb{L}_{i,j} &=
     \frac{
@@
     %
-    K_{i,j} &=
+    \mathbb{M}_{i,j} &=
     \frac{
@@
     }
-    \quad.
-\end{proof}
+    \quad,
+\end{proof}
+%
+where $\Gamma$ is the gamma function.
 %
@@
     \begin{align}
-        H_{0}(b) & = \frac{\arccos(b) - bb_c}{2}
-        %
-        \nonumber                                \\
-        %
-        H_{1}(b) & = \frac{b_c^3}{3}
+        \mathbb{k}_{0}(b) & = \frac{\arccos(b) - bb_c}{2}
+        %
+        \nonumber                                         \\
+        %
+        \mathbb{k}_{1}(b) & = \frac{b_c^3}{3}
         %
@@
     \begin{align}
-        J_{0,0} & = \pi
-        %
-        \nonumber               \\
-        %
-        J_{0,1} & = \frac{4}{3}
+        \mathbb{L}_{0,0} & = \pi
+        %
+        \nonumber                        \\
+        %
+        \mathbb{L}_{0,1} & = \frac{4}{3}
         %
@@
         \label{eq:IJK0}
-        K_{0,0} &= \frac{4}{3}
-        %
-        \nonumber \\
-        K_{0,1} &= \frac{3\pi}{8}
+        \mathbb{M}_{0,0} &= \frac{4}{3}
+        %
+        \nonumber \\
+        \mathbb{M}_{0,1} &= \frac{3\pi}{8}
     \end{proof}
@@
     \label{eq:IJKrec}
-    H_{j}(b) &= \frac{b^n b_c^3 + (j - 1) H_{j - 2}(b)}{j + 2}
-    %
-    \nonumber \\
-    %
-    J_{0,j} &= \left(\frac{j - 1}{j + 2}\right) J_{0,j-2}
-    %
-    \nonumber \\
-    %
-    K_{0,j} &= \left(\frac{j + 2}{j + 3}\right) K_{0,j-2}
-    %
-    \nonumber \\
-    %
-    J_{i,j} &= \left(\frac{i - 1}{i + j + 2}\right) J_{i-2,j}
-    %
-    \nonumber \\
-    %
-    K_{i,j} &= \left(\frac{i - 1}{i + j + 3}\right) K_{i-2,j}
-    \quad.
-\end{proof}
-%
-Once $\pmb{\rho}^\top$ is known, the observed flux is computed from
+    \mathbb{k}_{j}(b) &= \frac{b^n b_c^3 + (j - 1) \mathbb{k}_{j - 2}(b)}{j + 2}
+    %
+    \nonumber \\
+    %
+    \mathbb{L}_{0,j} &= \left(\frac{j - 1}{j + 2}\right) \mathbb{L}_{0,j-2}
+    %
+    \nonumber \\
+    %
+    \mathbb{M}_{0,j} &= \left(\frac{j + 2}{j + 3}\right) \mathbb{M}_{0,j-2}
+    %
+    \nonumber \\
+    %
+    \mathbb{L}_{i,j} &= \left(\frac{i - 1}{i + j + 2}\right) \mathbb{L}_{i-2,j}
+    %
+    \nonumber \\
+    %
+    \mathbb{M}_{i,j} &= \left(\frac{i - 1}{i + j + 3}\right) \mathbb{M}_{i-2,j}
+    \quad.
+\end{proof}
+%
+Once $\overset{\quad\pmb{\wedge}}{\mathbbb{r}}{^\top}$ is known,
+the observed flux is computed from
 (c.f. Equation~\ref{eq:rTIA1RRy})
@@
     f_0 & =
-    \pmb{\rho}^\top(b, r_s)
+    \overset{\quad\pmb{\wedge}}{\mathbbb{r}}{^\top}(b, r_s)
     \mathbf{A_1}
     \mathbf{R}''(x_s, y_s)
-    \mathbf{R}(i, \lambda, \vartheta)
+    \mathbf{R}(\text{I}, \Lambda, \Theta)
     \mathbf{y}
@@
     \hat{f}_0 & =
-    -\pmb{\rho}^\top(-b, r_s)
+    -\overset{\quad\pmb{\wedge}}{\mathbbb{r}}{^\top}(-b, r_s)
     \mathbf{A_1}
     \mathbf{R}''(-x_s, -y_s)
-    \mathbf{R}(i, \lambda, \vartheta)
+    \mathbf{R}(\text{I}, \Lambda, \Theta)
     \mathbf{y}
@@
 of intersection with the terminator is easier if we temporarily switch to
-the frame $\mathcal{F}''$ (via Equation~\ref{eq:R''}) in which the terminator
+the frame $\mathcal{F}''$, in which the terminator
 is parallel to the $x''$-axis.
@@
 %
-where the indices $l, m, \mu, \nu$ are given by Equation~(\ref{eq:l-m-mu-nu}).
+where the indices $l, m, \mu, \nu$ are given by
+Equations~(\ref{eq:l-m}) and (\ref{eq:mu-nu}).
 
@@
 \begin{align}
+    \label{eq:V}
     V\left(u, v, w; \mathbf{x}\right) \equiv
@@
     \label{eq:F}
-    \mathbb{F}(\psi \,|\, m) & \equiv \int_0^{\psi} \frac{\dd \varphi}{\sqrt{1 - m \sin^2 \varphi}}
+    F(\psi \,|\, m) & \equiv \int_0^{\psi} \frac{\dd \varphi}{\sqrt{1 - m \sin^2 \varphi}}
     \\
@@
     \label{eq:E}
-    \mathbb{E}(\psi \,|\, m) & \equiv \int_0^{\psi} \sqrt{1 - m \sin^2 \varphi} \, \dd \varphi
+    E(\psi \,|\, m) & \equiv \int_0^{\psi} \sqrt{1 - m \sin^2 \varphi} \, \dd \varphi
     \quad,
@@
 \begin{align}
-    \mathbb{F}\left(\psi \,\Big|\, \frac{1}{k^2}\right) & =
-    k \, \mathbb{F}(\beta \,|\, k^2)
-    \nonumber                                                                                        \\
-    \mathbb{E}\left(\psi \,\Big|\, \frac{1}{k^2}\right) & =
-    \frac{\mathbb{E}(\beta \,|\, k^2) - (1 - k^2) \mathbb{F}(\beta \,|\, k^2)}{k}
+    F\left(\psi \,\Big|\, \frac{1}{k^2}\right) & =
+    k \, F(\beta \,|\, k^2)
+    \nonumber                                                                               \\
+    E\left(\psi \,\Big|\, \frac{1}{k^2}\right) & =
+    \frac{E(\beta \,|\, k^2) - (1 - k^2) F(\beta \,|\, k^2)}{k}
     \\
@@
     \,
-    {_2\mathbbb{F}_1}\left(
+    {_2\pmb{F}_1}\left(
     -\frac{1}{2},
@@
 %
-and ${_2\mathbbb{F}_1}(a, b; c; \mathbf{z})$ is the Gauss
+and ${_2\pmb{F}_1}(a, b; c; \mathbf{z})$ is the Gauss
 hypergeometric function, which we compute via its series
@@
 %
-The quantities $\mathbbb{F}(\valpha \,|\, \nicefrac{1}{k^2})$ and
-$\mathbbb{E}(\valpha \,|\, \nicefrac{1}{k^2})$
+The quantities $\pmb{F}(\valpha \,|\, \nicefrac{1}{k^2})$ and
+$\pmb{E}(\valpha \,|\, \nicefrac{1}{k^2})$
 are the same incomplete elliptic integrals as those in
@@
     \label{eq:Pi}
-    \mathbb{\Pi}(n; \psi \,|\, m) & \equiv
+    \Pi(n; \psi \,|\, m) & \equiv
     \int_0^{\psi}
@@
 \begin{proof}{p2}
+    \label{eq:n}
     n & = -\frac{4 b_o r_o}{(r_o - b_o)^2}
@@
 
-While stable algorithms exist to evaluate $\mathbb{\Pi}(n; \psi \,|\, m)$
+While stable algorithms exist to evaluate $\Pi(n; \psi \,|\, m)$
 \citep[e.g.][]{Bulirsch1969}, we find that the parametrization above has
@@
 %
-The components of the vector $\viH$ are given by the integral
+The components of the matrix $\viH$ are given by the integral
 %
@@
 %
-where the vector $\viH$ is given by Equation~(\ref{eq:H}).
+where the matrix $\viH$ is given by Equation~(\ref{eq:H}).
 

### 2020-04-16 tex/ms.tex
added figure

@@
 %
+\section{Overview}
+\label{sec:overview}
+
+\begin{figure}[h!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/earthmoon_emitted.pdf}
+        \includegraphics[width=\linewidth]{figures/earthmoon.pdf}
+        \oscaption{earthmoon}{%
+            Mock light curves of the Moon occulting a rotating,
+            cloudless Earth expanded to spherical harmonic degree $l = 25$.
+            Black curves show the analytic solution; orange dots correspond
+            to brute force numerical integration on a grid of
+            ${\sim}10^6$ points.
+            The top panel shows the light curve in emitted light and is
+            equivalent to Figure~7 in \citet{Luger2019}.
+            The bottom panel (this work) shows the same light curve in
+            reflected light during northern summer.
+            \label{fig:earthmoon}
+        }
+    \end{centering}
+\end{figure}
 

### 2020-04-16 tex/figures/earthmoon.py

@@ -1,0 +1,137 @@
+"""Earth occultation example."""
+import starry
+import matplotlib.pyplot as plt
+import numpy as np
+from matplotlib.colors import LinearSegmentedColormap
+
+# Disable lazy mode
+starry.config.lazy = False
+
+cmap = LinearSegmentedColormap(
+    "cmap1",
+    segmentdata={
+        "red": [[0.0, 0.0, 0.122], [1.0, 1.0, 1.0]],
+        "green": [[0.0, 0.0, 0.467], [1.0, 1.0, 1.0]],
+        "blue": [[0.0, 0.0, 0.706], [1.0, 1.0, 1.0]],
+    },
+    N=256,
+)
+cmap.set_under("k")
+
+for reflected in False, True:
+
+    # Set up the plot
+    nim = 12
+    npts = 100
+    nptsnum = 10
+    res = 999
+    fig = plt.figure(figsize=(12, 5))
+    ax_im = [plt.subplot2grid((4, nim), (0, n)) for n in range(nim)]
+    ax_lc = plt.subplot2grid((4, nim), (1, 0), colspan=nim, rowspan=3)
+
+    # Instantiate the Earth
+    map = starry.Map(25, reflected=reflected)
+    map.load("earth", sigma=0.06)
+
+    # Moon occultation params
+    ro = 0.273
+    yo = np.linspace(-0.5, 0.5, npts)
+    yonum = np.linspace(-0.5, 0.5, nptsnum)
+    xo = np.linspace(-1.5, 1.5, npts)
+    xonum = np.linspace(-1.5, 1.5, nptsnum)
+
+    # Say the occultation occurs over ~1 radian of the Earth's rotation
+    # That's equal to 24 / (2 * pi) hours
+    time = np.linspace(0, 24 / (2 * np.pi), npts)
+    timenum = np.linspace(0, 24 / (2 * np.pi), nptsnum)
+    theta0 = 0
+    theta = np.linspace(theta0, theta0 + 180.0 / np.pi, npts, endpoint=True)
+    thetanum = np.linspace(theta0, theta0 + 180.0 / np.pi, nptsnum, endpoint=True)
+
+    # Compute and plot the flux *analytically*
+    if reflected:
+        # Position of the illumination source (the sun).
+        # We'll assume it's constant for simplicity
+        xs = -1.0 * np.ones_like(time)
+        ys = 0.3 * np.ones_like(time)
+        zs = 1.0 * np.ones_like(time)
[…]

### 2020-04-22 tex/ms.tex
better normalization for lambertian spheres

@@
 %
-This is an extension of \citet{Luger2019}.
+Introduction here.
 
@@
 \label{sec:overview}
+
+Our goal in this paper is to derive analytic expressions for the
+flux received by a distant observer from a non-uniform Lambert sphere
+illuminated by a monochromatic source that may or may not be
+occulted by a (possibly different) spherical body. This applies, for example,
+to the
+case of exoplanet phase curves, exoplanet secondary
+eclipse (occultation) light curves, or exoplanet-moon and exoplanet-exoplanet
+occultations, all seen in reflected light. We explicitly assume the reflecting
+body is Lambertian, i.e., it scatters light isotropically, although with an
+intensity that varies across the surface according to a spatially-dependent
+albedo $A$. Throughout this paper, we will take $A$ to mean the \emph{spherical}
+albedo, the fraction of power incident on a body at a given wavelength
+that is scattered back out to space (in all directions).
+Note that the spherical albedo
+is closely related to the Bond albedo: the Bond albedo is the stellar
+flux-weighted integral of $A(\lambda)$ over all wavelengths $\lambda$. For
+more details, see \S4.5 of \citet{Schwartz2015}.
+
+As in \citet{Luger2019}, we compute fluxes by first expanding the surface
+in terms of spherical harmonics.
+While in \citet{Luger2019} we expanded the emissivity of the surface, here
+we instead expand the spherical albedo $A$.
+Specifically, if $\bvec{y}$ is the vector
+of spherical harmonic coefficients describing the albedo anywhere on
+the surface and
+$\by$ is the spherical harmonics basis (Equation~\ref{eq:by}),
+the albedo $A$ at a point $(x, y)$ on the sky-projected disk of the body
+is given by the dot product
+%
+\begin{align}
+    \label{eq:albedo}
+    A(x, y) = \by^\top (x, y) \, \bvec{y}
+    \quad.
+\end{align}
+%
+The flux measured from this body is the surface integral over the visible
+portion of the body's projected disk of the albedo $A$
+times the illumination profile $\mathcal{I}$ of the surface, given by
+Lambert's law as
+%
+\begin{align}
+    \label{eq:LambertsLaw}
+    \mathcal{I}(\phi) = \mathcal{I}_0 \, \text{max}\big( 0, \cos\phi \big)
+    \quad,
+\end{align}
+%
+where $\mathcal{I}_0$ is the peak illumination (at the sub-source point),
+which we discuss in more detail in \S\ref{sec:adapting-starry}.
 
@@
 \end{figure}
+
+\section{Extended illumination source}
+\label{sec:extended}
+Planets to consider: 55 Cnc e, Kelt-9b.
+The angular extent of the terminator past $\nicefrac{\pi}{2}$ is
+%
+\begin{align}
+    \tau = \arcsin\left( \frac{\Delta R}{d} \right)
+\end{align}
+
+\section{Non-Lambertian scatterers}
+\label{sec:nonlambertian}
+In principle, we can just change $\mathbf{I}$.
 
@@
     \label{eq:by}
-    \by & =
+    \by(x, y) & =
     \begin{pmatrix}
@@
 %
-where the component at index $n$ is $Y_{l,m}$ with
+where the component at index $n$ is the spherical harmonic $Y_{l,m}(x, y)$ with
 %
@@
 %
+The spherical harmonics are traditionally expressed in spherical coordinates,
+but for our purposes
+it is more conventient to express them in Cartesian coordinates on
+the sky-projected disk, in which case they are simply polynomials in
+$x$, $y$, and $z$ \citep[see Appendix~A in][]{Luger2019}.
+
 An observer views the body from a large distance in the sky frame
@@
 reflectance, in which case the vector $\mathbf{y}$ is taken to describe the
-surface \emph{reflectivity} (or \emph{Bond albedo}).
+spherical albedo of the surface, $A$.
 
 Second, we must explicitly model the illumination of the body. We assume the
-body is illuminated by a point-like source of unit luminosity, in which case
-the radiance at any
-point on the surface is proportional to the cosine of the angle between
+body is illuminated by a point-like source whose flux measured by the observer
+is unity. In this case, the observed intensity at any
+point on the surface is proportional to the cosine of the angle $\phi$ between
 the incident light and the surface normal. Points for which
-this angle is greater than $\nicefrac{\pi}{2}$ are unilluminated and
-therefore have radiance of zero.
+$\phi \ge \nicefrac{\pi}{2}$ are unilluminated and
+therefore have an intensity of zero.
 %
 If the point-like illumination source is placed at sky coordinates
-$(x_s, y_s, z_s)$, the day/night terminator on the body is a half-ellipse
+$(x_s, y_s, z_s)$ in units of the radius of the illuminated body,
+the day/night terminator on the body is a half-ellipse
 of semi-major axis unity that is fully described by its (signed) semi-minor
@@
     \label{eq:illum_poly}
-    I(b, \theta, r_s; x, y) &= \frac{1}{4\pi r_s^2}
+    I(b, \theta, r_s; x, y) &= \frac{1}{\pi r_s^2}
     \bigg(
@@
 with $b_c \equiv \sqrt{1 - b^2}$ and $z(x, y) = \sqrt{1 - x^2 - y^2}$.
+A quick note on the normalization of Equation~(\ref{eq:illum_poly}):
+if we place the illumination source along the $+z$-axis at $(0, 0, z_s)$,
+the body is seen at full phase, so $b = -1$, $b_c = 0$, and
+%
+\begin{proof}{}
+    \mathcal{I}_\text{full}(x, y) = \frac{\sqrt{1 - x^2 - y^2}}{\pi z_s^2}
+    \quad.
+\end{proof}
+%
+Integrating this over the full disk, we obtain the reflected flux measured
+by the observer if the body has unit spherical albedo,
+%
+\begin{proof}{}
+    \mathcal{f}_\text{full} &=
+    \int_{-1}^{1}
+    \int_{-\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
+    \frac{\sqrt{1 - x^2 - y^2}}{\pi z_s^2}
+    \,
+    \dd y
+    \,
+    \dd x
+    \nonumber \\[0.5em]
+    &= \left(\frac{2}{3}\right) \frac{1}{z_s^2}
+    \quad,
+\end{proof}
+%
+recalling that $z_s$ is measured in units of the illuminated body's
+radius. The factor of $\nicefrac{2}{3}$ is
+precisely the ratio of the geometric albedo to the spherical
+albedo of a Lambert sphere \citep[see, e.g.][]{Seager2010}. If we placed
+the source at $z_s = 1$, reflection off the illuminated body would increase
+the total flux measured at the observer by $\nicefrac{2}{3}$ (since, by
+assumption, the source flux at the observer is unity). As a sanity check,
+if all radiation incident on the body were instead scattered back toward the
+source (and hence toward the observer), $f_\text{full}$ would instead be unity:
+the flux at the observer would \emph{double}.
+\xxx{Is this explanation satisfactory? Does it make sense?}
 
@@
     \mathbf{i}(b, \theta, r_s) & =
-    \frac{1}{4\pi r_s^2}
+    \frac{1}{\pi r_s^2}
     \begin{pmatrix}
@@
     \mathbf{I}(b, \theta, r_s) & =
-    \frac{1}{4\pi r_s^2}
+    \frac{1}{\pi r_s^2}
     \begin{pmatrix}
@@
     \overset{\quad\wedge}{\mathbb{r}}_n(b, r_s) & =
-    \frac{1}{4\pi r_s^2}
+    \frac{1}{\pi r_s^2}
     \begin{cases}

### 2020-04-22 tex/figures/55cancrie.py

@@ -6,20 +6,11 @@ import astropy.units as u
 
 # Config
 starry.config.lazy = False
-# plt.switch_backend("MacOSX")
-
-# Time array
-t = np.linspace(0, 0.002, 1000)
-t0 = 0.400473685  # ingress start
-
-# Approximate relative luminosity of the planet
-tstar = 5172
-te = 2709
-rprs = 0.0182
-e_amp = rprs ** 2 * (te / tstar) ** 4
+plt.switch_backend("MacOSX")
 
 # Star
 star_map = starry.Map(udeg=2, amp=1)
+star_map[1:] = [0.5, 0.25]
 star = starry.Primary(
     star_map, m=0.905, mass_unit=u.M_sun, r=0.943, length_unit=u.R_sun
 )
@@ -32,40 +23,58 @@ kwargs = dict(
     r=1.875,
     length_unit=u.earthRad,
     inc=83.59,
-    t0=t0,
+    t0=0.400473685,
 )
 
-e_map = starry.Map(ydeg=1, reflected=False, amp=e_amp)
-e = starry.Secondary(e_map, **kwargs)
-flux_em = starry.System(star, e).flux(t=t)
-flux_em -= flux_em[-1]
-flux_em /= flux_em[0]
+# Time arrays (secondary eclipse ingress / full phase curve)
+t_ingress = np.linspace(0, 0.002, 1000)
+t_phase = kwargs["t0"] + kwargs["porb"] * np.linspace(-0.5, 0.5, 1000)
 
-e_map = starry.Map(udeg=1, reflected=False, amp=e_amp)
+# Uniform
+e_map = starry.Map(ydeg=1, reflected=False)
+e = starry.Secondary(e_map, **kwargs)
+sys = starry.System(star, e)
+flux_em = sys.flux(t=t_ingress, total=False)[1]
+
+# Noon approximation
+e_map = starry.Map(udeg=1, reflected=False)
 e_map[1] = 1
 e = starry.Secondary(e_map, **kwargs)
-flux_ld = starry.System(star, e).flux(t=t)
-flux_ld -= flux_ld[-1]
-flux_ld /= flux_ld[0]
+sys = starry.System(star, e)
+flux_ld = sys.flux(t=t_ingress, total=False)[1]
 
-e_map = starry.Map(ydeg=1, reflected=True, amp=e_amp)
+# Reflected, point source
[…]

### 2020-04-22 tex/figures/earthmoon.py

@@ -123,7 +123,7 @@ for reflected in False, True:
     ax_lc.plot(t_num, F_num, "C1o", label="numerical")
 
     # Appearance
-    ax_lc.set_ylim(0.65, 1.05)
+    ax_lc.set_ylim(0.6, 1.05)
     ax_lc.set_xlabel("time [hours]", fontsize=16)
     ax_lc.set_ylabel("normalized flux", fontsize=16)
     for tick in ax_lc.get_xticklabels() + ax_lc.get_yticklabels():

### 2020-04-22 tex/ms.tex
added io europa occ

@@
 %
-Introduction here.
-
-%
-\section{Overview}
-\label{sec:overview}
+\xxx{A few paragraphs of introduction here. \citet{Russell1906}.}
 
@@
 is closely related to the Bond albedo: the Bond albedo is the stellar
-flux-weighted integral of $A(\lambda)$ over all wavelengths $\lambda$. For
-more details, see \S4.5 of \citet{Schwartz2015}.
+flux-weighted integral of $A(\lambda)$ over all wavelengths $\lambda$
+\citep[see, e.g.,][]{Seager2010}.
 
@@
 %
-where $\mathcal{I}_0$ is the peak illumination (at the sub-source point),
-which we discuss in more detail in \S\ref{sec:adapting-starry}.
+where $\mathcal{I}_0$ is the peak illumination (at the sub-source point).
+%
+
+The piecewise nature of the illumination function at the day/night terminator
+makes the problem of computing the visible flux particularly difficult; most
+studies to date have tackled the problem numerically, by discretizing the surface
+and computing the relevant integrals by summing over the visible
+pixels \xxx{(cite)}. Recently, \citep{Haggard2018} developed an analytic
+framework for computing light curves of unocculted bodies illuminated
+by a point source. In this paper, we re-derive their solution under the
+\starry framework and extend it for the first time to the case where
+the body is occulted by another spherical body, which may or may not be the
+illumination source.
+
+In \citet{Luger2019}, we reduced the problem of computing the flux from
+an occulted body in emitted light to a series of efficient, analytical
+operations involving trigonometric functions of the position and size of the
+occultor and certain complete elliptic integrals. In the case of reflected
+light, however, the change in the limits of integration due to the
+unilluminated night side breaks many of the symmetries that simplified
+the flux calculation. In particular, the limits of integration now depend
+on the solution to a quartic equation specifying the points of intersection
+between the occultor and the day/night terminator, and the solution to
+those integrals is now a function of \emph{incomplete} elliptic integrals.
+The procedure for computing the flux is therefore significantly more complex.
+%
+We therefore defer all calculations to the Appendix, and devote the body of
+the paper to validating and demonstrating applications of our approach.
+
+\section{Reflected light curves in \starry}
+\label{sec:validation}
+
+\subsection{Sample light curves}
+\label{sec:sample}
+
+Figure~\ref{fig:earthmoon} shows a sample application of the algorithm
+developed in this paper. The figure shows two mock occultation light curves
+of the cloudless Earth as the Moon is seen to transit its disk, both computed
+using \starry from an $l=25$ expansion of the map of the Earth.
+The top panel shows an occultation in emitted light and is a reproduction of
+Figure~7 in \citet{Luger2019}. The bottom panel shows a light curve for the
+same occultation geometry, but seen instead in reflected light, with the
+Sun to the top left and slightly out of the page.
+The black curves correspond to the analytical solution, and the orange dots
+to the brute force numerical solution, obtained by discretizing the disk
+on a grid of ${\sim}10^6$ points. The solutions agree to within the
+numerical precision of the brute force solution (about 100 ppm in this
+case).
 
@@
 
-\section{Extended illumination source}
-\label{sec:extended}
-Planets to consider: 55 Cnc e, Kelt-9b.
-The angular extent of the terminator past $\nicefrac{\pi}{2}$ is
-%
-\begin{align}
-    \tau = \arcsin\left( \frac{\Delta R}{d} \right)
-\end{align}
-
-\section{Non-Lambertian scatterers}
-\label{sec:nonlambertian}
-In principle, we can just change $\mathbf{I}$.
-
-\section{Performance}
+\subsection{Performance}
 \label{sec:performance}
-%
-See Figure~\ref{fig:speed}.
-%
+
+Figure~\ref{fig:speed}
+
 \begin{figure}[h!]
@@
 \end{figure}
+
+\section{Extensions}
+\label{sec:extensions}
+
+\subsection{Extended illumination source}
+\label{sec:extended}
+Planets to consider: 55 Cnc e, Kelt-9b.
+The angular extent of the terminator past $\nicefrac{\pi}{2}$ is
+%
+\begin{align}
+    \tau = \arcsin\left( \frac{\Delta R}{d} \right)
+\end{align}
+
+\subsection{Non-Lambertian scatterers}
+\label{sec:nonlambertian}
+In principle, we can just change $\mathbf{I}$.
+
+%
 

### 2020-04-22 tex/figures/55cancrie.py

@@ -6,7 +6,6 @@ import astropy.units as u
 
 # Config
 starry.config.lazy = False
-plt.switch_backend("MacOSX")
 
 # Star
 star_map = starry.Map(udeg=2, amp=1)
@@ -62,9 +61,10 @@ fig, ax = plt.subplots(1, figsize=(8, 5))
 t = t_phase - kwargs["t0"]
 ax.plot(t, flux_phase * 1e6, "C0-", label="point source")
 ax.plot(t, flux_phase_fin * 1e6, "C1-", label="extended source")
-ax.set_xlabel("time [days]", fontsize=18)
-ax.set_ylabel("flux [ppm]", fontsize=18)
+ax.set_xlabel("time [days]", fontsize=16)
+ax.set_ylabel("flux [ppm]", fontsize=16)
 ax.legend(loc="best")
+fig.savefig("55cancrie.pdf", bbox_inches="tight")
 
 # Plot eclipse ingress
 fig, ax = plt.subplots(1, figsize=(8, 5))
@@ -73,8 +73,7 @@ ax.plot(t, flux_em / flux_em[0], "C2-", label="uniform")
 ax.plot(t, flux_ld / flux_ld[0], "C3-", label="noon")
 ax.plot(t, flux_ref / flux_ref[0], "C0-", label="point source")
 ax.plot(t, flux_ref_fin / flux_ref_fin[0], "C1-", label="extended source")
-ax.set_xlabel("time [minutes]", fontsize=18)
-ax.set_ylabel("flux [relative]", fontsize=18)
+ax.set_xlabel("time [minutes]", fontsize=16)
+ax.set_ylabel("flux [relative]", fontsize=16)
 ax.legend(loc="best")
-
-plt.show()
+fig.savefig("55cancrie_ingress.pdf", bbox_inches="tight")

### 2020-04-22 tex/figures/earthmoon.py

@@ -122,6 +122,8 @@ for reflected in False, True:
     F_num /= maxF
     ax_lc.plot(t_num, F_num, "C1o", label="numerical")
 
+    breakpoint()
+
     # Appearance
     ax_lc.set_ylim(0.6, 1.05)
     ax_lc.set_xlabel("time [hours]", fontsize=16)

### 2020-04-22 tex/figures/io_europa.py

@@ -1,0 +1,175 @@
+"""Europa-Io occultation from the PHEMU campaign."""
+import numpy as np
+from matplotlib import pyplot as plt
+from astropy.time import Time
+import astropy.units as u
+from astropy.timeseries import TimeSeries
+from astroquery.jplhorizons import Horizons
+import os
+import starry
+
+
+starry.config.lazy = False
+
+
+def get_body_ephemeris(times, body_id="501", step="1m"):
+
+    start = times.isot[0]
+
+    # Because Horizons time range doesn't include the endpoint
+    # we need to add some extra time
+    if step[-1] == "m":
+        padding = 2 * float(step[:-1]) / (60 * 24)
+    elif step[-1] == "h":
+        padding = 2 * float(step[:-1]) / 24
+    elif step[-1] == "d":
+        padding = 2 * float(step[:-1])
+    else:
+        raise ValueError(
+            "Unrecognized JPL Horizons step size. Use '1m' or '1h' for example."
+        )
+    end = Time(times.mjd[-1] + padding, format="mjd").isot
+
+    # Query JPL Horizons
+    epochs = {"start": start, "stop": end, "step": step}
+    obj = Horizons(id=body_id, epochs=epochs, id_type="id")
+    eph = obj.ephemerides(extra_precision=True)
+    times_jpl = Time(eph["datetime_jd"], format="jd")
+
+    # Store all data in a TimeSeries object
+    data = TimeSeries(time=times)
+    data["RA"] = np.interp(times.mjd, times_jpl.mjd, eph["RA"]) * eph["RA"].unit
+    data["DEC"] = np.interp(times.mjd, times_jpl.mjd, eph["DEC"]) * eph["DEC"].unit
+    data["ang_width"] = (
+        np.interp(times.mjd, times_jpl.mjd, eph["ang_width"]) * eph["ang_width"].unit
+    )
+    data["phase_angle"] = (
+        np.interp(times.mjd, times_jpl.mjd, eph["alpha_true"]) * eph["alpha_true"].unit
+    )
+    eph = obj.ephemerides(extra_precision=True)
+
+    # Boolean flags for occultations/eclipses
+    occ_sunlight = eph["sat_vis"] == "O"
+    umbra = eph["sat_vis"] == "u"
[…]

### 2020-05-01 tex/figures/io_europa.py
better fit

@@ -7,7 +7,7 @@ from astropy.timeseries import TimeSeries
 from astroquery.jplhorizons import Horizons
 import os
 import starry
-from scipy.optimize import minimize
+from matplotlib.patches import ConnectionPatch
 
 
 starry.config.lazy = False
@@ -158,101 +158,104 @@ def get_starry_args(time):
     return inc, obl, dict(theta=theta, xo=xo, yo=yo, ro=ro, xs=xs, ys=ys, zs=zs)
 
 
-# DEBUG
-if False:
+# Grab the PHEMU light curve
+time, flux, phemu_model = get_phemu_data()
 
-    # Grab the PHEMU light curve
-    time, flux, phemu_model = get_phemu_data()
+# Instantiate a starry map & get geometrical parameters
+map = starry.Map(ydeg=15, reflected=True)
+map.inc, map.obl, kwargs = get_starry_args(time)
 
-    # Instantiate a starry map & get geometrical parameters
-    map = starry.Map(ydeg=20, reflected=True)
-    map.inc, map.obl, kwargs = get_starry_args(time)
+# Load the Galileo SSI / Voyager composite
+# https://astrogeology.usgs.gov/search/map/Io/
+# Voyager-Galileo/Io_GalileoSSI-Voyager_Global_Mosaic_1km
+map.load("data/io_mosaic.jpg")
 
-    # Load the Galileo SSI / Voyager composite
-    # https://astrogeology.usgs.gov/search/map/Io/
-    # Voyager-Galileo/Io_GalileoSSI-Voyager_Global_Mosaic_1km
-    map.load("data/io_mosaic.jpg")
+# Fitted params (see `io_europa.ipynb`)
+dx = 0.06095157484199265
+dy = 0.01138082906950788
+amp = 43.93375998007594
+europa_amp = 0.46504556572406075
+roughness = 141.37543727300337
 
-    # Model
-    xo = kwargs.pop("xo")
-    yo = kwargs.pop("yo")
+# Compute the model
+map.roughness = roughness
+kwargs["xo"] += dx
+kwargs["yo"] += dy
+model = europa_amp + amp * map.flux(**kwargs)
 
-    # Very rough uncertainty (eyeballed)
-    ferr = 0.02
+# Set up the plot
+nim = 7
+res = 300
[…]

### 2020-05-01 tex/figures/oren_nayar.py

@@ -10,7 +10,7 @@ map = starry.Map(reflected=True)
 # Settings
 res = 300
 theta_im = np.linspace(0, 360, 9)[1:-1] * np.pi / 180
-theta_lr = np.linspace(0, 360, 20) * np.pi / 180
+theta_lr = np.linspace(0, 360, 100) * np.pi / 180
 theta_hr = np.linspace(0, 360, 1000) * np.pi / 180
 rs = [0, 15, 30, 45]
 
@@ -19,9 +19,7 @@ fig = plt.figure(figsize=(12, 8))
 ax_im = np.array(
     [
         [
-            plt.subplot2grid(
-                (4 * len(rs), len(theta_im)), (2 * i, j), rowspan=2
-            )
+            plt.subplot2grid((4 * len(rs), len(theta_im)), (2 * i, j), rowspan=2)
             for j in range(len(theta_im))
         ]
         for i in range(len(rs))
@@ -50,11 +48,7 @@ for i, roughness in enumerate(rs):
 
     # Plot the images for all phases
     img = map.render(
-        xs=np.sin(theta_im),
-        ys=0,
-        zs=-np.cos(theta_im),
-        res=res,
-        on94_exact=False,
+        xs=np.sin(theta_im), ys=0, zs=-np.cos(theta_im), res=res, on94_exact=False,
     )
     for j in range(len(theta_im)):
         if j < len(theta_im) - 1:
@@ -94,17 +88,13 @@ for i, roughness in enumerate(rs):
     # Render the exact Oren-Nayar image and compute
     # the numerical flux based on their Equation (30)
     img = map.render(
-        xs=np.sin(theta_lr),
-        ys=0,
-        zs=-np.cos(theta_lr),
-        res=res,
-        on94_exact=True,
+        xs=np.sin(theta_lr), ys=0, zs=-np.cos(theta_lr), res=res, on94_exact=True,
     )
     ax_lc.plot(
         theta_lr / (2 * np.pi),
         np.nansum(img, axis=(1, 2)) * 4 / res ** 2,
         "o",
-        ms=3,
+        ms=2,
         color="C{}".format(i),
     )
 

### 2020-05-02 tex/ms.tex
added fig
better fit
more reasonable sigr

@@
 \label{sec:nonlambertian}
-In principle, we can just change $\mathbf{I}$.
-
+Just change $\mathbf{I}$. \citep{OrenNayar1994}.
+
+\begin{figure}[h!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/oren_nayar.pdf}
+        \oscaption{oren_nayar}{%
+            Phase curves for different surface roughness coefficients.
+            \label{fig:oren_nayar}
+        }
+    \end{centering}
+\end{figure}
+%
+
+\section{Applications}
+\label{sec:applications}
+
+\begin{figure}[h!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/io_europa.pdf}
+        \oscaption{io_europa}{%
+            Occultation of Io by Europa.
+            \label{fig:io_europa}
+        }
+    \end{centering}
+\end{figure}
 %
@@
 A quick note on the normalization of Equation~(\ref{eq:illum_poly}):
-if we place the illumination source along the $+z$-axis at $(0, 0, z_s)$,
+if we place the illumination source along the $+z$-axis at $(0, 0, 1)$,
 the body is seen at full phase, so $b = -1$, $b_c = 0$, and
@@
 \begin{proof}{}
-    \mathcal{I}_\text{full}(x, y) = \frac{\sqrt{1 - x^2 - y^2}}{\pi z_s^2}
+    \mathcal{I}_\text{full}(x, y) = \frac{\sqrt{1 - x^2 - y^2}}{\pi}
     \quad.
@@
     \int_{-\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
-    \frac{\sqrt{1 - x^2 - y^2}}{\pi z_s^2}
+    \frac{\sqrt{1 - x^2 - y^2}}{\pi}
     \,
@@
     \nonumber \\[0.5em]
-    &= \left(\frac{2}{3}\right) \frac{1}{z_s^2}
-    \quad,
-\end{proof}
-%
-recalling that $z_s$ is measured in units of the illuminated body's
-radius. The factor of $\nicefrac{2}{3}$ is
-precisely the ratio of the geometric albedo to the spherical
-albedo of a Lambert sphere \citep[see, e.g.][]{Seager2010}. If we placed
-the source at $z_s = 1$, reflection off the illuminated body would increase
-the total flux measured at the observer by $\nicefrac{2}{3}$ (since, by
-assumption, the source flux at the observer is unity). As a sanity check,
-if all radiation incident on the body were instead scattered back toward the
-source (and hence toward the observer), $f_\text{full}$ would instead be unity:
-the flux at the observer would \emph{double}.
-\xxx{Is this explanation satisfactory? Does it make sense?}
+    &= \frac{2}{3}
+    \quad,
+\end{proof}
+%
+which is precisely the geometric albedo of a Lambert
+sphere \citep[see, e.g.][]{Seager2010}.
 
@@
 %
+\xxx{NO LONGER TRUE. FIX THIS DEFINITION.}
+%
 \begin{align}
@@
 \end{proof}
+%
+\xxx{FIX THIS DEFINITION. NO LONGER HOW WE COMPUTE IT.}
 %

### 2020-05-02 tex/figures/io_europa.py

@@ -154,7 +154,10 @@ def get_starry_args(time):
     xs = np.mean(eph_io["xs"].value)
     ys = np.mean(eph_io["ys"].value)
     zs = np.mean(eph_io["zs"].value)
-
+    rs = np.sqrt(xs ** 2 + ys ** 2 + zs ** 2)
+    xs /= rs
+    ys /= rs
+    zs /= rs
     return inc, obl, dict(theta=theta, xo=xo, yo=yo, ro=ro, xs=xs, ys=ys, zs=zs)
 
 
@@ -171,11 +174,11 @@ map.inc, map.obl, kwargs = get_starry_args(time)
 map.load("data/io_mosaic.jpg")
 
 # Fitted params (see `io_europa.ipynb`)
-dx = 0.06095157484199265
-dy = 0.01138082906950788
-amp = 43.93375998007594
-europa_amp = 0.46504556572406075
-roughness = 141.37543727300337
+dx = 0.06008183547425794
+dy = 0.004225467744578548
+amp = 1.5660538382102391
+europa_amp = 0.4695859742417233
+roughness = 55.766858039463685
 
 # Compute the model
 map.roughness = roughness

### 2020-05-04 tex/ms.tex
more figs

@@
 
-\begin{figure}[h!]
+\begin{figure}[ht!]
     \begin{centering}
@@
 Planets to consider: 55 Cnc e, Kelt-9b.
-The angular extent of the terminator past $\nicefrac{\pi}{2}$ is
-%
-\begin{align}
-    \tau = \arcsin\left( \frac{\Delta R}{d} \right)
-\end{align}
+Assuming $R_\star > R_p$, the angular extent of the terminator
+past $\nicefrac{\pi}{2}$ is
+%
+\begin{proof}{}
+    \label{eq:tau}
+    \tau &= \arcsin\left( \frac{R_\star - R_p}{d} \right)
+\end{proof}
+%
+where $R_\star$ is the radius of the star,
+$R_p$ is the radius of the planet, and $d$ is the separation of their
+centers.
+
+For Kelt-9b, $\nicefrac{R_p}{R_\star} = 0.083$ and
+$\nicefrac{a}{R_\star} = 3.16$, where $a$ is the semi-major axis of the
+planet \citep{Wong2019}. Asssuming zero eccentricity and ignoring any
+stellar oblateness
+\citep[see][]{Ahlers2020}, we find that
+the day/night terminator extends $\tau \approx 17^\circ$ past the limb
+of the planet. Figure~\ref{fig:extended} shows...
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/extended.pdf}
+        \oscaption{extended}{%
+            Normalized surface intensity on Kelt-9b viewed in a
+            Mollweide projection assuming a point illumination source
+            (left) and accounting for the finite extent of the star
+            (right). The day/night terminator extends about $17^\circ$
+            past where it is in the point source case. The sub-stellar
+            intensity is higher in the extended source case because the
+            sub-planet point on the star is 
+            closer to the planet than in the case where the star is a point
+            source located at the center of the star.
+            \label{fig:extended}
+        }
+    \end{centering}
+\end{figure}
+
+Figure~\ref{fig:kelt9b} shows...
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/kelt9b.pdf}
+        \oscaption{kelt9b}{%
+            Reflected light phase curve model (left) and
+            secondary eclipse model for Kelt-9b, assuming
+            a spherical albedo $A = 0.2$. The transit (phase zero)
+            is not included. Blue is the \starry model
+            assuming a point source illumination; orange accounts for
+            the finite size of the star. The right panel shows
+            the normalized flux during secondary eclipse ingress
+            for the two \starry models and for two approximations:
+            a surface with uniform intensity (solid purple)
+            and a surface whose intensity falls as the cosine of the
+            viewing angle from the center of the planet disk
+            (dashed purple).
+            \label{fig:kelt9b}
+        }
+    \end{centering}
+\end{figure}
 
@@
         \oscaption{oren_nayar}{%
-            Phase curves for different surface roughness coefficients.
+            Intensity measured from a sphere at varying illumination
+            phase under the \citet{OrenNayar1994} scattering model.
+            The top panel shows spheres rendered with different surface
+            roughness coefficients ranging from $\sigma = 0^\circ$
+            (the Lambertian case) to $\sigma = 45^\circ$. The bottom
+            panel shows the corresponding phase curves for a sphere
+            of unit spherical albedo illuminated by a point source
+            at $r_s = 1$, computed
+            analytically from a degree \STARRYQUADPOINTS expansion
+            of the scattering law. Dots
+            correspond to the intensity computed numerically directly
+            from Equation~(30) in \citet{OrenNayar1994}.
             \label{fig:oren_nayar}
@@
         \oscaption{io_europa}{%
-            Occultation of Io by Europa.
+            Visible-light occultation of Io by Europa observed
+            on 04 Dec 2009 by the PHEMU09 campaign \citep{Arlot2014}.
+            The blue line is the \starry model, based of an
+            $l=15$ spherical harmonic fit to the
+            Galileio global color mosaic of Io \citep{Becker2005},
+            an $l=\STARRYQUADPOINTS$ expansion of the
+            \citep{OrenNayar1994} scattering law, and orbital
+            information from the JPL Horizons \xxx{(cite)} database.
+            See text for details.
             \label{fig:io_europa}

### 2020-05-04 tex/figures/extended.py

@@ -1,0 +1,80 @@
+"""Extend illumination source."""
+import starry
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+import numpy as np
+
+# Config
+starry.config.lazy = False
+
+# Params from Wong et al. (2019)
+aRs = 3.16
+RpRs = 0.08229
+
+# Get the two images
+res = 999
+map = starry.Map(reflected=True, source_npts=1)
+img1 = map.render(projection="moll", xs=0, ys=0, zs=aRs / RpRs, res=res)
+map = starry.Map(reflected=True, source_npts=300)
+img2 = map.render(projection="moll", xs=0, ys=0, zs=aRs / RpRs, rs=1 / RpRs, res=res)
+norm = np.nanmax(img2)
+img1 /= norm
+img2 /= norm
+
+# Plot them. We'll instantiate a *regular* starry map and pass
+# in the images so that the intensity gets plotted with the
+# regular colormap (instead of with an alpha filter).
+fig, ax = plt.subplots(1, 2, figsize=(14, 4), constrained_layout=True)
+for axis in ax:
+    axis.grid(False)
+    axis.set_xticks([])
+    axis.set_yticks([])
+ax[0].set_title("point source")
+ax[1].set_title("extended source")
+norm = mpl.colors.Normalize(vmin=0, vmax=1)
+map = starry.Map(1)
+map.show(image=img1, projection="moll", ax=ax[0], norm=norm)
+map.show(image=img2, projection="moll", ax=ax[1], norm=norm)
+
+# Plot contours
+X = np.linspace(-2 * np.sqrt(2), 2 * np.sqrt(2), img2.shape[1])
+Y = np.linspace(-np.sqrt(2), np.sqrt(2), img2.shape[0])
+levels = np.array([0.0, 0.01, 0.05, 0.10, 0.30, 0.50, 0.75]) * 100
+for i, axis, img in zip([0, 1], ax, [img1, img2]):
+    cont = axis.contour(
+        X,
+        Y,
+        img / np.nanmax(img) * 100,
+        levels,
+        colors="w",
+        antialiased=True,
+        linewidths=0.5,
+        linestyles="dotted",
+    )
+    if i == 0:
+        x = np.array([-90, -80, -70, -60, -40]) * 2 * np.sqrt(2) / 180.0
+    else:
[…]

### 2020-05-04 tex/figures/kelt9b.py

@@ -1,0 +1,90 @@
+"""Kelt-9b secondary eclipse example."""
+import starry
+import matplotlib.pyplot as plt
+import numpy as np
+import astropy.units as u
+
+
+# Config
+starry.config.lazy = False
+
+
+# Star
+star_map = starry.Map(udeg=2, amp=1)
+star_map[1:] = [0.5, 0.25]
+star = starry.Primary(star_map, m=2.50, mass_unit=u.M_sun, r=2.36, length_unit=u.R_sun)
+
+# Planet
+kwargs = dict(
+    m=0.0,
+    mass_unit=u.earthMass,
+    porb=1.481,
+    r=21.1770214,
+    length_unit=u.earthRad,
+    inc=87.2,
+    t0=-0.65625,
+)
+
+# Time arrays (secondary eclipse ingress / full phase curve)
+t_ingress = np.linspace(0, 0.0174, 1000)
+t_phase = kwargs["t0"] + kwargs["porb"] * np.linspace(-0.5, 0.5, 1000)
+
+# Uniform
+e_map = starry.Map(ydeg=1, reflected=False)
+e = starry.Secondary(e_map, **kwargs)
+sys = starry.System(star, e)
+flux_em = sys.flux(t=t_ingress, total=False)[1]
+
+# Noon approximation
+e_map = starry.Map(udeg=1, reflected=False)
+e_map[1] = 1
+e = starry.Secondary(e_map, **kwargs)
+sys = starry.System(star, e)
+flux_ld = sys.flux(t=t_ingress, total=False)[1]
+
+# Reflected, point source
+e_map = starry.Map(ydeg=1, reflected=True)
+e_map.amp *= 0.2
+e = starry.Secondary(e_map, **kwargs)
+sys = starry.System(star, e)
+flux_ref = sys.flux(t=t_ingress, total=False)[1]
+flux_phase = sys.flux(t=t_phase, total=False)[1]
+
+# Reflected, extended source
+e_map = starry.Map(ydeg=1, reflected=True, source_npts=300)
+e_map.amp *= 0.2
+e = starry.Secondary(e_map, **kwargs)
+sys = starry.System(star, e)
+flux_ref_fin = sys.flux(t=t_ingress, total=False)[1]
+flux_phase_fin = sys.flux(t=t_phase, total=False)[1]
+
+# Plot phase curves
+fig, ax = plt.subplots(1, 2, figsize=(14, 4))
[…]

### 2020-05-04 tex/ms.tex
more figs

@@
 and computing the relevant integrals by summing over the visible
-pixels \xxx{(cite)}. Recently, \citep{Haggard2018} developed an analytic
+pixels \xxx{(cite)}. Recently, \citet{Haggard2018} developed an analytic
 framework for computing light curves of unocculted bodies illuminated
@@
 
+Figure~\ref{fig:earthphase} shows...
+
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/earthphase.pdf}
+        \oscaption{earthphase}{%
+            Mock reflected light  phase curve of the cloudless Earth expanded
+            to spherical harmonic degree $l = 25$. The main plot shows the
+            phase curve over the course of one year.
+            \label{fig:earthphase}
+        }
+    \end{centering}
+\end{figure}
+
 Figure~\ref{fig:earthmoon} shows a sample application of the algorithm
@@
 on a grid of ${\sim}10^6$ points. The solutions agree to within the
-numerical precision of the brute force solution (about 100 ppm in this
-case).
-
-\begin{figure}[ht!]
+numerical precision of the brute force solution (about 100 ppm of the
+planetary flux in this case).
+
+\begin{figure}[p!]
     \begin{centering}
@@
             The top panel shows the light curve in emitted light and is
-            equivalent to Figure~7 in \citet{Luger2019}.
+            the same as in Figure~7 in \citet{Luger2019}.
             The bottom panel (this work) shows the same light curve in
@@
 \end{figure}
+
+Figure~\ref{fig:earthsun} shows
+
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/earthsun_emitted.pdf}
+        \includegraphics[width=\linewidth]{figures/earthsun.pdf}
+        \includegraphics[width=\linewidth]{figures/earthsun_diff.pdf}
+        \oscaption{earthsun}{%
+            Mock secondary eclipse light curves of the
+            cloudless Earth expanded to spherical harmonic degree $l = 25$.
+            Black curves show the analytic solution; orange dots correspond
+            to brute force numerical integration on a grid of
+            ${\sim}10^6$ points.
+            The top panel shows the light curve in emitted light and is
+            similar to Figure~13 in \citet{Luger2019}.
+            The middle panel (this work) shows the same light curve in
+            reflected light.
+            The bottom panel shows the difference between the
+            normalized reflected and normalized emitted light curves.
+            \label{fig:earthsun}
+        }
+    \end{centering}
+\end{figure}
+
+% DEBUG
+\pagebreak
 
@@
 
-\begin{figure}[ht!]
+\begin{figure}[p!]
     \begin{centering}
@@
             an $l=\STARRYQUADPOINTS$ expansion of the
-            \citep{OrenNayar1994} scattering law, and orbital
+            \citet{OrenNayar1994} scattering law, and orbital
             information from the JPL Horizons \xxx{(cite)} database.
@@
 %
+
+\pagebreak
 

### 2020-05-04 tex/figures/earthphase.py

@@ -1,0 +1,108 @@
+"""Earth phase curve example."""
+import starry
+import matplotlib.pyplot as plt
+import numpy as np
+from matplotlib.colors import LinearSegmentedColormap
+
+# Disable lazy mode
+starry.config.lazy = False
+
+
+# Instantiate the Earth in reflected light
+map = starry.Map(25, reflected=True)
+map.load("earth", sigma=0.06)
+map.obl = 23.5
+
+# Earth colormap
+cmap = LinearSegmentedColormap(
+    "earth",
+    segmentdata={
+        "red": [[0.0, 0.0, 0.122], [1.0, 1.0, 1.0]],
+        "green": [[0.0, 0.0, 0.467], [1.0, 1.0, 1.0]],
+        "blue": [[0.0, 0.0, 0.706], [1.0, 1.0, 1.0]],
+    },
+    N=256,
+)
+
+# Set up the plot
+nim = 12
+npts = 5000
+nptsnum = 10
+res = 300
+fig = plt.figure(figsize=(12, 6.5))
+ax_im = [plt.subplot2grid((9, nim), (0, n), rowspan=2) for n in range(nim)]
+ax_in = [plt.subplot2grid((9, nim), (2, n)) for n in range(nim)]
+ax_lc = plt.subplot2grid((9, nim), (3, 0), colspan=nim, rowspan=6)
+
+# Orbital stuff
+Porb = 365.256
+Prot = 1.0
+time = np.linspace(0, Porb, npts)
+theta = (360.0 * time / Prot) % 360.0
+xs = np.sin(2 * np.pi * time / Porb)
+ys = np.zeros_like(time)
+zs = -np.cos(2 * np.pi * time / Porb)
+
+# Compute and plot the flux *analytically*
+F = map.flux(theta=theta, xs=xs, ys=ys, zs=zs)
+maxF = np.max(F)
+F /= maxF
+ax_lc.plot(time, F, "C0-", label="analytic", lw=0.5)
+
+# Plot the earth images & compute the numerical flux
+t_num = np.zeros(nim)
+F_num = np.zeros(nim)
+for n in range(nim):
+    i = int(np.linspace(0, npts - 1, nim + 2)[n + 1])
+
+    # Show the image at zero rotational phase
+    map.show(
+        ax=ax_im[n],
+        cmap=cmap,
+        xs=xs[i],
+        ys=ys[i],
[…]

### 2020-05-04 tex/figures/earthsun.py

@@ -10,10 +10,12 @@ starry.config.lazy = False
 # Instantiate the Earth in emitted light
 map_e = starry.Map(25)
 map_e.load("earth", sigma=0.06)
+map_e.inc = 90 - 23.5
 
 # Instantiate the Earth in reflected light
 map_r = starry.Map(25, reflected=True)
 map_r.load("earth", sigma=0.06)
+map_r.inc = 90 - 23.5
 
 # Earth colormap
 cmap = LinearSegmentedColormap(
@@ -37,34 +39,30 @@ for reflected in (True, False):
     ax_im = [plt.subplot2grid((4, nim), (0, n)) for n in range(nim)]
     ax_lc = plt.subplot2grid((4, nim), (1, 0), colspan=nim, rowspan=3)
 
-    # Moon occultation params
-    ro = 0.273
-    yo = np.linspace(-0.5, 0.5, npts)
-    yonum = np.linspace(-0.5, 0.5, nptsnum)
-    xo = np.linspace(-1.5, 1.5, npts)
-    xonum = np.linspace(-1.5, 1.5, nptsnum)
-
-    # Say the occultation occurs over ~1 radian of the Earth's rotation
-    # That's equal to 24 / (2 * pi) hours
-    time = np.linspace(0, 24 / (2 * np.pi), npts)
-    timenum = np.linspace(0, 24 / (2 * np.pi), nptsnum)
-    theta0 = 0
-    theta = np.linspace(theta0, theta0 + 180.0 / np.pi, npts, endpoint=True)
-    thetanum = np.linspace(theta0, theta0 + 180.0 / np.pi, nptsnum, endpoint=True)
+    # Sun occultation params
+    t1 = -342
+    t2 = -332
+    time = np.linspace(t1, t2, npts)  # in minutes
+    timenum = np.linspace(t1, t2, nptsnum)
+    ro = 6.957e8 / 6.3781e6  # 1 R_sun in R_earth
+    yo = -0.5 * ro * np.ones(npts)
+    yonum = -0.5 * ro * np.ones(nptsnum)
+    a = 1.496e11 / 6.3781e6  # 1 AU in R_earth
+    P = 365.25 * 24 * 60  # 1 year in minutes
+    xo = a * np.sin(2 * np.pi * time / P)
+    xonum = a * np.sin(2 * np.pi * timenum / P)
+    zo = a * np.cos(2 * np.pi * time / P)
+    zonum = a * np.cos(2 * np.pi * timenum / P)
[…]

### 2020-05-04 tex/figures/kelt9b.py

@@ -64,7 +64,7 @@ fig.subplots_adjust(hspace=0.025)
 t = t_phase - kwargs["t0"]
 phase = t / kwargs["porb"]
 ax[0].plot(t, flux_phase * 1e6, "C0-", label="point source")
-ax[0].plot(t, flux_phase_fin * 1e6, "C1-", label="extended source")
+ax[0].plot(t, flux_phase_fin * 1e6, "C4-", label="extended source")
 ax[0].set_xlabel("time [days]", fontsize=16)
 ax[0].set_ylabel("flux [ppm]", fontsize=16)
 ax[0].xaxis.labelpad = 10
@@ -74,10 +74,10 @@ ax[0].legend(loc="best", fontsize=12)
 
 # Plot eclipse ingress
 t = (t_ingress * u.day).to(u.minute)
-ax[1].plot(t, flux_em / flux_em[0], "C4-", label="uniform")
-ax[1].plot(t, flux_ld / flux_ld[0], "C4--", label="cosine")
+ax[1].plot(t, flux_em / flux_em[0], "C1-", label="uniform")
+ax[1].plot(t, flux_ld / flux_ld[0], "C1--", label="cosine")
 ax[1].plot(t, flux_ref / flux_ref[0], "C0-", label="point source")
-ax[1].plot(t, flux_ref_fin / flux_ref_fin[0], "C1-", label="extended source")
+ax[1].plot(t, flux_ref_fin / flux_ref_fin[0], "C4-", label="extended source")
 ax[1].set_xlabel("phase", fontsize=16)
 ax[1].set_ylabel("flux [normalized]", fontsize=16)
 ax[1].yaxis.tick_right()

### 2020-05-04 tex/figures/speed.py

@@ -337,10 +337,10 @@ class Compare(object):
         styles = [
             ("starry: reflected", "C0", "-"),
             ("starry: reflected (grad)", "C0", "--"),
-            ("starry: emitted", "C1", "-"),
-            ("starry: emitted (grad)", "C1", "--"),
-            ("grid", "C4", "-"),
-            ("dblquad", "C4", "--"),
+            ("starry: emitted", "C4", "-"),
+            ("starry: emitted (grad)", "C4", "--"),
+            ("grid", "C1", "-"),
+            ("dblquad", "C1", "--"),
         ]
 
         # Loop over all degrees

### 2020-05-05 tex/ms.tex
more progress

@@
 In \citet{Luger2019}, we reduced the problem of computing the flux from
-an occulted body in emitted light to a series of efficient, analytical
+an occulted body in thermal (emitted) light to a series of efficient, analytical
 operations involving trigonometric functions of the position and size of the
@@
 
-Figure~\ref{fig:earthphase} shows...
-
-\begin{figure}[p!]
+\begin{figure}[t!]
     \begin{centering}
@@
             Mock reflected light phase curve of the cloudless Earth expanded
-            to spherical harmonic degree $l = 25$. The main plot shows the
-            phase curve over the course of one year.
+            to spherical harmonic degree $l = 25$, viewed along the
+            ecliptic. The main plot shows the phase curve over the course of
+            one year.
+            The images at the top show the corresponding progression of
+            the phases of the Earth, from new phase to full phase and back
+            to new phase. Below each image we show a normalized 24-hour
+            segment of the light curve at that phase (blue).
+            Orange dots correspond
+            to the flux computed from brute force numerical integration on
+            a grid of
+            ${\sim}10^6$ points.
             \label{fig:earthphase}
@@
 
-Figure~\ref{fig:earthmoon} shows a sample application of the algorithm
-developed in this paper. The figure shows two mock occultation light curves
-of the cloudless Earth as the Moon is seen to transit its disk, both computed
-using \starry from an $l=25$ expansion of the map of the Earth.
-The top panel shows an occultation in emitted light and is a reproduction of
-Figure~7 in \citet{Luger2019}. The bottom panel shows a light curve for the
-same occultation geometry, but seen instead in reflected light, with the
-Sun to the top left and slightly out of the page.
-The black curves correspond to the analytical solution, and the orange dots
-to the brute force numerical solution, obtained by discretizing the disk
-on a grid of ${\sim}10^6$ points. The solutions agree to within the
+Figure~\ref{fig:earthphase} shows a sample application of the algorithm
+developed in this paper: a reflected light phase curve of the
+Earth over the course of one year. The model is computed using the
+methodology in Appendix~\ref{sec:solution-no-occ} from an $l=25$
+spherical harmonic expansion of the cloudless Earth, where the oceans
+are given an albedo of zero and the continents an albedo of unity
+(note, however, that since the light curve is normalized, the model does
+not depend on the value of the latter).
+The Earth is assumed to be a perfect Lambertian scatterer,
+so effects like the phase dependence of Rayleigh scattering and
+specular reflection (glint) from the oceans are neglected
+(but see \S\ref{sec:extensions} for an extension of the model to
+non-Lambertian scatterers).
+The observer is assumed to be along
+the ecliptic, so the illumination source is along the $x-z$ plane of a
+right-handed Cartesian coordinate system, with $\hat{z}$ pointing toward the
+observer and $\hat{x}$ pointing to the right on the sky. The axis of rotation
+of the Earth is therefore tilted clockwise away from
+$\hat{y}$ by $23.5^\circ$.
+The images at the top show snapshots of the disk of the Earth throughout
+the observation; below each one, we plot in blue the normalized phase curve
+at that phase over a single rotation. The orange dots correspond to a
+brute force numerical solution, obtained by discretizing the disk
+on a grid of ${\sim}10^6$ points and summing over the dayside.
+The models agree to within the
 numerical precision of the brute force solution (about 100 ppm of the
@@
 
-\begin{figure}[p!]
+While the dominant signal in the phase curve is the sine-like envelope
+due to the changing phases of the Earth, the local behavior of the light
+curve at each phase is complex and varies significantly over the course
+of the year. Unlike phase curves in thermal light, which primarily encode
+low-order spatial information (since the region of integration is always
+the full disk), phase curves in reflected light encode information at
+different scales depending on the phase. At crescent phase, the region of the
+disk contributing to the total flux is a narrow lune; these measurements
+therefore encode information primarily about high-$l$ modes. At full
+phase, the region of integration is the full disk, so these measurements
+encode information about low-$l$ modes. Furthermore, because of the obliquity
+of the Earth,
+the orientation of the crescent lune changes relative to features on the
+surface over the course of one orbit, changing the relative contribution of
+different portions of the surface to the flux and increasing the
+overall information content of the observation.
+As we will show in \S\ref{sec:information}, the information content of
+reflected light phase curves is overwhelmingly higher than that of
+phase curves in thermal light, particularly for planets with significant
+obliquity.
+
+%
+
+\begin{figure}[t!]
     \begin{centering}
@@
 
-Figure~\ref{fig:earthsun} shows
+Figure~\ref{fig:earthmoon} shows another light curve of the rotating
+Earth, but this time taken during an occultation by the Moon. The map
+of the Earth is the same as before, but the observer is now in the
+equatorial frame of the Earth.
+The top panel is a reproduction of
+Figure~7 in \citet{Luger2019} for the case of thermal light,
+where the Moon is seen to travel across the
+disk of the Earth from southwest to northeast, progressively occulting
+South America (dip), the Atlantic (peak), and Africa (dip).
+As before,
+the blue curve is the analytic solution and the orange dots correspond
+to the numerical solution.
+
+The bottom panel of the figure shows a light curve for the
+same occultation geometry, but seen instead in reflected light, with the
+Sun to the top left and slightly out of the page, corresponding to
+some point during northern summer. Note the same dip-peak-dip pattern,
+albeit with significantly different amplitudes. In particular, the
+transit across South America is deeper, since it occurs close to local
+noon, when the illumination is highest; conversely, the transit across
+Africa occurs close to local dusk, when the illumination is close to zero.
+As before, the light curves computed using \starry agree to within the
+numerical precision of the brute force solution.
+
+%
 
@@
         \oscaption{earthsun}{%
-            Mock secondary eclipse light curves of the
-            cloudless Earth expanded to spherical harmonic degree $l = 25$.
+            Mock secondary eclipse ingress light curves of the
+            cloudless Earth expanded to spherical harmonic degree $l = 25$,
+            viewed from an orientation where the Earth is occulted behind
+            a solar latitude of $30^\circ$.
             Black curves show the analytic solution; orange dots correspond
@@
             The bottom panel shows the difference between the
-            normalized reflected and normalized emitted light curves.
+            normalized reflected and emitted light curves.
             \label{fig:earthsun}
@@
 
-% DEBUG
-\pagebreak
+Our last sample light curve is Figure~\ref{fig:earthsun}, which shows
+a secondary eclipse light curve of the Earth as it is occulted by the
+Sun. The model for the Earth is the same as above, and the observer is
+now close to the ecliptic, but slightly misaligned so that the
+Earth is occulted behind a solar latitude of $30^\circ$ (i.e., at
+a solar impact parameter of $0.5$). The observation takes place at the
+June solstice, so the Earth is tilted by $23.5^\circ$ out of the page.
+As before, the top panel shows the light curve in thermal light; this
+is similar to the top panel of Figure~13 in \citet{Luger2019}. The orange
+dots again correspond to the numerical solution.
+%
+The center panel shows the same light curve in reflected light.
+Because the observation occurs very close to full phase, the normalized
+light curves look very similar to each other.
+The bottom panel shows the difference between the two
+(reflected minus thermal), which is only on the order of a few percent.
+%
+In fact, because
+the illumination profile is proportional to the cosine of the viewing
+angle, $\mu$, and the reflection is assumed to be isotropic, the
+(normalized) secondary eclipse light curve in reflected light is to
+good approximation equal
+to a limb-darkened thermal occultation light curve with
+linear limb darkening coefficient $u_1 = 1$. As we will see later, for very
+close-in planets this approximation breaks down, since the illumination
+phases at secondary eclipse ingress and egress are sufficiently different
+from full phase.
+
+%
 
@@
 
-Figure~\ref{fig:speed}
-
-\begin{figure}[ht!]
+As we discuss in the Appendix, the model for phase curves and
+occultation light curves in reflected light may be expressed
+analytically in terms of purely algebraic and trigonometric functions
+and in some cases incomplete elliptic integrals of the first, second,
+and third kinds. We have derived efficient and numerically stable
+recursion relations to compute the relevant expressions and their
+derivatives. At times, these involve the evaluation of certain
+expressions numerically, especially when doing so
+leads to either a speed-up or a significant gain in numerical precision.
+In particular, as we discuss in Appendix~\ref{sec:which-case}, the
+integration boundaries during an occultation sometimes depend on the
+solution to a quartic equation. While this can be solved in closed form,
+the analytic solution can often be very unstable. We therefore solve
+the quartic numerically, attaining a precision for the roots within a
+few orders of magnitude of machine (double) precision.
+
+Figures~\ref{fig:speed_no_occ} and \ref{fig:speed} summarize
+the precision and computation time of the \starry algorithm for
+two typical scenarios: a phase curve evaluation
+(Figure~\ref{fig:speed_no_occ}) and an occultation evaluation
+(Figure~\ref{fig:speed}).
+
+\begin{figure}[p!]
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/speed.pdf}
+        \includegraphics[width=\linewidth]{figures/speed_no_occ.pdf}
         \oscaption{speed}{%
@@
             and numerical precision (point size)
-            for a single flux evaluation as a function of spherical
+            for a single phase curve evaluation as a function of spherical
             harmonic degree for different methods.
-            In orange we show results for the emitted light
+            In purple we show results for the emitted light
             \starry algorithm from \citet{Luger2019} (solid: no gradient,
@@
             light algorithm from this paper (solid: no gradient,
-            dashed: with gradient). For comparison, in purple we show
+            dashed: with gradient). For comparison, in orange we show
             results for discrete integration on a grid (solid) and
@@
             quadrature (dashed); neither of these include gradient
-            evaluations. The reflected light algorithm is around one
-            order of magnitude slower and less precise than the emitted
-            light algorithm, but still ${\sim}4$ orders of magnitude faster
+            evaluations. The reflected light algorithm is
+            comparable in efficiency and precision to the emitted
+            light algorithm. It is ${\sim}5$ orders of magnitude faster
+            and ${\sim}10$ orders of magnitude more precise than numerical
+            integration.
+            \label{fig:speed_no_occ}
+        }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/speed.pdf}
+        \oscaption{speed}{%
+            Same as Figure~\ref{fig:speed_no_occ}, but for an occultation
+            evaluation in which the occultor intersects the terminator
+            (case 6 in Appendix~\ref{sec:solution-occ}).
+            The reflected light algorithm is around one
+            order of magnitude slower and comparably precise to the emitted
+            light algorithm. It is ${\sim}4$ orders of magnitude faster
             and ${\sim}10$ orders of magnitude more precise than numerical
@@
 \end{figure}
+
+\subsection{Implementation and usage}
+\label{sec:usage}
+
+Hello.
+
+% DEBUG
+\clearpage
 
@@
         \oscaption{kelt9b}{%
-            Reflected light phase curve model (left) and
-            secondary eclipse model for Kelt-9b, assuming
+            Reflected light phase curve model for Kelt-9b, assuming
             a spherical albedo $A = 0.2$. The transit (phase zero)
             is not included. Blue is the \starry model
-            assuming a point source illumination; orange accounts for
-            the finite size of the star. The right panel shows
-            the normalized flux during secondary eclipse ingress
-            for the two \starry models and for two approximations:
-            a surface with uniform intensity (solid purple)
-            and a surface whose intensity falls as the cosine of the
+            assuming a point source illumination; purple accounts for
+            the finite size of the star.
+            The left panel shows the two models in parts per million
+            of the stellar flux; the right panel shows the models
+            normalized so their maximum value is unity.
+            The primary effect of the extended source size is to
+            increase the planet flux near full phase, since the stellar
+            surface is on average slightly closer to the planet, and
+            to change the overall curvature of the phase curve.
+            The shape of secondary eclipse, however, is relatively
+            insensitive to the point source approximation
+            (see Figure~\ref{fig:kelt9b_eclipse}).
+            \label{fig:kelt9b}
+        }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/kelt9b_eclipse.pdf}
+        \oscaption{kelt9b}{%
+            Normalized reflected light secondary eclipse model for Kelt-9b,
+            assuming a spherical albedo $A = 0.2$. Blue is the \starry model
+            assuming a point source illumination; purple accounts for
+            the finite size of the star. The orange curves show
+            approximate models computed using the \citet{MandelAgol2002}
+            model: a sphere of uniform intensity (solid orange)
+            and a sphere whose intensity falls as the cosine of the
             viewing angle from the center of the planet disk
-            (dashed purple).
-            \label{fig:kelt9b}
+            (dashed orange).
+            Because Kelt-9b is so close to its host star, the illumination
+            phase changes significantly from ingress to egress, and neither
+            approximation accurately captures the behavior of the light curve.
+            On the other hand, the point source approximation agrees well with
+            the extended source solution, modulo an overall amplitude
+            difference (see Figure~\ref{fig:kelt9b}).
+            \label{fig:kelt9b_eclipse}
         }
@@
 %
+
+\subsection{Information}
+\label{sec:information}
 

### 2020-05-05 tex/figures/earthphase.py

@@ -11,7 +11,7 @@ starry.config.lazy = False
 # Instantiate the Earth in reflected light
 map = starry.Map(25, reflected=True)
 map.load("earth", sigma=0.06)
-map.obl = 23.5
+map.obl = -23.5
 
 # Earth colormap
 cmap = LinearSegmentedColormap(

### 2020-05-05 tex/figures/earthsun.py

@@ -143,7 +143,7 @@ ax.set_xlabel("time [minutes]", fontsize=16)
 ax.set_ylabel("difference", fontsize=16, labelpad=0)
 for tick in ax.get_xticklabels() + ax.get_yticklabels():
     tick.set_fontsize(14)
-ax.set_ylim(-6, 6)
+ax.set_ylim(-6.5, 6.5)
 ax.set_yticks([-5, 0, 5])
 ax.set_yticklabels(["-5%", "0%", "5%"])
 fig.savefig("earthsun_diff.pdf", bbox_inches="tight", dpi=500)

### 2020-05-05 tex/figures/extended.py

@@ -40,7 +40,7 @@ map.show(image=img2, projection="moll", ax=ax[1], norm=norm)
 # Plot contours
 X = np.linspace(-2 * np.sqrt(2), 2 * np.sqrt(2), img2.shape[1])
 Y = np.linspace(-np.sqrt(2), np.sqrt(2), img2.shape[0])
-levels = np.array([0.0, 0.01, 0.05, 0.10, 0.30, 0.50, 0.75]) * 100
+levels = np.array([0, 1, 5, 10, 30, 50, 75])
 for i, axis, img in zip([0, 1], ax, [img1, img2]):
     cont = axis.contour(
         X,
@@ -53,12 +53,13 @@ for i, axis, img in zip([0, 1], ax, [img1, img2]):
         linestyles="dotted",
     )
     if i == 0:
-        x = np.array([-90, -80, -70, -60, -40]) * 2 * np.sqrt(2) / 180.0
+        x = np.array([-90, -70, -60, -40]) * 2 * np.sqrt(2) / 180.0
     else:
         x = np.array([-106, -98, -92, -86, -70, -60, -40]) * 2 * np.sqrt(2) / 180.0
     y = np.zeros(len(x))
     manual = zip(x, y)
-    labels = axis.clabel(cont, inline=1, fontsize=6, fmt=r"%.0f", manual=manual)
+    fmt = {0: "0%", 1: "1", 5: "5", 10: "10", 30: "30", 50: "50", 75: "75%"}
+    labels = axis.clabel(cont, inline=1, fontsize=6, fmt=fmt, manual=manual)
     for l in labels:
         l.set_rotation(0)
 

### 2020-05-05 tex/figures/kelt9b.py

@@ -26,28 +26,30 @@ kwargs = dict(
 )
 
 # Time arrays (secondary eclipse ingress / full phase curve)
-t_ingress = np.linspace(0, 0.0174, 1000)
+t_ingress = np.linspace(0, 0.017, 1000)
+t_egress = 218 / 60 / 24 + t_ingress
+t_sec = np.append(t_ingress, t_egress)
 t_phase = kwargs["t0"] + kwargs["porb"] * np.linspace(-0.5, 0.5, 1000)
 
 # Uniform
 e_map = starry.Map(ydeg=1, reflected=False)
 e = starry.Secondary(e_map, **kwargs)
 sys = starry.System(star, e)
-flux_em = sys.flux(t=t_ingress, total=False)[1]
+flux_em = sys.flux(t=t_sec, total=False)[1]
 
 # Noon approximation
 e_map = starry.Map(udeg=1, reflected=False)
 e_map[1] = 1
 e = starry.Secondary(e_map, **kwargs)
 sys = starry.System(star, e)
-flux_ld = sys.flux(t=t_ingress, total=False)[1]
+flux_ld = sys.flux(t=t_sec, total=False)[1]
 
 # Reflected, point source
 e_map = starry.Map(ydeg=1, reflected=True)
 e_map.amp *= 0.2
 e = starry.Secondary(e_map, **kwargs)
 sys = starry.System(star, e)
-flux_ref = sys.flux(t=t_ingress, total=False)[1]
+flux_ref = sys.flux(t=t_sec, total=False)[1]
 flux_phase = sys.flux(t=t_phase, total=False)[1]
 
 # Reflected, extended source
@@ -55,36 +57,78 @@ e_map = starry.Map(ydeg=1, reflected=True, source_npts=300)
 e_map.amp *= 0.2
 e = starry.Secondary(e_map, **kwargs)
 sys = starry.System(star, e)
-flux_ref_fin = sys.flux(t=t_ingress, total=False)[1]
+flux_ref_fin = sys.flux(t=t_sec, total=False)[1]
 flux_phase_fin = sys.flux(t=t_phase, total=False)[1]
 
 # Plot phase curves
 fig, ax = plt.subplots(1, 2, figsize=(14, 4))
-fig.subplots_adjust(hspace=0.025)
+fig.subplots_adjust(hspace=0.01)
 t = t_phase - kwargs["t0"]
 phase = t / kwargs["porb"]
[…]

### 2020-05-05 tex/figures/speed.py

@@ -113,7 +113,9 @@ class Compare(object):
                 theano_code(_y, _x, _xs, _ys, _zs, _xo, _yo, _ro),
             )
 
-        return self._intensity(np.array([y]), np.array([x]), xs, ys, zs, xo, yo, ro)
+        return self.map_ref.amp * self._intensity(
+            np.array([y]), np.array([x]), xs, ys, zs, xo, yo, ro
+        )
 
     def flux(self, xs, ys, zs, xo, yo, ro, reset=False):
 
@@ -137,7 +139,7 @@ class Compare(object):
                 theano_code(_xs, _ys, _zs, _xo, _yo, _ro),
             )
 
-        flux = self._flux(xs, ys, zs, xo, yo, ro)
+        flux = self.map_ref.amp * self._flux(xs, ys, zs, xo, yo, ro)
         err = np.max(flux) - np.min(flux)
         return np.median(flux), err
 
@@ -166,7 +168,7 @@ class Compare(object):
                 theano_code(_xs, _ys, _zs, _xo, _yo, _ro),
             )
 
-        return self._dfluxdro(xs, ys, zs, xo, yo, ro), np.nan
+        return self.map_ref.amp * self._dfluxdro(xs, ys, zs, xo, yo, ro), np.nan
 
     def flux_emitted(self, xs, ys, zs, xo, yo, ro, reset=False):
 
@@ -189,7 +191,7 @@ class Compare(object):
                 [_xo, _yo, _ro], theano_code(_xo, _yo, _ro),
             )
 
-        flux = self._flux_emitted(xo, yo, ro)
+        flux = self.map_emi.amp * self._flux_emitted(xo, yo, ro)
         err = np.max(flux) - np.min(flux)
         return np.median(flux), err
 
@@ -217,13 +219,13 @@ class Compare(object):
                 [_xo, _yo, _ro], theano_code(_xo, _yo, _ro),
             )
 
-        return self._dfluxdro_emitted(xo, yo, ro), np.nan
+        return self.map_emi.amp * self._dfluxdro_emitted(xo, yo, ro), np.nan
 
     def flux_brute(self, xs, ys, zs, xo, yo, ro, res=999, **kwargs):
         # Compute the flux by brute force grid integration
[…]

### 2020-05-06 tex/ms.tex
more text

@@
             a grid of
-            ${\sim}10^6$ points.
+            ${\sim}10^5$ points.
             \label{fig:earthphase}
@@
 brute force numerical solution, obtained by discretizing the disk
-on a grid of ${\sim}10^6$ points and summing over the dayside.
+on a grid of ${\sim}10^5$ points and summing over the dayside.
 The models agree to within the
@@
             to brute force numerical integration on a grid of
-            ${\sim}10^6$ points.
+            ${\sim}10^5$ points.
             The top panel shows the light curve in emitted light and is
@@
 
-Figures~\ref{fig:speed_no_occ} and \ref{fig:speed} summarize
-the precision and computation time of the \starry algorithm for
-two typical scenarios: a phase curve evaluation
-(Figure~\ref{fig:speed_no_occ}) and an occultation evaluation
-(Figure~\ref{fig:speed}).
-
 \begin{figure}[p!]
@@
             and numerical precision (point size)
-            for a single phase curve evaluation as a function of spherical
+            for a single flux evaluation in the absence of an occultor
+            as a function of spherical
             harmonic degree for different methods.
@@
             light algorithm from this paper (solid: no gradient,
-            dashed: with gradient). For comparison, in orange we show
-            results for discrete integration on a grid (solid) and
+            dashed: with gradient). For comparison, in we also show
+            results for discrete integration on a grid (orange) and for
             numerical integration using two-dimensional Gaussian
-            quadrature (dashed); neither of these include gradient
+            quadrature (red); neither of these include gradient
             evaluations. The reflected light algorithm is
@@
 
+Figures~\ref{fig:speed_no_occ} and \ref{fig:speed} summarize
+the precision and computation time of the \starry algorithm for
+two typical scenarios: a phase curve evaluation
+(Figure~\ref{fig:speed_no_occ}) and an occultation evaluation
+(Figure~\ref{fig:speed}).
+Blue points correspond to the reflected light algorithm developed
+in this paper, while purple points correspond to the thermal light
+algorithm from \citet{Luger2019} for the same occultation geometry,
+but without an illumination source.
+Solid and dashed lines correspond to evaluations without and
+with gradient propagation, respectively (see \S\ref{sec:usage}
+for details).
+The orange and red dots
+correspond to numerical evaluation of the flux:
+brute force integration by summation on a grid of ${\sim}10^6$ points
+(orange) and two-dimensional adaptive Gaussian quadrature using the
+\textsf{dblquad} function in \textsf{scipy} \citep{scipy} with
+both absolute and relative error tolerances set to $10^{-3}$ (red).
+%
+In both figures, the vertical axis corresponds to the evaluation
+time in seconds for a single flux computation, while the size of the
+points is proportional to the base-10 log of the relative error. For the
+\starry solutions, the latter is estimated as the max-min difference
+in the flux over one thousand evaluations in which the input parameters
+are perturbed within an order of magnitude of machine epsilon; this is
+therefore a probe of the condition number of the starry algorithm and
+captures only error due to numerical instabilities. For the numerical
+solutions, the error is estimated as the difference between the numerical
+flux and the \starry flux.
+
+For both phase curves and occultations, the \starry reflected
+light algorithm is 1--2 orders of
+magnitude slower than the emitted light algorithm, owing
+primarily to the increased complexity of the reflected light model.
+For phase curves (Figure~\ref{fig:speed_no_occ}),
+the thermal solution vector $\rTe$ (Equation~\ref{eq:rTA1Ry}) is a constant
+that can be pre-computed, while the analogous vector in the reflected
+light case, $\rT$ (Equation~\ref{eq:rTsoln}), must be evaluated
+recursively each time. For occultations (Figure~\ref{fig:speed}),
+the slower evaluation in the reflected light case is primarily due to
+the time spent solving the quartic equation for the points of intersection
+between the occultor and the day/night terminator of the illuminated
+body (Appendix~\ref{sec:solution-occ}). This contributes the
+same overhead at all map degrees $l$, resulting in a gentler scaling
+in $l$ than for the thermal case; for large $l$, the evaluation time
+for the two algorithms is within a factor of 2--3.
+%
+In terms of precision, the algorithms are comparable, particularly
+for occultations. For both phase curves and occultations, the numerical error up
+to $l=10$ is less than one part per trillion ($10^{-12}$) for both thermal
+and reflected light curves.
+
+Compared to either numerical evaluation method, the \starry reflected light
+solutions are
+\textbf{4--5 orders of magnitude faster} and about
+\textbf{10 orders of magnitude more precise}. While different
+grid sizes and different error settings for the numerical integration change
+the balance slightly between these numbers, the \starry solution is always
+many orders of magnitude faster and more precise than either method.
+In particular, because of the complicated integration boundaries
+(see, for example, Figure~\ref{fig:cases}), two-dimensional Gaussian quadrature
+struggles to reach adequate precision in a reasonable amount of time,
+while integration on a grid fails to capture the curvature of the
+integration boundaries. Moreover, neither method yields the gradient of the
+solution with respect to the input parameters, which can be extremely useful
+for optimization and inference problems (see \S\ref{sec:usage}) below.
+
+Note, importantly, that as we mentioned above, the reported error of the \starry
+solution is only the \emph{numerical} error of the algorithm: it does not
+capture any systematic error due to, say, an error in the derivation of
+the method. To this end, we rely on the Jupyter notebooks containing
+derivations and validations of the main equations in the Appendix, whose
+links \prooficon\, appear next to the equation labels.
+%
+We have also developed an extensive suite of
+\href{https://github.com/rodluger/starry/tree/master/tests}{unit tests}
+comparing the \starry solution to the numerical solution over a large
+grid of input parameter values, and verified that the solutions agree
+to within the precision of the numerical method.
+%
+That said, there are specific cases in which the algorithm presented in the
+Appendix suffers from numerical instabilities. These generally happen due
+to division by small numbers or catastrophic cancellation in the recursion,
+and often occur near configurations involving grazing occultations,
+near-total occultations, terminator semi-minor axis $b \approx 0$ or
+$b \approx 1$, etc. To mitigate these, we introduce various tolerance
+parameters in the code to either nudge the inputs away from these singular
+points or switch to a different evaluation method. These parameters are
+outlined in Table~\ref{tab:tolerance} at the end. In the vicinity of the cases
+described in that table, the precision of the \starry algorithm will be
+reduced to (roughly) the value of the tolerance parameter, which in
+extremely rare cases can be as high as $10^{-5}$.
+
 \subsection{Implementation and usage}
@@
 
-Hello.
+The algorithm presented in this paper has been implemented in the \Python
+package \starry, which can be installed from
+\href{https://github.com/rodluger/starry}{GitHub} or via the Python package
+manager \textsf{pip}. The algorithm is coded in a mixture of \textsf{C++}
+with forward automatic differentation using the \textsf{Eigen} library
+\citep{eigen} and \Python with backward differentiation using
+just-in-time compiled \textsf{theano}
+operations \citep{theano}. The user interface, however, is purely in
+\Python. The \textsf{theano} backend facilitates integration with the
+\textsf{exoplanet} modeling package \citep{exoplanet} and in particular
+with \textsf{pymc3} \citep{pymc3} for inference with gradient-based
+Markov Chain Monte Carlo (MCMC) schemes.
+%
+Complete \href{https://rodluger.github.io/starry}{documentation} and an
+extensive library of tutorials is available online.
+The links next to each
+of the figures \codeicon\, point to the \Python scripts used to generate
+them and may also help in learning how to use \starry.
 
@@
             at $r_s = 1$, computed
-            analytically from a degree \STARRYQUADPOINTS expansion
+            analytically from a degree \STARRYORENNAYARDEG expansion
             of the scattering law. Dots

### 2020-05-06 tex/figures/speed.py

@@ -328,7 +328,7 @@ class Compare(object):
         kwargs = dict(xs=xs, ys=ys, zs=zs, xo=xo, yo=yo, ro=ro)
 
         # Vectorized params (for the starry computation)
-        # We perturb them close to the machine level, and compute
+        # HACK: We perturb them close to the machine level, and compute
         # the "error" as the max-min difference in the flux over
         # the interval. This is essentially a probe of the condition number
         # of the starry algorithm.
@@ -342,7 +342,7 @@ class Compare(object):
             ("starry: emitted", "C4", "-"),
             ("starry: emitted (grad)", "C4", "--"),
             ("grid", "C1", "-"),
-            ("dblquad", "C1", "--"),
+            ("dblquad", "C3", "-"),
         ]
 
         # Loop over all degrees
@@ -368,18 +368,26 @@ class Compare(object):
                 self.flux_quad, epsabs=epsabs, epsrel=epsrel, **kwargs
             )
 
-        # Zero-degree emitted light maps are limb-darkened maps,
+        # HACK: Zero-degree emitted light maps are limb-darkened maps,
         # so let's just set them equal to the l = 1 result for
         # simplicity
         teval[2, 0], value[2, 0], error[2, 0] = teval[2, 1], value[2, 1], error[2, 1]
         teval[3, 0], value[3, 0], error[3, 0] = teval[3, 1], value[3, 1], error[3, 1]
 
-        # Compute the error on the numerical solution
+        # HACK: If there's no occultation, the deriv with respect to the radius
+        # is trivially zero, so the computation time is really tiny. Starry
+        # computes derivatives *whenever* the flux is computed, so we'll
+        # just set the evaluation time to be that of the flux call.
+        if ro == 0:
+            teval[1] = teval[0]
+            teval[3] = teval[2]
+
+        # HACK: Compute the error on the numerical solution
         # assuming the starry solution is the ground truth
         error[4] = np.abs(value[4] - value[0])
         error[5] = np.abs(value[5] - value[0])
 
-        # Propagate the error to the starry-grad terms
+        # HACK: Propagate the error to the starry-grad terms
         # (identical by construction)
         error[1] = error[0]
         error[3] = error[2]

### 2020-05-06 tex/ms.tex
more text

@@
     \label{eq:LambertsLaw}
-    \mathcal{I}(\phi) = \mathcal{I}_0 \, \text{max}\big( 0, \cos\phi \big)
-    \quad,
-\end{align}
-%
-where $\mathcal{I}_0$ is the peak illumination (at the sub-source point).
+    \mathcal{I}(\vartheta_i) = \mathcal{I}_0 \, \text{max}\big( 0, \cos\vartheta_i \big)
+    \quad,
+\end{align}
+%
+where $\mathcal{I}_0$ is the peak illumination (at the sub-source point)
+and $\vartheta_i$ is the angle between the incident radiation and the surface
+normal.
 %
@@
 the illumination profile is proportional to the cosine of the viewing
-angle, $\mu$, and the reflection is assumed to be isotropic, the
+angle, $\upmu$, and the reflection is assumed to be isotropic, the
 (normalized) secondary eclipse light curve in reflected light is to
@@
 
-% DEBUG
-\clearpage
-
 \section{Extensions}
@@
 
+The algorithm discussed above and derived in the Appendix computes light
+curves in the limit that (1) the body is illuminated by a point source
+and (2) the body is an ideal Lambertian scatterer. Both of these
+assumptions can be relaxed within \starry, and below we discuss modifications
+to the code to allow for this.
+
 \subsection{Extended illumination source}
 \label{sec:extended}
-Planets to consider: 55 Cnc e, Kelt-9b.
-Assuming $R_\star > R_p$, the angular extent of the terminator
-past $\nicefrac{\pi}{2}$ is
+
+In the limit that the angular size of the star as seen from the planet is
+small, the illumination profile on the surface of the planet will
+decrease as the cosine of the angle between the surface normal and the star,
+reaching zero at the day/night terminator, an angle $\nicefrac{\pi}{2}$
+away from the sub-stellar point. However, if the star is sufficiently large
+and the planet is sufficiently close-in, rays originating from near the limb
+of the star will reach points on the planet surface beyond this angle.
+It is straightforward to show that, provided the stellar radius $R_\star$
+is larger than the planet radius $R_p$, the angular extent of the true
+day/night terminator past $\nicefrac{\pi}{2}$ is given by
 %
@@
     \label{eq:tau}
-    \tau &= \arcsin\left( \frac{R_\star - R_p}{d} \right)
-\end{proof}
-%
-where $R_\star$ is the radius of the star,
-$R_p$ is the radius of the planet, and $d$ is the separation of their
-centers.
-
-For Kelt-9b, $\nicefrac{R_p}{R_\star} = 0.083$ and
-$\nicefrac{a}{R_\star} = 3.16$, where $a$ is the semi-major axis of the
+    \tau &= \arcsin\left( \frac{1 - \nicefrac{R_p}{R_\star}}{\nicefrac{a}{R_\star}} \right)
+\end{proof}
+%
+where $a$ the semi-major axis of the orbit (where we implictly assume
+the eccentricity is zero).
+For planets like the Earth, this quantity is only about $0.26^\circ$,
+resulting in a negligible effect on the planet's light curve. However,
+for very close-in planets, the effect can be significant. For instance,
+the hot Jupiter Kelt-9b has $\nicefrac{R_p}{R_\star} = 0.083$ and
+$\nicefrac{a}{R_\star} = 3.16$
 planet \citep{Wong2019}. Asssuming zero eccentricity and ignoring any
 stellar oblateness
-\citep[see][]{Ahlers2020}, we find that
+\citep[see][]{Ahlers2020},
 the day/night terminator extends $\tau \approx 17^\circ$ past the limb
-of the planet. Figure~\ref{fig:extended} shows...
-
-\begin{figure}[ht!]
+of that planet. Figure~\ref{fig:extended} shows the illumination profile
+of this planet in a Mollweide projection, with the sub-stellar point at
+the center, for the point source approximation (left) and accounting for
+the finite size of the star (right). In addition to the
+displaced day/night terminator, the main difference between
+the two profiles is the sub-stellar intensity, which is significantly higher
+in the extended source case. This is due to the simple fact that in the point
+source case the illumination source is placed at the center of the star,
+which is one stellar radius farther from the planet than the point closest
+to the planet (the sub-planetary point) in the extended source case.
+Once accounting for this difference, the fractional change in the intensity
+on the planet away from the sub-stellar point is similar in both cases,
+and the intensity anywhere beyond $\nicefrac{\pi}{2}$ is less than one-tenth
+the peak value.
+
+\begin{figure}[t!]
     \begin{centering}
@@
 
-Figure~\ref{fig:kelt9b} shows...
+The illumination profile in the extended source case may be computed as the
+two-dimensional integral of the point source illumination profile over
+the visible portion of the stellar disk. While this integral may in theory be
+computed analytically, the resulting profile on the planet surface
+will not in general be exactly expressible in terms of spherical harmonics, a
+necessary condition for the \starry algorithm.
+For simplicity, we therefore compute the illumination profile for
+extended sources by averaging the contribution of \textsf{source\_npts} point
+sources uniformly distributed across the projected disk corresponding to
+the portion of the stellar surface
+visible from the planet, where \textsf{source\_npts} is a user-supplied
+value. In the limit $R_p \ll R_\star$, this is a spherical cap centered at
+the sub-planet point with radius $R_\star \cos\tau$. In
+Figure~\ref{fig:extended} we set
+\textsf{source\_npts} = 300, but in practice we find that ${\sim}30$
+points are sufficient for even the most extreme cases such as Kelt-9b.
+%
+Note, importantly, that while this method allows one to account for the
+effect of stellar limb darkening on the illumination profile of the planet,
+this has not been implemented in \starry.
 
@@
 
+Figure~\ref{fig:kelt9b} shows the practical implications of the finite
+stellar size for the phase curve of Kelt-9b. The left panel shows the
+reflected light phase curve of the planet in parts per million, assuming
+a spherical albedo of 0.2, for the point source approximation
+(blue) and including the effect of the extended source with
+\textsf{source\_npts} = 300 (purple). The increased
+illumination at the sub-stellar point results in a ${\sim}30$ increase
+in the value of the phase curve close to full phase ($\pm\nicefrac{1}{2}$).
+Close to a phase of zero, the extended source results in decreased
+flux, since the portion of the star illuminating the planet (the region
+close to the limb) is slightly
+\emph{farther} away, by a factor of
+$\sqrt{1 + (\nicefrac{a}{R_\star})^{-2}}$. This results in a steeper
+phase curve, which can be seen in the right panel, where the light curves
+have been normalized to their maximum value.
+
 \begin{figure}[p!]
@@
             On the other hand, the point source approximation agrees well with
-            the extended source solution, modulo an overall amplitude
-            difference (see Figure~\ref{fig:kelt9b}).
+            the extended source solution, modulo the difference in
+            the depth (see Figure~\ref{fig:kelt9b}).
             \label{fig:kelt9b_eclipse}
@@
 
+While modeling the extended size of the star is essential to
+getting the shape of the phase curve correct, the same is not true
+for secondary eclipse. Figure~\ref{fig:kelt9b_eclipse} shows
+the normalized secondary eclipse model for Kelt-9b under the point
+source approximation (blue) and the extended source model (purple).
+Neglecting the fact that the \emph{depth} of secondary eclipse is
+significantly different between the two models (see the left panel
+of Figure~\ref{fig:kelt9b}), the difference in \emph{shape} between
+the two curves is almost negligible.
+%
+For reference, the figure shows
+two additional models one might consider using to fit a secondary
+eclipse light curve: a uniform (unilluminated) disk (solid orange)
+and a disk whose intensity falls as $\upmu$, the cosine of the
+viewing angle (dashed orange). Both can be computed using the
+classical \citet{MandelAgol2002} transit model; the latter corresponds
+to a linearly limb-darkened sphere and is functionally equivalent to
+a Lambertian sphere seen at full phase.
+However, neither approximation is particularly good, since Kelt-9b
+changes illumination phase significantly from ingress to egress
+owing to its proximity to the star.
+
 \subsection{Non-Lambertian scatterers}
 \label{sec:nonlambertian}
-Just change $\mathbf{I}$. \citep{OrenNayar1994}.
+
+The second assumption we now seek to relax is that of Lambertian
+scattering. A perfect Lambert sphere reflects light isotropically, so
+the measured intensity at a point on the surface is strictly
+proportional to the product of the cosine of the angle of incidence
+and the cosine of the viewing angle. While this is convenient
+from a modeling standpoint, it is hardly ever true in practice.
+For planets and moons in particular, there is often a strong phase
+dependence in the scattering. Rayleigh scattering in planetary
+atmospheres is preferentially in the forward/backward direction,
+while clouds and oceans can contribute strong specular reflection.
+Moreover, rough surfaces can have complex scattering behavior due
+to changes in the orientation of the surface normal on small scales
+and effects such as multiple reflections and self-shading.
+
+In principle, any of these processes can be accounted for in
+the \starry algorithm by modiying the illumination matrix
+$\mathbf{I}$ (Equation~\ref{eq:Imat}).
+\xxx{TODO} \citep{OrenNayar1994}.
 
@@
 
-\section{Applications}
-\label{sec:applications}
-
 \begin{figure}[p!]
@@
 
-\subsection{Information}
+\section{Discussion}
+\label{sec:discussion}
+
+\subsection{Information theory}
 \label{sec:information}
+
+\xxx{TODO.}
+
+\section{Conclusions}
+\label{sec:conclusionss}
+
+\xxx{TODO.}
 
@@
 is unity. In this case, the observed intensity at any
-point on the surface is proportional to the cosine of the angle $\phi$ between
+point on the surface is proportional to the cosine of the angle $\vartheta_i$ between
 the incident light and the surface normal. Points for which
-$\phi \ge \nicefrac{\pi}{2}$ are unilluminated and
+$\vartheta_i \ge \nicefrac{\pi}{2}$ are unilluminated and
 therefore have an intensity of zero.

### 2020-05-06 tex/figures/kelt9b.py

@@ -92,21 +92,27 @@ ax = [fig.add_axes([0, 0, 0.5 - eps, 1]), fig.add_axes([0.5 + eps, 0, 0.5 - eps,
 t = t_sec * 60 * 24
 idx = t <= t_ingress[-1] * 60 * 24
 tmid = 0.5 * t_egress[-1] * 60 * 24
-ax[0].plot(t[idx] - tmid, flux_ref[idx] / flux_ref[0], "C0-", label="point source")
+ax[0].plot(t[idx] - tmid, flux_ref[idx] / np.max(flux_ref), "C0-", label="point source")
 ax[0].plot(
-    t[idx] - tmid, flux_ref_fin[idx] / flux_ref_fin[0], "C4-", label="extended source"
+    t[idx] - tmid,
+    flux_ref_fin[idx] / np.max(flux_ref_fin),
+    "C4-",
+    label="extended source",
 )
-ax[0].plot(t[idx] - tmid, flux_em[idx] / flux_em[0], "C1-", label="uniform")
-ax[0].plot(t[idx] - tmid, flux_ld[idx] / flux_ld[0], "C1--", label="cosine")
+ax[0].plot(t[idx] - tmid, flux_em[idx] / np.max(flux_em), "C1-", label="uniform")
+ax[0].plot(t[idx] - tmid, flux_ld[idx] / np.max(flux_ld), "C1--", label="cosine")
 
 # Plot egress
 idx = t >= t_egress[0] * 60 * 24
-ax[1].plot(t[idx] - tmid, flux_ref[idx] / flux_ref[0], "C0-", label="point source")
+ax[1].plot(t[idx] - tmid, flux_ref[idx] / np.max(flux_ref), "C0-", label="point source")
 ax[1].plot(
-    t[idx] - tmid, flux_ref_fin[idx] / flux_ref_fin[0], "C4-", label="extended source"
+    t[idx] - tmid,
+    flux_ref_fin[idx] / np.max(flux_ref_fin),
+    "C4-",
+    label="extended source",
 )
-ax[1].plot(t[idx] - tmid, flux_em[idx] / flux_em[0], "C1-", label="uniform")
-ax[1].plot(t[idx] - tmid, flux_ld[idx] / flux_ld[0], "C1--", label="cosine")
+ax[1].plot(t[idx] - tmid, flux_em[idx] / np.max(flux_em), "C1-", label="uniform")
[…]

### 2020-05-07 tex/ms.tex
added scattering section

@@
 %
-The flux measured from this body is the surface integral over the visible
+The flux measured from this body is proportional to the surface integral
+over the visible
 portion of the body's projected disk of the albedo $A$
@@
 
+\begin{figure}[t!]
+    \begin{centering}
+        \includegraphics[width=0.5\linewidth]{figures/scattering.pdf}
+        \oscaption{scattering}{%
+            Scattering geometry for non-Lambertian reflection. Based on
+            Figure~3 of \citet{OrenNayar1994}. The incident radiation
+            is labeled $\mathbf{s}$ and the outgoing radiation is
+            labeled $\mathbf{v}$. The shaded region is a small patch
+            of surface, oriented so that the normal vector points along
+            $\hat{z}$. The four angles relevant to the computation of
+            the emergent intensity are also indicated.
+            \label{fig:scattering}
+        }
+    \end{centering}
+\end{figure}
+
 In principle, any of these processes can be accounted for in
-the \starry algorithm by modiying the illumination matrix
-$\mathbf{I}$ (Equation~\ref{eq:Imat}).
-\xxx{TODO} \citep{OrenNayar1994}.
+the \starry algorithm by modifying the linear operator
+$\mathbf{I}$ (Equation~\ref{eq:Imat}), which in the Lambertian
+case simply weights the spherical harmonic expansion of the albedo
+by the cosine-like illumination profile to obtain the observed
+intensity at a point on the surface
+(see Equations~\ref{eq:sTA2IA1RRy} and \ref{eq:rTIA1RRy}).
+For non-Lambertian scattering, this matrix must also account for
+the phase dependence of the reflection: in particular, it will depend
+not only on the angle between the surface normal and the incident
+radiation, $\vartheta_i$, but also on the angle between the surface
+normal and the reflected radiation (i.e., the direction toward the
+observer), $\vartheta_r$. It may also depend on the azimuthal angles
+of the incident and reflected rays, $\phi_i$ and $\phi_r$, respectively.
+These four angles are shown in Figure~\ref{fig:scattering}, showing
+the incoming radiation (source) vector $\mathbf{s}$ and the outgoing
+radiation (viewer) vector $\mathbf{v}$ in a frame in which the $z$-axis
+points along the surface normal.
+
+Treatment of a generalized, flexible scattering model is beyond the scope
+of this paper. However, as an example of how a scattering model may be
+incorporated
+into the \starry algorithm, we consider in detail the case of the rough surface
+scattering model of \citet{OrenNayar1994}, commonly used in computer
+graphics applications and solar system body modeling
+\citep[e.g.,][]{Morgado2019}. In this model, the surface is treated as a
+collection of a large number of Lambertian facets oriented at random
+angles relative to the average surface normal, whose net contribution to
+the total intensity can depart significantly from the Lambertian case.
+While the general model accounts for interreflections, shadowing, and
+an arbitrary distribution of facet orientations, in its simplest form
+the intensity observed at a point $(x, y)$ on the (projected) surface of a
+body of unit radius and unit spherical albedo may be approximated as
+%
+\begin{align}
+    \mathcal{I} & = \frac{1}{\pi r_s^2}
+    \text{max}\Big(0 \, ,
+    \cos \vartheta_i\Big)
+    \bigg\{ c_0 + c_1 \, \text{max}\Big( 0, \, \cos(\phi_r - \phi_i) \Big)
+    \sin \alpha \tan \beta
+    \bigg\}
+\end{align}
+%
+where%
+%
+\\
+\begin{minipage}{.5\linewidth}
+    \begin{align}
+        c_0 & = 1 - 0.5 \left(\frac{\sigma^2}{\sigma^2 + 0.33}\right)
+        \nonumber                                                     \\
+        c_1 & = 0.45 \left(\frac{\sigma^2}{\sigma^2 + 0.09}\right)
+        \nonumber
+    \end{align}
+\end{minipage}%
+\begin{minipage}{.49\linewidth}
+    \begin{align}
+        \alpha & = \text{max}\Big( \vartheta_r, \, \vartheta_i \Big)
+        \nonumber                                                    \\
+        \beta  & = \text{min}\Big( \vartheta_r, \, \vartheta_i \Big)
+    \end{align}
+\end{minipage}
+\\[1em]
+%
+and $r_s$ is the distance to the illumination source, whose flux measured by
+the observer is unity.
+The expression above is based on Equation~(30) in \citet{OrenNayar1994}. At
+a given point on the surface, this intensity is a function of a single
+parameter, $\sigma$, defined as the standard deviation in radians of the
+distribution of facet angles (which is assumed to be a zero-mean Gaussian).
+The angles $\vartheta_i$, $\vartheta_r$, $\phi_i$, $\phi_r$ are all
+implicit functions of $x$, $y$, and the source position.
+\xxx{TODO.}
 
@@
 
+\vfill
 \pagebreak
@@
     \label{eq:illum_poly}
-    I(b, \theta, r_s; x, y) &= \frac{1}{\pi r_s^2}
+    I(b, \theta, r_s; x, y) &=
+    \frac{1}{\pi r_s^2}
+    \cos \vartheta_i
+    \nonumber \\
+    &= \frac{1}{\pi r_s^2}
     \bigg(

### 2020-05-07 tex/figures/scattering.py

@@ -1,0 +1,156 @@
+import numpy as np
+from matplotlib import pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+from matplotlib.patches import FancyArrowPatch
+from mpl_toolkits.mplot3d import proj3d
+
+
+plt.switch_backend("MacOSX")
+
+
+class Arrow3D(FancyArrowPatch):
+    """
+    From https://stackoverflow.com/a/22867877.
+    """
+
+    def __init__(self, xs, ys, zs, *args, **kwargs):
+        FancyArrowPatch.__init__(self, (0, 0), (0, 0), *args, **kwargs)
+        self._verts3d = xs, ys, zs
+        self.shrinkA = 0
+        self.shrinkB = 0
+
+    def draw(self, renderer):
+        xs3d, ys3d, zs3d = self._verts3d
+        xs, ys, zs = proj3d.proj_transform(xs3d, ys3d, zs3d, renderer.M)
+        self.set_positions((xs[0], ys[0]), (xs[1], ys[1]))
+        FancyArrowPatch.draw(self, renderer)
+
+
+def add_arrow(ax, u, v, label=None, offset=0.1, **kwargs):
+    kwargs["mutation_scale"] = kwargs.get("mutation_scale", 10)
+    kwargs["lw"] = kwargs.get("lw", 1)
+    kwargs["arrowstyle"] = kwargs.get("arrowstyle", "-|>")
+    kwargs["color"] = kwargs.get("color", "k")
+    a = Arrow3D([u[0], v[0]], [u[1], v[1]], [u[2], v[2]], **kwargs)
+    ax.add_artist(a)
+
+    if label is not None:
+        ax.text(
+            v[0] * (1 + offset),
+            v[1] * (1 + offset),
+            v[2] * (1 + offset),
+            label,
+            transform=ax.transData,
+            fontsize=10,
+            va="center",
+            ha="center",
+            clip_on=False,
+        )
+
+    return a
+
+
+def add_projection(ax, u, v, **kwargs):
+    kwargs["lw"] = kwargs.get("lw", 0.75)
+    kwargs["ls"] = kwargs.get("ls", "--")
[…]

### 2020-05-08 tex/ms.tex
more text, bugfix

@@
 The flux measured from this body is proportional to the surface integral
-over the visible
-portion of the body's projected disk of the albedo $A$
-times the illumination profile $\mathcal{I}$ of the surface, given by
-Lambert's law as
+over the projected disk
+of the albedo $A$ times the illumination profile $\mathcal{I}$ of the surface,
+given by Lambert's law as
 %
@@
 %
-where $\mathcal{I}_0$ is the peak illumination (at the sub-source point)
-and $\vartheta_i$ is the angle between the incident radiation and the surface
-normal.
-%
+where $\vartheta_i$ is the angle between the incident radiation and the surface
+normal and $\mathcal{I}_0$ is the peak illumination. We show in
+Appendix~\ref{sec:adapting-starry} that in the case of, say, a planet
+illuminated by its host star,
+%
+\begin{align}
+    \mathcal{I}_0 = \frac{f_s}{\pi r_s^2}
+\end{align}
+%
+where $r_s$ is the distance between the planet and the star (in units
+of the planet's radius) and $f_s$ is the stellar flux measured at the observer
+(in arbitrary units). Following the convention in \citet{Luger2019}, we assume
+throughout this paper that $f_s = 1$, so all fluxes are defined as a fraction of
+the flux of the illumination source.
 
@@
 the intensity observed at a point $(x, y)$ on the (projected) surface of a
-body of unit radius and unit spherical albedo may be approximated as
-%
-\begin{align}
-    \mathcal{I} & = \frac{1}{\pi r_s^2}
-    \text{max}\Big(0 \, ,
-    \cos \vartheta_i\Big)
+body of unit spherical albedo may be approximated as
+\citep[c.f. Equation~30 in][]{OrenNayar1994}
+%
+\begin{proof}{OrenNayar}
+    \label{eq:OrenNayar}
+    \mathcal{I} & =
+    \mathcal{I}_\text{Lamb}
     \bigg\{ c_0 + c_1 \, \text{max}\Big( 0, \, \cos(\phi_r - \phi_i) \Big)
@@
     \bigg\}
-\end{align}
+\end{proof}
 %
@@
 \begin{minipage}{.49\linewidth}
-    \begin{align}
+    \begin{proof}{OrenNayar}
         \alpha & = \text{max}\Big( \vartheta_r, \, \vartheta_i \Big)
@@
         \beta  & = \text{min}\Big( \vartheta_r, \, \vartheta_i \Big)
-    \end{align}
+    \end{proof}
 \end{minipage}
 \\[1em]
-%
-and $r_s$ is the distance to the illumination source, whose flux measured by
-the observer is unity.
-The expression above is based on Equation~(30) in \citet{OrenNayar1994}. At
-a given point on the surface, this intensity is a function of a single
+and the angles $\vartheta_i$, $\vartheta_r$, $\phi_i$, and $\phi_r$ are all
+implicit functions of $x$, $y$, and the illumination source position.
+The term $\mathcal{I}_\text{Lamb}$ is the Lambertian illumination profile,
+given by Equation~(\ref{eq:LambertsLaw}).
+%
+At a given point on the surface, and for a given source position,
+the intensity $\mathcal{I}$ is therefore a function of a single
 parameter, $\sigma$, defined as the standard deviation in radians of the
 distribution of facet angles (which is assumed to be a zero-mean Gaussian).
-The angles $\vartheta_i$, $\vartheta_r$, $\phi_i$, $\phi_r$ are all
-implicit functions of $x$, $y$, and the source position.
-\xxx{TODO.}
-
-\begin{figure}[p!]
+
+\begin{figure}[t!]
     \begin{centering}
@@
             panel shows the corresponding phase curves for a sphere
-            of unit spherical albedo illuminated by a point source
-            at $r_s = 1$, computed
+            of unit spherical albedo illuminated by a point source, computed
             analytically from a degree \STARRYORENNAYARDEG expansion
@@
 \end{figure}
-%
-
-\begin{figure}[p!]
+
+In order to incorporate this scattering model into \starry, we must weight
+the spherical harmonic expansion of the albedo, $\mathbf{y}$, by
+Equation~(\ref{eq:OrenNayar}) instead of Equation~(\ref{eq:LambertsLaw}).
+Weighting by Equation~(\ref{eq:LambertsLaw}) is (relatively) straightforward,
+since $\mathcal{I}_\text{Lamb}$ is a piecewise function of the $l=1$ spherical
+harmonics (see Appendix~\ref{sec:adapting-starry}).
+The function we must integrate when computing fluxes is therefore
+exactly expressible in terms of spherical harmonics and thus
+\starry-integrable. However, Equation~(\ref{eq:OrenNayar}) cannot be expressed
+exactly in terms of spherical harmonics, so we must instead approximate it.
+To this end, we evaluate Equation~(\ref{eq:OrenNayar}) on a
+grid of $x$ and $y$ spanning the unit disk, as well as the illumination phase,
+parametrized by $b$, the semi-minor axis of the elliptical segment defining
+the day/night terminator (see Appendix~\ref{sec:adapting-starry}).
+We then fit to this a polynomial of total degree \STARRYORENNAYARDEG
+in $x$, $y$, and $z \equiv \sqrt{1 - x^2 - y^2}$ and degree
+\STARRYORENNAYARNB in $b$ and degree \STARRYORENNAYARNBC in
+$b_c \equiv \sqrt{1 - b^2}$.
+%
+Then, for a given value of $b$ and $b_c$, we construct the operator
+$\mathbf{I}$ out of the polynomial coefficients in the same way as we
+constructed the Lambertian operator in Appendix~\ref{sec:adapting-starry}.
+%
+More details about our approximation can be found in the Jupyter notebook
+accompanying Equation~(\ref{eq:OrenNayar}).
+
+Figure~\ref{fig:oren_nayar} shows spheres of unit albedo
+with different surface roughness
+coefficients $\sigma$ and their corresponding phase curves.
+The sphere in the top row is perfectly Lambertian; its phase curve (blue)
+peaks at a value of $\nicefrac{2}{3}$, equal to the geometric albedo
+of a Lambert sphere. Increasing the surface roughness results in a greater
+relative contribution of flux from the limb of the object near full
+phase, since there now exist facets reflecting light directly back toward the
+observer (remaining rows and curves in the phase curve plot).
+Conversely, less light is scattered
+back to the observer at the
+sub-illumination point. These competing effects lead to phase curves that
+peak at a super-Lambertian value for small roughness
+coefficients ($\sigma = 15^\circ$, orange) and at a sub-Lambertian value for
+large roughness coefficients ($\sigma = 45^\circ$, red).
+%
+We validate our calculations by computing the phase curves by numerically
+integrating the \citet{OrenNayar1994} model over the visible disk; these
+are shown as the small dots in the figure, which agree to within
+$350$ ppm of the body's flux for $\sigma = 45^\circ$.
+
+\begin{figure}[t!]
     \begin{centering}
@@
             Galileio global color mosaic of Io \citep{Becker2005},
-            an $l=\STARRYQUADPOINTS$ expansion of the
+            an $l=\STARRYORENNAYARDEG$ expansion of the
             \citet{OrenNayar1994} scattering law, and orbital
@@
 \end{figure}
-%
+
+Our implementation of the scattering model extends just as easily
+to occultations and to cases where the surface does not have uniform albedo.
+Figure~\ref{fig:io_europa} shows a visible-light observation of the
+occultation of Io by Europa on 04 Dec 2009 taken by the PHEMU09
+campaign \citep{Arlot2014}. The trajectory of Europa relative to Io,
+computed from the JPL Horizons databse \xxx{(cite)}
+is shown at the top. We fit to this data a \starry occultation model
+with the scattering law discussed above.
+For simplicity, we set the surface map equal too
+an $l=15$ spherical harmonic expansion of the Galileo global color mosaic
+of Io \citep{Becker2005} and use ephemerides from the JPL Horizons
+database, allowing for a small static $x-y$ offset between Europa and Io as
+in \citep{Arlot2014} due to the uncertainty in the database. In total,
+we fit for five parameters: the two Cartesian offset terms,
+the flux contribution from Europa, the average
+albedo of Io, and the average surface roughness of Io, $\sigma$. The model
+is displayed in blue and closely matches the data.
+%
+Note, however, that this is meant simply as a demonstration of the \starry
+algorithm, as our model for the surface is approximate at best, given
+differences in the wavelength band between the Galileo observations and
+those of the PHEMU09 campaign, changes in the albedo of Io since the Galileo
+measurements, and the fact that the orientation and extent of any shadows
+due to volcanoes on the surface are likely different between the Galileo
+and PHEMU09 observations. Furthermore,
+proper modeling would entail the
+joint analysis of all light curves of Io taken in a given season, for which
+we can afford to simultaneously fit for the surface map without risk of
+overfitting (Bartoli\'c, Luger, et al., in prep).
 
@@
 
-\xxx{TODO.}
+\xxx{A few notes here on how constraining reflected light curves can be.}
+
+\subsection{Limitations}
+\label{sec:limitations}
+
+\xxx{Limitations of the model: can't capture shadowing. Unstable above degree 20 or so.}
 
 \section{Conclusions}
-\label{sec:conclusionss}
+\label{sec:conclusions}
 
@@
 Integrating this over the full disk, we obtain the reflected flux measured
-by the observer if the body has unit spherical albedo,
+by the observer (as a fraction of the flux of the illumination source)
+if the body has unit spherical albedo,
 %

### 2020-05-08 tex/figures/oren_nayar.py

@@ -10,8 +10,8 @@ map = starry.Map(reflected=True)
 # Settings
 res = 300
 theta_im = np.linspace(0, 360, 9)[1:-1] * np.pi / 180
-theta_lr = np.linspace(0, 360, 100) * np.pi / 180
 theta_hr = np.linspace(0, 360, 1000) * np.pi / 180
+theta_lr = theta_hr[5::10]
 rs = [0, 15, 30, 45]
 
 # Set up the figure
@@ -79,10 +79,9 @@ for i, roughness in enumerate(rs):
         ax_im[i, j].axis("off")
 
     # Plot the analytic light curve
+    flux = map.flux(xs=np.sin(theta_hr), ys=0, zs=-np.cos(theta_hr))
     ax_lc.plot(
-        theta_hr / (2 * np.pi),
-        map.flux(xs=np.sin(theta_hr), ys=0, zs=-np.cos(theta_hr)),
-        color="C{}".format(i),
+        theta_hr / (2 * np.pi), flux, color="C{}".format(i),
     )
 
     # Render the exact Oren-Nayar image and compute
@@ -90,13 +89,14 @@ for i, roughness in enumerate(rs):
     img = map.render(
         xs=np.sin(theta_lr), ys=0, zs=-np.cos(theta_lr), res=res, on94_exact=True,
     )
+    flux_num = np.nansum(img, axis=(1, 2)) * 4 / res ** 2
     ax_lc.plot(
-        theta_lr / (2 * np.pi),
-        np.nansum(img, axis=(1, 2)) * 4 / res ** 2,
-        "o",
-        ms=2,
-        color="C{}".format(i),
+        theta_lr / (2 * np.pi), flux_num, "o", ms=2, color="C{}".format(i),
     )
+
+    # Print the difference
+    diff = flux[5::10] - flux_num
+    print("std = {:.0f} ppm".format(np.std(diff) * 1e6))
 
 ax_lc.set_xlabel("illumination phase", fontsize=18)
 ax_lc.set_ylabel("observed intensity", fontsize=18)

### 2020-05-08 tex/figures/scattering.py

@@ -5,9 +5,6 @@ from matplotlib.patches import FancyArrowPatch
 from mpl_toolkits.mplot3d import proj3d
 
 
-plt.switch_backend("MacOSX")
-
-
 class Arrow3D(FancyArrowPatch):
     """
     From https://stackoverflow.com/a/22867877.

### 2020-05-08 tex/ms.tex
added figure

@@
 % Title
-\title{Analytic Occultation Light Curves in Reflected Light}
+\title{%
+    Analytic Light Curves in Reflected Light:%
+    \\%
+    Phase Curves, Occultations, and Non-Lambertian Scattering
+}
 
@@
 Our goal in this paper is to derive analytic expressions for the
-flux received by a distant observer from a non-uniform Lambert sphere
+flux received by a distant observer from a sphere of non-uniform albedo
 illuminated by a monochromatic source that may or may not be
 occulted by a (possibly different) spherical body. This applies, for example,
-to the
-case of exoplanet phase curves, exoplanet secondary
-eclipse (occultation) light curves, or exoplanet-moon and exoplanet-exoplanet
-occultations, all seen in reflected light. We explicitly assume the reflecting
-body is Lambertian, i.e., it scatters light isotropically, although with an
-intensity that varies across the surface according to a spatially-dependent
+to the case of planetary phase curves, secondary
+eclipse (occultation) light curves, and moon-moon, planet-moon, and
+planet-planet occultations (in the Solar System or not),
+all seen in reflected light. We derive all expressions in
+the limit that the reflecting
+body is Lambertian, i.e., it scatters light isotropically, but we relax
+this assumption in later sections.
+We model the general case of an
+intensity that varies across the surface of the body according to a
+spatially-dependent
 albedo $A$. Throughout this paper, we will take $A$ to mean the \emph{spherical}
@@
 throughout this paper that $f_s = 1$, so all fluxes are defined as a fraction of
-the flux of the illumination source.
+the flux of the illumination source at the observer.
 
@@
 
+\begin{figure}[t!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/inference.pdf}
+        \oscaption{inference}{%
+            Example of an inference problem for a thermal phase curve
+            (center left) and a reflected phase curve (center right).
+            In both cases,
+            a mock phase curve is generated from an $l=20$ expansion
+            of the cloudless Earth (top) with 1,000 evenly spaced points
+            over the course of one year and an extremely small
+            photometric uncertainty of 1 ppm. The observer sits along the
+            ecliptic and the obliquity of the Earth is set to $23.5^\circ$.
+            Data is shown as the black points, and the maximum likelihood
+            \starry model is shown in blue. While both models fit the
+            data equally well, the same is not true of the inferred
+            surface maps (bottom row): only in the reflected case are the
+            continental outlines recovered.
+            The thermal phase curve problem is
+            extremely ill-conditioned, but the analogous problem in reflected
+            light is much better posed.
+            \label{fig:inference}
+        }
+    \end{centering}
+\end{figure}
+
 \subsection{Limitations}

### 2020-05-08 tex/figures/inference.py

@@ -1,0 +1,82 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import starry
+
+# Config
+starry.config.lazy = False
+np.random.seed(0)
+
+# Setup figure
+fig, ax = plt.subplots(3, 2, figsize=(13, 7))
+fig.subplots_adjust(hspace=0.4)
+ax[0, 0].set_visible(False)
+ax[0, 1].set_visible(False)
+ax[1, 0].set_ylabel("flux", fontsize=10)
+ax[1, 0].set_title("thermal", fontsize=12, fontweight="bold")
+ax[1, 1].set_title("reflected", fontsize=12, fontweight="bold")
+
+for axis in ax[1, :]:
+    axis.tick_params(labelsize=8)
+    axis.set_ylim(-0.05, 1.05)
+
+# Show the true map
+ax_top = fig.add_subplot(3, 1, 1)
+map = starry.Map(20)
+map.load("earth", sigma=0.1)
+map.show(ax=ax_top, projection="moll")
+
+# Solve the least-squares problem for thermal & reflected phase curves
+for i, reflected in enumerate([False, True]):
+
+    # Instantiate a map of the Earth
+    map = starry.Map(20, reflected=reflected)
+    map.load("earth", sigma=0.1)
+    obl = 23.5
+    porb = 365.25
+    prot = 1.0
+
+    # Hack: these amplitudes give us unit maximum flux
+    if reflected:
+        map.amp = 3.3958
+    else:
+        map.amp = 0.7560
+
+    # Light curve over one year
+    time = np.linspace(0, porb, 1000)
+
+    # Starry settings
+    map.obl = obl
+    kwargs = {}
+    kwargs["theta"] = (time % prot) * 360
+    if reflected:
+        kwargs["xs"] = np.sin(2 * np.pi * time / porb)
+        kwargs["ys"] = 0
+        kwargs["zs"] = -np.cos(2 * np.pi * time / porb)
+
+    # Generate a fake dataset
+    flux0 = map.flux(**kwargs)
+    ferr = 1e-6
+    flux = flux0 + ferr * np.random.randn(len(flux0))
+
+    # Clear the map coefficients
+    map.reset(obl=obl)
+
+    # Solve the linear problem
+    map.set_data(flux, C=ferr ** 2)
+    L = np.zeros(map.Ny)
+    L[0] = 1e-1
+    L[1:] = 1e-3
+    map.set_prior(L=L)
[…]

### 2020-05-11 tex/ms.tex
new fig

@@
 %
-\xxx{A few paragraphs of introduction here. \citet{Russell1906}.}
+\xxx{A few paragraphs of introduction here.
+    Papers to cite: \citet{Russell1906}, \citet{Cowan2009},
+    \citet{Kawahara2010}, \citet{Kawahara2011}, \citet{Fujii2012}}
 
@@
 we can afford to simultaneously fit for the surface map without risk of
-overfitting (Bartoli\'c, Luger, et al., in prep).
+overfitting (Bartoli\'c, Luger et al., in prep).
 
@@
 
-\subsection{Information theory}
+\subsection{Linearity}
+\label{sec:linearity}
+
+\xxx{The starry problem is linear. We compute fluxes but can easily
+    compute design matrices instead.}
+
+\subsection{The information content of reflected light curves}
 \label{sec:information}
 
-\xxx{A few notes here on how constraining reflected light curves can be.}
+One of the fundamental difficulties with the mapping problem is that
+the process of inferring a two-dimensional map from a light curve
+is almost always ill-posed. This has been known since at least
+the turn of the last century, when \citet{Russell1906} discussed
+how, because of symmetry,
+all odd harmonics above $l = 1$ are in the null space for thermal
+phase curves of spherical bodies, meaning those terms do not contribute
+at all to the disk-integrated flux. As discussed in \citet{Luger2019},
+the problem is even more ill-posed than that: for any even
+degree $l > 0$, there are $2l + 1$ modes on the \emph{surface}
+(one for each value of $m$), but only $2$ Fourier modes in the
+\emph{light curve} (i.e., a sine and a cosine). Thus, for every
+mode that can be constrained from the light curve, there are far
+more modes that cannot, a problem that only gets worse as $l$
+increases.
 
@@
 \end{figure}
+
+The left panel of Figure~\ref{fig:inference} shows this issue in practice.
+We generate a mock thermal light curve (center left) from an $l = 20$
+expansion of the Earth (top) with 1,000 points over the course of one year
+with an exquisite photometric precision of 1 ppm. The Earth is given
+an obliquity of $23.5^\circ$ on the plane of the sky but is viewed
+along the ecliptic, rotating edge-on with an inclination of $90^\circ$.
+The data are shown in black, and in blue is our least-squares fit,
+in which we assume a prior variance of $10^{-3}$ for all spherical
+harmonic coefficients (and zero covariance). The corresponding surface
+map is shown at the bottom. As expected, this looks nothing like the
+true map of the Earth. For a body seen rotating edge-on, the information
+content of the light curve is strictly longitudinal. While the
+inferred map captures the average brightness of the Earth at each
+longitude fairly well, it is missing all latitudinal information.
+This is independent of the signal-to-noise or the cadence of the
+dataset---it is a fundamental limitation of phase curves in thermal light.
+
+The same is not true for the case of reflected light phase curves. In
+the right panel of Figure~\ref{fig:inference} we show the same
+mock light curve and perform the same inference step,
+but this time for observations in reflected light; the light curve
+is similar to that in Figure~\ref{fig:earthphase}. Because of the
+presence of a day-night terminator beyond which features on the surface
+contribute zero flux, none of the symmetry arguments above apply. In
+particular, the facts that (1) the Earth is seen at different phases and
+(2) the terminator is inclined relative to the rotational axis mean
+that the region of the surface contributing to the phase curve is
+always changing, resulting in a complex light curve that encodes
+signficicantly more information than its thermal counterpart.
+%
+The result is an inferred map that is largely faithful to the
+true map (bottom). While the continental outlines are somewhat fuzzy and some
+artifacts are present at high latitudes, it is clear that the
+inference problem is much less ill-posed in this case.
+
+Unlike thermal light curves, reflected light phase curves have the
+potential to robustly constrain two-dimensional maps of exoplanets.
+This result is
+not new, and has been discussed at length in the literature
+\citep[e.g.,][]{Fujii2012,Berdyugina2017,Luger2019b,Aizawa2020,Kawahara2020}.
+In particular, \citet{Kawahara2010} demonstrated the uniqueness of their
+inferred map from mock reflected light curves of the Earth. As we argued
+above, for specific geometrical configurations, the mapping problem
+in reflected light can actually be well-posed, meaning it has no
+null space up to a certain degree $l$. Reflected light phase curves of
+terrestrial planets with JWST and future direct imaging missions thus
+have the potential to reveal detailed information about their surfaces.
+
+\begin{figure}[p!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/inference_occ.pdf}
+        \oscaption{inference_occ}{%
+            Similar to Figure~\ref{fig:inference}, but for 500 high
+            signal to noise observations taken
+            over ten days near quadrature.
+            At the top we show the thermal and reflected
+            phase curves and the corresponding inferred maps.
+            At the bottom, we show the same light curves but this
+            time including 7 equatorial occultations by
+            a (very) short period moon one-quarter the size of the planet.
+            %
+            The presence of the occultations significantly increases the
+            fidelity of the recovered maps near the equator (the path
+            of the occultor). While in the thermal case there is significant
+            overfitting at high latitudes, in the reflected case the map
+            accurately recovers features across the entire planet.
+            \label{fig:inference_occ}
+        }
+    \end{centering}
+\end{figure}
+
+Nevertheless, at finite signal to noise and for limited observation
+duration or cadence, there may still be significant degeneracies in
+the reflected phase curve problem. In \citet{Luger2019} we argued that
+occultations can be used to break many of these degeneracies, since they
+directly probe the surface at scales inaccessible to phase curves.
+The same is true in reflected light. Figure~\ref{fig:inference_occ}
+demonstrates this for mock observations of the same Earth-like
+planet as in Figure~\ref{fig:inference}, but this time taken
+over ten days near quadrature, when the disk of the planet is seen at
+half phase. The top rows show the thermal and reflected phase
+curves and the inferred maps, which look similar to those in
+the previous figure.
+At the bottom we show the same light curve, but this time including
+seven equatorial occultations by a moon one-quarter the size of the planet.
+The moon's period and occultation duration are unrealistically short, but
+the inferred maps at the bottom show the exquisite constraining power of these
+occultations.
+In the thermal case, the presence of the moon allows us to infer the
+two-dimensional distribution of surface features along its equatorial
+occultation path; however, there is little information
+in the light curve about features at higher latitudes, and the \starry model
+overfits. Conversely, in the reflected light case, there is information
+about all latitudes and longitudes, and the inferred map is
+largely faithful to the true map.
+
+It should be kept in mind that the kinds of observations
+mentioned above will be very challenging for exoplanets, even with
+next-generation observatories such as HabEx or LUVOIR. Observations of
+occultations of planets by moons, in particular, are likely several decades
+away at least. There is some hope that planet-planet occultations may
+be detectable in the near future for specific planetary
+systems such as TRAPPIST-1
+\citep{Luger2019b}, but at extremely limited signal-to-noise.
+Even phase curve observations will be difficult
+because of their limited signal-to-noise, and in practice many
+degeneracies will likely remain. Several studies have found
+that color information can greatly help in the interpretation of
+reflected phase curves \xxx{(cite)}, while others
+have explored in detail the best kinds of priors to assume
+\citep[e.g.,][]{Aizawa2020}. Future maps of exoplanets---particularly
+terrestrial ones in the habitable zone---will require every tool
+in the toolbox.
 

### 2020-05-11 tex/figures/inference.py

@@ -7,13 +7,13 @@ starry.config.lazy = False
 np.random.seed(0)
 
 # Setup figure
-fig, ax = plt.subplots(3, 2, figsize=(13, 7))
+fig, ax = plt.subplots(3, 2, figsize=(13, 8))
 fig.subplots_adjust(hspace=0.4)
 ax[0, 0].set_visible(False)
 ax[0, 1].set_visible(False)
 ax[1, 0].set_ylabel("flux", fontsize=10)
-ax[1, 0].set_title("thermal", fontsize=12, fontweight="bold")
-ax[1, 1].set_title("reflected", fontsize=12, fontweight="bold")
+ax[1, 0].set_title("thermal phase curve", fontsize=12, fontweight="bold")
+ax[1, 1].set_title("reflected phase curve", fontsize=12, fontweight="bold")
 
 for axis in ax[1, :]:
     axis.tick_params(labelsize=8)
@@ -21,6 +21,7 @@ for axis in ax[1, :]:
 
 # Show the true map
 ax_top = fig.add_subplot(3, 1, 1)
+ax_top.set_title("input", fontsize=12, fontweight="bold")
 map = starry.Map(20)
 map.load("earth", sigma=0.1)
 map.show(ax=ax_top, projection="moll")
@@ -47,7 +48,7 @@ for i, reflected in enumerate([False, True]):
     # Starry settings
     map.obl = obl
     kwargs = {}
-    kwargs["theta"] = (time % prot) * 360
+    kwargs["theta"] = ((time % prot) / prot) * 360
     if reflected:
         kwargs["xs"] = np.sin(2 * np.pi * time / porb)
         kwargs["ys"] = 0
@@ -70,13 +71,16 @@ for i, reflected in enumerate([False, True]):
     map.solve(**kwargs)
 
     # Plot the light curve and the solution
-    ax[1, i].plot(time, flux, "k.", ms=2, alpha=0.5, label="data")
-    ax[1, i].plot(time, map.flux(**kwargs), "C0-", lw=0.5, alpha=0.25, label="model")
+    ax[1, i].plot(time, flux, "k.", ms=2, alpha=0.5, label="data", zorder=-2)
+    ax[1, i].plot(
+        time, map.flux(**kwargs), "C0-", lw=0.5, alpha=0.25, label="model", zorder=-1
+    )
     ax[1, i].legend(loc="best", fontsize=6)
     if reflected:
[…]

### 2020-05-11 tex/figures/inference_occ.py

@@ -1,0 +1,125 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import starry
+
+# Config
+starry.config.lazy = False
+np.random.seed(0)
+
+# Setup figure
+fig, ax = plt.subplots(5, 2, figsize=(13, 14))
+fig.subplots_adjust(hspace=0.4)
+ax[0, 0].set_visible(False)
+ax[0, 1].set_visible(False)
+ax[1, 0].set_ylabel("flux [normalized]", fontsize=10)
+ax[1, 0].set_title("thermal phase curve", fontsize=12, fontweight="bold")
+ax[1, 1].set_title("reflected phase curve", fontsize=12, fontweight="bold")
+ax[2, 0].set_ylabel("flux [normalized]", fontsize=10)
+ax[3, 0].set_title("thermal occultation", fontsize=12, fontweight="bold")
+ax[3, 1].set_title("reflected occultation", fontsize=12, fontweight="bold")
+for axis in np.append(ax[1, :], ax[3, :]):
+    axis.tick_params(labelsize=8)
+    axis.set_ylim(-0.05, 1.65)
+
+# Show the true map
+ax_top = fig.add_subplot(5, 1, 1)
+ax_top.set_title("input", fontsize=12, fontweight="bold")
+map = starry.Map(20)
+map.load("earth", sigma=0.1)
+map.show(ax=ax_top, projection="moll")
+
+# Solve the least-squares problem for thermal & reflected phase curves
+for j, rmoon in enumerate([0, 0.25]):
+    for i, reflected in enumerate([False, True]):
+
+        # Instantiate a map of the Earth
+        map = starry.Map(20, reflected=reflected)
+        map.load("earth", sigma=0.1)
+        obl = 23.5
+        porb = 365.25
+        prot = 1.0
+        pmoon = 1.37
+        amoon = 2.0
+        imoon = 85 * np.pi / 180
+
+        # Hack: these amplitudes give us unit median flux
+        if reflected:
+            map.amp = 1.0 / 0.123
+        else:
+            map.amp = 1.0
+
+        # Light curve over 10 days wiith 7 occultations
+        time = np.linspace(120.0, 130.0, 325)
+        for n in range(7):
+            time = np.append(time, (88.25 + n) * pmoon + np.linspace(-0.15, 0.15, 25))
+        time = np.sort(time)
+
+        # Starry settings
+        map.obl = obl
+        kwargs = {}
[…]

### 2020-05-11 tex/ms.tex
more text

@@
     Papers to cite: \citet{Russell1906}, \citet{Cowan2009},
-    \citet{Kawahara2010}, \citet{Kawahara2011}, \citet{Fujii2012}}
+    \citet{Kawahara2010}, \citet{Kawahara2011}, \citet{Fujii2012},
+    \citet{Farr2018}, \citet{Louden2018}.}
 
@@
 manager \textsf{pip}. The algorithm is coded in a mixture of \textsf{C++}
-with forward automatic differentation using the \textsf{Eigen} library
+with forward automatic differentiation using the \textsf{Eigen} library
 \citep{eigen} and \Python with backward differentiation using
@@
 $\nicefrac{a}{R_\star} = 3.16$
-planet \citep{Wong2019}. Asssuming zero eccentricity and ignoring any
+planet \citep{Wong2019}. Assuming zero eccentricity and ignoring any
 stellar oblateness
@@
             $l=15$ spherical harmonic fit to the
-            Galileio global color mosaic of Io \citep{Becker2005},
+            Galileo global color mosaic of Io \citep{Becker2005},
             an $l=\STARRYORENNAYARDEG$ expansion of the
@@
 campaign \citep{Arlot2014}. The trajectory of Europa relative to Io,
-computed from the JPL Horizons databse \xxx{(cite)}
+computed from the JPL Horizons database \xxx{(cite)}
 is shown at the top. We fit to this data a \starry occultation model
@@
 we can afford to simultaneously fit for the surface map without risk of
-overfitting (Bartoli\'c, Luger et al., in prep).
+overfitting (Bartoli\'c, Luger et al., \emph{in prep}).
 
@@
 
-\xxx{The starry problem is linear. We compute fluxes but can easily
-    compute design matrices instead.}
+In the Appendix we derive closed-form expressions for the flux
+as a function of the spherical harmonic expansion of the albedo,
+$\mathbf{y}$: Equation~(\ref{eq:sTA2IA1RRy}) for occultations and
+Equation~(\ref{eq:rTA1Ry}) for phase curves. Inspection of those
+equations reveals that they are both \emph{linear} in $\mathbf{y}$:
+the flux is simply the dot product of several matrices and the
+vector of spherical harmonic coefficients. We may therefore write
+both expressions in the form
+%
+\begin{align}
+    f = \mathbf{x}^\top \mathbf{y}
+\end{align}
+%
+where $f$ is a scalar representing the model for the flux at a particular
+point in time and $\mathbf{x}^\top$ is a row vector equal to
+$\sT\mathbf{A_2}\mathbf{I}\mathbf{A_1}\mathbf{R'}\mathbf{R}$
+(in the case of an occultation)
+or
+$\rT\mathbf{I}\mathbf{A_1}\mathbf{R''}\mathbf{R}$
+(in the case of a phase curve; see Appendix~\ref{sec:adapting-starry}
+for details on what each of the terms represent). Now, if we let $\mathbf{f}$
+be the vector of values of $f$ for each point in the timeseries and
+construct the matrix $\mathbf{X}$ out of the stacked row vectors
+$\mathbf{x}^\top$, we may write our model for the entire timeseries as
+the dot product
+%
+\begin{align}
+    \mathbf{f} = \mathbf{X} \mathbf{y}
+    \quad.
+\end{align}
+%
+The linearity of the \starry model is useful in several ways. For one,
+it can be exploited to cheaply compute the same model for different
+input vectors $\mathbf{y}$. This is useful for multi-band light curves,
+where the same matrix $\mathbf{X}$ dots into several vectors $\mathbf{y}$,
+one for each observation band, or for time-dependent models, in which
+the model for the flux might be the Taylor series
+%
+\begin{align}
+    \mathbf{f} =
+    \mathbf{X}
+    \bigg(
+    \mathbf{y}(t)\bigg|_{t=t_0} +
+    \frac{\dd\mathbf{y'}(t)}{\dd t}\bigg|_{t=t_0} t +
+    \frac{1}{2}\frac{\dd^2\mathbf{y'}(t)}{\dd t^2}\bigg|_{t=t_0} t^2 +
+    \cdots
+    \bigg)
+    \quad,
+\end{align}
+%
+where $\mathbf{y}(t)$ is a time-dependent representation of the surface
+map, which we expand about $t=t_0$ \citep[see][]{Luger2019b}.
+But perhaps even more importantly, linear
+models are particularly useful for inference, since under Gaussian
+noise properties the posterior is analytic. In particular, if
+our light curve measurements are given by the data vector $\mathbf{d}$
+whose noise model is specified by the covariance matrix $\pmb{\Sigma}$,
+and we place a Gaussian prior on $\mathbf{y}$ with mean $\pmb{\mu}$ and
+covariance $\pmb{\Lambda}$, the posterior mean may be written
+%
+\begin{align}
+    \label{eq:posterior_mu}
+    \hat{\bvec{y}} & =
+    \bvec{C}
+    \left(
+    \mathbf{X}^\top
+    \pmb{\Sigma}^{-1}
+    \bvec{d}
+    +
+    \pmb{\Lambda}^{-1}
+    \pmb{\mu}
+    \right)
+    \quad,
+\end{align}
+%
+where $\bvec{C}$ is the posterior covariance, given by
+%
+\begin{align}
+    \label{eq:posterior_cov}
+    \bvec{C} & =
+    \left(
+    \mathbf{X}^\top
+    \pmb{\Sigma}^{-1}
+    \mathbf{X}
+    +
+    \pmb{\Lambda}^{-1}
+    \right)^{-1}
+    \quad.
+\end{align}
+%
+Because of this linearity, and the analyticity of the \starry
+model, inference on datasets comprising thousands of points and
+spherical harmonic degree $l \leq 20$ takes a
+\emph{fraction of a second} on a typical computer.
+\textbf{Full posterior inference with \starry is thus faster than
+    the numerical evaluation of a single forward model}
+(c.f. Figure~\ref{fig:speed}).
+
+It is important to note, however, that the \starry model is linear
+only in the map coefficients $\mathbf{y}$. In any real application,
+there will be uncertainty in the inputs of $\mathbf{X}$, such
+as the orbital parameters, the occultor parameters, the scattering
+law, etc. These parameters must typically be sampled over, since the model
+is a nonlinear function of them. However, the analyticity---and in particular,
+the differentiability---of the \starry model makes sampling via
+gradient-based MCMC easy. Moreover, the linearity of the model
+with respect to $\mathbf{y}$ allows one to efficiently marginalize over
+those parameters when sampling over the nonlinear parameters.
+Tutorials on how to do this can be found in the
+\starry \href{https://rodluger.github.io/starry}{documentation}.
 
@@
 along the ecliptic, rotating edge-on with an inclination of $90^\circ$.
-The data are shown in black, and in blue is our least-squares fit,
+The data are shown in black, and in blue is the posterior mean model
+(Equation~\ref{eq:posterior_mu}),
 in which we assume a prior variance of $10^{-3}$ for all spherical
@@
 always changing, resulting in a complex light curve that encodes
-signficicantly more information than its thermal counterpart.
+significantly more information than its thermal counterpart.
 %
@@
 
-\xxx{Limitations of the model: can't capture shadowing. Unstable above degree 20 or so.}
+There are several limitations to the \starry model that are important
+to bear in mind. The primary limitation concerns the maximum spherical
+harmonic degree of the model. While the expressions derived here are
+valid at arbitrary degree, we find that their numerical stability begins
+to degrade above $l \sim 20-25$ for occultations and $l \sim 35-40$ for phase
+curves. The same is true for the model in thermal light \citep{Luger2019},
+and is due to (1) the large condition number of the change-of-basis matrix
+from spherical harmonics to polynomials and (2) instabilities in the
+many recursion relations used to evaluate the solution vectors
+$\sT$ and $\rT$.
+In principle, one could improve the numerical stability by evaluating
+all expressions at higher floating-point precision, but in practice
+the computational cost of this becomes quickly prohibitive.
+However, it is important to keep in mind that our current best image
+of an exoplanet is the $l=1$ map of HD189733b
+\citep{Knutson2007,Majeau2012,deWit2012}. Next-generation facilities
+such as JWST may allow us to probe surface modes as small as $l=5$
+for some planets (Luger et al., \emph{in prep}), but even with future
+telescopes such as LUVOIR it is extremely unlikely we will do better than
+$l=20$. If we are ever able to probe resolutions smaller than
+$180^\circ / 20 = 9^\circ$ on the surface, the \starry algorithm
+will have to be revisited.
+
+The second limitation involves a potential failure of the \starry
+algorithm. The \starry code includes a large suite of unit tests that compare
+the flux computations to numerical models and to various benchmarks
+for a wide variety of inputs. While we have done our best to
+develop tests over the full range of occultation configurations,
+there may be edge cases in which the \starry algorithm fails and returns
+the wrong flux. This could happen, for instance, if the quartic root
+solver (\S\ref{sec:which-case}) fails to find the points of intersection
+between the occultor and the day/night terminator, leading to
+an incorrect case identification (Figure~\ref{fig:cases}) and thus the
+wrong value for the flux. In the development of the algorithm, these cases
+would occasionally show up as a single, obvious outlier in a light curve
+model. All such cases we encountered
+have been fixed by adding consistency
+checks in the root solver and switching to alternate evaluation methods
+near known singularities. However, it is possible that there may still be
+rare cases in which this happens, in which case we ask that users
+raise an \href{https://github.com/rodluger/starry/issues}{issue} on
+GitHub so that we can provide a fix.
+
+The third limitation concerns the flexibility of the \starry model.
+While we presented ways to capture non-Lambertian scattering
+in \starry (\S\ref{sec:nonlambertian}), there are certain aspects
+of light curves in reflected light that cannot be captured by the model.
+One example of this is shadowing. Craters on the moon or
+volcanoes on Io can cast large shadows visible from space, particularly
+if viewed near crescent phase. Unfortunately, there is no way to model
+this within the \starry framework. Another example is specular reflection,
+or ``glint'', which is a pronounced signal for the Earth due its
+oceans \citep{Robinson2014} and on Titan due to
+its hydrocarbon lakes \citep{Barnes2011}. In principle, glint could be
+modeled in the same way as non-Lambertian sccattering, by constructing the
+linear operator $\mathbf{I}$ in such a way as to downweight portions of the
+projected disk where $\vartheta_i \neq \vartheta_r$. In practice, however,
+if the size of the glint spot is small (which is typically the case),
+an expansion at extremely high $l$ ($l \sim 360$ in the case of the Earth)
+would be required, which would not work for the reasons above.
+Instead, it may be possible to combine the \starry algorithm with the
+formalism of \citet{Haggard2018}, who derived analytic expressions for
+phase curves of delta function maps ($\delta$-map), to model glint.
+As discussed in \citet{LustigYaeger2018}, glint mapping is an extremely
+powerful way to not only map terrestrial planets but also to confirm
+their habitability via the presence of an ocean.
+
+Finally, we would like to emphasize that while spherical harmonics are
+a convenient basis for the purpose of computing light curves, they
+have a significant drawback when it comes to modeling real planetary
+surfaces: it can be difficult to strictly enforce physical
+values of the albedo everywhere on the surface map when doing inference.
+That is because there is no analytic way to determine whether a
+spherical harmonic representation is positive-valued
+(or restricted to a given range) everywhere on the sphere.
+Instead, this must be checked numerically, by evaluating the function on a
+discrete grid. This makes it somewhat cumbersome to implement positivity as a prior
+when doing inference; in particular, this prior cannot be expressed as
+a Gaussian, so the analytic expression for the posterior
+discussed in \S\ref{sec:linearity} will generally have nonzero support for
+negative albedo values. This is particularly problematic when the data is
+not very constraining and the posterior is prior-dominated, as
+positivity can be an \emph{extremely} informative prior
+\citep[e.g.,][]{Fienup1978}.
+We therefore recommend that in such cases
+users of the \starry algorithm use MCMC to do inference, either
+(1) sampling over the spherical
+harmonic coefficients $\mathbf{y}$ and imposing a uniform prior in the range
+$[0, 1]$ on the albedo values $\mathbf{a}$
+evaluated on a discrete grid on the sphere or
+(2) sampling over the albedo values $\mathbf{a}$ with the same uniform prior,
+but using $\mathbf{y}$ to compute the actual light curve model. In both
+cases, there exists a linear operator that transforms between
+$\mathbf{y}$ and $\mathbf{a}$:
+%
+\begin{align}
+    \label{eq:Py}
+    \mathbf{a} = \mathbf{P} \mathbf{y}
+\end{align}
+%
+and
+%
+\begin{align}
+    \label{eq:PInvy}
+    \mathbf{y} = \mathbf{P}^+ \mathbf{a}
+    \quad,
+\end{align}
+%
+where
+%
+\begin{align}
+    \label{eq:PInv}
+    \mathbf{P}^+ =
+    (\mathbf{P}^\top \mathbf{P} + \lambda \mathbf{I})^{-1} \mathbf{P}^\top
+\end{align}
+%
+is the pseudoinverse of $\mathbf{P}$, with (small) regularization parameter
+$\lambda$ and where $\mathbf{I}$ is the identity matrix.
+%
+Each row of the matrix $\mathbf{P}$ is constructed from the value
+of each of the spherical harmonics at the corresponding point on the
+grid; both $\mathbf{P}$ and its inverse may be pre-computed for
+efficiency. In both cases, the grid should be fine enough to ensure
+positivity over most of the sphere but not so fine as to throttle the
+computation; in practice, we find that grids with $2-5$ times as many pixels
+as spherical harmonic coefficients are ideal.
+%
+The \href{https://rodluger.github.io/starry}{documentation}
+includes tutorials on how to implement this in practice.
 
@@
 identify the relevant integration boundaries, which depend on the points
-of intesection between the limb of the body, the limb of the occultor, and
+of intersection between the limb of the body, the limb of the occultor, and
 the terminator. We do so in the following sections.
@@
 \emph{all} of the nightside of the body and \emph{some} of the dayside.
-Since the visible portion of the disk consistss only of dayside, we can
+Since the visible portion of the disk consists only of dayside, we can
 simply use the weighted solution in emitted light

### 2020-05-12 tex/ms.tex
woot; complete draft

@@
 
+\keywords{methods: analytic --- techniques: photometric}
+
 \begin{abstract}
-    Abstract here.
+    We derive efficient, closed form, differentiable, and numerically stable
+    solutions for the flux measured from a planet or moon seen in reflected
+    light, either in our out of occultation.
+    %
+    Our expressions apply to the computation of scattered
+    light phase curves of exoplanets, secondary eclipse light curves in
+    the optical, or future measurements of planet-moon and planet-planet
+    occultations, as well as to photometry of solar system bodies.
+    %
+    We derive our solutions for Lambertian bodies illuminated by a point
+    source, but extend them to model illumination sources of finite
+    angular size and rough surfaces with phase-dependent scattering.
+    %
+    Our algorithm is implemented in \Python within the open-source
+    \starry mapping framework and is designed with efficient gradient-based
+    inference in mind.
+    %
+    The algorithm is ${\sim}4-5$ orders of magnitude faster than direct
+    numerical evaluation methods and ${\sim}10$ orders of magnitude more
+    precise.
+    %
+    We show how the techniques developed here may one day lead to the
+    construction of two-dimensional maps of terrestrial planet surfaces,
+    potentially enabling the detection of continents and oceans on
+    exoplanets in the habitable zone.
     %
@@
 %
-\xxx{A few paragraphs of introduction here.
-    Papers to cite: \citet{Russell1906}, \citet{Cowan2009},
-    \citet{Kawahara2010}, \citet{Kawahara2011}, \citet{Fujii2012},
-    \citet{Farr2018}, \citet{Louden2018}.}
+
+Despite recent advances in instrumentation and the dawn of
+thirty meter-class telescopes and kilometer-wide interferomer arrays,
+extrasolar planets will remain unresolved point sources for decades
+to come. Nevertheless, modulations in the light received from these distant
+bodies due to their rotation, changing illumination, and eclipses
+by their host stars or other bodies in the system can be harnessed to
+reconstruct two-dimensional views of their surfaces.
+In particular, next-generation space-based telescopes such as the
+Large UV/Optical/IR Surveyor (LUVOIR) may enable us to measure
+variations in the reflected light signature of terrestrial planets in
+the habitable zone, which can be used to map their surfaces and
+indirectly infer the presence of clouds, continents, oceans, and perhaps
+even life.
+
+There is a vast literature on techniques for mapping exoplanet surfaces
+based on their phase curves
+\citep[e.g.,][]{Russell1906,Lacis1972,Knutson2007,Cowan2008,Oakley2009,Berdyugina2017}
+and occultation light curves
+\citep[e.g.,][]{Williams2006,Rauscher2007,Majeau2012,deWit2012,Rauscher2018},
+both in thermal and reflected (scattered) light.
+In particular, much attention has been given to techniques for mapping
+Earth-like planets from visible-light reflected phase curves
+\citep[e.g.,][]{Ford2001,Kawahara2010,Kawahara2011,Fujii2012,Kawahara2020,Aizawa2020}.
+Unlike thermal phase curves, which primarily encode (often degenerate)
+information about longitudinal surface brightness variations
+\citep{Russell1906}, reflected light curves often contain information
+about the full two-dimensional surface albedo distribution
+\citep[e.g.,][]{Kawahara2010}.
+
+Occultation light curves in reflected light can encode even more information
+about the surface. Thus far, these have been studied primarily within our
+solar system. Mutual occultations among the Galilean moons of Jupiter
+have been studied to infer surface properties of Io \xxx{...more on this,
+    and add citations.}
+
+Many studies have analyzed real Earth reflected light curves to
+infer surface properties of our planet as an exercise in
+prepartion for the mapping of exoplanets.
+%
+\citet{Cowan2009} analyzed visible-light disk-integrated light curves
+of the Earth taken by the Deep Impact spacecraft to produce
+longitudinal maps of the surface, harnessing multi-band observations
+to disentangle static surface brightness features from temporally
+variable clouds. More recently, \citet{Jiang2018} and \citet{Fan2019}
+used data from the L1-stationed DSCOVR satellite to infer surface
+and cloud properties of the Earth, and \citet{Luger2019b} analyzed
+background scattered light in TESS photometry to reconstruct a cloud
+map of the Earth.
+
+On the open-source software front, \citet{Louden2018} developed
+\textsf{spiderman}, an efficient discretization scheme
+on the sphere that enables fast computation of exoplanet
+phase curves and occultation light curves in \Python.
+%
+\citet{Haggard2018} presented
+\textsf{EARL} (Exoplanet Analytic Reflected Lightcurves),
+a \textsf{Mathematica} code to compute analytic, closed form
+solutions for the phase curve of a Lambert sphere, i.e., one that
+scatters light isotropically, in the case that the surface albedo
+distribution is characterized by either a sum of delta functions
+or a sum of spherical harmonics.
+%
+\citet{Farr2018} released \textsf{exocartographer}, a Bayesian
+framework for doing inference on exoplanet phase curves based on
+a HEALPix \citep{healpix} discretization scheme.
+%
+Finally, \citet{Luger2019} introduced \starry, a light curve
+modeling package that computes thermal phase curves and occultation
+light curves, as well as their derivatives, analytically from a spherical
+harmonic expansion of the surface brightness.
+
+The present paper is an extension to the \starry algorithm,
+adapting it to model phase curves and occultation light curves
+in reflected light. The expressions
+we derive are analytic: they may all be expressed in closed form
+in terms of algebraic operations involving trigonometric functions
+and (at times) elliptic integrals. We derive numerically
+stable recursion relations for the efficient evaluation of all
+expressions and code them within an autodifferentiation framework
+to enable the computation of high precision derivatives for use in
+gradient-based inference and optimization schemes.
+Our code is fully
+\href{https://github.com/rodluger/starry}{open-source},
+comprehensively
+\href{https://dev.azure.com/rodluger/starry/_test/analytics?definitionId=4}{unit-tested},
+and supplemmented with an extensive
+\href{https://rodluger.github.io/starry}{API documentation}
+and suite of
+\href{https://rodluger.github.io/starry/latest/tutorials.html}{tutorials}.
+%
+As in \citet{Luger2019}, in the caption of each of the figures
+we provide links \codeicon\ to the exact \Python scripts that
+generated them. Next to many of the equations we also provide
+links \prooficon\ to \textsf{Jupyter} notebooks containing
+detailed derivations and/or validations.
+
+\section{Overview}
+\label{sec:overview}
 
@@
 makes the problem of computing the visible flux particularly difficult; most
-studies to date have tackled the problem numerically, by discretizing the surface
+studies to date have tackled the problem numerically, either
+via Monte Carlo integration \citep[e.g.,][]{Ford2001} or by discretizing the surface
 and computing the relevant integrals by summing over the visible
@@
 the body is occulted by another spherical body, which may or may not be the
-illumination source.
+illumination source. We also extend the solution to the case of an extended
+illumination source and to non-Lambertian scattering.
 
@@
 the paper to validating and demonstrating applications of our approach.
+
+This paper is organized as follows.
+In \S\ref{sec:validation} we present sample light curves computed
+using our algorithm, validate it against numerical integration, and
+discuss its performance in terms of computational speed and precision.
+In \S\ref{sec:extensions} we extend the model to apply to illumination
+sources of finite size and surfaces that scatter light anisotropically.
+We discuss implications, applications, and limitations of our model in
+\S\ref{sec:discussion} and summarize our findings in \S\ref{sec:conclusions}.
+For convenience, Tables~\ref{tab:symbols}--\ref{tab:matrices} at the end
+list all symbols and variables used in the text, with descriptions and
+links to the equations in which they are defined.
 
@@
 with \textsf{pymc3} \citep{pymc3} for inference with gradient-based
-Markov Chain Monte Carlo (MCMC) schemes.
+Markov Chain Monte Carlo (MCMC) schemes
+such as Hamiltonian Monte Carlo \citep[HMC;][]{Duane1987}
+and No-U-Turn Sampling \citep[NUTS;][]{Hoffman2011}.
 %
@@
 if viewed near crescent phase. Unfortunately, there is no way to model
-this within the \starry framework. Another example is specular reflection,
+this within the \starry framework. Another example is multiple scattering,
+as in optically thick atmospheres, for which a proper radiative transfer model
+must be used. There is also the case of specular reflection,
 or ``glint'', which is a pronounced signal for the Earth due its
@@
     \mathbf{P}^+ =
-    (\mathbf{P}^\top \mathbf{P} + \lambda \mathbf{I})^{-1} \mathbf{P}^\top
+    (\mathbf{P}^\top \mathbf{P} + \lambda \boldsymbol{\mathsf{I}})^{-1} \mathbf{P}^\top
 \end{align}
@@
 is the pseudoinverse of $\mathbf{P}$, with (small) regularization parameter
-$\lambda$ and where $\mathbf{I}$ is the identity matrix.
+$\lambda$ and where $\boldsymbol{\mathsf{I}}$ is the identity matrix.
 %
@@
 positivity over most of the sphere but not so fine as to throttle the
-computation; in practice, we find that grids with $2-5$ times as many pixels
-as spherical harmonic coefficients are ideal.
+computation; as a rule of thumb, we find that grids with $2-5$ times
+as many pixels
+as spherical harmonic coefficients are sufficient.
 %
@@
 
-\xxx{TODO.}
-
-\vfill
-\pagebreak
+We have presented an efficient, numerically stable,
+closed-form algorithm for computing phase curves
+and occultation light curves of spherical bodies in reflected
+(scattered) light.
+This algorithm is an extension of the algorithm presented
+in \citet{Luger2019} for light curves in thermal light and
+is generally applicable to exoplanetary phase
+curves, secondary eclipses, and occultations by moons and other planets,
+as well as to light curves of planets and moons in our solar system.
+We derive the solution for the case of a Lambert sphere illuminated by a
+point source, but extend it to the case of an extended illumination
+source and non-Lambertian scattering parametrized by a surface roughness
+coefficient.
+%
+The algorithm is ${\sim}4-5$ orders of magnitude faster
+and ${\sim}10$ orders of magnitude more precise than other numerical
+approaches for computing these light curves. The algorithm is
+also differentiable, enabling inference with efficient gradient-based samplers
+such as Hamiltonian Monte Carlo (HMC), and linear in the spherical
+harmonic coefficients describing the surface albedo, enabling fast,
+closed-form solutions for the albedo posterior distribution under a
+Gaussian noise model.
+%
+We implement the algorithm within the \starry software, an open-source \Python
+package for inferring surface maps of unresolved celestial bodies. The
+algorithm is coded in a combination of \cpp and \Python compiled using
+the \textsf{theano}. The interface was designed specifically for
+compatibility with the \textsf{exoplanet} modeling package
+\citep{exoplanet} and the \textsf{pymc3} inference suite \citep{pymc3}.
+
+Upcoming telescopes will enable measurements of exoplanet phase curves
+and secondary eclipses at unprecendented precision. While the
+James Webb Space Telescope (JWST) will be primarily sensitive to thermal
+emission from exoplanets (which can currently be modeled with \starry),
+next-generation direct imaging facilities such as the
+Large UV/Optical/IR Surveyor (LUVOIR)
+will enable measurements in reflected light, in particular for terrestrial
+planets in the habitable zone. Because of the changing illumination
+pattern over the course of an orbit of the planet, phase curves and
+occultation light curves in reflected
+light contain vastly more information about the two-dimension albedo
+distribution of the body than their thermal counterparts.
+With careful modeling, light curves in reflected light are likely to give us
+the first images of potentially habitable exoplanets, enabling the
+detection of clouds, continents, oceans, and perhaps even life.
+
+\vspace{1em}
+
+The software presented in this work is open source under the MIT License and
+is available at \url{https://github.com/rodluger/starry}, with documentation
+and tutorials hosted at \url{https://rodluger.github.io/starry}.
+A permanent version of the code used to generate the figures and results in
+this paper is archived at \xxx{https://doi.org/XX.XXXX/zenodo.XXXXXXX}.
+
+\software{
+    Eigen v3 \citep{eigen},
+    exoplanet \citep{exoplanet},
+    HEALPix \citep{healpix},
+    pybind11 \citep{pybind11},
+    pymc3 \citep{pymc3},
+    scipy \citep{scipy},
+    starry \citep{starry}.
+}
 
@@
 sections and equations in which they are defined.
+Because of the large number of symbols used in this paper, we adopt
+the following conventions: scalars are represented by regular lowercase or
+occasionally uppercase letters (i.e., $x$ or $X$), vectors are
+represented by boldface lowercase letters
+($\mathbf{x}$), and matrices and other linear operators are represented
+by boldface capital letters ($\mathbf{X}$).
+With a few exceptions,
+Greek letters are reserved for angular quantities and may be either
+scalars ($\alpha$) or vectors ($\pmb{\alpha}$).
+Script font is typically used to denote curves or frames of reference
+($\mathcal{F}$). Primes are used to
+distinguish between frames of reference ($x$ and $x'$ are used
+to denote the same quantity, but in frames $\mathcal{F}$ and $\mathcal{F}'$,
+respectively). Tildes are used to denote basis vectors ($\by$). Finally,
+blackboard vectors ($\mathbbb{x}$) correspond to solutions
+to the various ``primitive'' integrals that arise in the occultation
+problem.
 
@@
 an occultor of radius $r_o$ is located at sky position $(x_o, y_o)$,
-we compute the visible flux $f$ from
+we compute the visible thermal flux $f_T$ from
 %
@@
     \label{eq:sTARRy}
-    f = \sTe \mathbf{A} \mathbf{R}' \mathbf{R} \mathbf{y}
+    f_T = \sTe \mathbf{A} \mathbf{R}' \mathbf{R} \mathbf{y}
     \quad,
@@
 If instead no occultor is present, we compute the total
-visible flux $f_0$ from this body as
+visible thermal flux $f_{T_0}$ from this body as
 %
@@
     \label{eq:rTA1Ry}
-    f_0 = \rTe \mathbf{A_1} \mathbf{R}'' \mathbf{R} \mathbf{y}
+    f_{T_0} = \rTe \mathbf{A_1} \mathbf{R}'' \mathbf{R} \mathbf{y}
     \quad,
@@
 %
-and the angle $\theta$ by which its semi-major axis is rotated away from the
-$+x$-axis (a frame-dependent quantity, defined below).
+and the angle by which its semi-major axis is rotated away from the
+$+x$-axis,
+%
+\begin{proof}{}
+    \label{eq:theta}
+    \theta = \atantwo(y_s, x_s)
+    \quad.
+\end{proof}
+%
 Given this formulation, and assuming that
@@
 with $b_c \equiv \sqrt{1 - b^2}$ and $z(x, y) = \sqrt{1 - x^2 - y^2}$.
-A quick note on the normalization of Equation~(\ref{eq:illum_poly}):
-if we place the illumination source along the $+z$-axis at $(0, 0, 1)$,
-the body is seen at full phase, so $b = -1$, $b_c = 0$, and
+The illumination $\mathcal{I}$ is a unitless quantity, normalized such that
+the integral of $\mathcal{I} A$ over the unit
+disk is equal to the flux measured
+by the observer as a fraction of the flux of the illumination source.
+In particular, if we place the illumination source along the $+z$-axis at
+$(0, 0, 1)$, the body is seen at full phase, so $b = -1$, $b_c = 0$, and
 %
@@
 %
-Integrating this over the full disk, we obtain the reflected flux measured
-by the observer (as a fraction of the flux of the illumination source)
-if the body has unit spherical albedo,
+Multiplying this by the albedo and integrating over the unit disk,
+we obtain the reflected flux measured
+by the observer in units of the flux of the illumination source:
 %
@@
     \int_{-\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
+    A
     \frac{\sqrt{1 - x^2 - y^2}}{\pi}
@@
     \nonumber \\[0.5em]
-    &= \frac{2}{3}
+    &= \frac{2}{3}A
     \quad,
@@
 which is precisely the geometric albedo of a Lambert
-sphere \citep[see, e.g.][]{Seager2010}.
+sphere of spherical albedo $A$ \citep[see, e.g.][]{Seager2010}.
 
@@
 %
-For computational efficiency, in practice we compute the integral of the
-intensity-weighted basis directly,
-%
-\xxx{NO LONGER TRUE. FIX THIS DEFINITION.}
-%
-\begin{align}
-    \label{eq:rTI}
-    \overset{\quad\pmb{\wedge}}{\mathbbb{r}}{^\top}(b, r_s) & \equiv
-    \rT(b) \mathbf{I}(b, \theta'', r_s)
-    \nonumber                                                        \\
-                                                            & =
-    \int_{-1}^{1}
-    \int_{b\sqrt{1 - x''^2}}^{\sqrt{1 - x''^2}}
-    \bp(x'', y'')
-    \mathbf{I}(b, 0, r_s)
-    \ \dd y'' \ \dd x''
-    \quad,
-\end{align}
-%
-recalling that in frame $\mathcal{F}''$, $\theta'' = 0$ by
-definition.
-%
-Equation~(\ref{eq:rTI}) may be solved analytically in terms of purely
+Equation~(\ref{eq:rT}) may be solved analytically in terms of purely
 trigonometric and algebraic functions of $b$.
-The component of $\overset{\quad\pmb{\wedge}}{\mathbbb{r}}{^\top}$
+The component of $\rT$
 at index $n$ is given by
@@
     \label{eq:rTsoln}
-    \overset{\quad\wedge}{\mathbb{r}}_n(b, r_s) & =
-    \frac{1}{\pi r_s^2}
+    \mathbb{r}_n(b) & =
     \begin{cases}
-        \frac{b_c\left(1 - b^{\frac{\nu + 4}{2}}\right)}{2}
-        \mathbb{L}_{\frac{\mu}{2}, \frac{\nu + 2}{2}} -
-        b \mathbb{k}_\frac{\nu}{2}(b) \mathbb{M}_{\frac{\mu}{2}, \frac{\nu}{2}}
+        \frac{\left(1 - b^{\frac{\nu + 4}{2}}\right)}{2}
+        \mathbb{L}_{\frac{\mu}{2}, \frac{\nu + 2}{2}}
         %
@@
         %
-        b_c
         \mathbb{k}_{\frac{\nu + 1}{2}}(b) \mathbb{M}_{\frac{\mu - 1}{2}, \frac{\nu + 1}{2}}
-        %
-        \\[0.5em]
-        \qquad
-        %
-        - \frac{b}{2} \bigg\{
-        \left(1 - b^{\frac{\nu + 1}{2}}\right)
-        \left(
-        \mathbb{L}_{\frac{\mu - 1}{2}, \frac{\nu - 1}{2}} -
-        \mathbb{L}_{\frac{\mu + 3}{2}, \frac{\nu - 1}{2}}
-        \right)
-        \\[0.5em]
-        \qquad\qquad
-        -
-        \left(1 - b^{\frac{\nu + 5}{2}}\right)
-        \mathbb{L}_{\frac{\mu - 1}{2}, \frac{\nu + 3}{2}}
-        \bigg\}
         %
@@
 %
-Once $\overset{\quad\pmb{\wedge}}{\mathbbb{r}}{^\top}$ is known,
-the observed flux is computed from
-(c.f. Equation~\ref{eq:rTIA1RRy})
-%
-\begin{proof}{}
+Once $\rT$ is known,
+the observed total flux in reflected light
+is computed from (c.f. Equation~\ref{eq:rTIA1RRy})
+%
+\begin{align}
     \label{eq:f0}
     f_0 & =
-    \overset{\quad\pmb{\wedge}}{\mathbbb{r}}{^\top}(b, r_s)
+    \rT(b)
+    \mathbf{I}(b, \theta'', r_s)
     \mathbf{A_1}
@@
     \quad.
-\end{proof}
+\end{align}
 %
@@
     \label{eq:f0hat}
-    \hat{f}_0 & =
-    -\overset{\quad\pmb{\wedge}}{\mathbbb{r}}{^\top}(-b, r_s)
+    \hat{f}_0 &=
+    \Big(
+    \mathbf{r}^\top
+    -
+    \rT(b)
+    \Big)
+    \mathbf{I}(b, \theta'', r_s)
     \mathbf{A_1}
-    \mathbf{R}''(-x_s, -y_s)
+    \mathbf{R}''(x_s, y_s)
     \mathbf{R}(\text{I}, \Lambda, \Theta)
     \mathbf{y}
-    \quad,
-\end{proof}
-%
-\xxx{FIX THIS DEFINITION. NO LONGER HOW WE COMPUTE IT.}
-%
-This is the flux we would get if we placed a \emph{negative} illumination
-source at the antipode $(-x_s, -y_s, -z_s)$ of the true source, and
-will be useful in negating the unphysical negative contribution from our
-polynomial illumination function (Equation~\ref{eq:illum_poly}) in
-the following section.
+    \quad.
+\end{proof}
+%
+This is the flux contribution from the unphysical night side
+(if we were to integrate over it), where
+our polynomial illumination (Equation~\ref{eq:illum_poly}) function
+yields \emph{negative} intensities. This quantity
+will be useful in negating the unphysical contribution
+in the integrals of the following section.
 

### 2020-05-12 tex/ms.tex
new proof

@@
 %
-\begin{proof}{}
+\begin{proof}{tau}
     \label{eq:tau}
@@
 and tutorials hosted at \url{https://rodluger.github.io/starry}.
-A permanent version of the code used to generate the figures and results in
-this paper is archived at \xxx{https://doi.org/XX.XXXX/zenodo.XXXXXXX}.
+The code used to generate the figures in this paper is hosted
+at \url{https://github.com/rodluger/starrynight}, with a permanent
+version archived at \xxx{https://doi.org/XX.XXXX/zenodo.XXXXXXX}.
 

### 2020-05-12 tex/ms.tex
working on proof

@@
 %
-\begin{proof}{}
+\begin{proof}{illumination}
     \label{eq:b}
@@
 %
-\begin{proof}{}
+\begin{proof}{illumination}
     \label{eq:theta}
-    \theta = \atantwo(y_s, x_s)
+    \theta = -\atantwo(x_s, y_s)
     \quad.
@@
 %
-\begin{proof}{}
+\begin{proof}{illumination}
     \label{eq:illum}
@@
 %
-\begin{proof}{}
+\begin{proof}{illumination}
     \label{eq:illum_poly}
@@
 The illumination $\mathcal{I}$ is a unitless quantity, normalized such that
-the integral of $\mathcal{I} A$ over the unit
+the integral of $A\mathcal{I}$ over the unit
 disk is equal to the flux measured
@@
 %
-\begin{proof}{}
+\begin{proof}{illumination}
     \mathcal{I}_\text{full}(x, y) = \frac{\sqrt{1 - x^2 - y^2}}{\pi}
@@
 %
-\begin{proof}{}
+\begin{proof}{illumination}
     \mathcal{f}_\text{full} &=
@@
 sphere of spherical albedo $A$ \citep[see, e.g.][]{Seager2010}.
+\xxx{Is this explanation sufficient? Why does it matter that this
+    is the geometric albedo of a Lambert sphere?}
 

### 2020-05-13 python/cases.py
added proof

@@ -1,87 +1,0 @@
-import numpy as np
-
-# These are lists of [b, theta, bo, ro]
-# corresponding to specific geometries
-# we need to test.
-CASE = [None for n in range(6)]
-
-# Occultor does not touch the terminator
-CASE[0] = [
-    [0.5, 0.1, 1.2, 0.1],
-    [0.5, 0.1, 0.1, 1.2],
-    [0.5, 0.1, 0.8, 0.1],
-    [0.5, 0.1, 0.9, 0.2],
-    [0.5, np.pi + 0.1, 0.8, 0.1],
-    [0.5, np.pi + 0.1, 0.9, 0.2],
-    [0.5, 0.1, 0.5, 1.25],
-    [0.5, np.pi + 0.1, 0.5, 1.25],
-]
-
-# Occultations involving all three primitive integrals
-CASE[1] = [
-    [0.4, np.pi / 3, 0.5, 0.7],
-    [0.4, 2 * np.pi - np.pi / 3, 0.5, 0.7],
-    [0.4, np.pi / 2, 0.5, 0.7],
-    [0.4, np.pi / 2, 1.0, 0.2],
-    [0.00001, np.pi / 2, 0.5, 0.7],
-    [0, np.pi / 2, 0.5, 0.7],
-    [0.4, -np.pi / 2, 0.5, 0.7],
-    [-0.4, np.pi / 3, 0.5, 0.7],
-    [-0.4, 2 * np.pi - np.pi / 3, 0.5, 0.7],
-    [-0.4, np.pi / 2, 0.5, 0.7],
-]
-
-# Occultations involving only P and T
-CASE[2] = [
-    [0.4, np.pi / 6, 0.3, 0.3],
-    [0.4, np.pi + np.pi / 6, 0.1, 0.6],
-    [0.4, np.pi + np.pi / 3, 0.1, 0.6],
-    [0.4, np.pi / 6, 0.6, 0.5],
-    [0.4, -np.pi / 6, 0.6, 0.5],
-    [0.4, 0.1, 2.2, 2.0],
-    [0.4, -0.1, 2.2, 2.0],
-    [0.4, np.pi + np.pi / 6, 0.3, 0.8],
-    [0.75, np.pi + 0.1, 4.5, 5.0],
-    [-0.95, 0.0, 2.0, 2.5],
-    [-0.1, np.pi / 6, 0.6, 0.75],
-    [-0.5, np.pi, 0.8, 0.5],
-    [-0.1, 0.0, 0.5, 1.0],
-]
-
[…]

### 2020-05-13 python/test_analytic.py

@@ -1,39 +1,0 @@
-from test_utils import compare
-from cases import CASE
-from numerical import Numerical
-from starrynight import StarryNight
-import numpy as np
-import pytest
-
-# Params
-ydeg = 5
-S = StarryNight(ydeg)
-N = Numerical(ydeg)
-args = CASE[1] + CASE[2] + CASE[3] + CASE[4] + CASE[5]
-
-
-@pytest.mark.parametrize(
-    "b,theta,bo,ro", args,
-)
-def test_P(b, theta, bo, ro):
-    N.precompute(b, theta, bo, ro)
-    S.precompute(b, theta, bo, ro)
-    compare(N.P, S.P)
-
-
-@pytest.mark.parametrize(
-    "b,theta,bo,ro", args,
-)
-def test_T(b, theta, bo, ro):
-    N.precompute(b, theta, bo, ro)
-    S.precompute(b, theta, bo, ro)
-    compare(N.T, S.T)
-
-
-@pytest.mark.parametrize(
-    "b,theta,bo,ro", args,
-)
-def test_Q(b, theta, bo, ro):
-    N.precompute(b, theta, bo, ro)
-    S.precompute(b, theta, bo, ro)
-    compare(N.Q, S.Q)

### 2020-05-13 python/test_derivs.py

@@ -1,346 +1,0 @@
-import numpy as np
-from special import J, pal, EllipF, EllipE, EllipJ, el2, rj
-from primitive import compute_Q
-from geometry import get_roots
-import matplotlib.pyplot as plt
-from tqdm import tqdm
-
-# DEBUG
-if __name__ == "__main__":
-
-    from mpmath import ellipf, ellipe, ellippi
-
-    phi = 1.3
-    bo = 0.95
-    ro = 0.1
-
-    # What starry computes anyways
-    k2 = (1 - ro ** 2 - bo ** 2 + 2 * bo * ro) / (4 * bo * ro)
-    k = np.sqrt(k2)
-    kinv = 1 / k
-    k2inv = 1 / k2
-    kc2 = 1 - k2
-    tanphi = np.tan([phi])
-    if k2 < 1:
-        F = EllipF(tanphi, k2)[0] * k
-        E = kinv * (EllipE(tanphi, k2)[0] - kc2 * kinv * F)
-    else:
-        F = EllipF(tanphi, k2inv)[0]
-        E = EllipE(tanphi, k2inv)[0]
-    p = (ro * ro + bo * bo + 2 * ro * bo * np.cos(phi)) / (
-        ro * ro + bo * bo - 2 * ro * bo
-    )
-    cx = np.cos(phi / 2)
-    sx = np.sin(phi / 2)
-    w = 1 - cx ** 2 / k2
-    RJ = (np.cos(phi) + 1) * cx * rj(w, sx * sx, 1.0, p)
-
-    #
-
-    # Deriv with respect to n
-    n = -4 * bo * ro / (ro - bo) ** 2
-    phip = (phi - np.pi) / 2
-    kp = np.sqrt(1 / k2)
-    kp2 = 1 / k2
-    tanphi_ = np.array([-cx / (k * np.sqrt(w))])
-    F_ = k * EllipF(tanphi_, k2)[0]  # = ellipf(phip, kp2)
-    E_ = kinv * (EllipE(tanphi_, k2)[0] - kc2 * kinv * F_)  # = ellipe(phip, kp2)
-    PI_ = -n * RJ / 6 + F_  # = ellippi(n, phip, kp2)
-    s2 = np.sin(phip) ** 2
-    s_2 = np.sin(2 * phip)
-    dPIdn = (
-        1
-        / (2 * (kp2 - n) * (n - 1))
-        * (
-            E_
-            + (kp2 - n) / n * F_
-            + (n * n - kp2) / n * PI_
[…]

### 2020-05-13 python/test_lightcurve.py

@@ -1,80 +1,0 @@
-from starrynight import StarryNight
-from viz import visualize
-from numerical import Brute
-import numpy as np
-import pytest
-from tqdm import tqdm
-import matplotlib.pyplot as plt
-from scipy.interpolate import interp1d
-
-
-@pytest.mark.parametrize(
-    "b,theta,ro",
-    [
-        [0.25, np.pi / 3, 0.3],
-        [-0.25, np.pi / 3, 0.3],
-        [0.25, -np.pi / 3, 0.3],
-        [-0.25, -np.pi / 3, 0.3],
-        [0.25, 2 * np.pi / 3, 0.3],
-        [-0.25, 2 * np.pi / 3, 0.3],
-        [0.25, 4 * np.pi / 3, 0.3],
-        [-0.25, 4 * np.pi / 3, 0.3],
-        [0.5, np.pi / 2, 1.0],
-        [0.0, 0.0, 0.5],
-        [0.5, 0.0, 0.1],
-        [1.0 - 1e-3, 0.0, 0.5],
-        [-1.0 + 1e-3, 0.0, 0.5],
-        [-1.0, 0.0, 0.5],
-        [1.0, 0.0, 0.5],
-        [0.25, np.pi / 2, 0.5],
-    ],
-)
-def test_lightcurve(b, theta, ro, y=[1], ns=1000, nb=50, res=999, plot=True):
-
-    # Array over full occultation, including all singularities
-    bo = np.linspace(0, 1 + ro, ns, endpoint=True)
-    for pt in [ro, 1, 1 - ro, b + ro]:
-        if pt >= 0:
-            bo[np.argmin(np.abs(bo - pt))] = pt
-
-    # Setup
-    ydeg = int(np.sqrt(len(y)) - 1)
-    flux = np.zeros_like(bo)
-    flux_num = np.zeros_like(bo) * np.nan
-    map = StarryNight(ydeg)
-    map_num = Brute(ydeg, res=res)
-    computed = np.zeros(ns, dtype=bool)
-
-    # Compute
-    for i, boi in tqdm(enumerate(bo), total=len(bo)):
-        flux[i] = map.flux(y, b, theta, boi, ro)
-        if (i == 0) or (i == ns - 1) or (i % (ns // nb) == 0):
-            flux_num[i] = map_num.flux(y, b, theta, boi, ro)
-            computed[i] = True
-
-    # Fix baseline in numerical result
-    map_num.res = 4999
[…]

### 2020-05-13 python/test_mc.py

@@ -1,42 +1,0 @@
-from numerical import Numerical, Brute
-import numpy as np
-import pytest
-
-# Settings
-seed = 0
-nruns = 100
-atol = 1e-2
-res = 999
-ydeg = 1
-y = [1, 1, 1, 1]
-
-N = Numerical(ydeg)
-B = Brute(ydeg, res=res)
-
-
-def get_args():
-    bo = 0
-    ro = 2
-    while (bo <= ro - 1) or (bo >= 1 + ro):
-        if np.random.random() > 0.5:
-            ro = np.random.random() * 10
-            bo = np.random.random() * 20
-        else:
-            ro = np.random.random()
-            bo = np.random.random() * 2
-    theta = np.random.random() * 2 * np.pi
-    b = 1 - 2 * np.random.random()
-    return b, theta, bo, ro
-
-
-np.random.seed(seed)
-args = [get_args() for n in range(nruns)]
-
-
-@pytest.mark.parametrize(
-    "b,theta,bo,ro", args,
-)
-def test_mc(b, theta, bo, ro):
-    assert np.allclose(
-        N.flux(y, b, theta, bo, ro), B.flux(y, b, theta, bo, ro), atol=atol
-    )

### 2020-05-13 python/test_numerical.py

@@ -1,52 +1,0 @@
-from cases import CASE
-from numerical import Numerical, Brute
-import numpy as np
-import pytest
-
-
-ydeg = 1
-y = [1, 1, 1, 1]
-N = Numerical(ydeg)
-B = Brute(ydeg, res=4999)
-
-
-def run(b, theta, bo, ro):
-    assert np.allclose(
-        N.flux(y, b, theta, bo, ro), B.flux(y, b, theta, bo, ro), atol=0.002
-    )
-
-
-@pytest.mark.parametrize("b,theta,bo,ro", CASE[0])
-def test_simple(b, theta, bo, ro):
-    """Test cases where the occultor does not touch the terminator."""
-    run(b, theta, bo, ro)
-
-
-@pytest.mark.parametrize("b,theta,bo,ro", CASE[1])
-def test_PQT(b, theta, bo, ro):
-    """Test cases involving the three primitive integrals."""
-    run(b, theta, bo, ro)
-
-
-@pytest.mark.parametrize("b,theta,bo,ro", CASE[2])
-def test_PT(b, theta, bo, ro):
-    """Test cases involving only the P and T primitive integrals."""
-    run(b, theta, bo, ro)
-
-
-@pytest.mark.parametrize("b,theta,bo,ro", CASE[3])
-def test_triple(b, theta, bo, ro):
-    """Test cases with three points of intersection b/w occultor and terminator."""
-    run(b, theta, bo, ro)
-
-
-@pytest.mark.parametrize("b,theta,bo,ro", CASE[4])
-def test_quadruple(b, theta, bo, ro):
-    """Test cases with four points of intersection b/w occultor and terminator."""
-    run(b, theta, bo, ro)
-
-
-@pytest.mark.parametrize("b,theta,bo,ro", CASE[5])
-def test_edge_cases(b, theta, bo, ro):
-    """Test various edge cases."""
-    run(b, theta, bo, ro)

### 2020-05-13 python/test_utils.py

@@ -1,18 +1,0 @@
-import numpy as np
-
-
-def compare(expected, got):
-    ydeg = int(np.sqrt(len(expected)) - 1)
-    errors = []
-    n = 0
-    for l in range(ydeg + 1):
-        for m in range(-l, l + 1):
-            if not np.allclose(expected[n], got[n]):
-                errors.append(
-                    "ERROR for (l, m) = ({:2d}, {:2d}): expected {:11.8f}, got {:11.8f}.".format(
-                        l, m, expected[n], got[n]
-                    )
-                )
-            n += 1
-
-    assert not errors, "\n{}".format("\n".join(errors))

### 2020-05-13 tex/figures/cases.py

@@ -1,4 +1,4 @@
-from code import *
+from support_code import *
 import numpy as np
 import matplotlib.pyplot as plt
 

### 2020-05-13 tex/figures/geometry.py

@@ -1,4 +1,4 @@
-from code import visualize
+from support_code import visualize
 import numpy as np
 import matplotlib.pyplot as plt
 

### 2020-05-14 tex/ms.tex
finished proof
fixed several typos in rT
fixed one more in rT
added new proof
added proof
new proof

@@
 %
-\begin{proof}{}
+\begin{proof}{illumination}
     \label{eq:ivec}
@@
 %
-\begin{proof}{}
+\begin{proof}{illumination}
     \label{eq:Imat}
@@
 %
-\begin{proof}{}
+\begin{proof}{PhaseCurve}
     \label{eq:rTsoln}
@@
     \begin{cases}
-        \frac{\left(1 - b^{\frac{\nu + 4}{2}}\right)}{2}
-        \mathbb{L}_{\frac{\mu}{2}, \frac{\nu + 2}{2}}
+        \frac{\left(1 - b^{\frac{\nu + 2}{2}}\right)}{2}
+        \mathbb{L}_{\frac{\mu}{2}, \frac{\nu}{2}}
         %
@@
         \qquad
-        \mu, \nu \ \text{even}
+        \frac{\mu}{2} \ \text{even}
         %
@@
         %
-        \mathbb{k}_{\frac{\nu + 1}{2}}(b) \mathbb{M}_{\frac{\mu - 1}{2}, \frac{\nu + 1}{2}}
+        \mathbb{k}_{\frac{\nu - 1}{2}}(b) \mathbb{M}_{\frac{\mu - 1}{2}, \frac{\nu - 1}{2}}
+        %
+         &
+        %
+        \qquad
+        \frac{\mu - 1}{2} \ \text{even}
+        %
+        \\[1em]
+        %
+        0
         %
@@
         \text{otherwise}
-        %
     \end{cases}
@@
 %
-\begin{proof}{}
+\begin{proof}{PhaseCurve}
     \label{eq:HJK}
@@
 \begin{minipage}{.33\linewidth}
-    \begin{proof}{}
+    \begin{proof}{PhaseCurve}
         \label{eq:IJK0}
@@
 %
-we may compute all higher order terms from the recurrence relations
-%
-\begin{proof}{}
+we may compute all the required higher order terms from the recurrence relations
+%
+\begin{proof}{PhaseCurve}
     \label{eq:IJKrec}
-    \mathbb{k}_{j}(b) &= \frac{b^n b_c^3 + (j - 1) \mathbb{k}_{j - 2}(b)}{j + 2}
+    \mathbb{k}_{j}(b) &= \frac{b^{j-1} b_c^3 + (j - 1) \mathbb{k}_{j - 2}(b)}{j + 2}
     %
@@
 %
-\begin{proof}{}
+\begin{align}
     \label{eq:f0hat}
-    \hat{f}_0 &=
+    \hat{f}_0 & =
     \Big(
@@
 %
-\begin{proof}{}
+\begin{proof}{quartic}
     y''_1(x'') & = b \sqrt{1 - x''^2}
@@
 %
-\begin{proof}{}
+\begin{proof}{quartic}
     x''_o = b_o\sin\theta'
@@
 %
-\begin{proof}{}
+\begin{proof}{quartic}
     \label{eq:quartic}
@@
 %
-\begin{proof}{}
+\begin{proof}{quartic}
     \label{eq:quartic-coeffs}
@@
 %
-\begin{proof}{}
+\begin{align}
     \label{eq:fI}
-    f_I &=
+    f_I & =
     \sTe(b_o, r_o)
@@
     \quad,
-\end{proof}
+\end{align}
 %
@@
 %
-\begin{proof}{}
+\begin{align}
     \label{eq:f3}
     f_3 = f_I
-\end{proof}
+\end{align}
 %
@@
     \label{eq:f4}
-    f_2 = f_0
+    f_4 = f_0
     \quad.
@@
 %
-\begin{proof}{}
+\begin{align}
     \label{eq:f5}
@@
     \quad.
-\end{proof}
+\end{align}
 
@@
 %
-\begin{proof}{}
+\begin{align}
     \label{eq:f6}
@@
 %
-\begin{proof}{}
+\begin{align}
     \label{eq:f7}
@@
     \quad.
-\end{proof}
-%
-Case 8, on the other hand, is topologically equivalent to case 6, since
+\end{align}
+%
+Case 8, on the other hand, is equivalent to case 6, since
 the integration region consists of occulted dayside:
 %
-\begin{proof}{}
+\begin{align}
     \label{eq:f8}
@@
 %
-\begin{proof}{}
+\begin{align}
     \label{eq:f9}
@@
 %
-\begin{proof}{}
+\begin{align}
     \label{eq:f10}
@@
 Cases 11--14 correspond to (rare) configurations involving three
-or four roots to Equation~\ref{eq:quartic} and are
+or four roots to Equation~(\ref{eq:quartic}) and are
 illustrated in Figure~\ref{fig:pathological}. All four involve integration over
@@
 %
-\begin{proof}{}
+\begin{align}
     \label{eq:f11}
@@
 %
-\begin{proof}{}
+\begin{align}
     \label{eq:f12}
@@
 %
-\begin{proof}{}
+\begin{align}
     \label{eq:f13}
@@
 %
-\begin{proof}{}
+\begin{align}
     \label{eq:f14}
@@
 %
-\begin{proof}{}
+\begin{proof}{Greens}
     \label{eq:sT}
@@
 %
-\begin{proof}{}
+\begin{proof}{Greens}
     \label{eq:pT}
@@
 \begin{minipage}{0.3\linewidth}
-    \begin{proof}{}
+    \begin{proof}{Greens}
         \label{eq:xy_pqt}
@@
 %
-\begin{align}
+\begin{proof}{pT}
     \phi_0 & =
@@
     \quad,
-\end{align}
+\end{proof}
 %
@@
 %
-\begin{align}
+\begin{proof}{pT}
     \pmb{\phi_1} & =
@@
     \atantwo
-    \left(b\sqrt{1 - {\mathbf{x''}}^2 - y''_o}, \mathbf{x''} - x''_o\right)
+    \left(b\sqrt{1 - {\mathbf{x''}}^2} - y''_o, \mathbf{x''} - x''_o\right)
     \quad
-\end{align}
+\end{proof}
 %
@@
 %
-\begin{proof}{}
+\begin{proof}{pT}
     \label{eq:pTsoln}
@@
                     \left(
-                    \frac{\mu + 2}{2},
+                    \frac{\mu + 2}{4},
                     \frac{\nu}{2},
@@
                         %
-                         & \qquad \quad
+                         & \qquad \quad  \enspace
                         l \, \text{even}
@@
                         %
-                         & \qquad \quad
+                         & \qquad \quad  \enspace
                         l \, \text{odd} \ne 1
@@
 %
-\begin{align}
+\begin{proof}{pT}
     \label{eq:V}
@@
     \mathcal{A}_{u, v, i}
-    \mathbf{x}_{u + w + i}
-\end{align}
+    x_{u + w + i}
+\end{proof}
 %
@@
 %
-\begin{align}
+\begin{proof}{pT}
     \label{eq:vieta}
@@
     \quad.
-\end{align}
+\end{proof}
 %

### 2020-05-14 tex/ms.tex
added proof

@@
 %
-\begin{proof}{}
+\begin{proof}{tT}
     \pmb{\xi_0} &=
@@
 %
-\begin{proof}{}
+\begin{proof}{tT}
     \xi_1 &=
@@
 The solution to Equation~(\ref{eq:tT}) involves repeated application
-of the binomial theorem. As before, we simply present the result, with
-validation links:
-%
-\begin{proof}{}
+of the binomial theorem. The result is given on the following
+page in Equation~(\ref{eq:tn}) along with the usual validation link,
+where we define
+%
+\begin{proof}{tT}
+    \label{eq:Zuvjk}
+    Z^{u,v}_{j,k}(b, \theta') & =
+    \binom{u}{j}
+    \binom{v}{k}
+    (-1)^{v-k}
+    b^{u+v-j-k}
+    \sin^{v+j-k}\theta'
+    \cos^{u-j+k}\theta'
+    \nonumber
+    \\
+    \intertext{and}
+    %
+    \delta(b, \xi) & =
+    \begin{cases}
+        0               & \qquad 0 \leq \xi < \frac{\pi}{2}     \\
+        \pi             & \qquad \frac{\pi}{2} \leq \xi < \pi   \\
+        2 |b| b_c       & \qquad \pi \leq \xi < \frac{3\pi}{2}  \\
+        \pi + 2 |b| b_c & \qquad \frac{3\pi}{2} \leq \xi < 2\pi
+        \quad.
+    \end{cases}
+\end{proof}
+%
+\afterpage{
+    \begin{proof}{tT}
+        \label{eq:tn}
+        \tag{\ref*{eq:Zuvjk}*}
         \mathbb{t}_n & =
@@
             %
-        -b\sin\theta'
+            -bb_c^3\sin\theta'
             \sum\limits_{j=0}^{l-2}
-        Z^{0, l-2}_{0,k}
+            Z^{0, l-2}_{0,j}
             (b, \theta') \,
@@
             \quad\quad\quad\quad
-        - \, \cos\theta'
+            - \, b_c^3\cos\theta'
             \sum\limits_{j=0}^{l-2}
-        Z^{0, l-2}_{0,k}
+            Z^{0, l-2}_{0,j}
             (b, \theta') \,
@@
             %
-        -b\sin\theta'
+            -bb_c^3\sin^2\theta'
             \sum\limits_{j=0}^{l-3}
-        \bigg(
-        \sin\theta'
-        Z^{0, l-3}_{0,k}
+            Z^{0, l-3}_{0,j}
             (b, \theta') \,
@@
             \\
-        \qquad\qquad\qquad
-        +
-        \, b\cos\theta'
+            \quad\quad\quad\quad
+            - \, b b_c^3\cos^2\theta'
+            \sum\limits_{j=0}^{l-3}
+            Z^{0, l-3}_{0,j}
+            (b, \theta') \,
+            \iH_{j, l + 2 - j}(\pmb{\xi})
+            %
+            %
+             & \qquad
+            \mathrel{\raisebox{0em}{$\nu \, \text{odd}, \mu = 1, l \, \text{odd}$}}
+            %
+            \\
+            \quad\quad\quad\quad
+            - \, b_c^5\sin\theta'\cos\theta'
+            \sum\limits_{j=0}^{l-3}
             Z^{0, l-3}_{0,k}
@@
             \iH_{j + 1, l + 1 - j}(\pmb{\xi})
-        \bigg)
-        \\
-        \quad\quad\quad\quad
-        - \, \cos\theta'
-        \sum\limits_{j=0}^{l-3}
-        \bigg(
-        \sin\theta'
-        Z^{0, l-3}_{0,k}
-        (b, \theta') \,
-        \iH_{j + 1, l + 1 - j}(\pmb{\xi})
-        %
-         & \qquad
-        \mathrel{\raisebox{1.25em}{$\nu \, \text{odd}, \mu = 1, l \, \text{odd}$}}
-        %
-        \\
-        \qquad\qquad\qquad
-        +
-        \, b\cos\theta'
-        Z^{0, l-3}_{0,k}
-        (b, \theta') \,
-        \iH_{j, l + 2 - j}(\pmb{\xi})
-        \bigg)
             %
@@
             \\[3em]
-        b\cos\theta'
+            bb_c^3\cos\theta'
             \sum\limits_{j=0}^{\frac{\nu}{2}}
@@
             \quad\quad\quad\quad
-        - \, \sin\theta'
+            - \, b_c^3\sin\theta'
             \sum\limits_{j=0}^{\frac{\nu}{2}}
@@
     \end{proof}
-%
-where we define
-%
-\begin{proof}{}
-    Z^{u,v}_{j,k}(b, \theta') & =
-    \binom{u}{j}
-    \binom{v}{k}
-    (-1)^{v-k}
-    b^{u+v-j-k}
-    \sin^{v+j-k}\theta'
-    \cos^{u-j+k}\theta'
-\end{proof}
-%
-and
-%
-\begin{proof}{}
-    \delta(b, \xi) & =
-    \begin{cases}
-        0               & \qquad 0 \leq \xi < \frac{\pi}{2}     \\
-        \pi             & \qquad \frac{\pi}{2} \leq \xi < \pi   \\
-        2 |b| b_c       & \qquad \pi < \xi \leq \frac{3\pi}{2}  \\
-        \pi + 2 |b| b_c & \qquad \frac{3\pi}{2} \leq \xi < 2\pi
-        \quad.
-    \end{cases}
-\end{proof}
-%
-The components of the matrix $\viH$ are given by the integral
+    \vfill
+}
+%
+The solution to Equation~(\ref{eq:tn}) depends on the matrix
+$\viH$, whose components are given by the integral
 %
@@
 %
-This integral is the same as that in Equation (D27)
+The $\viH$ integral is the same as that in Equation (D27)
 of \citet{Luger2019}, except for a change in the limits of integration.

### 2020-05-14 tex/ms.tex
added final proof
added co-authors

@@
 \title{%
+    \textbf{
         Analytic Light Curves in Reflected Light:%
@@
     }
+}
 
 % Author list
-\author[0000-0002-0296-3826]{Rodrigo Luger}
+\author[0000-0002-0296-3826]{Rodrigo Luger}\altaffiliation{Flatiron Fellow}
 \email{rluger@flatironinstitute.org}
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
-%
+\affil{Virtual~Planetary~Laboratory, University~of~Washington, Seattle, WA}
+%
+\author[0000-0002-0802-9145]{Eric Agol}
+\affil{Department~of~Astronomy, University~of~Washington, Seattle, WA}
+\affil{Virtual~Planetary~Laboratory, University~of~Washington, Seattle, WA}
+%
+\author[0000-0001-8630-9794]{Fran Bartoli\'c}
+\affil{Centre for Exoplanet Science, University of St. Andrews, St. Andrews, UK}
+\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
+%
+\author[0000-0002-9328-5652]{Daniel Foreman-Mackey}
+\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
 
@@
 solar system. Mutual occultations among the Galilean moons of Jupiter
-have been studied to infer surface properties of Io \xxx{...more on this,
-    and add citations.}
+have been studied to infer surface properties of Io
+\xxx{\textbf{Fran:}... more on this, and add citations.}
 
@@
 and computing the relevant integrals by summing over the visible
-pixels \xxx{(cite)}. Recently, \citet{Haggard2018} developed an analytic
+pixels \citep[e.g.,][]{Kawahara2010,Fujii2012}.
+Recently, \citet{Haggard2018} developed an analytic
 framework for computing light curves of unocculted bodies illuminated
@@
             \citet{OrenNayar1994} scattering law, and orbital
-            information from the JPL Horizons \xxx{(cite)} database.
+            information from the JPL Horizons database.
             See text for details.
@@
 campaign \citep{Arlot2014}. The trajectory of Europa relative to Io,
-computed from the JPL Horizons database \xxx{(cite)}
+computed from the \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database}
 is shown at the top. We fit to this data a \starry occultation model
@@
 that color information can greatly help in the interpretation of
-reflected phase curves \xxx{(cite)}, while others
+reflected phase curves \citep{Cowan2009,Kawahara2011,LustigYaeger2018,Kawahara2020}, while others
 have explored in detail the best kinds of priors to assume
@@
 The code used to generate the figures in this paper is hosted
-at \url{https://github.com/rodluger/starrynight}, with a permanent
-version archived at \xxx{https://doi.org/XX.XXXX/zenodo.XXXXXXX}.
+at \url{https://github.com/rodluger/starrynight}.
+% --- TODO ---
+% with a permanent
+% version archived at \url{https://doi.org/XX.YYYY/zenodo.ZZZZZZZ}.
 
 \software{
+    astroquery \citep{astroquery},
     Eigen v3 \citep{eigen},
@@
 sphere of spherical albedo $A$ \citep[see, e.g.][]{Seager2010}.
-\xxx{Is this explanation sufficient? Why does it matter that this
+\xxx{\textbf{Eric:} Is this explanation sufficient? Why does it matter that this
     is the geometric albedo of a Lambert sphere?}
@@
 and the latter (of which there may be multiple) is given by
-%
-% Introduce the function
-% %
-% \begin{proof}{}
-%     \textrm{\faAdjust}(x, y) &=
-%     \begin{cases}
-%         \textrm{\faCircleO} & \qquad -x \sin\theta' + y\cos\theta' \ge b \sqrt{1 - (x\cos\theta' + y\sin\theta') ^ 2}
-%         \\
-%         \textrm{\faCircle}  & \qquad \text{otherwise}
-%     \end{cases}
-% \end{proof}
-% %
-% which returns \faCircleO\ if point $(x, y)$ is on the dayside of the body and
-% \faCircle\ if it is on the nightside.
-%
 %
@@
 %
-\begin{proof}{}
+\begin{proof}{qT}
     \lambda_0 &=
@@
 %
-\begin{proof}{}
+\begin{proof}{qT}
     \lambda_1 & =
@@
 %
-\begin{proof}{}
+\begin{proof}{qT}
     \mathbb{q}_n &=

### 2020-05-18 tex/ms.tex

@@
         \\%
-        Phase Curves, Occultations, and Non-Lambertian Scattering
+        Phase Curves, Occultations, and Non-Lambertian Scattering for Spherical Planets
     }
@@
     We derive efficient, closed form, differentiable, and numerically stable
-    solutions for the flux measured from a planet or moon seen in reflected
+    solutions for the flux measured from a spherical planet or moon seen in reflected
     light, either in our out of occultation.
@@
 
-There is a vast literature on techniques for mapping exoplanet surfaces
+There is an extensive literature on techniques for mapping spherical exoplanet surfaces
 based on their phase curves
@@
 %
-\citet{Cowan2009} analyzed visible-light disk-integrated light curves
+\citet{Cowan2009} and \citet{Cowan2011b} analyzed visible-light disk-integrated light curves
 of the Earth taken by the Deep Impact spacecraft to produce
@@
 to disentangle static surface brightness features from temporally
-variable clouds. More recently, \citet{Jiang2018} and \citet{Fan2019}
+variable clouds.  A transit of Earth by the Moon was observed
+as well \citep{Livengood2011}, although this data has yet to be
+exploited for mapping purposes.
+More recently, \citet{Jiang2018} and \citet{Fan2019}
 used data from the L1-stationed DSCOVR satellite to infer surface
@@
 \href{https://dev.azure.com/rodluger/starry/_test/analytics?definitionId=4}{unit-tested},
-and supplemmented with an extensive
+and supplemented with an extensive
 \href{https://rodluger.github.io/starry}{API documentation}
@@
 powerful way to not only map terrestrial planets but also to confirm
-their habitability via the presence of an ocean.
+their habitability via the presence of an ocean.  Finally, the presence
+of time-variable features, such as clouds, dust storms, or seasonal
+variations of vegetation are not accounted for in the model.
 
@@
 in the case of the latter three, a bit of algebra
-(\S\ref{sec:cases-pathological}--\S\ref{sec:cases-pathological}) is needed
+(\S\ref{sec:cases-hard}--\S\ref{sec:cases-pathological}) is needed
 to relate these to the observed flux. Additionally, in some cases we can
@@
 
-Cases with zero roots (case 1 -- case 4) are treated in \S\ref{sec:cases-easy},
-while cases with one or two roots (case 5 -- case 8) are treated in
+Cases with zero roots (case 1 -- case 5) are treated in \S\ref{sec:cases-easy},
+while cases with one or two roots (case 6 -- case 10) are treated in
 \S\ref{sec:cases-hard}. Cases with three or four roots
-(case 9 -- case 10) are rarely encountered
+(case 11 -- case 14) are rarely encountered
 in practice, but are possible for some pathological configurations; these are
@@
 separately due to the fact that the corresponding antiderivative
-in Equation~(\ref{eq:G}) is not a polynomial in $x$, $y$, and $z(x, y)$.
+in Equation~(\ref{eq:G}) is not a polynomial in $x$, $y$, and $z(x, y)$;
+also see \citet{Agol2020}.
 The integral we must solve is

### 2020-05-19 tex/ms.tex
misc

@@
 the visible portion of the stellar disk. While this integral may in theory be
-computed analytically, the resulting profile on the planet surface
+computed analytically
+\citep[see, for instance,][who derived series solutions to this problem]{Kopal1954},
+the resulting profile on the planet surface
 will not in general be exactly expressible in terms of spherical harmonics, a
@@
 \end{figure}
-
-Figure~\ref{fig:kelt9b} shows the practical implications of the finite
-stellar size for the phase curve of Kelt-9b. The left panel shows the
-reflected light phase curve of the planet in parts per million, assuming
-a spherical albedo of 0.2, for the point source approximation
-(blue) and including the effect of the extended source with
-\textsf{source\_npts} = 300 (purple). The increased
-illumination at the sub-stellar point results in a ${\sim}30$ increase
-in the value of the phase curve close to full phase ($\pm\nicefrac{1}{2}$).
-Close to a phase of zero, the extended source results in decreased
-flux, since the portion of the star illuminating the planet (the region
-close to the limb) is slightly
-\emph{farther} away, by a factor of
-$\sqrt{1 + (\nicefrac{a}{R_\star})^{-2}}$. This results in a steeper
-phase curve, which can be seen in the right panel, where the light curves
-have been normalized to their maximum value.
-
+%
 \begin{figure}[p!]
@@
 \end{figure}
+
+Figure~\ref{fig:kelt9b} shows the practical implications of the finite
+stellar size for the phase curve of Kelt-9b. The left panel shows the
+reflected light phase curve of the planet in parts per million, assuming
+a spherical albedo of 0.2, for the point source approximation
+(blue) and including the effect of the extended source with
+\textsf{source\_npts} = 300 (purple). The increased
+illumination at the sub-stellar point results in a ${\sim}30$ increase
+in the value of the phase curve close to full phase ($\pm\nicefrac{1}{2}$).
+Close to a phase of zero, the extended source results in decreased
+flux, since the portion of the star illuminating the planet (the region
+close to the limb) is slightly
+\emph{farther} away, by a factor of
+$\sqrt{1 + (\nicefrac{a}{R_\star})^{-2}}$. This results in a steeper
+phase curve, which can be seen in the right panel, where the light curves
+have been normalized to their maximum value.
 

### 2020-05-19 tex/figures/earthmoon.py

@@ -113,7 +113,7 @@ for reflected in (True, False):
         ax_im[n].set_rasterization_zorder(0)
 
         # Compute the numerical flux by discretely summing over the unocculted region
-        x, y, z = map_e.ops.compute_ortho_grid(res)
+        (lat, lon), (x, y, z) = map_e.ops.compute_ortho_grid(res)
         if reflected:
             img = map_r.render(xs=xs[i], ys=ys[i], zs=zs[i], theta=theta[i], res=res)
         else:

### 2020-05-19 tex/figures/earthphase.py

@@ -89,7 +89,7 @@ for n in range(nim):
 
     # Inset view of the phase curve: numerical
     theta_in = np.linspace(0, 360, 10)
-    x, y, z = map.ops.compute_ortho_grid(res)
+    (lat, lon), (x, y, z) = map.ops.compute_ortho_grid(res)
     img = map.render(theta=theta_in, xs=xs[i], ys=ys[i], zs=zs[i], res=res)
     F = np.nansum(img, axis=(1, 2)) * 4 / res ** 2
     F /= maxF

### 2020-05-19 tex/figures/earthsun.py

@@ -104,7 +104,7 @@ for reflected in (True, False):
         ax_im[n].set_rasterization_zorder(0)
 
         # Compute the numerical flux by discretely summing over the unocculted region
-        x, y, z = map_e.ops.compute_ortho_grid(res)
+        (lat, lon), (x, y, z) = map_e.ops.compute_ortho_grid(res)
         if reflected:
             img = map_r.render(xs=xo[i], ys=yo[i], zs=zo[i], theta=theta, res=res)
         else:

### 2020-05-19 tex/figures/speed.py

@@ -224,7 +224,7 @@ class Compare(object):
     def flux_brute(self, xs, ys, zs, xo, yo, ro, res=999, **kwargs):
         # Compute the flux by brute force grid integration
         img = self.map_ref.render(xs=xs, ys=ys, zs=zs, res=res)
-        x, y, z = self.map_ref.ops.compute_ortho_grid(res)
+        (lat, lon), (x, y, z) = self.map_ref.ops.compute_ortho_grid(res)
         idx = (x - xo) ** 2 + (y - yo) ** 2 > ro ** 2
         return np.nansum(img.flat[idx]) * 4 / res ** 2, np.nan
 
@@ -267,7 +267,7 @@ class Compare(object):
         img = self.map_ref.render(xs=xs, ys=ys, zs=zs, res=res)
 
         # Mask the occultor
-        x, y, z = self.map_ref.ops.compute_ortho_grid(res)
+        (lat, lon), (x, y, z) = self.map_ref.ops.compute_ortho_grid(res)
         idx = (x - xo) ** 2 + (y - yo) ** 2 <= ro ** 2
         img.flat[idx] = HUGE
 

### 2020-05-19 tex/ms.tex
precise -> accurate

@@
     numerical evaluation methods and ${\sim}10$ orders of magnitude more
-    precise.
+    accurate.
     %
@@
             light algorithm. It is ${\sim}5$ orders of magnitude faster
-            and ${\sim}10$ orders of magnitude more precise than numerical
+            and ${\sim}10$ orders of magnitude more accurate than numerical
             integration.
@@
             The reflected light algorithm is around one
-            order of magnitude slower and comparably precise to the emitted
+            order of magnitude slower and comparably accurate to the emitted
             light algorithm. It is ${\sim}4$ orders of magnitude faster
-            and ${\sim}10$ orders of magnitude more precise than numerical
+            and ${\sim}10$ orders of magnitude more accurate than numerical
             integration.
@@
 \textbf{4--5 orders of magnitude faster} and about
-\textbf{10 orders of magnitude more precise}. While different
+\textbf{10 orders of magnitude more accurate}. While different
 grid sizes and different error settings for the numerical integration change
 the balance slightly between these numbers, the \starry solution is always
-many orders of magnitude faster and more precise than either method.
+many orders of magnitude faster and more accurate than either method.
 In particular, because of the complicated integration boundaries
@@
 The algorithm is ${\sim}4-5$ orders of magnitude faster
-and ${\sim}10$ orders of magnitude more precise than other numerical
+and ${\sim}10$ orders of magnitude more accurate than other numerical
 approaches for computing these light curves. The algorithm is

### 2020-05-19 tex/ms.tex
Update ms.tex

@@
 expressions and code them within an autodifferentiation framework
-to enable the computation of high precision derivatives for use in
+to enable the computation of accurate derivatives for use in
 gradient-based inference and optimization schemes.
@@
 using our algorithm, validate it against numerical integration, and
-discuss its performance in terms of computational speed and precision.
+discuss its performance in terms of computational speed and accuracy.
 In \S\ref{sec:extensions} we extend the model to apply to illumination
@@
 The models agree to within the
-numerical precision of the brute force solution (about 100 ppm of the
+numerical accuracy of the brute force solution (about 100 ppm of the
 planetary flux in this case).
@@
 As before, the light curves computed using \starry agree to within the
-numerical precision of the brute force solution.
+numerical accuracy of the brute force solution.
 
@@
 expressions numerically, especially when doing so
-leads to either a speed-up or a significant gain in numerical precision.
+leads to either a speed-up or a significant gain in numerical accuracy.
 In particular, as we discuss in Appendix~\ref{sec:which-case}, the
@@
             Evaluation time (vertical axis)
-            and numerical precision (point size)
+            and numerical accuracy (point size)
             for a single flux evaluation in the absence of an occultor
@@
             evaluations. The reflected light algorithm is
-            comparable in efficiency and precision to the emitted
+            comparable in efficiency and accuracy to the emitted
             light algorithm. It is ${\sim}5$ orders of magnitude faster
@@
 Figures~\ref{fig:speed_no_occ} and \ref{fig:speed} summarize
-the precision and computation time of the \starry algorithm for
+the accuracy and computation time of the \starry algorithm for
 two typical scenarios: a phase curve evaluation
@@
 %
-In terms of precision, the algorithms are comparable, particularly
+In terms of accuracy, the algorithms are comparable, particularly
 for occultations. For both phase curves and occultations, the numerical error up
@@
 (see, for example, Figure~\ref{fig:cases}), two-dimensional Gaussian quadrature
-struggles to reach adequate precision in a reasonable amount of time,
+struggles to reach adequate accuracy in a reasonable amount of time,
 while integration on a grid fails to capture the curvature of the
@@
 grid of input parameter values, and verified that the solutions agree
-to within the precision of the numerical method.
+to within the accuracy of the numerical method.
 %
@@
 analytically from Equation~(\ref{eq:Jrec}),
-in practice we achieve better precision via numerical
+in practice we achieve better accuracy via numerical
 integration (as above), with negligible effects on computational performance.

### 2020-05-19 tex/ms.tex
Don't tell the reader how to feel

@@
 of the star will reach points on the planet surface beyond this angle.
-It is straightforward to show that, provided the stellar radius $R_\star$
+If the stellar radius $R_\star$
 is larger than the planet radius $R_p$, the angular extent of the true

### 2020-05-19 tex/ms.tex
tweaks

--- 2020-05-19 tex/ms.tex
@@
         \\%
-        Phase Curves, Occultations, and Non-Lambertian Scattering for Spherical Planets
+        Phase Curves, Occultations, and Non-Lambertian Scattering for
+        Spherical Planets and Moons
     }
@@
     numerical evaluation methods and ${\sim}10$ orders of magnitude more
-    accurate.
+    precise.
     %
@@
 solar system. Mutual occultations among the Galilean moons of Jupiter
-have been studied to infer surface properties of Io
-\xxx{\textbf{Fran:}... more on this, and add citations.}
+have been extensively studied to infer surface properties of the moons and to refine
+their ephemerides
+\citep[e.g.,][]{Arlot1974,Aksnes1984,Arlot2014,deKleer2017,Saquet2018,Morgado2019}.
+Farther out in the solar system,
+mutual occultations of Pluto and Charon in the late 1980s
+were used to confirm Charon's existence
+\citep{Stern1992},
+establish the sizes and orbital parameters of the two bodies
+\citep{Tholen1990},
+and infer their surface properties
+\citep{Marcialis1990}.
+In particular, \citet{Dunbar1986} developed an efficient analytic
+algorithm to model Pluto-Charon occultation light curves in reflected light
+assuming uniform surfaces and used it to infer the two body's
+average geometrical albedos. Later, \citet{Reinsch1994} analyzed
+the complete mutual occultation dataset to infer longitudinal maps of Pluto's
+albedo.
 
@@
             light algorithm. It is ${\sim}5$ orders of magnitude faster
-            and ${\sim}10$ orders of magnitude more accurate than numerical
+            and ${\sim}10$ orders of magnitude more precise than numerical
             integration.
@@
             The reflected light algorithm is around one
-            order of magnitude slower and comparably accurate to the emitted
+            order of magnitude slower and comparably precise to the emitted
             light algorithm. It is ${\sim}4$ orders of magnitude faster
-            and ${\sim}10$ orders of magnitude more accurate than numerical
+            and ${\sim}10$ orders of magnitude more precise than numerical
             integration.
@@
 \textbf{4--5 orders of magnitude faster} and about
-\textbf{10 orders of magnitude more accurate}. While different
+\textbf{10 orders of magnitude more precise}. While different
 grid sizes and different error settings for the numerical integration change
 the balance slightly between these numbers, the \starry solution is always
-many orders of magnitude faster and more accurate than either method.
+many orders of magnitude faster and more precise than either method.
 In particular, because of the complicated integration boundaries
@@
 computed from the \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database}
+using ephemerides from \citet{Folkner2014}
 is shown at the top. We fit to this data a \starry occultation model
@@
 The algorithm is ${\sim}4-5$ orders of magnitude faster
-and ${\sim}10$ orders of magnitude more accurate than other numerical
+and ${\sim}10$ orders of magnitude more precise than other numerical
 approaches for computing these light curves. The algorithm is
@@
 \software{
-    astroquery \citep{astroquery},
+    astroquery \citep{astroquery1,astroquery2},
     Eigen v3 \citep{eigen},
@@
     \theta = -\atantwo(x_s, y_s)
-    \quad.
-\end{proof}
-%
+    \quad,
+\end{proof}
+%
+where $\atantwo(a, b)$ is the quadrant-aware arctangent of
+$\nicefrac{a}{b}$.
 Given this formulation, and assuming that
@@
 sphere of spherical albedo $A$ \citep[see, e.g.][]{Seager2010}.
-\xxx{\textbf{Eric:} Is this explanation sufficient? Why does it matter that this
-    is the geometric albedo of a Lambert sphere?}
+%\xxx{\textbf{Eric:} Is this explanation sufficient? Why does it matter that this
+%    is the geometric albedo of a Lambert sphere?}
 

### 2020-05-19 tex/ms.tex
tiny tweaks

@@
 telescopes such as LUVOIR it is extremely unlikely we will do better than
-$l=20$. If we are ever able to probe resolutions smaller than
+$l=20$. If cases arise requiring a resolution smaller than about
 $180^\circ / 20 = 9^\circ$ on the surface, the \starry algorithm
@@
 powerful way to not only map terrestrial planets but also to confirm
-their habitability via the presence of an ocean.  Finally, the presence
+their habitability via the presence of an ocean.  Lastly, the presence
 of time-variable features, such as clouds, dust storms, or seasonal
-variations of vegetation are not accounted for in the model.
+variations of vegetation are not accounted for in the model, although
+the \href{https://rodluger.github.io/starry}{documentation} discusses
+how one may approach the modeling of temporal features.
 

### 2020-05-21 tex/ms.tex
typo

@@
 \textsf{source\_npts} = 300 (purple). The increased
-illumination at the sub-stellar point results in a ${\sim}30$ increase
+illumination at the sub-stellar point results in a ${\sim}30$ ppm increase
 in the value of the phase curve close to full phase ($\pm\nicefrac{1}{2}$).

### 2020-06-03 tex/ms.tex
Update ms.tex

--- 2020-05-19 tex/ms.tex
@@
         \\%
-        Phase Curves, Occultations, and Non-Lambertian Scattering for
-        Spherical Planets and Moons
+        Phase Curves, Occultations, and Non-Lambertian Scattering for Spherical Planets
     }
@@
 solar system. Mutual occultations among the Galilean moons of Jupiter
-have been extensively studied to infer surface properties of the moons and to refine
-their ephemerides
-\citep[e.g.,][]{Arlot1974,Aksnes1984,Arlot2014,deKleer2017,Saquet2018,Morgado2019}.
-Farther out in the solar system,
-mutual occultations of Pluto and Charon in the late 1980s
-were used to confirm Charon's existence
-\citep{Stern1992},
-establish the sizes and orbital parameters of the two bodies
-\citep{Tholen1990},
-and infer their surface properties
-\citep{Marcialis1990}.
-In particular, \citet{Dunbar1986} developed an efficient analytic
-algorithm to model Pluto-Charon occultation light curves in reflected light
-assuming uniform surfaces and used it to infer the two body's
-average geometrical albedos. Later, \citet{Reinsch1994} analyzed
-the complete mutual occultation dataset to infer longitudinal maps of Pluto's
-albedo.
+have been studied to infer surface properties of Io
+\xxx{\textbf{Fran:}... more on this, and add citations.}
 
@@
 therefore a probe of the condition number of the starry algorithm and
-captures only error due to numerical instabilities. For the numerical
+captures only error due to numerical instabilities.
+It is worth emphasizing that this is a measurement of the precision of
+the algorithm, rather than the accuracy, because it would be computationally
+intractable to compute a solution more accurate than this using a different
+algorithm.
+We argue that this measurement can be interpreted to mean that the algorithm
+is also accurate, but detailed quantification of this difference is beyond the
+scope of this paper.
+For the numerical
 solutions, the error is estimated as the difference between the numerical
@@
 computed from the \href{https://ssd.jpl.nasa.gov/horizons.cgi}{JPL Horizons database}
-using ephemerides from \citet{Folkner2014}
 is shown at the top. We fit to this data a \starry occultation model
@@
 \software{
-    astroquery \citep{astroquery1,astroquery2},
+    astroquery \citep{astroquery},
     Eigen v3 \citep{eigen},
@@
     \theta = -\atantwo(x_s, y_s)
-    \quad,
-\end{proof}
-%
-where $\atantwo(a, b)$ is the quadrant-aware arctangent of
-$\nicefrac{a}{b}$.
+    \quad.
+\end{proof}
+%
 Given this formulation, and assuming that
@@
 sphere of spherical albedo $A$ \citep[see, e.g.][]{Seager2010}.
-%\xxx{\textbf{Eric:} Is this explanation sufficient? Why does it matter that this
-%    is the geometric albedo of a Lambert sphere?}
+\xxx{\textbf{Eric:} Is this explanation sufficient? Why does it matter that this
+    is the geometric albedo of a Lambert sphere?}
 

### 2021-02-25 tex/gitlinks.tex
try to fix environment

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starrynight/blob/474eb00c5b87a26fb323129b3b73ea8e1b9dc20a/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starrynight/blob/474eb00c5b87a26fb323129b3b73ea8e1b9dc20a/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starrynight/blob/474eb00c5b87a26fb323129b3b73ea8e1b9dc20a/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starrynight/_build}{#1}}

### 2021-02-25 tex/figures/speed.py

@@ -128,10 +128,9 @@ class Compare(object):
                 obl = tt.as_tensor_variable(0.0).astype(tt.config.floatX)
                 u = tt.as_tensor_variable([-1.0]).astype(tt.config.floatX)
                 f = tt.as_tensor_variable([np.pi]).astype(tt.config.floatX)
-                alpha = tt.as_tensor_variable(0.0).astype(tt.config.floatX)
                 y = tt.as_tensor_variable(self.y).astype(tt.config.floatX)
                 return self.map_ref.ops.flux_point_source(
-                    theta, xs, ys, zs, xo, yo, zo, ro, inc, obl, y, u, f, alpha, 0.0
+                    theta, xs, ys, zs, xo, yo, zo, ro, inc, obl, y, u, f, 0.0
                 )
 
             self._flux = theano.function(
@@ -154,11 +153,10 @@ class Compare(object):
                 obl = tt.as_tensor_variable(0.0).astype(tt.config.floatX)
                 u = tt.as_tensor_variable([-1.0]).astype(tt.config.floatX)
                 f = tt.as_tensor_variable([np.pi]).astype(tt.config.floatX)
-                alpha = tt.as_tensor_variable(0.0).astype(tt.config.floatX)
                 y = tt.as_tensor_variable(self.y).astype(tt.config.floatX)
                 return theano.grad(
                     self.map_ref.ops.flux_point_source(
-                        theta, xs, ys, zs, xo, yo, zo, ro, inc, obl, y, u, f, alpha, 0.0
+                        theta, xs, ys, zs, xo, yo, zo, ro, inc, obl, y, u, f, 0.0
                     )[0],
                     ro,
                 )
@@ -181,11 +179,8 @@ class Compare(object):
                 obl = tt.as_tensor_variable(0.0).astype(tt.config.floatX)
                 u = tt.as_tensor_variable([-1.0]).astype(tt.config.floatX)
                 f = tt.as_tensor_variable([np.pi]).astype(tt.config.floatX)
-                alpha = tt.as_tensor_variable(0.0).astype(tt.config.floatX)
                 y = tt.as_tensor_variable(self.y).astype(tt.config.floatX)
-                return self.map_emi.ops.flux(
-                    theta, xo, yo, zo, ro, inc, obl, y, u, f, alpha
-                )
+                return self.map_emi.ops.flux(theta, xo, yo, zo, ro, inc, obl, y, u, f)
 
[…]

### 2021-02-25 tex/gitlinks.tex
tweak io-europa plot; switch to py3.9

@@
-\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starrynight/blob/474eb00c5b87a26fb323129b3b73ea8e1b9dc20a/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starrynight/blob/474eb00c5b87a26fb323129b3b73ea8e1b9dc20a/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starrynight/blob/474eb00c5b87a26fb323129b3b73ea8e1b9dc20a/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starrynight/blob/0b2200131a5df828a979f33af6dedcc1f1009a59/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starrynight/blob/0b2200131a5df828a979f33af6dedcc1f1009a59/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starrynight/blob/0b2200131a5df828a979f33af6dedcc1f1009a59/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
 \newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starrynight/_build}{#1}}

### 2021-02-25 tex/figures/io_europa.py

@@ -174,11 +174,11 @@ map.inc, map.obl, kwargs = get_starry_args(time)
 map.load("data/io_mosaic.jpg")
 
 # Fitted params (see `io_europa.ipynb`)
-dx = 0.06008183547425794
-dy = 0.004225467744578548
-amp = 1.5660538382102391
-europa_amp = 0.4695859742417233
-roughness = 55.766858039463685
+dx = 0.06476496696729728
+dy = 0.0057834182077649565
+amp = 1.5755520732349917
+europa_amp = 0.4686307909766523
+roughness = 55.73260017637845
 
 # Compute the model
 map.roughness = roughness

### 2021-02-25 tex/proofs/notebook_setup.py

@@ -28,7 +28,10 @@ plt.rcParams["font.family"] = "sans-serif"
 plt.rcParams["font.sans-serif"] = ["Liberation Sans"]
 plt.rcParams["font.cursive"] = ["Liberation Sans"]
 plt.rcParams["mathtext.fontset"] = "cm"
-plt.rcParams["mathtext.fallback_to_cm"] = True
+try:
+    plt.rcParams["mathtext.fallback"] = "cm"
+except KeyError:
+    plt.rcParams["mathtext.fallback_to_cm"] = True
 
 
 # TODO: In case we need to patch some symbols.
@@ -44,64 +47,3 @@ if False:
             if symbol == "\\times"
             else old_get_unicode_index(symbol, math)
         )
-
-# Several hacks to `corner` to make it prettier
-import corner
-import numpy as np
-
-
-try:
-    old_corner
-except NameError:
-    old_corner = corner.corner
-
-
-def new_corner(*args, **kwargs):
-    # Get the usual corner plot
-    figure = old_corner(*args, **kwargs)
-
-    # Get the axes
-    ndim = int(np.sqrt(len(figure.axes)))
-    axes = np.array(figure.axes).reshape((ndim, ndim))
-
-    # Smaller tick labels
-    for ax in axes[1:, 0]:
-        for tick in ax.yaxis.get_major_ticks():
-            tick.label.set_fontsize(8)
-        formatter = matplotlib.ticker.ScalarFormatter(useOffset=False)
-        ax.yaxis.set_major_formatter(formatter)
-    for ax in axes[-1, :]:
-        for tick in ax.xaxis.get_major_ticks():
-            tick.label.set_fontsize(8)
-        formatter = matplotlib.ticker.ScalarFormatter(useOffset=False)
-        ax.xaxis.set_major_formatter(formatter)
-
-    # Pad the axes to always include the truths
-    truths = kwargs.get("truths", None)
-    if truths is not None:
-        for row in range(1, ndim):
-            for col in range(row):
-                lo, hi = np.array(axes[row, col].get_xlim())
-                if truths[col] < lo:
-                    lo = truths[col] - 0.1 * (hi - truths[col])
-                    axes[row, col].set_xlim(lo, hi)
-                    axes[col, col].set_xlim(lo, hi)
-                elif truths[col] > hi:
-                    hi = truths[col] - 0.1 * (hi - truths[col])
-                    axes[row, col].set_xlim(lo, hi)
[…]

### 2021-02-25 tex/ms.tex
acknowledgm

@@
 and supplemented with an extensive
-\href{https://rodluger.github.io/starry}{API documentation}
+\href{https://starry.readthedocs.io}{API documentation}
 and suite of
-\href{https://rodluger.github.io/starry/latest/tutorials.html}{tutorials}.
+\href{https://starry.readthedocs.io/en/latest/tutorials/}{tutorials}.
 %
@@
 %
-Complete \href{https://rodluger.github.io/starry}{documentation} and an
+Complete \href{https://starry.readthedocs.io}{documentation} and an
 extensive library of tutorials is available online.
@@
 Tutorials on how to do this can be found in the
-\starry \href{https://rodluger.github.io/starry}{documentation}.
+\starry \href{https://starry.readthedocs.io}{documentation}.
 
@@
 variations of vegetation are not accounted for in the model, although
-the \href{https://rodluger.github.io/starry}{documentation} discusses
+the \href{https://starry.readthedocs.io}{documentation} discusses
 how one may approach the modeling of temporal features.
@@
 %
-The \href{https://rodluger.github.io/starry}{documentation}
+The \href{https://starry.readthedocs.io}{documentation}
 includes tutorials on how to implement this in practice.
@@
 is available at \url{https://github.com/rodluger/starry}, with documentation
-and tutorials hosted at \url{https://rodluger.github.io/starry}.
+and tutorials hosted at \url{https://starry.readthedocs.io}.
 The code used to generate the figures in this paper is hosted
@@
     exoplanet \citep{exoplanet},
-    HEALPix \citep{healpix},
     pybind11 \citep{pybind11},
@@
 }
+
+\vspace{1em}
+
+We would like to thank Nicolas Cowan, Christina Hedges, and the
+Astronomical Data Group at the Center for Computational Astrophysics for
+many thought-provoking discussions that helped shape this paper.
 

### 2021-02-26 tex/ms.tex
tweaks

@@
 
-There is an extensive literature on techniques for mapping spherical exoplanet surfaces
+There is an extensive literature on techniques for mapping exoplanet surfaces
 based on their phase curves
-\citep[e.g.,][]{Russell1906,Lacis1972,Knutson2007,Cowan2008,Oakley2009,Berdyugina2017}
+\citep[e.g.,][]{Russell1906,Lacis1972,Knutson2007,Cowan2008,Oakley2009,Berdyugina2017,PaperI,PaperII}
 and occultation light curves
@@
 their ephemerides
-\citep[e.g.,][]{Arlot1974,Aksnes1984,Arlot2014,deKleer2017,Saquet2018,Morgado2019}.
+\citep[e.g.,][]{Arlot1974,Aksnes1984,Arlot2014,deKleer2017,Saquet2018,Morgado2019,Bartolic2021}.
 Farther out in the solar system,
@@
     \label{eq:LambertsLaw}
-    \mathcal{I}(\vartheta_i) = \mathcal{I}_0 \, \text{max}\big( 0, \cos\vartheta_i \big)
+    \mathcal{I}(\vartheta_\mathrm{i}) = \mathcal{I}_0 \, \text{max}\big( 0, \cos\vartheta_\mathrm{i} \big)
     \quad,
@@
 %
-where $\vartheta_i$ is the angle between the incident radiation and the surface
+where $\vartheta_\mathrm{i}$ is the angle between the incident radiation and the surface
 normal and $\mathcal{I}_0$ is the peak illumination. We show in
@@
 \begin{align}
-    \mathcal{I}_0 = \frac{f_s}{\pi r_s^2}
-\end{align}
-%
-where $r_s$ is the distance between the planet and the star (in units
+    \mathcal{I}_0 = \frac{f_s}{\pi r_\mathrm{s}^2}
+\end{align}
+%
+where $r_\mathrm{s}$ is the distance between the planet and the star (in units
 of the planet's radius) and $f_s$ is the stellar flux measured at the observer
@@
 Earth, but this time taken during an occultation by the Moon. The map
-of the Earth is the same as before, but the observer is now in the
-equatorial frame of the Earth.
+of the Earth is the same as before, but the observer is now along the
+equatorial plane of the Earth.
 The top panel is a reproduction of
@@
 If the stellar radius $R_\star$
-is larger than the planet radius $R_p$, the angular extent of the true
+is larger than the planet radius $R_\mathrm{p}$, the angular extent of the true
 day/night terminator past $\nicefrac{\pi}{2}$ is given by
@@
     \label{eq:tau}
-    \tau &= \arcsin\left( \frac{1 - \nicefrac{R_p}{R_\star}}{\nicefrac{a}{R_\star}} \right)
+    \tau &= \arcsin\left( \frac{1 - \nicefrac{R_\mathrm{p}}{R_\star}}{\nicefrac{a}{R_\star}} \right)
 \end{proof}
@@
 for very close-in planets, the effect can be significant. For instance,
-the hot Jupiter Kelt-9b has $\nicefrac{R_p}{R_\star} = 0.083$ and
+the hot Jupiter Kelt-9b has $\nicefrac{R_\mathrm{p}}{R_\star} = 0.083$ and
 $\nicefrac{a}{R_\star} = 3.16$
@@
 visible from the planet, where \textsf{source\_npts} is a user-supplied
-value. In the limit $R_p \ll R_\star$, this is a spherical cap centered at
+value. In the limit $R_\mathrm{p} \ll R_\star$, this is a spherical cap centered at
 the sub-planet point with radius $R_\star \cos\tau$. In
@@
 not only on the angle between the surface normal and the incident
-radiation, $\vartheta_i$, but also on the angle between the surface
+radiation, $\vartheta_\mathrm{i}$, but also on the angle between the surface
 normal and the reflected radiation (i.e., the direction toward the
-observer), $\vartheta_r$. It may also depend on the azimuthal angles
-of the incident and reflected rays, $\phi_i$ and $\phi_r$, respectively.
+observer), $\vartheta_\mathrm{r}$. It may also depend on the azimuthal angles
+of the incident and reflected rays, $\phi_\mathrm{i}$ and $\phi_\mathrm{r}$, respectively.
 These four angles are shown in Figure~\ref{fig:scattering}, showing
@@
     \mathcal{I}_\text{Lamb}
-    \bigg\{ c_0 + c_1 \, \text{max}\Big( 0, \, \cos(\phi_r - \phi_i) \Big)
+    \bigg\{ c_0 + c_1 \, \text{max}\Big( 0, \, \cos(\phi_\mathrm{r} - \phi_\mathrm{i}) \Big)
     \sin \alpha \tan \beta
@@
     \begin{proof}{OrenNayar}
-        \alpha & = \text{max}\Big( \vartheta_r, \, \vartheta_i \Big)
+        \alpha & = \text{max}\Big( \vartheta_\mathrm{r}, \, \vartheta_\mathrm{i} \Big)
         \nonumber                                                    \\
-        \beta  & = \text{min}\Big( \vartheta_r, \, \vartheta_i \Big)
+        \beta  & = \text{min}\Big( \vartheta_\mathrm{r}, \, \vartheta_\mathrm{i} \Big)
     \end{proof}
@@
 \\[1em]
-and the angles $\vartheta_i$, $\vartheta_r$, $\phi_i$, and $\phi_r$ are all
+and the angles $\vartheta_\mathrm{i}$, $\vartheta_\mathrm{r}$, $\phi_\mathrm{i}$, and $\phi_\mathrm{r}$ are all
 implicit functions of $x$, $y$, and the illumination source position.
@@
 \STARRYORENNAYARNB in $b$ and degree \STARRYORENNAYARNBC in
-$b_c \equiv \sqrt{1 - b^2}$.
-%
-Then, for a given value of $b$ and $b_c$, we construct the operator
+$b_\mathrm{c} \equiv \sqrt{1 - b^2}$.
+%
+Then, for a given value of $b$ and $b_\mathrm{c}$, we construct the operator
 $\mathbf{I}$ out of the polynomial coefficients in the same way as we
@@
 we can afford to simultaneously fit for the surface map without risk of
-overfitting (Bartoli\'c, Luger et al., \emph{in prep}).
+overfitting \citep{Bartolic2021}.
 
@@
 \emph{fraction of a second} on a typical computer.
-\textbf{Full posterior inference with \starry is thus faster than
+\textbf{Full posterior inference with \starry can thus be faster than
     the numerical evaluation of a single forward model}
@@
 phase curves of spherical bodies, meaning those terms do not contribute
-at all to the disk-integrated flux. As discussed in \citet{Luger2019},
+at all to the disk-integrated flux. As discussed in \citet{Luger2019}
+and \citet{PaperI},
 the problem is even more ill-posed than that: for any even
@@
 harmonic degree of the model. While the expressions derived here are
-valid at arbitrary degree, we find that their numerical stability begins
-to degrade above $l \sim 20-25$ for occultations and $l \sim 35-40$ for phase
+valid at arbitrary degree, we find that their numerical stability quickly
+degrades above $l \sim 20-25$ for occultations and $l \sim 35-40$ for phase
 curves. The same is true for the model in thermal light \citep{Luger2019},
@@
 linear operator $\mathbf{I}$ in such a way as to downweight portions of the
-projected disk where $\vartheta_i \neq \vartheta_r$. In practice, however,
+projected disk where $\vartheta_\mathrm{i} \neq \vartheta_\mathrm{r}$. In practice, however,
 if the size of the glint spot is small (which is typically the case),
@@
 We therefore recommend that in such cases
-users of the \starry algorithm use MCMC to do inference, either
+users of the \starry algorithm use HMC/MCMC to do inference, either
 (1) sampling over the spherical
@@
 (2) sampling over the albedo values $\mathbf{a}$ with the same uniform prior,
-but using $\mathbf{y}$ to compute the actual light curve model. In both
+but using $\mathbf{y}$ to compute the actual light curve model
+\citep{Bartolic2021}. In both
 cases, there exists a linear operator that transforms between
@@
 positivity over most of the sphere but not so fine as to throttle the
-computation; as a rule of thumb, we find that grids with $2-5$ times
+computation; as a rule of thumb, we find that grids with ${\sim}4$ times
 as many pixels
@@
 algorithm is coded in a combination of \cpp and \Python compiled using
-the \textsf{theano}. The interface was designed specifically for
+the \textsf{theano} package \citep{theano}. The interface was designed specifically for
 compatibility with the \textsf{exoplanet} modeling package
@@
     scipy \citep{scipy},
-    starry \citep{starry}.
+    starry \citep{starry},
+    theano \citep{theano}.
 }
@@
 toward the observer. Following \citet{Luger2019}, if
-an occultor of radius $r_o$ is located at sky position $(x_o, y_o)$,
-we compute the visible thermal flux $f_T$ from
+an occultor of radius $r_\mathrm{o}$ is located at sky position $(x_\mathrm{o}, y_\mathrm{o})$,
+we compute the visible thermal flux $f_\mathrm{T}$ from
 %
@@
     \label{eq:sTARRy}
-    f_T = \sTe \mathbf{A} \mathbf{R}' \mathbf{R} \mathbf{y}
+    f_\mathrm{T} = \sTe \mathbf{A} \mathbf{R}' \mathbf{R} \mathbf{y}
     \quad,
@@
 %
-$\mathbf{R}' = \mathbf{R}'(x_o, y_o)$ rotates the body on the plane
+$\mathbf{R}' = \mathbf{R}'(x_\mathrm{o}, y_\mathrm{o})$ rotates the body on the plane
 of the sky into the integration frame $\mathcal{F}'$, in which the
@@
 %
-and $\sTe = \sTe(b_o, r_o)$ is the vector of solutions to the integral over
+and $\sTe = \sTe(b_\mathrm{o}, r_\mathrm{o})$ is the vector of solutions to the integral over
 the projected visible disk of the body for each term in $\bg$
-\citep[Equation~26 in][]{Luger2019}, with $b_o = \sqrt{x_o^2 + y_o^2}$.
+\citep[Equation~26 in][]{Luger2019}, with $b_\mathrm{o} = \sqrt{x_\mathrm{o}^2 + y_\mathrm{o}^2}$.
 
 If instead no occultor is present, we compute the total
-visible thermal flux $f_{T_0}$ from this body as
+visible thermal flux $f_\mathrm{T_0}$ from this body as
 %
@@
     \label{eq:rTA1Ry}
-    f_{T_0} = \rTe \mathbf{A_1} \mathbf{R}'' \mathbf{R} \mathbf{y}
+    f_\mathrm{T_0} = \rTe \mathbf{A_1} \mathbf{R}'' \mathbf{R} \mathbf{y}
     \quad,
@@
 is unity. In this case, the observed intensity at any
-point on the surface is proportional to the cosine of the angle $\vartheta_i$ between
+point on the surface is proportional to the cosine of the angle $\vartheta_\mathrm{i}$ between
 the incident light and the surface normal. Points for which
-$\vartheta_i \ge \nicefrac{\pi}{2}$ are unilluminated and
+$\vartheta_\mathrm{i} \ge \nicefrac{\pi}{2}$ are unilluminated and
 therefore have an intensity of zero.
@@
 If the point-like illumination source is placed at sky coordinates
-$(x_s, y_s, z_s)$ in units of the radius of the illuminated body,
+$(x_\mathrm{s}, y_\mathrm{s}, z_\mathrm{s})$ in units of the radius of the illuminated body,
 the day/night terminator on the body is a half-ellipse
@@
     \label{eq:b}
-    b = -\frac{z_s}{r_s}
+    b = -\frac{z_\mathrm{s}}{r_\mathrm{s}}
     \quad,
@@
 %
-where $r_s = \sqrt{x_s^2 + y_s^2 + z_s^2}$ is the distance to the source,
+where $r_\mathrm{s} = \sqrt{x_\mathrm{s}^2 + y_\mathrm{s}^2 + z_\mathrm{s}^2}$ is the distance to the source,
 %
@@
     \label{eq:theta}
-    \theta = -\atantwo(x_s, y_s)
+    \theta = -\atantwo(x_\mathrm{s}, y_\mathrm{s})
     \quad,
@@
 Given this formulation, and assuming that
-$r_s \gg 1$,
+$r_\mathrm{s} \gg 1$,
 it is straightforward to show that the illumination
@@
     \label{eq:illum}
-    \mathcal{I}(b, \theta, r_s; x, y)&=
-    \text{max}\bigg( 0, I(b, \theta, r_s; x, y) \bigg)
+    \mathcal{I}(b, \theta, r_\mathrm{s}; x, y)&=
+    \text{max}\bigg( 0, I(b, \theta, r_\mathrm{s}; x, y) \bigg)
 \end{proof}
@@
     \label{eq:illum_poly}
-    I(b, \theta, r_s; x, y) &=
-    \frac{1}{\pi r_s^2}
-    \cos \vartheta_i
+    I(b, \theta, r_\mathrm{s}; x, y) &=
+    \frac{1}{\pi r_\mathrm{s}^2}
+    \cos \vartheta_\mathrm{i}
     \nonumber \\
-    &= \frac{1}{\pi r_s^2}
+    &= \frac{1}{\pi r_\mathrm{s}^2}
     \bigg(
-    -b_c\sin\theta x + b_c\cos\theta y - bz(x, y)
+    -b_\mathrm{c}\sin\theta x + b_\mathrm{c}\cos\theta y - bz(x, y)
     \bigg)
@@
 %
-with $b_c \equiv \sqrt{1 - b^2}$ and $z(x, y) = \sqrt{1 - x^2 - y^2}$.
+with $b_\mathrm{c} \equiv \sqrt{1 - b^2}$ and $z(x, y) = \sqrt{1 - x^2 - y^2}$.
 The illumination $\mathcal{I}$ is a unitless quantity, normalized such that
@@
 In particular, if we place the illumination source along the $+z$-axis at
-$(0, 0, 1)$, the body is seen at full phase, so $b = -1$, $b_c = 0$, and
+$(0, 0, 1)$, the body is seen at full phase, so $b = -1$, $b_\mathrm{c} = 0$, and
 %
@@
     \label{eq:ivec}
-    \mathbf{i}(b, \theta, r_s) & =
-    \frac{1}{\pi r_s^2}
+    \mathbf{i}(b, \theta, r_\mathrm{s}) & =
+    \frac{1}{\pi r_\mathrm{s}^2}
     \begin{pmatrix}
         0                       \\
-        -b_c\sin\theta \\
+        -b_\mathrm{c}\sin\theta \\
         -b                      \\
-        b_c\cos\theta
+        b_\mathrm{c}\cos\theta
     \end{pmatrix}
@@
     \label{eq:Imat}
-    \mathbf{I}(b, \theta, r_s) & =
-    \frac{1}{\pi r_s^2}
+    \mathbf{I}(b, \theta, r_\mathrm{s}) & =
+    \frac{1}{\pi r_\mathrm{s}^2}
     \begin{pmatrix}
         0                       & 0                       & -b                      & 0                       & \cdots \\
-        -b_c\sin\theta & 0              & 0              & 0              & \cdots \\
+        -b_\mathrm{c}\sin\theta & 0                       & 0                       & 0                       & \cdots \\
         -b                      & 0                       & 0                       & 0                       & \cdots \\
-        b_c\cos\theta  & 0              & 0              & 0              & \cdots \\
-        0              & -b_c\sin\theta & b              & 0              & \cdots \\
-        0              & -b             & -b_c\sin\theta & 0              & \cdots \\
-        0              & b_c\cos\theta  & 0              & -b_c\sin\theta & \cdots \\
-        0              & 0              & b_c\cos\theta  & -b             & \cdots \\
-        0              & 0              & b              & b_c\cos\theta  & \cdots \\
+        b_\mathrm{c}\cos\theta  & 0                       & 0                       & 0                       & \cdots \\
+        0                       & -b_\mathrm{c}\sin\theta & b                       & 0                       & \cdots \\
+        0                       & -b                      & -b_\mathrm{c}\sin\theta & 0                       & \cdots \\
+        0                       & b_\mathrm{c}\cos\theta  & 0                       & -b_\mathrm{c}\sin\theta & \cdots \\
+        0                       & 0                       & b_\mathrm{c}\cos\theta  & -b                      & \cdots \\
+        0                       & 0                       & b                       & b_\mathrm{c}\cos\theta  & \cdots \\
         \vdots                  & \vdots                  & \vdots                  & \vdots                  & \ddots
@@
     f & =
-    \sT(b, \theta', b_o, r_o)
+    \sT(b, \theta', b_\mathrm{o}, r_\mathrm{o})
     \mathbf{A_2}
-    \mathbf{I}(b, \theta', r_s)
+    \mathbf{I}(b, \theta', r_\mathrm{s})
     \mathbf{A_1}
-    \mathbf{R}'(x_o, y_o)
+    \mathbf{R}'(x_\mathrm{o}, y_\mathrm{o})
     \mathbf{R}(\text{I}, \Lambda, \Theta)
@@
     \label{eq:theta'}
-    \theta' = \atantwo(x_o, y_o) - \atantwo(x_s, y_s)
+    \theta' = \atantwo(x_\mathrm{o}, y_\mathrm{o}) - \atantwo(x_\mathrm{s}, y_\mathrm{s})
 \end{align}
@@
     \rT(b)
-    \mathbf{I}(b, \theta'', r_s)
+    \mathbf{I}(b, \theta'', r_\mathrm{s})
     \mathbf{A_1}
-    \mathbf{R}''(x_s, y_s)
+    \mathbf{R}''(x_\mathrm{s}, y_\mathrm{s})
     \mathbf{R}(\text{I}, \Lambda, \Theta)
@@
 construction. The transformation
-$\mathbf{R}'' = \mathbf{R}''(x_s, y_s)$ rotates
+$\mathbf{R}'' = \mathbf{R}''(x_\mathrm{s}, y_\mathrm{s})$ rotates
 the body
-through an angle $\atantwo(x_s, y_s)$
+through an angle $\atantwo(x_\mathrm{s}, y_\mathrm{s})$
 so the semi-major axis of the terminator is aligned
@@
 Note that in both equations we replaced the integral vectors
-$\rTe$ and $\sTe(b_o, r_o)$
+$\rTe$ and $\sTe(b_\mathrm{o}, r_\mathrm{o})$
 with the vectors
-$\rT(b)$ and $\sT(b, \theta', b_o, r_o)$,
+$\rT(b)$ and $\sT(b, \theta', b_\mathrm{o}, r_\mathrm{o})$,
 respectively.
@@
         %
-        \mathbb{k}_{1}(b) & = \frac{b_c^3}{3}
+        \mathbb{k}_{1}(b) & = \frac{b_\mathrm{c}^3}{3}
         %
@@
     \label{eq:IJKrec}
-    \mathbb{k}_{j}(b) &= \frac{b^{j-1} b_c^3 + (j - 1) \mathbb{k}_{j - 2}(b)}{j + 2}
+    \mathbb{k}_{j}(b) &= \frac{b^{j-1} b_\mathrm{c}^3 + (j - 1) \mathbb{k}_{j - 2}(b)}{j + 2}
     %
@@
     \Big)
-    \mathbf{I}(b, \theta'', r_s)
+    \mathbf{I}(b, \theta'', r_\mathrm{s})
     \mathbf{A_1}
-    \mathbf{R}''(x_s, y_s)
+    \mathbf{R}''(x_\mathrm{s}, y_\mathrm{s})
     \mathbf{R}(\text{I}, \Lambda, \Theta)
@@
 develop a procedure to identify the relevant case given the occultor
-impact parameter $b_o = \sqrt{x_o^2 + y_o^2}$ and radius $r_o$ and
+impact parameter $b_\mathrm{o} = \sqrt{x_\mathrm{o}^2 + y_\mathrm{o}^2}$ and radius $r_\mathrm{o}$ and
 the terminator semi-minor
@@
     \nonumber                                               \\
-    y''_2(x'') & = y''_o \pm \sqrt{r_o^2 - (x'' - x''_o)^2}
+    y''_2(x'') & = y''_\mathrm{o} \pm \sqrt{r_\mathrm{o}^2 - (x'' - x''_\mathrm{o})^2}
 \end{proof}
@@
 \begin{proof}{quartic}
-    x''_o = b_o\sin\theta'
+    x''_\mathrm{o} = b_\mathrm{o}\sin\theta'
     \nonumber \\
-    y''_o = b_o\cos\theta'
+    y''_\mathrm{o} = b_\mathrm{o}\cos\theta'
 \end{proof}
@@
     \nonumber \\
-    B &= -4 x''_o (1 - b^2)
+    B &= -4 x''_\mathrm{o} (1 - b^2)
     \nonumber \\
@@
     b^4
-    + r_o^2
-    - 3 {x''_o}^2
-    - {y''_o}^2
-    - b^2 \big(1 + r_o^2 - {x''_o}^2 + {y''_o}^2\big)
+    + r_\mathrm{o}^2
+    - 3 {x''_\mathrm{o}}^2
+    - {y''_\mathrm{o}}^2
+    - b^2 \big(1 + r_\mathrm{o}^2 - {x''_\mathrm{o}}^2 + {y''_\mathrm{o}}^2\big)
     \bigg)
     \nonumber \\
-    D &= -4 x''_o (b^2 - r_o^2 + {x''_o}^2 + {y''_o}^2)
+    D &= -4 x''_\mathrm{o} (b^2 - r_\mathrm{o}^2 + {x''_\mathrm{o}}^2 + {y''_\mathrm{o}}^2)
     \nonumber \\
@@
     b^4
-    - 2 b^2 \big(r_o^2 - {x''_o}^2 + {y''_o}^2\big)
-    + \big(r_o^2 - {x''_o}^2 - {y''_o}^2\big)^2
+    - 2 b^2 \big(r_\mathrm{o}^2 - {x''_\mathrm{o}}^2 + {y''_\mathrm{o}}^2\big)
+    + \big(r_\mathrm{o}^2 - {x''_\mathrm{o}}^2 - {y''_\mathrm{o}}^2\big)^2
     \quad.
@@
     \label{eq:fI}
-    f_I & =
-    \sTe(b_o, r_o)
+    f_\mathrm{I} & =
+    \sTe(b_\mathrm{o}, r_\mathrm{o})
     \mathbf{A_2}
-    \mathbf{I}(b, \theta', r_s)
+    \mathbf{I}(b, \theta', r_\mathrm{s})
     \mathbf{A_1}
-    \mathbf{R}'(x_o, y_o)
+    \mathbf{R}'(x_\mathrm{o}, y_\mathrm{o})
     \mathbf{R}(\text{I}, \Lambda, \Theta)
@@
 %
-where $\sTe(b_o, r_o)$ is the emitted light solution vector
-\citep[Equation~26 in][]{Luger2019}. The flux $f_I$ is the flux one would
+where $\sTe(b_\mathrm{o}, r_\mathrm{o})$ is the emitted light solution vector
+\citep[Equation~26 in][]{Luger2019}. The flux $f_\mathrm{I}$ is the flux one would
 measure from a body whose surface map is weighted by the illumination function
-$\mathbf{I}(b, \theta', r_s)$ during an occultation. Note that this is not
+$\mathbf{I}(b, \theta', r_\mathrm{s})$ during an occultation. Note that this is not
 necessarily the \emph{observed} flux, since this may include the unphysical
@@
 Case 1 corresponds to any complete occultation of the body
-($b_o \le r_o - 1$), so the solution for the flux is trivial:
+($b_\mathrm{o} \le r_\mathrm{o} - 1$), so the solution for the flux is trivial:
 %
@@
     \label{eq:f3}
-    f_3 = f_I
+    f_3 = f_\mathrm{I}
 \end{align}
@@
 intersects with the limb). We first compute the illumination-weighted flux
-$f_I$ as above, then negate the unphysical nightside contribution
+$f_\mathrm{I}$ as above, then negate the unphysical nightside contribution
 using Equation~(\ref{eq:f0hat}):
@@
     \label{eq:f5}
-    f_5 = f_I - \hat{f}_0
+    f_5 = f_\mathrm{I} - \hat{f}_0
     \quad.
@@
     \label{eq:sTint}
-    \sT(b, \theta', b_o, r_o) & =
-    \iint\limits_{S(b, \theta', b_o, r_o)}
+    \sT(b, \theta', b_\mathrm{o}, r_\mathrm{o}) & =
+    \iint\limits_{S(b, \theta', b_\mathrm{o}, r_\mathrm{o})}
     \bg^\top(x', y')
@@
 We defer the solution to Equation~(\ref{eq:sTint}) to \S\ref{sec:sT} below,
-as it is quite lengthy. Given $\sT$, the flux $f_S$ over the integration
+as it is quite lengthy. Given $\sT$, the flux $f_\mathrm{S}$ over the integration
 region $S$ is computed from Equation~(\ref{eq:sTA2IA1RRy}):
@@
     \label{eq:fS}
-    f_S & =
-    \sT(b, \theta', b_o, r_o)
+    f_\mathrm{S} & =
+    \sT(b, \theta', b_\mathrm{o}, r_\mathrm{o})
     \mathbf{A_2}
-    \mathbf{I}(b, \theta', r_s)
+    \mathbf{I}(b, \theta', r_\mathrm{s})
     \mathbf{A_1}
-    \mathbf{R}'(x_o, y_o)
+    \mathbf{R}'(x_\mathrm{o}, y_\mathrm{o})
     \mathbf{R}(\text{I}, \Lambda, \Theta)
@@
 The total flux may
-be computed by subtracting the occulted flux $f_S$ from the total dayside
+be computed by subtracting the occulted flux $f_\mathrm{S}$ from the total dayside
 flux $f_0$:
@@
     \label{eq:f6}
-    f_6 = f_0 - f_S
+    f_6 = f_0 - f_\mathrm{S}
     \quad.
@@
 In case 7, we begin by computing the
-flux over the unocculted region, $f_I$, which includes the spurious
+flux over the unocculted region, $f_\mathrm{I}$, which includes the spurious
 nightside contribution. We then remove this contribution by noting that it
 is equal to the total nightside contribution, $\hat{f}_0$, minus the
-occulted nightside flux, $f_S$:
+occulted nightside flux, $f_\mathrm{S}$:
 %
@@
     \label{eq:f7}
-    f_7 = f_I - (\hat{f}_0 - f_S)
+    f_7 = f_\mathrm{I} - (\hat{f}_0 - f_\mathrm{S})
     \quad.
@@
     \label{eq:f8}
-    f_8 = f_0 - f_S
+    f_8 = f_0 - f_\mathrm{S}
     \quad.
@@
 dayside, along with \emph{both} of the extrema of the ellipse; these are
-therefore exclusively for large occultors ($r_o > 1$). Case 9
+therefore exclusively for large occultors ($r_\mathrm{o} > 1$). Case 9
 involves occultations in which only a small lens-shaped region of the
 nightside is visible. The total flux is the visible dayside plus unphysical
-nightside contribution, $f_I$, minus the nightside contribution, which we
+nightside contribution, $f_\mathrm{I}$, minus the nightside contribution, which we
 compute from Equation~(\ref{eq:fS}):
@@
     \label{eq:f9}
-    f_9 = f_I - f_S
+    f_9 = f_\mathrm{I} - f_\mathrm{S}
     \quad.
@@
     \label{eq:f10}
-    f_{10} = f_S
+    f_{10} = f_\mathrm{S}
     \quad.
@@
     \label{eq:f11}
-    f_{11} = f_0 - (f_{S_1} + f_{S_2})
+    f_{11} = f_0 - (f_{\mathrm{S}_1} + f_{\mathrm{S}_2})
     \quad,
@@
 %
-where $f_{S_1}$ and $f_{S_2}$ are computed from Equation~(\ref{eq:fS}) for
+where $f_{\mathrm{S}_1}$ and $f_{\mathrm{S}_2}$ are computed from Equation~(\ref{eq:fS}) for
 each of the integration regions. Conversely, in case 12 the two regions
@@
     \label{eq:f12}
-    f_{12} = f_I - \big(\hat{f}_0 - (f_{S_1} + f_{S_2})\big)
+    f_{12} = f_\mathrm{I} - \big(\hat{f}_0 - (f_{\mathrm{S}_1} + f_{\mathrm{S}_2})\big)
     \quad,
@@
     \label{eq:f13}
-    f_{13} = f_I - (f_{S_1} + f_{S_2})
+    f_{13} = f_\mathrm{I} - (f_{\mathrm{S}_1} + f_{\mathrm{S}_2})
     \quad.
@@
     \label{eq:f14}
-    f_{14} = f_{S_1} + f_{S_2}
+    f_{14} = f_{\mathrm{S}_1} + f_{\mathrm{S}_2}
     \quad.
@@
     the primitive
-    integrals on the geometrical parameters $b, \theta', b_o, r_o$
+    integrals on the geometrical parameters $b, \theta', b_\mathrm{o}, r_\mathrm{o}$
     for clarity.
@@
     \int\limits_{\pmb{\phi}}
-    \mathbf{G}^\top(x'_p, y'_p)
-    \cdot \dd \mathbf{r}(x'_p, y'_p)
+    \mathbf{G}^\top(x'_\mathrm{p}, y'_\mathrm{p})
+    \cdot \dd \mathbf{r}(x'_\mathrm{p}, y'_\mathrm{p})
     %
@@
     \int\limits_{\pmb{\xi}}
-    \mathbf{G}^\top(x'_t, y'_t)
-    \cdot \dd \mathbf{r}(x'_t, y'_t)
+    \mathbf{G}^\top(x'_\mathrm{t}, y'_\mathrm{t})
+    \cdot \dd \mathbf{r}(x'_\mathrm{t}, y'_\mathrm{t})
     %
@@
     \int\limits_{\pmb{\lambda}}
-    \mathbf{G}^\top(x'_q, y'_q)
-    \cdot \dd \mathbf{r}(x'_q, y'_q)
+    \mathbf{G}^\top(x'_\mathrm{q}, y'_\mathrm{q})
+    \cdot \dd \mathbf{r}(x'_\mathrm{q}, y'_\mathrm{q})
 \end{proof}
@@
     \begin{align}
-        x'_p & = r_o \cos\varphi
+        x'_\mathrm{p} & = r_\mathrm{o} \cos\varphi
         \nonumber                                                 \\
-        y'_p & = b_o + r_o \sin\varphi
+        y'_\mathrm{p} & = b_\mathrm{o} + r_\mathrm{o} \sin\varphi
         \nonumber
@@
     \begin{align}
-        x'_t & = \cos\theta' \cos\varphi - b \sin\theta' \sin\varphi
+        x'_\mathrm{t} & = \cos\theta' \cos\varphi - b \sin\theta' \sin\varphi
         \nonumber                                                             \\
-        y'_t & = \sin\theta' \cos\varphi + b \cos\theta' \sin\varphi
+        y'_\mathrm{t} & = \sin\theta' \cos\varphi + b \cos\theta' \sin\varphi
         \nonumber
@@
         \label{eq:xy_pqt}
-        x'_q & =\cos\varphi
+        x'_\mathrm{q} & =\cos\varphi
         \nonumber           \\
-        y'_q & = \sin\varphi
+        y'_\mathrm{q} & = \sin\varphi
         \quad,
@@
     \phi_0 & =
-    \frac{\pi}{2} \pm \left(\arcsin\left(\frac{1 - r_o ^ 2 - b_o ^ 2}{2 b_o r_o}\right) - \frac{\pi}{2}\right)
+    \frac{\pi}{2} \pm \left(\arcsin\left(\frac{1 - r_\mathrm{o} ^ 2 - b_\mathrm{o} ^ 2}{2 b_\mathrm{o} r_\mathrm{o}}\right) - \frac{\pi}{2}\right)
     \quad,
@@
 where the sign is chosen such that the point
-$(r_o\cos\phi_0, b_o + r_o\sin\phi_0)$ is on the dayside of the occulted body,
+$(r_\mathrm{o}\cos\phi_0, b_\mathrm{o} + r_\mathrm{o}\sin\phi_0)$ is on the dayside of the occulted body,
 and the latter (of which there may be multiple) is given by
@@
     \atantwo
-    \left(b\sqrt{1 - {\mathbf{x''}}^2} - y''_o, \mathbf{x''} - x''_o\right)
+    \left(b\sqrt{1 - {\mathbf{x''}}^2} - y''_\mathrm{o}, \mathbf{x''} - x''_\mathrm{o}\right)
     \quad
@@
 limb-terminator intersection. Both angles are measured counter-clockwise
-from the line $x' = b_o$.
+from the line $x' = b_\mathrm{o}$.
 
@@
                 %
-                2(2r_o)^{l+2}
+                2(2r_\mathrm{o})^{l+2}
                 %
@@
                 %
-                \beta (2r_o)^{l-1}
+                \beta (2r_\mathrm{o})^{l-1}
                 %
@@
 %
-where $\beta = \left(1 - (b_o - r_o)^2\right)^\frac{3}{2}$
+where $\beta = \left(1 - (b_\mathrm{o} - r_\mathrm{o})^2\right)^\frac{3}{2}$
 and we define the Vieta operator
@@
     \binom{v}{u+v-i-j}
-    (-1)^{u+j}\left(\frac{b_o-r_o}{2r_o}\right)^{u+v-i-j}
+    (-1)^{u+j}\left(\frac{b_\mathrm{o}-r_\mathrm{o}}{2r_\mathrm{o}}\right)^{u+v-i-j}
     \quad.
@@
     \label{eq:k2}
-    k^2 & \equiv \frac{1 - r_o^2 - b_o^2 + 2 b_o r_o}{4 b_o r_o}
+    k^2 & \equiv \frac{1 - r_\mathrm{o}^2 - b_\mathrm{o}^2 + 2 b_\mathrm{o} r_\mathrm{o}}{4 b_\mathrm{o} r_\mathrm{o}}
     \quad.
@@
         \frac{
-            1 - z(r_o\cos\varphi, b_o + r_o\sin\varphi)^3
+            1 - z(r_\mathrm{o}\cos\varphi, b_\mathrm{o} + r_\mathrm{o}\sin\varphi)^3
         }{
-            1 - z(r_o\cos\varphi, b_o + r_o\sin\varphi)^2
+            1 - z(r_\mathrm{o}\cos\varphi, b_\mathrm{o} + r_\mathrm{o}\sin\varphi)^2
         }
         \right)
-        \left(r_o^2 + b_o r_o \sin\varphi\right)
+        \left(r_\mathrm{o}^2 + b_\mathrm{o} r_\mathrm{o} \sin\varphi\right)
     }
@@
     -\atantwo\left(
-    -(b_o - r_o) \cos\valpha, (b_o + r_o) \sin\valpha
+    -(b_\mathrm{o} - r_\mathrm{o}) \cos\valpha, (b_\mathrm{o} + r_\mathrm{o}) \sin\valpha
     \right)
@@
     &\qquad\enspace\enspace
-    - \frac{4}{3} b_o r_o
+    - \frac{4}{3} b_\mathrm{o} r_\mathrm{o}
     \sin\valpha \cos\valpha
-    \sqrt{1 - (b_o - r_o)^2 - 4 b_o r_o \sin^2\alpha}
+    \sqrt{1 - (b_\mathrm{o} - r_\mathrm{o})^2 - 4 b_\mathrm{o} r_\mathrm{o} \sin^2\alpha}
     \nonumber \\
     &\qquad\enspace\enspace
-    + \pmb{\delta}(b_o, r_o, \valpha)
+    + \pmb{\delta}(b_\mathrm{o}, r_\mathrm{o}, \valpha)
     \Bigg\}
@@
     c_1 &=
-    \frac{1 + b_o^4 - b_o^2(5 + 2 r_o^2) + r_o^4 + r_o^2}{3 \sqrt{1 - (b_o - r_o)^2}}
+    \frac{1 + b_\mathrm{o}^4 - b_\mathrm{o}^2(5 + 2 r_\mathrm{o}^2) + r_\mathrm{o}^4 + r_\mathrm{o}^2}{3 \sqrt{1 - (b_\mathrm{o} - r_\mathrm{o})^2}}
     \nonumber \\[0.5em]
-    c_2 &= \frac{(b_o^2+7r_o^2-4)\sqrt{1 - (b_o - r_o)^2}}{3}
+    c_2 &= \frac{(b_\mathrm{o}^2+7r_\mathrm{o}^2-4)\sqrt{1 - (b_\mathrm{o} - r_\mathrm{o})^2}}{3}
     \nonumber \\[0.5em]
-    c_3 &= \frac{b_o + r_o}{(b_o - r_o)\sqrt{1 - (b_o - r_o)^2}}
+    c_3 &= \frac{b_\mathrm{o} + r_\mathrm{o}}{(b_\mathrm{o} - r_\mathrm{o})\sqrt{1 - (b_\mathrm{o} - r_\mathrm{o})^2}}
     \quad,
@@
     %
-    \delta(b_o, r_o, \alpha) &=
+    \delta(b_\mathrm{o}, r_\mathrm{o}, \alpha) &=
     \begin{cases}
@@
         \qquad
-        \alpha > \frac{3\pi}{2} \,\, \text{and} \,\, b_o > r_o
+        \alpha > \frac{3\pi}{2} \,\, \text{and} \,\, b_\mathrm{o} > r_\mathrm{o}
         \\
@@
         \qquad
-        \alpha > \frac{3\pi}{2} \,\, \text{and} \,\, b_o < r_o
+        \alpha > \frac{3\pi}{2} \,\, \text{and} \,\, b_\mathrm{o} < r_\mathrm{o}
         \\
@@
     \label{eq:n}
-    n & = -\frac{4 b_o r_o}{(r_o - b_o)^2}
+    n & = -\frac{4 b_\mathrm{o} r_\mathrm{o}}{(r_\mathrm{o} - b_\mathrm{o})^2}
     \quad.
@@
 poor numerical stability, particularly in the vicinity of the singular
-points $b_o = r_o$ and $b_o = 1 + r_o$. In practice, we find that
+points $b_\mathrm{o} = r_\mathrm{o}$ and $b_\mathrm{o} = 1 + r_\mathrm{o}$. In practice, we find that
 numerical evaluation of Equation~(\ref{eq:p2}) via Gaussian quadrature
@@
     \begin{cases}
-        0   & \qquad \qquad (1 - x_o'')^2 + {y_o''}^2 < r_o^2
+        0   & \qquad \qquad (1 - x_\mathrm{o}'')^2 + {y_\mathrm{o}''}^2 < r_\mathrm{o}^2
         \\
@@
 The solution to Equation~(\ref{eq:tT}) involves repeated application
-of the binomial theorem. The result is given on the following
-page in Equation~(\ref{eq:tn}) along with the usual validation link,
-where we define
+of the binomial theorem.
+If we define the quantities
 %
@@
         \pi                      & \qquad \frac{\pi}{2} \leq \xi < \pi   \\
-        2 |b| b_c       & \qquad \pi \leq \xi < \frac{3\pi}{2}  \\
-        \pi + 2 |b| b_c & \qquad \frac{3\pi}{2} \leq \xi < 2\pi
-        \quad.
+        2 |b| b_\mathrm{c}       & \qquad \pi \leq \xi < \frac{3\pi}{2}  \\
+        \pi + 2 |b| b_\mathrm{c} & \qquad \frac{3\pi}{2} \leq \xi < 2\pi
+        \quad,
     \end{cases}
@@
 %
-\afterpage{
+we may express the solution to the $\mathbb{t}_n$ integral as
+
+%
+\clearpage
+%
+
 \begin{proof}{tT}
     \label{eq:tn}
-        \tag{\ref*{eq:Zuvjk}*}
     \mathbb{t}_n & =
@@
                 \left(\frac{\sin\vxi}{1 + \cos\vxi}\right)^2 + 2 b^2 - 1
-                }{2 |b| b_c}
+            }{2 |b| b_\mathrm{c}}
             \right)
-            + |b| b_c \cos\vxi
+        + |b| b_\mathrm{c} \cos\vxi
         \right)
@@
         \quad\quad\quad\quad
-            - \, b_c^3\cos\theta'
+        - \, b_\mathrm{c}^3\cos\theta'
         \sum\limits_{j=0}^{l-2}
@@
         \quad\quad\quad\quad
-            - \, b b_c^3\cos^2\theta'
+        - \, b b_\mathrm{c}^3\cos^2\theta'
         \sum\limits_{j=0}^{l-3}
@@
         \quad\quad\quad\quad
-            - \, b_c^5\sin\theta'\cos\theta'
+        - \, b_\mathrm{c}^5\sin\theta'\cos\theta'
         \sum\limits_{j=0}^{l-3}
@@
         \quad\quad\quad\quad
-            - \, b_c^3\sin\theta'
+        - \, b_\mathrm{c}^3\sin\theta'
         \sum\limits_{j=0}^{\frac{\nu}{2}}
@@
 \end{proof}
+
+%
 \vfill
-}
-%
+\clearpage
+%
+
 The solution to Equation~(\ref{eq:tn}) depends on the matrix
@@
     \begin{cases}
-        \theta'        & \qquad \qquad \cos^2\theta' + (\sin\theta' - b_o)^2 < r_o^2
+        \theta'        & \qquad \qquad \cos^2\theta' + (\sin\theta' - b_\mathrm{o})^2 < r_\mathrm{o}^2
         \\
@@
     \lambda_1 & =
-    \frac{\pi}{2} \pm \left(\arcsin\left(\frac{1 - r_o ^ 2 + b_o ^ 2}{2 b_o}\right) - \frac{\pi}{2}\right)
+    \frac{\pi}{2} \pm \left(\arcsin\left(\frac{1 - r_\mathrm{o} ^ 2 + b_\mathrm{o} ^ 2}{2 b_\mathrm{o}}\right) - \frac{\pi}{2}\right)
     \quad,

### 2021-03-02 tex/ms.tex
Update ms.tex
Corrected typo in abstract

@@
     solutions for the flux measured from a spherical planet or moon seen in reflected
-    light, either in our out of occultation.
+    light, either in or out of occultation.
     %

### 2021-03-10 tex/ms.tex
subscript fix
final revisions

@@
 assuming uniform surfaces and used it to infer the two body's
-average geometrical albedos. Later, \citet{Reinsch1994} analyzed
+average geometrical albedos. Later,
+\citet{Buie1992} used a maximum entropy approach to reconstruct two-dimensional
+maps of the two bodies and
+\citet{Reinsch1994} analyzed
 the complete mutual occultation dataset to infer longitudinal maps of Pluto's
@@
 %
-As in \citet{Luger2019}, in the caption of each of the figures
+As in all papers in the \starry series, in the caption of each of the figures
 we provide links \codeicon\ to the exact \Python scripts that
@@
 
-\section{Reflected light curves in \starry}
+\section{Reflected light curves in starry}
 \label{sec:validation}
@@
 
-There are several limitations to the \starry model that are important
+There are a few limitations to the \starry model that are important
 to bear in mind. The primary limitation concerns the maximum spherical
@@
 
-The second limitation involves a potential failure of the \starry
-algorithm. The \starry code includes a large suite of unit tests that compare
-the flux computations to numerical models and to various benchmarks
-for a wide variety of inputs. While we have done our best to
-develop tests over the full range of occultation configurations,
-there may be edge cases in which the \starry algorithm fails and returns
-the wrong flux. This could happen, for instance, if the quartic root
-solver (\S\ref{sec:which-case}) fails to find the points of intersection
-between the occultor and the day/night terminator, leading to
-an incorrect case identification (Figure~\ref{fig:cases}) and thus the
-wrong value for the flux. In the development of the algorithm, these cases
-would occasionally show up as a single, obvious outlier in a light curve
-model. All such cases we encountered
-have been fixed by adding consistency
-checks in the root solver and switching to alternate evaluation methods
-near known singularities. However, it is possible that there may still be
-rare cases in which this happens, in which case we ask that users
-raise an \href{https://github.com/rodluger/starry/issues}{issue} on
-GitHub so that we can provide a fix.
-
-The third limitation concerns the flexibility of the \starry model.
+The second limitation concerns the flexibility of the \starry model.
 While we presented ways to capture non-Lambertian scattering
@@
             elliptic integrals and are derived below.
+            %
+            Note, finally, that there are additional subcases not shown above.
+            For instance, cases 4, 5, 7, and 8 also encompass configurations
+            in which the occultor does not intersect the limb of the occulted
+            body. However, as this distinction does not affect the procedure
+            for computing the flux in these cases (see text), we omit these
+            subcases from the figure.
             \label{fig:cases}
@@
                                 & \equiv
-    \sum_{i = 0}^{\frac{N - 1}{2}}
+    \sum_{i = 0}^{\frac{N}{2} - 1}
     \int\limits_{\varphi_{2i}}^{\varphi_{2i+1}}
@@
     \label{eq:pairdiff}
-    \Delta \mathbf{x} \equiv \sum_{i=0}^{\frac{N - 1}{2}}
+    \Delta \mathbf{x} \equiv \sum_{i=0}^{\frac{N}{2} - 1}
     \left( x_{2i + 1} - x_{2i} \right)
@@
 
+\section{Caveats}
+\label{sec:cases-missing}
+%
+The \starry code includes a large suite of unit tests that compare
+the flux computations to numerical models and to various benchmarks
+for a wide variety of inputs. While we have done our best to
+develop tests over the full range of occultation configurations,
+there may be edge cases in which the \starry algorithm fails and returns
+the wrong flux. This could happen, for instance, if the quartic root
+solver (\S\ref{sec:which-case}) fails to find the points of intersection
+between the occultor and the day/night terminator, leading to
+an incorrect case identification (Figure~\ref{fig:cases}) and thus the
+wrong value for the flux. In the development of the algorithm, these cases
+would occasionally show up as a single, obvious outlier in a light curve
+model. All such cases we encountered
+have been fixed by adding consistency
+checks in the root solver and switching to alternate evaluation methods
+near known singularities. However, it is possible that there may still be
+rare cases in which this happens, in which case we ask that users
+raise an \href{https://github.com/rodluger/starry/issues}{issue} on
+GitHub so that we can provide a fix.
+
 % TABLE

### 2021-03-10 tex/ms.tex
minor tweaks

@@
 based on their phase curves
-\citep[e.g.,][]{Russell1906,Lacis1972,Knutson2007,Cowan2008,Oakley2009,Berdyugina2017,PaperI,PaperII}
+\citep[e.g.,][]{Russell1906,Lacis1972,Knutson2007,Cowan2008,Oakley2009,Berdyugina2017,PaperI,PaperII,Heng2021}
 and occultation light curves
@@
 
-\section{Reflected light curves in starry}
-\label{sec:validation}
-
-\subsection{Sample light curves}
-\label{sec:sample}
-
 \begin{figure}[t!]
@@
 \end{figure}
+
+% HACK
+\pagebreak
+
+\section{Reflected light curves in starry}
+\label{sec:validation}
+
+\subsection{Sample light curves}
+\label{sec:sample}
 
@@
 
+% HACK
+\pagebreak
+
 \subsection{Extended illumination source}
@@
 
+% HACK
+\pagebreak
+
 \subsection{Non-Lambertian scatterers}
@@
 Treatment of a generalized, flexible scattering model is beyond the scope
-of this paper. However, as an example of how a scattering model may be
+of this paper; see \citet{Heng2021} for recent results on this front.
+However, as an example of how a scattering model may be
 incorporated

### 2021-03-31 tex/ms.tex
linenos, citations, misc

@@
 % !TeX root = ./ms.tex
+\ifdefined\LINENOS
+    \documentclass[modern,linenumbers]{aastex62}
+\else
     \documentclass[modern]{aastex62}
+\fi
 
@@
 \input{style}
+
+% Force line numbers in paragraphs containing equations
+\ifdefined\LINENOS
+    \usepackage{lineno}
+    \linenumbers
+    \let\oldalign\align
+    \let\oldendalign\endalign
+    \renewenvironment{align}{%
+        \linenomath%
+            \oldalign%
+    }{%
+        \endlinenomath%
+            \oldendalign%
+    }
+\fi
 
@@
 eclipse (occultation) light curves, and moon-moon, planet-moon, and
-planet-planet occultations (in the Solar System or not),
+planet-planet occultations \citep[in the Solar System or not; e.g.,][]{Cabrera2007,Luger2019b},
 all seen in reflected light. We derive all expressions in
@@
 resulting in a negligible effect on the planet's light curve. However,
-for very close-in planets, the effect can be significant. For instance,
+for very close-in planets, the effect can be significant
+\citep{Knuth2017,Carter2019}. For instance,
 the hot Jupiter Kelt-9b has $\nicefrac{R_\mathrm{p}}{R_\star} = 0.083$ and
@@
 
-Finally, we would like to emphasize that while spherical harmonics are
+We would also like to emphasize that while spherical harmonics are
 a convenient basis for the purpose of computing light curves, they
@@
 
+%
+
+Finally, while the algorithm presented here can be used to model
+planet-planet and planet-moon occultations in reflected light, we only
+account for the physical blocking of light rays from the planet by the occultor;
+we do not account for the attenuation of the reflected light due to the
+\emph{shadow} of the occultor on the planet.
+This can be an important effect at certain orbital phases
+\citep[e.g.,][]{Cabrera2007}. However, since the shadow of the occultor is not necessarily
+circular, it is significantly harder to model in closed form. A proper treatment
+of this and other effects, such as occultations and shadows due to rings
+\citep[e.g.,][]{Arnold2004}, is deferred to future work.
+
 \section{Conclusions}

### 2021-03-31 tex/gitlinks.tex
Committing automatically from GitHub Actions

@@
-\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starrynight/blob/0b2200131a5df828a979f33af6dedcc1f1009a59/tex/figures/#1.py}{\codeicon}\,\,}
-\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starrynight/blob/0b2200131a5df828a979f33af6dedcc1f1009a59/tex/figures/#1.gif}{\animicon}\,\,}
-\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starrynight/blob/0b2200131a5df828a979f33af6dedcc1f1009a59/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
+\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starrynight/blob/5f79b24026133db207a88bee465e5e5080b64bcf/tex/figures/#1.py}{\codeicon}\,\,}
+\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starrynight/blob/5f79b24026133db207a88bee465e5e5080b64bcf/tex/figures/#1.gif}{\animicon}\,\,}
+\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starrynight/blob/5f79b24026133db207a88bee465e5e5080b64bcf/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
 \newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starrynight/_build}{#1}}

### 2021-03-31 tex/figures/55cancrie.py

@@ -1,0 +1,79 @@
+"""55 cancrie e secondary eclipse example."""
+import starry
+import matplotlib.pyplot as plt
+import numpy as np
+import astropy.units as u
+
+# Config
+starry.config.lazy = False
+
+# Star
+star_map = starry.Map(udeg=2, amp=1)
+star_map[1:] = [0.5, 0.25]
+star = starry.Primary(
+    star_map, m=0.905, mass_unit=u.M_sun, r=0.943, length_unit=u.R_sun
+)
+
+# Planet
+kwargs = dict(
+    m=7.99,
+    mass_unit=u.earthMass,
+    porb=0.73654737,
+    r=1.875,
+    length_unit=u.earthRad,
+    inc=83.59,
+    t0=0.400473685,
+)
+
+# Time arrays (secondary eclipse ingress / full phase curve)
+t_ingress = np.linspace(0, 0.002, 1000)
+t_phase = kwargs["t0"] + kwargs["porb"] * np.linspace(-0.5, 0.5, 1000)
+
+# Uniform
+e_map = starry.Map(ydeg=1, reflected=False)
+e = starry.Secondary(e_map, **kwargs)
+sys = starry.System(star, e)
+flux_em = sys.flux(t=t_ingress, total=False)[1]
+
+# Noon approximation
+e_map = starry.Map(udeg=1, reflected=False)
+e_map[1] = 1
+e = starry.Secondary(e_map, **kwargs)
+sys = starry.System(star, e)
+flux_ld = sys.flux(t=t_ingress, total=False)[1]
+
+# Reflected, point source
+e_map = starry.Map(ydeg=1, reflected=True, amp=1)
+e = starry.Secondary(e_map, **kwargs)
+sys = starry.System(star, e)
+flux_ref = sys.flux(t=t_ingress, total=False)[1]
+flux_phase = sys.flux(t=t_phase, total=False)[1]
+
+# Reflected, extended source
+e_map = starry.Map(ydeg=1, reflected=True, amp=1, source_npts=300)
+e = starry.Secondary(e_map, **kwargs)
+sys = starry.System(star, e)
+flux_ref_fin = sys.flux(t=t_ingress, total=False)[1]
+flux_phase_fin = sys.flux(t=t_phase, total=False)[1]
+
+# Plot phase curves
+fig, ax = plt.subplots(1, figsize=(8, 5))
+t = t_phase - kwargs["t0"]
[…]

### 2021-03-31 tex/figures/cases.py

@@ -1,0 +1,55 @@
+from support_code import *
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Setup figure
+fig, ax = plt.subplots(3, 4, figsize=(12, 8))
+ax = ax.flatten()
+
+# Legend
+ax[11].plot([0, 1], [0, 0], color="C0", lw=8, alpha=0.75, label="dayside")
+ax[11].plot(
+    [0, 1],
+    [0, 0],
+    color=(0.314, 0.431, 0.514),
+    lw=8,
+    alpha=0.5,
+    label="occulted dayside",
+)
+ax[11].plot([-1, 1], [0, 0], color="k", alpha=0.75, lw=8, label="nightside")
+ax[11].plot([0, 1], [0, 0], color="k", alpha=0.5, lw=8, label="occulted nightside")
+ax[11].plot([0, 1], [0, 0], color="k", lw=2, ls="--", label="occultor limb")
+ax[11].plot([0, 1], [0, 0], color="C1", lw=2, label="integration boundary")
+ax[11].set_ylim(1, 2)
+ax[11].legend(loc="center", fontsize=10, frameon=False)
+
+# Cases
+visualize_simple(ax[0], 0.5, 75 * np.pi / 180, 0, 0.0)
+visualize_simple(ax[1], 0.5, 75 * np.pi / 180, 0, 1.1)
+visualize_simple(ax[2], -0.25, 0, 0.175, 1.05)
+visualize_simple(ax[3], 0.25, np.pi, 0.175, 1.05)
+visualize_simple(ax[4], -0.25, 190 * np.pi / 180, 0.8, 0.3)
+visualize_simple(ax[5], 0.25, 10 * np.pi / 180, 0.8, 0.3)
+visualize_simple(ax[6], 0.5, 75 * np.pi / 180, 0.5, 0.7)
+visualize_simple(ax[7], 0.5, -10 * np.pi / 180, 0.5, 0.7)
+visualize_simple(ax[8], -0.5, -190 * np.pi / 180, 0.5, 0.7)
+visualize_simple(ax[9], 0.5, np.pi, 4.65, 5.0)
+visualize_simple(ax[10], -0.5, 0, 4.65, 5.0)
+
+# Appearance
+for i, axis in enumerate(ax):
+    axis.axis("off")
+    if i < 11:
+        axis.annotate(
+            "case {}".format(i),
+            xy=(0.5, 0.0),
+            xycoords="axes fraction",
+            xytext=(0, 0),
[…]

### 2021-03-31 tex/figures/earthmoon.py

@@ -1,0 +1,145 @@
+"""Earth occultation example."""
+import starry
+import matplotlib.pyplot as plt
+import numpy as np
+from matplotlib.colors import LinearSegmentedColormap
+
+# Disable lazy mode
+starry.config.lazy = False
+
+# Instantiate the Earth in emitted light
+map_e = starry.Map(25)
+map_e.load("earth", sigma=0.06)
+
+# Instantiate the Earth in reflected light
+map_r = starry.Map(25, reflected=True)
+map_r.load("earth", sigma=0.06)
+
+# Earth colormap
+cmap = LinearSegmentedColormap(
+    "earth",
+    segmentdata={
+        "red": [[0.0, 0.0, 0.122], [1.0, 1.0, 1.0]],
+        "green": [[0.0, 0.0, 0.467], [1.0, 1.0, 1.0]],
+        "blue": [[0.0, 0.0, 0.706], [1.0, 1.0, 1.0]],
+    },
+    N=256,
+)
+
+for reflected in (True, False):
+
+    # Set up the plot
+    nim = 12
+    npts = 100
+    nptsnum = 10
+    res = 300
+    fig = plt.figure(figsize=(12, 5))
+    ax_im = [plt.subplot2grid((4, nim), (0, n)) for n in range(nim)]
+    ax_lc = plt.subplot2grid((4, nim), (1, 0), colspan=nim, rowspan=3)
+
+    # Moon occultation params
+    ro = 0.273
+    yo = np.linspace(-0.5, 0.5, npts)
+    yonum = np.linspace(-0.5, 0.5, nptsnum)
+    xo = np.linspace(-1.5, 1.5, npts)
+    xonum = np.linspace(-1.5, 1.5, nptsnum)
+
+    # Say the occultation occurs over ~1 radian of the Earth's rotation
+    # That's equal to 24 / (2 * pi) hours
+    time = np.linspace(0, 24 / (2 * np.pi), npts)
+    timenum = np.linspace(0, 24 / (2 * np.pi), nptsnum)
+    theta0 = 0
+    theta = np.linspace(theta0, theta0 + 180.0 / np.pi, npts, endpoint=True)
+    thetanum = np.linspace(theta0, theta0 + 180.0 / np.pi, nptsnum, endpoint=True)
+
+    # Compute and plot the flux *analytically*
+    if reflected:
+        # Position of the illumination source (the sun).
+        # We'll assume it's constant for simplicity
+        xs = -1.0 * np.ones_like(time)
[…]

### 2021-03-31 tex/figures/earthphase.py

@@ -1,0 +1,108 @@
+"""Earth phase curve example."""
+import starry
+import matplotlib.pyplot as plt
+import numpy as np
+from matplotlib.colors import LinearSegmentedColormap
+
+# Disable lazy mode
+starry.config.lazy = False
+
+
+# Instantiate the Earth in reflected light
+map = starry.Map(25, reflected=True)
+map.load("earth", sigma=0.06)
+map.obl = -23.5
+
+# Earth colormap
+cmap = LinearSegmentedColormap(
+    "earth",
+    segmentdata={
+        "red": [[0.0, 0.0, 0.122], [1.0, 1.0, 1.0]],
+        "green": [[0.0, 0.0, 0.467], [1.0, 1.0, 1.0]],
+        "blue": [[0.0, 0.0, 0.706], [1.0, 1.0, 1.0]],
+    },
+    N=256,
+)
+
+# Set up the plot
+nim = 12
+npts = 5000
+nptsnum = 10
+res = 300
+fig = plt.figure(figsize=(12, 6.5))
+ax_im = [plt.subplot2grid((9, nim), (0, n), rowspan=2) for n in range(nim)]
+ax_in = [plt.subplot2grid((9, nim), (2, n)) for n in range(nim)]
+ax_lc = plt.subplot2grid((9, nim), (3, 0), colspan=nim, rowspan=6)
+
+# Orbital stuff
+Porb = 365.256
+Prot = 1.0
+time = np.linspace(0, Porb, npts)
+theta = (360.0 * time / Prot) % 360.0
+xs = np.sin(2 * np.pi * time / Porb)
+ys = np.zeros_like(time)
+zs = -np.cos(2 * np.pi * time / Porb)
+
+# Compute and plot the flux *analytically*
+F = map.flux(theta=theta, xs=xs, ys=ys, zs=zs)
+maxF = np.max(F)
+F /= maxF
+ax_lc.plot(time, F, "C0-", label="analytic", lw=0.5)
+
+# Plot the earth images & compute the numerical flux
+t_num = np.zeros(nim)
+F_num = np.zeros(nim)
+for n in range(nim):
+    i = int(np.linspace(0, npts - 1, nim + 2)[n + 1])
+
+    # Show the image at zero rotational phase
+    map.show(
+        ax=ax_im[n],
+        cmap=cmap,
+        xs=xs[i],
+        ys=ys[i],
[…]

### 2021-03-31 tex/figures/earthsun.py

@@ -1,0 +1,149 @@
+"""Earth occultation example."""
+import starry
+import matplotlib.pyplot as plt
+import numpy as np
+from matplotlib.colors import LinearSegmentedColormap
+
+# Disable lazy mode
+starry.config.lazy = False
+
+# Instantiate the Earth in emitted light
+map_e = starry.Map(25)
+map_e.load("earth", sigma=0.06)
+map_e.inc = 90 - 23.5
+
+# Instantiate the Earth in reflected light
+map_r = starry.Map(25, reflected=True)
+map_r.load("earth", sigma=0.06)
+map_r.inc = 90 - 23.5
+
+# Earth colormap
+cmap = LinearSegmentedColormap(
+    "earth",
+    segmentdata={
+        "red": [[0.0, 0.0, 0.122], [1.0, 1.0, 1.0]],
+        "green": [[0.0, 0.0, 0.467], [1.0, 1.0, 1.0]],
+        "blue": [[0.0, 0.0, 0.706], [1.0, 1.0, 1.0]],
+    },
+    N=256,
+)
+
+for reflected in (True, False):
+
+    # Set up the plot
+    nim = 12
+    npts = 100
+    nptsnum = 10
+    res = 300
+    fig = plt.figure(figsize=(12, 5))
+    ax_im = [plt.subplot2grid((4, nim), (0, n)) for n in range(nim)]
+    ax_lc = plt.subplot2grid((4, nim), (1, 0), colspan=nim, rowspan=3)
+
+    # Sun occultation params
+    t1 = -342
+    t2 = -332
+    time = np.linspace(t1, t2, npts)  # in minutes
+    timenum = np.linspace(t1, t2, nptsnum)
+    ro = 6.957e8 / 6.3781e6  # 1 R_sun in R_earth
+    yo = -0.5 * ro * np.ones(npts)
+    yonum = -0.5 * ro * np.ones(nptsnum)
+    a = 1.496e11 / 6.3781e6  # 1 AU in R_earth
+    P = 365.25 * 24 * 60  # 1 year in minutes
+    xo = a * np.sin(2 * np.pi * time / P)
+    xonum = a * np.sin(2 * np.pi * timenum / P)
+    zo = a * np.cos(2 * np.pi * time / P)
+    zonum = a * np.cos(2 * np.pi * timenum / P)
+    theta = 0
+
+    # Compute and plot the flux *analytically*
+    if reflected:
[…]

### 2021-03-31 tex/figures/extended.py

@@ -1,0 +1,81 @@
+"""Extend illumination source."""
+import starry
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+import numpy as np
+
+# Config
+starry.config.lazy = False
+
+# Params from Wong et al. (2019)
+aRs = 3.16
+RpRs = 0.08229
+
+# Get the two images
+res = 999
+map = starry.Map(reflected=True, source_npts=1)
+img1 = map.render(projection="moll", xs=0, ys=0, zs=aRs / RpRs, res=res)
+map = starry.Map(reflected=True, source_npts=300)
+img2 = map.render(projection="moll", xs=0, ys=0, zs=aRs / RpRs, rs=1 / RpRs, res=res)
+norm = np.nanmax(img2)
+img1 /= norm
+img2 /= norm
+
+# Plot them. We'll instantiate a *regular* starry map and pass
+# in the images so that the intensity gets plotted with the
+# regular colormap (instead of with an alpha filter).
+fig, ax = plt.subplots(1, 2, figsize=(14, 4), constrained_layout=True)
+for axis in ax:
+    axis.grid(False)
+    axis.set_xticks([])
+    axis.set_yticks([])
+ax[0].set_title("point source")
+ax[1].set_title("extended source")
+norm = mpl.colors.Normalize(vmin=0, vmax=1)
+map = starry.Map(1)
+map.show(image=img1, projection="moll", ax=ax[0], norm=norm)
+map.show(image=img2, projection="moll", ax=ax[1], norm=norm)
+
+# Plot contours
+X = np.linspace(-2 * np.sqrt(2), 2 * np.sqrt(2), img2.shape[1])
+Y = np.linspace(-np.sqrt(2), np.sqrt(2), img2.shape[0])
+levels = np.array([0, 1, 5, 10, 30, 50, 75])
+for i, axis, img in zip([0, 1], ax, [img1, img2]):
+    cont = axis.contour(
+        X,
+        Y,
+        img / np.nanmax(img) * 100,
+        levels,
+        colors="w",
+        antialiased=True,
+        linewidths=0.5,
+        linestyles="dotted",
+    )
+    if i == 0:
+        x = np.array([-90, -70, -60, -40]) * 2 * np.sqrt(2) / 180.0
+    else:
+        x = np.array([-106, -98, -92, -86, -70, -60, -40]) * 2 * np.sqrt(2) / 180.0
[…]

### 2021-03-31 tex/figures/frames.py

@@ -1,0 +1,324 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import starry
+from starry._plotting import get_ortho_latitude_lines, get_ortho_longitude_lines
+from matplotlib.colors import LinearSegmentedColormap
+from matplotlib.patches import FancyArrowPatch
+
+
+# Config
+starry.config.lazy = False
+starry.config.quiet = True
+
+
+def plot_grid(ax, inc, obl, theta):
+    inc *= np.pi / 180
+    obl *= np.pi / 180
+    theta *= np.pi / 180
+    x = np.linspace(-1, 1, 10000)
+    y = np.sqrt(1 - x ** 2)
+    borders = [None, None]
+    (borders[0],) = ax.plot(x, y, "k-", alpha=1, lw=1)
+    (borders[1],) = ax.plot(x, -y, "k-", alpha=1, lw=1)
+    lats = get_ortho_latitude_lines(inc=inc, obl=obl)
+    latlines = [None for n in lats]
+    for n, l in enumerate(lats):
+        (latlines[n],) = ax.plot(l[0], l[1], "k-", lw=0.5, alpha=0.5, zorder=99)
+    lons = get_ortho_longitude_lines(inc=inc, obl=obl, theta=theta)
+    lonlines = [None for n in lons]
+    for n, l in enumerate(lons):
+        (lonlines[n],) = ax.plot(l[0], l[1], "k-", lw=0.5, alpha=0.5, zorder=99)
+
+
+def add_arrow(ax1, ax2, label="", kind="straight", eps=0):
+    fig = ax1.figure
+
+    if kind == "straight":
+        fig.patches.append(
+            FancyArrowPatch(
+                fig.transFigure.inverted().transform(
+                    ax1.transData.transform((-0.9, 0))
+                ),
+                fig.transFigure.inverted().transform(
+                    ax2.transData.transform((0.9 - eps, 0))
+                ),
+                transform=fig.transFigure,
+                fc="k",
+                arrowstyle="-|>",
+                alpha=1,
+                mutation_scale=10.0,
[…]

### 2021-03-31 tex/figures/geometry.py

@@ -1,0 +1,13 @@
+from support_code import visualize
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+b = 0.5
+theta = 75 * np.pi / 180
+bo = 0.5
+ro = 0.7
+fig, ax = visualize(b, theta, bo, ro)
+for axis in ax:
+    axis.set_rasterization_zorder(0)
+fig.savefig("geometry.pdf", bbox_inches="tight")

### 2021-03-31 tex/figures/illum.py

@@ -1,0 +1,118 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.patches import Arc
+from matplotlib.colors import LinearSegmentedColormap
+
+fig, ax = plt.subplots(1, figsize=(6, 6))
+ax.set_aspect(1)
+ax.set_xlim(-1.1, 1.1)
+ax.set_ylim(-1.1, 1.1)
+ax.axis("off")
+b = 0.25
+theta = 0
+
+# Illumination
+cdict = {
+    "red": [[0.0, 0.0, 0.122], [1.0, 1.0, 1.0]],
+    "green": [[0.0, 0.0, 0.467], [1.0, 1.0, 1.0]],
+    "blue": [[0.0, 0.0, 0.706], [1.0, 1.0, 1.0]],
+}
+cmap = LinearSegmentedColormap("testCmap", segmentdata=cdict, N=256)
+cmap.set_under("k")
+x0, y0 = np.meshgrid(np.linspace(-1, 1, 3000), np.linspace(-1, 1, 3000))
+x = x0 * np.cos(theta) + y0 * np.sin(theta)
+y = -x0 * np.sin(theta) + y0 * np.cos(theta)
+z = np.sqrt(1 - x ** 2 - y ** 2)
+I = np.sqrt(1 - b ** 2) * y - b * z
+I[I < 0] = 0
+ax.imshow(
+    I,
+    extent=(-1, 1, -1, 1),
+    origin="lower",
+    vmin=1e-8,
+    vmax=1,
+    cmap=cmap,
+    alpha=0.75,
+    zorder=-1,
+)
+
+# Planet
+x = np.linspace(-1, 1, 1000)
+yp = np.sqrt(1 - x ** 2)
+ax.plot(x, yp, "k-", lw=1.5, zorder=98)
+ax.plot(x, -yp, "k-", lw=1.5, zorder=98)
+
+# Terminator
+x0 = np.linspace(-1, 1, 1000)
+y0 = b * np.sqrt(1 - x0 ** 2)
+x = x0 * np.cos(theta) - y0 * np.sin(theta)
+y = x0 * np.sin(theta) + y0 * np.cos(theta)
+plt.plot(x, y, "k-", lw=2, zorder=99)
+x = x0 * np.cos(theta) + y0 * np.sin(theta)
+y = x0 * np.sin(theta) - y0 * np.cos(theta)
[…]

### 2021-03-31 tex/figures/inference.py

@@ -1,0 +1,86 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import starry
+
+# Config
+starry.config.lazy = False
+np.random.seed(0)
+
+# Setup figure
+fig, ax = plt.subplots(3, 2, figsize=(13, 8))
+fig.subplots_adjust(hspace=0.4)
+ax[0, 0].set_visible(False)
+ax[0, 1].set_visible(False)
+ax[1, 0].set_ylabel("flux", fontsize=10)
+ax[1, 0].set_title("thermal phase curve", fontsize=12, fontweight="bold")
+ax[1, 1].set_title("reflected phase curve", fontsize=12, fontweight="bold")
+
+for axis in ax[1, :]:
+    axis.tick_params(labelsize=8)
+    axis.set_ylim(-0.05, 1.05)
+
+# Show the true map
+ax_top = fig.add_subplot(3, 1, 1)
+ax_top.set_title("input", fontsize=12, fontweight="bold")
+map = starry.Map(20)
+map.load("earth", sigma=0.1)
+map.show(ax=ax_top, projection="moll")
+
+# Solve the least-squares problem for thermal & reflected phase curves
+for i, reflected in enumerate([False, True]):
+
+    # Instantiate a map of the Earth
+    map = starry.Map(20, reflected=reflected)
+    map.load("earth", sigma=0.1)
+    obl = 23.5
+    porb = 365.25
+    prot = 1.0
+
+    # Hack: these amplitudes give us unit maximum flux
+    if reflected:
+        map.amp = 1.0873
+    else:
+        map.amp = 0.7560
+
+    # Light curve over one year
+    time = np.linspace(0, porb, 1000)
+
+    # Starry settings
+    map.obl = obl
+    kwargs = {}
+    kwargs["theta"] = ((time % prot) / prot) * 360
+    if reflected:
+        kwargs["xs"] = np.sin(2 * np.pi * time / porb)
+        kwargs["ys"] = 0
+        kwargs["zs"] = -np.cos(2 * np.pi * time / porb)
+
+    # Generate a fake dataset
+    flux0 = map.flux(**kwargs)
+    ferr = 1e-6
+    flux = flux0 + ferr * np.random.randn(len(flux0))
+
+    # Clear the map coefficients
+    map.reset(obl=obl)
+
+    # Solve the linear problem
+    map.set_data(flux, C=ferr ** 2)
[…]

### 2021-03-31 tex/figures/inference_occ.py

@@ -1,0 +1,125 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import starry
+
+# Config
+starry.config.lazy = False
+np.random.seed(0)
+
+# Setup figure
+fig, ax = plt.subplots(5, 2, figsize=(13, 14))
+fig.subplots_adjust(hspace=0.4)
+ax[0, 0].set_visible(False)
+ax[0, 1].set_visible(False)
+ax[1, 0].set_ylabel("flux [normalized]", fontsize=10)
+ax[1, 0].set_title("thermal phase curve", fontsize=12, fontweight="bold")
+ax[1, 1].set_title("reflected phase curve", fontsize=12, fontweight="bold")
+ax[2, 0].set_ylabel("flux [normalized]", fontsize=10)
+ax[3, 0].set_title("thermal occultation", fontsize=12, fontweight="bold")
+ax[3, 1].set_title("reflected occultation", fontsize=12, fontweight="bold")
+for axis in np.append(ax[1, :], ax[3, :]):
+    axis.tick_params(labelsize=8)
+    axis.set_ylim(-0.05, 1.65)
+
+# Show the true map
+ax_top = fig.add_subplot(5, 1, 1)
+ax_top.set_title("input", fontsize=12, fontweight="bold")
+map = starry.Map(20)
+map.load("earth", sigma=0.1)
+map.show(ax=ax_top, projection="moll")
+
+# Solve the least-squares problem for thermal & reflected phase curves
+for j, rmoon in enumerate([0, 0.25]):
+    for i, reflected in enumerate([False, True]):
+
+        # Instantiate a map of the Earth
+        map = starry.Map(20, reflected=reflected)
+        map.load("earth", sigma=0.1)
+        obl = 23.5
+        porb = 365.25
+        prot = 1.0
+        pmoon = 1.37
+        amoon = 2.0
+        imoon = 85 * np.pi / 180
+
+        # Hack: these amplitudes give us unit median flux
+        if reflected:
+            map.amp = 2.60
+        else:
+            map.amp = 1.00
+
+        # Light curve over 10 days wiith 7 occultations
+        time = np.linspace(120.0, 130.0, 325)
+        for n in range(7):
+            time = np.append(time, (88.25 + n) * pmoon + np.linspace(-0.15, 0.15, 25))
+        time = np.sort(time)
+
+        # Starry settings
+        map.obl = obl
+        kwargs = {}
[…]

### 2021-03-31 tex/figures/io_europa.py

@@ -1,0 +1,264 @@
+"""Europa-Io occultation from the PHEMU campaign."""
+import numpy as np
+from matplotlib import pyplot as plt
+from astropy.time import Time
+import astropy.units as u
+from astropy.timeseries import TimeSeries
+from astroquery.jplhorizons import Horizons
+import os
+import starry
+from matplotlib.patches import ConnectionPatch
+
+
+starry.config.lazy = False
+
+
+def get_body_ephemeris(times, body_id="501", step="1m"):
+
+    start = times.isot[0]
+
+    # Because Horizons time range doesn't include the endpoint
+    # we need to add some extra time
+    if step[-1] == "m":
+        padding = 2 * float(step[:-1]) / (60 * 24)
+    elif step[-1] == "h":
+        padding = 2 * float(step[:-1]) / 24
+    elif step[-1] == "d":
+        padding = 2 * float(step[:-1])
+    else:
+        raise ValueError(
+            "Unrecognized JPL Horizons step size. Use '1m' or '1h' for example."
+        )
+    end = Time(times.mjd[-1] + padding, format="mjd").isot
+
+    # Query JPL Horizons
+    epochs = {"start": start, "stop": end, "step": step}
+    obj = Horizons(id=body_id, epochs=epochs, id_type="id")
+    eph = obj.ephemerides(extra_precision=True)
+    times_jpl = Time(eph["datetime_jd"], format="jd")
+
+    # Store all data in a TimeSeries object
+    data = TimeSeries(time=times)
+    data["RA"] = np.interp(times.mjd, times_jpl.mjd, eph["RA"]) * eph["RA"].unit
+    data["DEC"] = np.interp(times.mjd, times_jpl.mjd, eph["DEC"]) * eph["DEC"].unit
+    data["ang_width"] = (
+        np.interp(times.mjd, times_jpl.mjd, eph["ang_width"]) * eph["ang_width"].unit
+    )
+    data["phase_angle"] = (
+        np.interp(times.mjd, times_jpl.mjd, eph["alpha_true"]) * eph["alpha_true"].unit
+    )
+    eph = obj.ephemerides(extra_precision=True)
+
[…]

### 2021-03-31 tex/figures/kelt9b.py

@@ -1,0 +1,140 @@
+"""Kelt-9b secondary eclipse example."""
+import starry
+import matplotlib.pyplot as plt
+import numpy as np
+import astropy.units as u
+
+
+# Config
+starry.config.lazy = False
+
+
+# Star
+star_map = starry.Map(udeg=2, amp=1)
+star_map[1:] = [0.5, 0.25]
+star = starry.Primary(star_map, m=2.50, mass_unit=u.M_sun, r=2.36, length_unit=u.R_sun)
+
+# Planet
+kwargs = dict(
+    m=0.0,
+    mass_unit=u.earthMass,
+    porb=1.481,
+    r=21.1770214,
+    length_unit=u.earthRad,
+    inc=87.2,
+    t0=-0.65625,
+)
+
+# Time arrays (secondary eclipse ingress / full phase curve)
+t_ingress = np.linspace(0, 0.017, 1000)
+t_egress = 218 / 60 / 24 + t_ingress
+t_sec = np.append(t_ingress, t_egress)
+t_phase = kwargs["t0"] + kwargs["porb"] * np.linspace(-0.5, 0.5, 1000)
+
+# Uniform
+e_map = starry.Map(ydeg=1, reflected=False)
+e = starry.Secondary(e_map, **kwargs)
+sys = starry.System(star, e)
+flux_em = sys.flux(t=t_sec, total=False)[1]
+
+# Noon approximation
+e_map = starry.Map(udeg=1, reflected=False)
+e_map[1] = 1
+e = starry.Secondary(e_map, **kwargs)
+sys = starry.System(star, e)
+flux_ld = sys.flux(t=t_sec, total=False)[1]
+
+# Reflected, point source
+e_map = starry.Map(ydeg=1, reflected=True)
+e_map.amp *= 0.2
+e = starry.Secondary(e_map, **kwargs)
+sys = starry.System(star, e)
+flux_ref = sys.flux(t=t_sec, total=False)[1]
+flux_phase = sys.flux(t=t_phase, total=False)[1]
+
+# Reflected, extended source
+e_map = starry.Map(ydeg=1, reflected=True, source_npts=300)
+e_map.amp *= 0.2
+e = starry.Secondary(e_map, **kwargs)
+sys = starry.System(star, e)
+flux_ref_fin = sys.flux(t=t_sec, total=False)[1]
[…]

### 2021-03-31 tex/figures/oren_nayar.py

@@ -1,0 +1,118 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import colors
+import starry
+
+# Instantiate a starry map
+starry.config.lazy = False
+map = starry.Map(reflected=True)
+
+# Settings
+res = 300
+theta_im = np.linspace(0, 360, 9)[1:-1] * np.pi / 180
+theta_hr = np.linspace(0, 360, 1000) * np.pi / 180
+theta_lr = theta_hr[5::10]
+rs = [0, 15, 30, 45]
+
+# Set up the figure
+fig = plt.figure(figsize=(12, 8))
+ax_im = np.array(
+    [
+        [
+            plt.subplot2grid((4 * len(rs), len(theta_im)), (2 * i, j), rowspan=2)
+            for j in range(len(theta_im))
+        ]
+        for i in range(len(rs))
+    ]
+)
+ax_lc = plt.subplot2grid(
+    (4 * len(rs), len(theta_im)),
+    (2 * len(rs) + 1, 0),
+    colspan=len(theta_im),
+    rowspan=2 * len(rs) - 1,
+)
+
+# Illumination colormap
+cmap = colors.LinearSegmentedColormap.from_list("illum", ["k", "k"], 256)
+cmap._init()
+alphas = np.linspace(1.0, 0.0, cmap.N + 3)
+cmap._lut[:, -1] = alphas
+cmap.set_under((0, 0, 0, 1))
+cmap.set_over((0, 0, 0, 0))
+
+# Plot the images & light curves
+for i, roughness in enumerate(rs):
+
+    # Set the roughness in degrees
+    map.roughness = roughness
+
+    # Plot the images for all phases
+    img = map.render(
+        xs=np.sin(theta_im), ys=0, zs=-np.cos(theta_im), res=res, on94_exact=False,
+    )
+    for j in range(len(theta_im)):
+        if j < len(theta_im) - 1:
+            ax_im[i, j].imshow(
+                np.pi * img[j],
+                origin="lower",
+                extent=(-1, 1, -1, 1),
+                cmap=cmap,
+                vmin=0,
+                vmax=1,
+            )
+            ax_im[i, j].add_artist(plt.Circle((0, 0), 1, ec="w", fc="none"))
+        else:
+            ax_im[i, j].plot([0, 1], [0, 0], "C{}".format(i), lw=3)
+            ax_im[i, j].set_xlim(0, 2.5)
+            ax_im[i, j].set_ylim(-1, 1)
[…]

### 2021-03-31 tex/figures/pathological.py

@@ -1,0 +1,113 @@
+from support_code import *
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Setup figure
+fig, ax = plt.subplots(2, 4, figsize=(12, 6))
+ax = ax.flatten()
+
+# Case 11
+visualize_simple(
+    ax[0], 0.5488316824842527, 4.03591586925189, 0.34988513192814663, 0.7753986686719786
+)
+axins0 = ax[0].inset_axes([1.15, 0.0, 1.0, 1.0])
+visualize_simple(
+    axins0,
+    0.5488316824842527,
+    4.03591586925189,
+    0.34988513192814663,
+    0.7753986686719786,
+    res=3999,
+)
+axins0.axis("on")
+ax[1].set_visible(False)
+x1, x2, y1, y2 = 0.6, 0.7, 0.7, 0.8
+axins0.set_xlim(x1, x2)
+axins0.set_ylim(y1, y2)
+axins0.set_xticks([])
+axins0.set_yticks([])
+rectangle_patch, connector_lines = ax[0].indicate_inset_zoom(axins0)
+rectangle_patch.set_ec("k")
+for line in connector_lines:
+    line.set_ec("k")
+
+# Case 12
+visualize_simple(
+    ax[2],
+    -0.5488316824842527,
+    4.03591586925189 - np.pi,
+    0.34988513192814663,
+    0.7753986686719786,
+)
+axins1 = ax[2].inset_axes([1.15, 0.0, 1.0, 1.0])
+visualize_simple(
+    axins1,
+    -0.5488316824842527,
+    4.03591586925189 - np.pi,
+    0.34988513192814663,
+    0.7753986686719786,
+    res=3999,
+)
+axins1.axis("on")
+ax[3].set_visible(False)
+x1, x2, y1, y2 = 0.6, 0.7, 0.7, 0.8
+axins1.set_xlim(x1, x2)
+axins1.set_ylim(y1, y2)
+axins1.set_xticks([])
+axins1.set_yticks([])
+rectangle_patch, connector_lines = ax[2].indicate_inset_zoom(axins1)
+rectangle_patch.set_ec("k")
+for line in connector_lines:
+    line.set_ec("k")
+
+# Case 13
+visualize_simple(ax[4], 0.5, np.pi, 0.99, 1.5)
+axins2 = ax[4].inset_axes([1.15, 0.0, 1.0, 1.0])
[…]

### 2021-03-31 tex/figures/scattering.py

@@ -1,0 +1,153 @@
+import numpy as np
+from matplotlib import pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+from matplotlib.patches import FancyArrowPatch
+from mpl_toolkits.mplot3d import proj3d
+
+
+class Arrow3D(FancyArrowPatch):
+    """
+    From https://stackoverflow.com/a/22867877.
+    """
+
+    def __init__(self, xs, ys, zs, *args, **kwargs):
+        FancyArrowPatch.__init__(self, (0, 0), (0, 0), *args, **kwargs)
+        self._verts3d = xs, ys, zs
+        self.shrinkA = 0
+        self.shrinkB = 0
+
+    def draw(self, renderer):
+        xs3d, ys3d, zs3d = self._verts3d
+        xs, ys, zs = proj3d.proj_transform(xs3d, ys3d, zs3d, renderer.M)
+        self.set_positions((xs[0], ys[0]), (xs[1], ys[1]))
+        FancyArrowPatch.draw(self, renderer)
+
+
+def add_arrow(ax, u, v, label=None, offset=0.1, **kwargs):
+    kwargs["mutation_scale"] = kwargs.get("mutation_scale", 10)
+    kwargs["lw"] = kwargs.get("lw", 1)
+    kwargs["arrowstyle"] = kwargs.get("arrowstyle", "-|>")
+    kwargs["color"] = kwargs.get("color", "k")
+    a = Arrow3D([u[0], v[0]], [u[1], v[1]], [u[2], v[2]], **kwargs)
+    ax.add_artist(a)
+
+    if label is not None:
+        ax.text(
+            v[0] * (1 + offset),
+            v[1] * (1 + offset),
+            v[2] * (1 + offset),
+            label,
+            transform=ax.transData,
+            fontsize=10,
+            va="center",
+            ha="center",
+            clip_on=False,
+        )
+
+    return a
+
+
+def add_projection(ax, u, v, **kwargs):
+    kwargs["lw"] = kwargs.get("lw", 0.75)
+    kwargs["ls"] = kwargs.get("ls", "--")
+    kwargs["color"] = kwargs.get("color", "k")
[…]

### 2021-03-31 tex/figures/speed.py

@@ -1,0 +1,480 @@
+"""Starry speed and stability tests."""
+import starry
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.integrate import dblquad
+import theano
+import theano.tensor as tt
+import theano.sparse as ts
+from theano.ifelse import ifelse
+from tqdm import tqdm
+import time
+import warnings
+
+
+# Config
+starry.config.lazy = False
+starry.config.quiet = True
+warnings.simplefilter("ignore")
+HUGE = 1e30
+np.random.seed(1234)
+
+
+# Theano dummy variables
+_y = tt.dvector()
+_x = tt.dvector()
+_xs = tt.dvector()
+_ys = tt.dvector()
+_zs = tt.dvector()
+_xo = tt.dvector()
+_yo = tt.dvector()
+_ro = tt.dscalar()
+
+
+class Compare(object):
+    """Compare different ways of evaluating the flux."""
+
+    def __init__(self, y):
+        self.y = y
+
+    @property
+    def y(self):
+        return self._y
+
+    @y.setter
+    def y(self, y):
+        self._y = np.array(y)
+        self.ydeg = int(np.sqrt(len(y)) - 1)
+        self.map_ref = starry.Map(ydeg=self.ydeg, reflected=True)
+        self.map_emi = starry.Map(ydeg=self.ydeg)
+        if self.ydeg > 0:
+            self.map_ref[1:, :] = y[1:]
+            self.map_emi[1:, :] = y[1:]
+        self._A1y = ts.dot(self.map_ref.ops.A1, tt.as_tensor_variable(y))
+
+        # Reset
+        self.intensity(0.0, 0.0, [0.0], [0.0], [0.0], [0.0], [0.0], 0.0, reset=True)
+        self.flux([0.0], [0.0], [0.0], [0.0], [0.0], 0.0, reset=True)
+        self.dfluxdro([0.0], [0.0], [0.0], [0.0], [0.0], 0.0, reset=True)
+        if self.ydeg > 0:
+            self.flux_emitted([0.0], [0.0], [0.0], [0.0], [0.0], 0.0, reset=True)
+            self.dfluxdro_emitted([0.0], [0.0], [0.0], [0.0], [0.0], 0.0, reset=True)
+
+    def intensity(self, y, x, xs, ys, zs, xo, yo, ro, reset=False):
+
+        if reset or not hasattr(self, "_intensity"):
+
[…]

### 2021-03-31 tex/figures/support_code/viz.py

@@ -1,0 +1,581 @@
+from .utils import *
+from .geometry import get_angles
+import matplotlib.pyplot as plt
+from matplotlib.colors import LinearSegmentedColormap
+from matplotlib.patches import Arc
+import numpy as np
+
+
+def visualize_simple(ax, b, theta, bo, ro, res=999):
+
+    # Find angles of intersection
+    kappa, lam, xi, code = get_angles(b, theta, np.cos(theta), np.sin(theta), bo, ro)
+    phi = kappa - np.pi / 2
+
+    # HACK
+    if (
+        code == FLUX_NIGHT_VIS
+        or code == FLUX_DAY_VIS
+        or code == FLUX_QUAD_DAY_VIS
+        or code == FLUX_QUAD_NIGHT_VIS
+    ):
+        phi = phi[::-1]
+
+    color_night = (0, 0, 0, 0.75)
+    color_day_occ = (0.314, 0.431, 0.514, 0.5)
+    color_night_occ = (0, 0, 0, 0.5)
+
+    # Equation of half-ellipse
+    x = np.linspace(-1, 1, 10000)
+    y = b * np.sqrt(1 - x ** 2)
+    x_t = x * np.cos(theta) - y * np.sin(theta)
+    y_t = x * np.sin(theta) + y * np.cos(theta)
+
+    # Shaded regions
+    p = np.linspace(-1, 1, res)
+    xpt, ypt = np.meshgrid(p, p)
+    cond1 = xpt ** 2 + (ypt - bo) ** 2 < ro ** 2  # inside occultor
+    cond2 = xpt ** 2 + ypt ** 2 < 1  # inside occulted
+    xr = xpt * np.cos(theta) + ypt * np.sin(theta)
+    yr = -xpt * np.sin(theta) + ypt * np.cos(theta)
+    cond3 = yr > b * np.sqrt(1 - xr ** 2)  # above terminator
+    img_day_occ = np.zeros_like(xpt)
+    img_day_occ[cond1 & cond2 & cond3] = 1
+    img_night_occ = np.zeros_like(xpt)
+    img_night_occ[cond1 & cond2 & ~cond3] = 1
+    img_night = np.zeros_like(xpt)
+    img_night[~cond1 & cond2 & ~cond3] = 1
+    x0, y0 = np.meshgrid(np.linspace(-1, 1, res), np.linspace(-1, 1, res))
[…]

### 2021-03-31 tex/gen_links.py

@@ -1,0 +1,27 @@
+from __future__ import print_function
+import subprocess
+import os
+
+# Generate the github links
+hash = subprocess.check_output(["git", "rev-parse", "HEAD"]).decode("utf-8")[:-1]
+slug = "rodluger/starrynight"
+with open("gitlinks.tex", "w") as f:
+    print(
+        r"\newcommand{\codelink}[1]{\href{https://github.com/%s/blob/%s/tex/figures/#1.py}{\codeicon}\,\,}"
+        % (slug, hash),
+        file=f,
+    )
+    print(
+        r"\newcommand{\animlink}[1]{\href{https://github.com/%s/blob/%s/tex/figures/#1.gif}{\animicon}\,\,}"
+        % (slug, hash),
+        file=f,
+    )
+    print(
+        r"\newcommand{\prooflink}[1]{\href{https://github.com/%s/blob/%s/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}"
+        % (slug, hash),
+        file=f,
+    )
+    print(
+        r"\newcommand{\cilink}[1]{\href{https://dev.azure.com/%s/_build}{#1}}" % (slug),
+        file=f,
+    )

### 2021-03-31 tex/proofs/notebook_setup.py

@@ -1,0 +1,49 @@
+# Pretty figures
+get_ipython().magic('config InlineBackend.figure_format = "retina"')
+
+
+import matplotlib
+import matplotlib.pyplot as plt
+import warnings
+
+
+# Disable annoying font warnings
+matplotlib.font_manager._log.setLevel(50)
+
+
+# Disable theano deprecation warnings
+warnings.filterwarnings("ignore", category=DeprecationWarning)
+warnings.filterwarnings("ignore", category=FutureWarning)
+warnings.filterwarnings("ignore", category=UserWarning, module="theano")
+
+
+# Style
+plt.style.use("default")
+plt.rcParams["savefig.dpi"] = 100
+plt.rcParams["figure.dpi"] = 100
+plt.rcParams["figure.figsize"] = (12, 4)
+plt.rcParams["font.size"] = 14
+plt.rcParams["text.usetex"] = False
+plt.rcParams["font.family"] = "sans-serif"
+plt.rcParams["font.sans-serif"] = ["Liberation Sans"]
+plt.rcParams["font.cursive"] = ["Liberation Sans"]
+plt.rcParams["mathtext.fontset"] = "cm"
+try:
+    plt.rcParams["mathtext.fallback"] = "cm"
+except KeyError:
+    plt.rcParams["mathtext.fallback_to_cm"] = True
+
+
+# TODO: In case we need to patch some symbols.
+if False:
+    try:
+        old_get_unicode_index
+    except NameError:
+        import matplotlib.mathtext as mathtext
+
+        old_get_unicode_index = mathtext.get_unicode_index
+        mathtext.get_unicode_index = (
+            lambda symbol, math=True: ord("x")
+            if symbol == "\\times"
+            else old_get_unicode_index(symbol, math)
+        )

### 2021-10-22 tex/ms.tex
reviewer comments

@@
 % !TeX root = ./ms.tex
+\def\LINENOS{1}
+
 \ifdefined\LINENOS
@@
 
-On the open-source software front, \citet{Louden2018} developed
+\textbf{%
+There have also been many developments on the open-source software front.
+These include \textsf{ReflectDirect}, a reflected light curve analysis 
+suite \citep{Schwartz2016};
+\textsf{samurai}, a tool for rotational unmixing of reflected light curves
+\citep{LustigYaeger2018};
 \textsf{spiderman}, an efficient discretization scheme
 on the sphere that enables fast computation of exoplanet
-phase curves and occultation light curves in \Python.
-%
+phase curves and occultation light curves \citep{Louden2018};
+\textsf{exocartographer}, a Bayesian
+framework for doing inference on exoplanet phase curves based on
+a HEALPix \citep{healpix} discretization scheme \citep{Farr2018};
+the \textsf{sot} package for spin-orbit tomography of exo-Earths \citep{Kawahara2020,Kawahara2020b};
+and 
+\textsf{neural\_exocartography}, a tool for mapping exoplanet surfaces with neural learned
+regularization \citep{AsensioRamos2021}.
+%
+Of particular relevance to the present work,
 \citet{Haggard2018} presented
@@
 %
-\citet{Farr2018} released \textsf{exocartographer}, a Bayesian
-framework for doing inference on exoplanet phase curves based on
-a HEALPix \citep{healpix} discretization scheme.
-%
-Finally, \citet{Luger2019} introduced \starry, a light curve
+And finally, \citet{Luger2019} introduced \starry, a light curve
 modeling package that computes thermal phase curves and occultation
@@
 harmonic expansion of the surface brightness.
+}
 
@@
 where $\mathbf{y}(t)$ is a time-dependent representation of the surface
-map, which we expand about $t=t_0$ \citep[see][]{Luger2019b}.
+map, which we expand about $t=t_0$ 
+\citep{Luger2019b}; \textbf{see also \citealt{Kawahara2020b} for an alternative linear model for time-dependent maps}.
 But perhaps even more importantly, linear
@@
 in which we assume a prior variance of $10^{-3}$ for all spherical
-harmonic coefficients (and zero covariance). The corresponding surface
+harmonic coefficients (and zero covariance).%
+\footnote{%
+\textbf{This choice is equivalent to assuming a flat prior on the power spectrum 
+with power $10^{-3}$ in each degree $l$ of the surface map.
+This particular value is roughly the average power per degree in the input
+map, although the results in the figure are not sensitive to this choice.
+For a detailed discussion of how to set one's priors in a realistic setting in 
+which the true map is not known, see \citet{PaperIII}.}
+} 
+The corresponding surface
 map is shown at the bottom. As expected, this looks nothing like the
@@
 have explored in detail the best kinds of priors to assume
-\citep[e.g.,][]{Aizawa2020}. Future maps of exoplanets---particularly
+\citep[e.g.,][]{Aizawa2020,AsensioRamos2021}. Future maps of exoplanets---particularly
 terrestrial ones in the habitable zone---will require every tool
@@
 approaches for computing these light curves. The algorithm is
-also differentiable, enabling inference with efficient gradient-based samplers
+also differentiable \textbf{in all of the model parameters}, 
+enabling inference with efficient gradient-based samplers
 such as Hamiltonian Monte Carlo (HMC), and linear in the spherical
@@
 \begin{proof}{illumination}
-    \mathcal{f}_\text{full} &=
+    f_\text{full} &=
     \int_{-1}^{1}
